---
title: "IQ1/IQ2 Comparison"
output: html_document
date: "`r Sys.Date()`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, dev="png")
```


## IQ1/IQ2 Data Comparison Fall 2023

Compares flux and biomet measurements between IQ1/IQ2 for overlapping Fall '23 dates 


## Data Loading


Clear console and add packages
```{r, warning=FALSE, echo=FALSE}
rm(list = ls())

library(data.table)
library(ggplot2)
library(cowplot)
library(openair)
library(plotrix)
library(signal)
library(svMisc)
library(zoo)
library(stringr)
library(plyr)
library(dplyr)
library(viridis)
library(lubridate)
```


To load cleaned data from respective cleaning scripts 

```{r, warning=FALSE}

IQ1_df = fread('C:/Users/dtrangmoe/Documents/IQ/IQ Loading & Cleaning/IQ1_Fall23_Clean.csv')


IQ2_df = fread('C:/Users/dtrangmoe/Documents/IQ/IQ Loading & Cleaning/IQ2_Fall23_Clean.csv')


df= merge(IQ1_df,IQ2_df,by='ts',all = F, suffixes = c(".IQ1", ".IQ2"))
## find way to add suffix to every col, not just duplicates


rm(IQ1_df, IQ2_df)
```



Creates a variable to input a date range for the plots

```{r, warning=FALSE}
compare_dates <- c('2023-08-15', '2023-10-18')
```




## Plotting Flux Data


#### NEE

Not great

```{r, warning=FALSE}
ggplot(data = df)+
  geom_point(aes(ts,co2_flux.c.IQ1,col='IQ1'))+
  geom_point(aes(ts,co2_flux.c.IQ2,col='IQ2'))+
  scale_y_continuous(limits = c(-13,13),
                     expression('NEE ('*mu*mol~m^-2~s^-1*')'))+
  scale_x_datetime(limits = as.POSIXct(compare_dates,format="%F"))

ggplot(data = df)+
  geom_point(aes(co2_flux.c.IQ1, co2_flux.c.IQ2))+ 
  geom_abline(slope = 1,intercept = 0,col='red')+
  scale_x_continuous(limits = c(-10,10),expression('IQ1'))+
  scale_y_continuous(limits = c(-10,10),expression('IQ2'))
```


#### H~2~O

```{r, warning=FALSE}
ggplot(data = df)+
  geom_point(aes(ts,h2o_flux.c.IQ1,col='IQ1'))+
  geom_point(aes(ts,h2o_flux.c.IQ2, col='IQ2'))+
  scale_y_continuous(limits = c(-3,5),
                     expression('H2O Flux ('*mmol~m^-2~s^-1*')'))+
  scale_x_datetime(limits = as.POSIXct(compare_dates,format="%F"))

ggplot(data = df)+
  geom_point(aes(h2o_flux.c.IQ1, h2o_flux.c.IQ2))+ 
  geom_abline(slope = 1,intercept = 0,col='red')+
  scale_x_continuous(limits = c(-2.5,5),expression('IQ1'))+
  scale_y_continuous(limits = c(-2.5,5),expression('IQ2'))
```


#### LE

```{r, warning=FALSE}
ggplot(data = df)+
  geom_point(aes(ts,LE.c.IQ1,col='IQ1'))+
  geom_point(aes(ts,LE.c.IQ2,col='IQ2'))+
  scale_y_continuous(limits = c(-75,130),
                     expression('LE ('*W~m^-2*')'))+
  scale_x_datetime(limits = as.POSIXct(compare_dates,format="%F"))

ggplot(data = df)+
  geom_point(aes(LE.c.IQ1, LE.c.IQ2))+ 
  geom_abline(slope = 1,intercept = 0,col='red')+
  scale_x_continuous(limits = c(-50,150),expression('IQ1'))+
  scale_y_continuous(limits = c(-50,150),expression('IQ2'))
```

#### H

```{r, warning=FALSE}
ggplot(data = df)+
  geom_point(aes(ts,H.c.IQ1,col='IQ1'))+
  geom_point(aes(ts,H.c.IQ2,col='IQ2'))+
  scale_y_continuous(expression('H ('*W~m^-2*')'))+
  scale_x_datetime(limits = as.POSIXct(compare_dates,format="%F"))

ggplot(data = df)+
  geom_point(aes(H.c.IQ1, H.c.IQ2))+ 
  geom_abline(slope = 1,intercept = 0,col='red')+
  scale_x_continuous(limits = c(-50,150),expression('IQ1'))+
  scale_y_continuous(limits = c(-50,150),expression('IQ2'))
```






## Plotting Biomet Data


#### Net Radiation

```{r, warning=FALSE}

ggplot(data = df)+
  geom_point(aes(ts,NR_Wm2_Avg.c,col='IQ1'))+
  geom_point(aes(ts,Rn_Avg.c,col='IQ2'))+
  scale_y_continuous(expression('Net Radiation ('*W~m^-2*')'))+
  scale_x_datetime(limits = as.POSIXct(compare_dates,format="%F"))

ggplot(data = df)+
  geom_point(aes(NR_Wm2_Avg.c, Rn_Avg.c))+ 
  geom_abline(slope = 1,intercept = 0,col='red')+
  scale_x_continuous(limits = c(-150,450),expression('IQ1'))+
  scale_y_continuous(limits = c(-150,450),expression('IQ2'))

```


#### Air Temperature


```{r, warning=FALSE}

ggplot(data = df)+
  geom_point(aes(ts,T_air_HC2S3_Avg.c,col='IQ1'))+
  geom_point(aes(ts,AirTC_Avg.c,col='IQ2'))+
  scale_y_continuous(expression('Air Temp ('*Celcius*')'))+
  scale_x_datetime(limits = as.POSIXct(compare_dates,format="%F"))

ggplot(data = df)+
  geom_point(aes(T_air_HC2S3_Avg.c, AirTC_Avg.c))+ 
  geom_abline(slope = 1,intercept = 0,col='red')+
  scale_x_continuous(limits = c(-15,15),expression('IQ1'))+
  scale_y_continuous(limits = c(-15,15),expression('IQ2'))

```


#### Relative Humidity

interesting at high vals

```{r, warning=FALSE}

ggplot(data = df)+
  geom_point(aes(ts,RH_HC2S3_Avg.c,col='IQ1'))+
  geom_point(aes(ts,RH_Avg.c,col='IQ2'))+
  scale_y_continuous(expression('Relative Humidity ('*percent*')'))+
  scale_x_datetime(limits = as.POSIXct(compare_dates,format="%F"))

 
ggplot(data = df)+
  geom_point(aes(RH_HC2S3_Avg.c, RH_Avg.c))+ 
  geom_abline(slope = 1,intercept = 0,col='red')+
  scale_x_continuous(limits = c(50,100),expression('IQ1'))+
  scale_y_continuous(limits = c(50,100),expression('IQ2'))

```

#### Rain

Not great
```{r, warning=FALSE}
ggplot(data = df)+
  geom_point(aes(ts,Rainfall_Tot.c,col='IQ1'))+
  geom_point(aes(ts,Rain_mm_Tot.c,col='IQ2'))+
  scale_y_continuous(expression('Rain ('*mm*')'))+
  scale_x_datetime(limits = as.POSIXct(compare_dates,format="%F"))


ggplot(data = df)+
  geom_point(aes(Rainfall_Tot.c, Rain_mm_Tot.c))+
  geom_abline(slope = 1,intercept = 0,col='red')+
  scale_x_continuous(limits = c(-2,12),expression('IQ1'))+
  scale_y_continuous(limits = c(-2,12),expression('IQ2'))

```


