---
title: "IQ1 Met & Flux Cleaning"
output:
  pdf_document: default
  html_document: default
date: "`r Sys.Date()`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, dev="png")
```




## IQ1 Biomet Data Cleaning


##### Designed to clean biomet variables collected at the Iqaluit 1 site. 

##### Uses original variable names as created by datalogger, not FluxNet standardized biomet names. 





Clear console and add packages
```{r, warning=FALSE, echo=FALSE}
rm(list = ls())

library(data.table)
library(ggplot2)
library(cowplot)
library(openair)
library(plotrix)
library(signal)
library(svMisc)
library(zoo)
library(stringr)
library(plyr)
library(dplyr)
library(viridis)
library(lubridate)
```


To load tidy, uncleaned biomet data as created by IQ loading script 
```{r, warning=FALSE}
df = fread('C:/Users/dtrangmoe/Documents/IQ/IQ1/tidy_IQ1metdata.csv')

mindate = floor_date(min(df$ts))
maxdate = ceiling_date(max(df$ts))
```

Creates a variable to input a date range for the plots in the biomet section of
cleaning code. Used to easily change date range for different data sets. 
```{r, warning=FALSE}
biomet_dates <- c('2021-07-10', '2023-10-22')
```

Converts biomet names to easier format
```{r, warning=FALSE}
colnames(df)[which(names(df) == 'Ground_Temp_C_Avg(1)')] <- 'Ground_Temp_C_Avg_1.1'
colnames(df)[which(names(df) == 'Ground_Temp_C_Avg(2)')] <- 'Ground_Temp_C_Avg_1.2'
colnames(df)[which(names(df) == 'Ground_Temp2_C_Avg(1)')] <- 'Ground_Temp_C_Avg_2.1'
colnames(df)[which(names(df) == 'Ground_Temp2_C_Avg(2)')] <- 'Ground_Temp_C_Avg_2.2'
```



#### Biomet cleaning Script 


Compares similar data: HMP & HC2S3 data- HC2S3 looks better for air temp and rel. humidity, CNR and NR are identical 
```{r, warning=FALSE}
 ggplot(data = df)+
   geom_point(aes(TIMESTAMP,T_air_HMP_Avg),col='red')+
   geom_point(aes(TIMESTAMP,T_air_HC2S3_Avg),col='black')


  ggplot(data = df)+
   geom_point(aes(TIMESTAMP,RH_HMP_Avg),col='red')+
   geom_point(aes(TIMESTAMP,RH_HC2S3_Avg),col='black')


  ggplot(data = df)+
   geom_point(aes(TIMESTAMP,NR_Wm2_Avg),col='red')+
   geom_point(aes(TIMESTAMP,CNR_Wm2_Avg),col='black')
```

Windvec and WS variables are all zeroes 

#### Air Temp


Doesn't clean anything right how- looks fine
```{r, warning=FALSE}
ggplot(data = df)+
  geom_point(aes(TIMESTAMP,T_air_HC2S3_Avg),col='black')+
  scale_y_continuous(limits = c(-45,25),
                     expression('Air Temperature ('*Celsius*')'))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates))

hist(df$T_air_HC2S3_Avg,breaks=100)

AirTC.limits = df$T_air_HC2S3_Avg

df$T_air_HC2S3_Avg.c = AirTC.limits

 
```




#### Relative Humidity


Doesn't clean anything right how- looks fine
```{r, warning=FALSE}
ggplot(data = df)+
  geom_point(aes(TIMESTAMP,RH_HC2S3_Avg),col='black')+
  scale_y_continuous(limits = c(0,100),
                     expression('Relative Humidity ('*percent*')'))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates))



RH.limits = df$RH_HC2S3_Avg
df$RH_HC2S3_Avg.c = RH.limits



ggplot(data = df)+
  geom_point(aes(TIMESTAMP,RH_HC2S3_Avg.c),col='black')+
  scale_y_continuous(limits = c(5,100),
                     expression('Relative Humidity ('*percent*')'))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates))
```



#### Ground Temp 



Plots all four values 
```{r, warning=FALSE}
ggplot(data = df)+
  geom_point(aes(TIMESTAMP,Ground_Temp_C_Avg_1.1,col='GT 1.1'))+
  geom_point(aes(TIMESTAMP,Ground_Temp_C_Avg_1.2,col='GT 1.2'))+
  geom_point(aes(TIMESTAMP,Ground_Temp_C_Avg_2.1,col='GT 2.1'))+
  geom_point(aes(TIMESTAMP,Ground_Temp_C_Avg_2.2,col='GT 2.2'))+
  scale_y_continuous(limits = c(-25, 25),
                     expression ('Ground Temp ('*Celcius*')'))+
  scale_color_manual(values = c('red','black', 'blue', 'purple'))+
  scale_x_datetime(limits = as.POSIXct(c(biomet_dates)))
```


Ground Temp 1.1 - does nothing, looks fine
```{r, warning=FALSE}
hist(df$Ground_Temp_C_Avg_1.1,breaks=100)
plot(df$TIMESTAMP,df$Ground_Temp_C_Avg_1.1,ylim = c(-25,25))

df$Ground_Temp_C_Avg_1.1.c = df$Ground_Temp_C_Avg_1.1
```


Ground Temp 1.2 - does nothing, looks fine
```{r, warning=FALSE}
hist(df$Ground_Temp_C_Avg_1.2,breaks=100)
plot(df$TIMESTAMP,df$Ground_Temp_C_Avg_1.2,ylim = c(-25,25))

df$Ground_Temp_C_Avg_1.2.c = df$Ground_Temp_C_Avg_1.2
```


Ground Temp 2.1 - does nothing, looks fine
```{r, warning=FALSE}
hist(df$Ground_Temp_C_Avg_2.1,breaks=100)
plot(df$TIMESTAMP,df$Ground_Temp_C_Avg_2.1,ylim = c(-25,25))

df$Ground_Temp_C_Avg_2.1.c = df$Ground_Temp_C_Avg_2.1
```


Ground Temp 2.2 - does nothing, looks fine
```{r, warning=FALSE}
hist(df$Ground_Temp_C_Avg_2.2,breaks=100)
plot(df$TIMESTAMP,df$Ground_Temp_C_Avg_2.2,ylim = c(-25,25))

df$Ground_Temp_C_Avg_2.2.c = df$Ground_Temp_C_Avg_2.2
```




#### Net Radiation

No initial cleaning
```{r, warning=FALSE, echo=FALSE}
ggplot(data = df)+
  geom_point(aes(TIMESTAMP, NR_Wm2_Avg),col='black')+
  scale_y_continuous(limits = c(-200,700),
                     expression('Net Radiation ('*W/m^2*')'))+
  scale_x_datetime(limits = as.POSIXct(c(biomet_dates)))

plot(df$TIMESTAMP, df$NR_Wm2_Avg)

RN.limits= df$NR_Wm2_Avg
```

Rolling SD
```{r, warning=FALSE}
f = RN.limits # first make a new flux vector to apply the above filters
# prepare the inputs for a zero-phase (forward and reverse) filter  
ind       = which(complete.cases(f))   # first save the index of all the NAs
b         = rep(1,8)/8                 # moving average coefficient
a         = 1                          # coefficient of the ARMA filter
mad_i    = filtfilt(b, a, na.omit(f)) #create a forward and reverse ARMA filter
mad_filt = f                          # make a copy of the full fluxes again
mad_filt[ind] = mad_i                # apply the filter where the real data exist

n = 7*48 # set the length of the rolling filter, 48 half hours in day * x days
roll.mad = rollapply(data = mad_filt,
                     width = n,
                     FUN = sd,
                     partial = TRUE,
                     na.rm = T,
                     fill = NA)  #create a rolling MAD or sd or other
roll.mad[is.na(mad_filt)] = NA  #make NA values where NAs exist in the real data




#adjust this value (N) to tweak how many MADs to be away from the norm
N = 3 

#Add clean value to dataframe (_.c)  (change these lines for new site)

df$NR_Wm2_Avg.c = ifelse(abs(RN.limits - mad_filt) > (N * roll.mad),NA,RN.limits)


# Compare cleaned vs. uncleaned

ggplot(df)+geom_hline(yintercept = 0)+
  geom_point(aes(TIMESTAMP,RN.limits,col='Uncleaned'))+
  geom_point(aes(TIMESTAMP,NR_Wm2_Avg.c,col='Cleaned'))+
  scale_y_continuous(limits = c(-200,750))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates,format="%F"))+
  scale_color_manual(values=c('black','red'))


ggplot(df)+geom_hline(yintercept = 0)+
  geom_point(aes(TIMESTAMP,RN.limits,col='Uncleaned'))+
  geom_point(aes(TIMESTAMP,NR_Wm2_Avg.c,col='Cleaned'))+
  scale_y_continuous(limits = c(-200,750))+
  scale_x_datetime(limits = as.POSIXct(c('2022-01-10', '2022-07-01')))+    scale_color_manual(values=c('black','red'))
```


Plots different seasons on different scales to see trends
``` {r, warning=FALSE}
ggplot(data = df)+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*6,ymin = mad_filt-roll.mad*6,fill='6'))+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*3,ymin = mad_filt-roll.mad*3,fill='3'))+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*2,ymin = mad_filt-roll.mad*2,fill='2'))+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*1,ymin = mad_filt-roll.mad*1,fill='1'))+
  geom_point(aes(TIMESTAMP,RN.limits),col='red')+
  geom_point(aes(TIMESTAMP, NR_Wm2_Avg.c),col='black')+
  scale_y_continuous(limits = c(-1000,1500))+
  scale_x_datetime(limits = as.POSIXct(c('2022-05-01', '2022-07-01'),format="%F"))

ggplot(data = df)+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*6,ymin = mad_filt-roll.mad*6,fill='6'))+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*3,ymin = mad_filt-roll.mad*3,fill='3'))+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*2,ymin = mad_filt-roll.mad*2,fill='2'))+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*1,ymin = mad_filt-roll.mad*1,fill='1'))+
  geom_point(aes(TIMESTAMP,RN.limits),col='red')+
  geom_point(aes(TIMESTAMP, NR_Wm2_Avg.c),col='black')+
  scale_y_continuous(limits = c(-1000,1500))+
  scale_x_datetime(limits = as.POSIXct(c('2022-07-24', '2022-10-01'),format="%F"))

ggplot(data = df)+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*6,ymin = mad_filt-roll.mad*6,fill='6'))+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*3,ymin = mad_filt-roll.mad*3,fill='3'))+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*2,ymin = mad_filt-roll.mad*2,fill='2'))+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*1,ymin = mad_filt-roll.mad*1,fill='1'))+
  geom_point(aes(TIMESTAMP,RN.limits),col='red')+
  geom_point(aes(TIMESTAMP, NR_Wm2_Avg.c),col='black')+
  scale_y_continuous(limits = c(-400,500))+
  scale_x_datetime(limits = as.POSIXct(c('2022-10-01', '2023-06-01'),format="%F"))

ggplot(data = df)+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*6,ymin = mad_filt-roll.mad*6,fill='6'))+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*3,ymin = mad_filt-roll.mad*3,fill='3'))+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*2,ymin = mad_filt-roll.mad*2,fill='2'))+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*1,ymin = mad_filt-roll.mad*1,fill='1'))+
  geom_point(aes(TIMESTAMP,RN.limits),col='red')+
  geom_point(aes(TIMESTAMP, NR_Wm2_Avg.c),col='black')+
  scale_y_continuous(limits = c(-1500,2000))+
  scale_x_datetime(limits = as.POSIXct(c('2023-06-01', '2023-08-15'),format="%F"))

ggplot(data = df)+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*6,ymin = mad_filt-roll.mad*6,fill='6'))+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*3,ymin = mad_filt-roll.mad*3,fill='3'))+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*2,ymin = mad_filt-roll.mad*2,fill='2'))+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*1,ymin = mad_filt-roll.mad*1,fill='1'))+
  geom_point(aes(TIMESTAMP,RN.limits),col='red')+
  geom_point(aes(TIMESTAMP, NR_Wm2_Avg.c),col='black')+
  scale_y_continuous(limits = c(-1000,1500))+
  scale_x_datetime(limits = as.POSIXct(c('2023-08-15', '2023-10-22'),format="%F"))

```



#### Rain 

Looks fine, doesn't do anything
```{r, warning=FALSE}
ggplot(data = df)+
  geom_point(aes(TIMESTAMP, Rainfall_Tot),col='black')+
  scale_y_continuous(limits = c(-0.1,12),
                     expression('Rain ('*mm*')'))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates))

df$Rainfall_Tot.c = df$Rainfall_Tot
```



#### T Pan Avg

Looks fine, doesn't do anything
```{r, warning=FALSE}

ggplot(data = df)+
  geom_point(aes(TIMESTAMP, T_pan_Avg))+  
  scale_y_continuous(limits = c(-40,30),
                     expression('Temp ('*Celcius*')'))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates))

```

#### T Ref Avg


```{r, warning=FALSE}

ggplot(data = df)+
  geom_point(aes(TIMESTAMP, T_ref_Avg))+  
  scale_y_continuous(limits = c(-290, -160),
                     expression('Temp ('*Celcius*')'))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates))

```


### Save Cleaned Biomet Data

```{r, warning=FALSE}
write.csv(x = df,file = 'C:/Users/dtrangmoe/Documents/IQ/IQ Loading & Cleaning/IQ1biomet_cleaned.csv',
          row.names = F,quote = F)
```




## IQ1 Flux Data Cleaning


Designed to clean EddyPro output variables collected at th Iqaluit 1 site,using cleaned biomet data and merged EddyPro output files created by IQ loading script

Uses original biomet variable names as created by datalogger, not FluxNet standardized biomet names.





Clear console and add packages

```{r, warning=FALSE, echo=FALSE}
rm(list = ls())

library(data.table)
library(ggplot2)
library(cowplot)
library(openair)
library(plotrix)
library(signal)
library(svMisc)
library(zoo)
library(stringr)
library(plyr)
library(viridis)
library(lubridate)
library(tidyverse)
```


Loads cleaned biomet file created above and EddyPro flux data 
```{r, warning=FALSE}
met = fread('C:/Users/dtrangmoe/Documents/IQ/IQ Loading & Cleaning/IQ1biomet_cleaned.csv')

flux = fread('C:/Users/dtrangmoe/Documents/IQ/IQ1/IQ1 Output Files/IQ1_fluxes_merged_2022.csv')

#creates dataframe only consisting of dates with flux data
mindate = floor_date(min(flux$ts))
maxdate = ceiling_date(max(flux$ts))

df = merge(flux,met,by='ts',all.x = T, suffixes = c(".flux", ".met")) 


rm(met, flux)

```


Creates a variable to input a date range for the plots in the flux section. Used 
to easily change date range for different data sets. 
```{r, warning=FALSE}

flux_dates <- c('2022-05-17', '2022-09-27')

```


## Initial Clean 

Initial Energy Balance Analysis
```{r, warning=FALSE}

df$met_EB = df$NR_Wm2_Avg.c
df$flux_EB = df$H + df$LE


plot(df$TIMESTAMP,df$NR_Wm2_Avg.c)

plot(df$TIMESTAMP, df$met_EB)
plot(df$TIMESTAMP, df$flux_EB)


ggplot(data = df)+
  geom_point(aes(TIMESTAMP,H,col='H'))+
  geom_point(aes(TIMESTAMP,LE,col='LE'))+
  scale_x_datetime(limits = as.POSIXct(flux_dates,format="%F"))

ggplot(data = df,aes(met_EB,flux_EB))+
  geom_point()


plot(df$met_EB,df$flux_EB, abline(0, 1, col= 'blue'),xlim = c(-300,500),ylim = c(-300,500)) 
# doesn't show all data, but shows important area

```


Statistical analysis of energy balance 


```{r, warning=FALSE, echo=FALSE}
summary(lm(df$flux_EB ~ df$met_EB))
```

#### R^2^ = `r summary(lm(df$flux_EB ~ df$met_EB))$r.squared`: not good! :(



Filter by EddyPro quality flags to remove 2's
```{r, warning=FALSE}
Tau.qc      = replace(df$Tau,df$qc_Tau == 2,NA)
co2_flux.qc = replace(df$co2_flux,df$qc_co2_flux == 2,NA)
h2o_flux.qc = replace(df$h2o_flux,df$qc_h2o_flux == 2,NA)
LE.qc       = replace(df$LE,df$qc_LE == 2,NA)
H.qc        = replace(df$H,df$qc_H == 2,NA)
```


#### Tau

Initial Cleaning with Limits
```{r, warning=FALSE}

hist(df$Tau,breaks=100)

plot(df$ts,df$Tau); abline(h=-1, col= 'red'); abline(h=1, col= 'red'); abline(h=0,col= 'black')

Tau.limits = replace(df$Tau,df$Tau > 0.5 | df$Tau < -0.75,NA)
hist(Tau.limits,breaks=100)

plot(df$ts, Tau.limits)

```


#### NEE

Initial Cleaning w/ Limits
```{r, warning=FALSE}
hist(df$co2_flux,breaks=100)

plot(df$ts,df$co2_flux, abline(h=75, col= 'red')); abline(h=-50, col= 'red'); abline(h=0,col= 'black')
 

# Clean based on graphs, create new variable, and see cleaned product


co2_flux.limits = replace(df$co2_flux,df$co2_flux > 75 | df$co2_flux < -50,NA)
hist(co2_flux.limits,breaks=100)
plot(df$TIMESTAMP, co2_flux.limits)


ggplot(data = df)+geom_hline(yintercept = 0)+
  geom_point(aes(x=ts,y=co2_flux),col = 'red')+
  geom_point(aes(x=ts,y=co2_flux.limits),col = 'black')+
  scale_y_continuous(limits = c(-300,220))+
  scale_x_datetime(limits = as.POSIXct(flux_dates,format="%F"))
```




#### H~2~O

Initial Cleaning w/ Limits
```{r, warning=FALSE}
hist(df$h2o_flux,breaks=100)

plot(df$ts,df$h2o_flux);abline(h=-2, col= 'red'); abline(h=8, col= 'red'); abline(h=0,col= 'black')
 

# Clean based on graphs, create new variable, and see cleaned product

h2o_flux.limits = replace(df$h2o_flux,df$h2o_flux < -2 | df$h2o_flux > 8,NA)
hist(h2o_flux.limits,breaks=100)
plot(df$TIMESTAMP, h2o_flux.limits)

ggplot(data = df)+geom_hline(yintercept = 0)+
  geom_point(aes(x=ts,y=h2o_flux),col = 'red')+
  geom_point(aes(x=ts,y=h2o_flux.limits),col = 'black')+
  scale_y_continuous(limits = c(-50,15))+
  scale_x_datetime(limits = as.POSIXct(flux_dates,format="%F"))
```



#### H

Initial Cleaning w/ Limits
```{r, warning=FALSE}
hist(df$H,breaks=100)

plot(df$ts,df$H);abline(h=-65, col= 'red');abline(h=350, col= 'red')
 

# Clean based on graphs, create new variable (H.limits), and see cleaned product

  
H.limits = replace(df$H, df$H < -65 | df$H > 350,NA)
hist(H.limits,breaks = 100)

ggplot(data = df)+geom_hline(yintercept = 0)+
  geom_point(aes(x=ts,y=H),col = 'red')+
  geom_point(aes(x=ts,y=H.limits),col = 'black')+
  scale_y_continuous(limits = c(-400,1750))+
  scale_x_datetime(limits = as.POSIXct(flux_dates,format="%F"))
```


#### LE


Initial Cleaning w/ limits
```{r, warning=FALSE}
hist(df$LE,breaks=100)

plot(df$ts,df$LE);abline(h=-75, col= 'red');abline(h=200, col= 'red')
 

# Clean based on graphs, create new variable, and see cleaned product

  
LE.limits = replace(df$LE, df$LE < -75 | df$LE > 200,NA)
hist(LE.limits)

ggplot(data = df)+geom_hline(yintercept = 0)+
  geom_point(aes(x=ts,y=LE),col = 'red')+
  geom_point(aes(x=ts,y=LE.limits),col = 'black')+
  scale_y_continuous(limits = c(-750,750))+
  scale_x_datetime(limits = as.POSIXct(flux_dates,format="%F"))
```



#### USTAR - friction velocity (turbulence)

Use night-time only flux values and plot Ustar based on data drop off
No 4 component radiation- use daytime variable?
```{r, warning=FALSE}
df$nightCO2 = co2_flux.limits
df$nightCO2 = replace(df$nightCO2,df$daytime == 0,NA)


ggplot(data = df, aes(x=ts, y=nightCO2))+
  geom_point()+
  scale_y_continuous(limits = c(-110,100))+
  scale_x_datetime(limits = as.POSIXct(flux_dates,format="%F"))


Uthreshold=0.06 # standard- safe value
ggplot(data = df,aes(`u*`,nightCO2))+
  ylab(expression(paste("Flux (g-C", ~CO[2], ~"m",""^"-2","d",""^"-1",")")))+
  geom_point()+xlab("U*")+
  scale_x_continuous(limits = c(0,1))+
  geom_vline(xintercept = Uthreshold,col='red') ## looking for point where co2 flux drops due to low turbulence
```
 

Pick threshold and filter based on plots above

```{r, warning=FALSE}
Tau.u  = replace(df$Tau ,df$`u*` < Uthreshold,NA)
H.u    = replace(df$H   ,df$`u*` < Uthreshold,NA)
LE.u   = replace(df$LE  ,df$`u*` < Uthreshold,NA)
co2_flux.u   = replace(df$co2_flux  ,df$`u*` < Uthreshold,NA)
h2o_flux.u   = replace(df$h2o_flux  ,df$`u*` < Uthreshold,NA)
```



## Combine Cleaning

Investigate the previous limits and combine all to create a new variable (clean), plot to see difference

```{r, warning=FALSE}
co2fluxclean = ifelse(is.na(co2_flux.qc) | is.na(co2_flux.limits) | is.na(co2_flux.u),NA,df$co2_flux)
h2ofluxclean = ifelse(is.na(h2o_flux.qc) | is.na(h2o_flux.limits) | is.na(h2o_flux.u),NA,df$h2o_flux)
Hclean = ifelse(is.na(H.qc) | is.na(H.limits) | is.na(H.u),NA,df$H)
LEclean = ifelse(is.na(LE.qc) | is.na(LE.limits) | is.na(LE.u),NA,df$LE)
Tauclean = ifelse(is.na(Tau.qc) | is.na(Tau.limits) | is.na(Tau.u),NA,df$Tau)

plot(df$ts,co2fluxclean)
plot(df$ts,h2ofluxclean)
plot(df$ts,Hclean)
plot(df$ts,LEclean)
plot(df$ts,Tauclean)
```


### MAD Filters 

#### NEE

Cutting a lot of data? 

```{r, warning=FALSE}
f = co2fluxclean # first make a new flux vector to apply the above filters
# prepare the inputs for a zero-phase (forward and reverse) filter  
ind       = which(complete.cases(f))   # first save the index of all the NAs
b         = rep(1,8)/8                 # moving average coefficient
a         = 1                          # coefficient of the ARMA filter
Flux_i    = filtfilt(b, a, na.omit(f)) #create a forward and reverse ARMA filter
Flux_filt = f                          # make a copy of the full fluxes again
Flux_filt[ind] = Flux_i                # apply the filter where the real data exist

n = 7*48 # set the length of the rolling filter, 48 half hours in day * x days
roll.mad = rollapply(data = Flux_filt,
                     width = n,
                     FUN = mad,
                     partial = TRUE,
                     na.rm = T,
                     fill = NA)  #create a rolling MAD or sd or other
roll.mad[is.na(Flux_filt)] = NA  #make NA values where NAs exist in the real data

ggplot(df)+geom_hline(yintercept = 0)+
  geom_point(aes(ts,co2fluxclean,col='CO2 flux'))+
  geom_line(aes(ts,Flux_filt,col='Filter'))+
  geom_line(aes(ts,roll.mad,col='MAD'))+
  scale_y_continuous(limits = c(-50, 50))+
  scale_x_datetime(limits = as.POSIXct(flux_dates,format="%F"))+
  scale_color_manual(values=c('black','yellow','red'))
 

#  now filter the data based on this signal

  
#adjust this value (N) to tweak how many MADs to be away from the norm
N = 5

#Add clean value to dataframe (_.c)

df$co2_flux.c = ifelse(abs(co2fluxclean - Flux_filt) > (N * roll.mad),NA,co2fluxclean)



 ggplot(data = df)+geom_hline(yintercept = 0)+
  geom_point(aes(TIMESTAMP,co2fluxclean,col='uncleaned'))+
  geom_point(aes(TIMESTAMP,co2_flux.c,col='cleaned'))+
  scale_y_continuous(limits=c(-50,50))+
  scale_x_datetime(limits = as.POSIXct(flux_dates,format="%F"))+
  scale_color_manual(values=c('black','red'))

 

# See data with multiple layers of the MAD filter to see if it should be changed


ggplot(data = df)+
  geom_ribbon(aes(x = ts,ymax = Flux_filt+roll.mad*6,ymin = Flux_filt-roll.mad*6,fill='6'))+
  geom_ribbon(aes(x = ts,ymax = Flux_filt+roll.mad*3,ymin = Flux_filt-roll.mad*3,fill='3'))+
  geom_ribbon(aes(x = ts,ymax = Flux_filt+roll.mad*2,ymin = Flux_filt-roll.mad*2,fill='2'))+
  geom_ribbon(aes(x = ts,ymax = Flux_filt+roll.mad*1,ymin = Flux_filt-roll.mad*1,fill='1'))+
  geom_point(aes(ts,co2fluxclean),col='red')+
  geom_point(aes(ts,co2_flux.c),col='black')+
  scale_y_continuous(limits = c(-30, 18))+
  scale_x_datetime(limits = as.POSIXct(c('2022-05-17', '2022-06-25'),format="%F"))



ggplot(data = df)+
  geom_ribbon(aes(x = ts,ymax = Flux_filt+roll.mad*6,ymin = Flux_filt-roll.mad*6,fill='6'))+
  geom_ribbon(aes(x = ts,ymax = Flux_filt+roll.mad*3,ymin = Flux_filt-roll.mad*3,fill='3'))+
  geom_ribbon(aes(x = ts,ymax = Flux_filt+roll.mad*2,ymin = Flux_filt-roll.mad*2,fill='2'))+
  geom_ribbon(aes(x = ts,ymax = Flux_filt+roll.mad*1,ymin = Flux_filt-roll.mad*1,fill='1'))+
  geom_point(aes(ts,co2fluxclean),col='red')+
  geom_point(aes(ts,co2_flux.c),col='black')+
  scale_y_continuous(limits = c(-50, 50))+
  scale_x_datetime(limits = as.POSIXct(c('2022-07-20', '2022-09-27'),format="%F"))
 
```




#### H~2~O

 

```{r, warning=FALSE}
f = h2ofluxclean # first make a new flux vector to apply the above filters
# prepare the inputs for a zero-phase (forward and reverse) filter  
ind       = which(complete.cases(f))   # first save the index of all the NAs
b         = rep(1,8)/8                 # moving average coefficient
a         = 1                          # coefficient of the ARMA filter
Flux_i    = filtfilt(b, a, na.omit(f)) #create a forward and reverse ARMA filter
Flux_filt = f                          # make a copy of the full fluxes again
Flux_filt[ind] = Flux_i                # apply the filter where the real data exist

n = 7*48 # set the length of the rolling filter, 48 half hours in day * x days
roll.mad = rollapply(data = Flux_filt,
                     width = n,
                     FUN = mad,
                     partial = TRUE,
                     na.rm = T,
                     fill = NA)  #create a rolling MAD or sd or other
roll.mad[is.na(Flux_filt)] = NA  #make NA values where NAs exist in the real data

ggplot(df)+geom_hline(yintercept = 0)+
  geom_point(aes(ts,h2ofluxclean,col='h2o flux'))+
  geom_line(aes(ts,Flux_filt,col='Filter'))+
  geom_line(aes(ts,roll.mad,col='MAD'))+
  scale_y_continuous(limits = c(-2.5, 7))+
  scale_x_datetime(limits = as.POSIXct(flux_dates,format="%F"))+
  scale_color_manual(values=c('yellow','black','red'))
 

#  now filter the data based on this signal

  
#adjust this value (N) to tweak how many MADs to be away from the norm
N = 5

#Add clean value to dataframe (_.c)

df$h2o_flux.c = ifelse(abs(h2ofluxclean - Flux_filt) > (N * roll.mad),NA,h2ofluxclean)



 ggplot(data = df)+geom_hline(yintercept = 0)+
  geom_point(aes(TIMESTAMP,h2ofluxclean,col='uncleaned'))+
  geom_point(aes(TIMESTAMP,h2o_flux.c,col='cleaned'))+
  scale_y_continuous(limits=c(-2.5,7))+
  scale_x_datetime(limits = as.POSIXct(flux_dates,format="%F"))+
  scale_color_manual(values=c('black','red'))

# See data with multiple layers of the MAD filter to see if it should be changed


ggplot(data = df)+
  geom_ribbon(aes(x = ts,ymax = Flux_filt+roll.mad*6,ymin = Flux_filt-roll.mad*6,fill='6'))+
  geom_ribbon(aes(x = ts,ymax = Flux_filt+roll.mad*3,ymin = Flux_filt-roll.mad*3,fill='3'))+
  geom_ribbon(aes(x = ts,ymax = Flux_filt+roll.mad*2,ymin = Flux_filt-roll.mad*2,fill='2'))+
  geom_ribbon(aes(x = ts,ymax = Flux_filt+roll.mad*1,ymin = Flux_filt-roll.mad*1,fill='1'))+
  geom_point(aes(ts,h2ofluxclean),col='red')+
  geom_point(aes(ts,h2o_flux.c),col='black')+
  scale_y_continuous(limits = c(-5, 7.5))+
  scale_x_datetime(limits = as.POSIXct(flux_dates,format="%F"))


```



#### H

```{r, warning=FALSE}
# apply the moving window filter
f = Hclean # first make a new flux vector to apply the above filters

# prepare the inputs for a zero-phase (forward and reverse) filter  
ind       = which(complete.cases(f))   # first save the index of all the NAs
b         = rep(1,8)/8                 # moving average coefficient
a         = 1                          # coefficient of the ARMA filter
Flux_i    = filtfilt(b, a, na.omit(f)) #create a forward and reverse ARMA filter
Flux_filt = f                          # make a copy of the full fluxes again
Flux_filt[ind] = Flux_i                # apply the filter where the real data exist

n = 7*48 # set the length of the rolling filter, 48 half hours in day * x days
roll.mad = rollapply(data = Flux_filt,
                     width = n,
                     FUN = mad,
                     partial = TRUE,
                     na.rm = T,
                     fill = NA)  #create a rolling MAD or sd or other
roll.mad[is.na(Flux_filt)] = NA  #make NA values where NAs exist in the real data

ggplot(df)+geom_hline(yintercept = 0)+
  geom_point(aes(ts,Hclean,col='H'))+
  geom_line(aes(ts,Flux_filt,col='Filter'))+
  geom_line(aes(ts,roll.mad,col='MAD'))+
  scale_y_continuous(limits = c(-70,350))+
  scale_x_datetime(limits = as.POSIXct(flux_dates,format="%F"))+
  scale_color_manual(values=c('yellow','black','red'))
 

# Now filter the data based on this signal (N) adjust this to tweak how many MADs to be away from the norm, add clean value to dataframe (_.c) and Compare Clean vs. Uncleaned

  
N = 5

df$H.c = ifelse(abs(Hclean - Flux_filt) > (N * roll.mad),NA,Hclean)

ggplot(data = df)+geom_hline(yintercept = 0)+
  geom_point(aes(TIMESTAMP,Hclean,col='uncleaned'))+
  geom_point(aes(TIMESTAMP,H.c,col='cleaned'))+
  scale_y_continuous(limits=c(-70,350))+
  scale_x_datetime(limits = as.POSIXct(flux_dates,format="%F"))+
  scale_color_manual(values=c('black','red'))
 

# See data with multiple layers of the MAD filter to see if it should be changed


ggplot(data = df)+
  geom_ribbon(aes(x = df$ts,ymax = Flux_filt+roll.mad*6,ymin = Flux_filt-roll.mad*6,fill='6'))+
  geom_ribbon(aes(x = df$ts,ymax = Flux_filt+roll.mad*3,ymin = Flux_filt-roll.mad*3,fill='3'))+
  geom_ribbon(aes(x = df$ts,ymax = Flux_filt+roll.mad*2,ymin = Flux_filt-roll.mad*2,fill='2'))+
  geom_ribbon(aes(x = df$ts,ymax = Flux_filt+roll.mad*1,ymin = Flux_filt-roll.mad*1,fill='1'))+
  geom_point(aes(df$ts,Hclean),col='red')+
  geom_point(aes(df$ts,H.c),col='black')+
  scale_y_continuous(limits = c(-200,550))+
  scale_x_datetime(limits = as.POSIXct(flux_dates))
 
```


#### LE


```{r, warning=FALSE}
# apply the moving window filter
f = LEclean # first make a new flux vector to apply the above filters

# prepare the inputs for a zero-phase (forward and reverse) filter  
ind       = which(complete.cases(f))   # first save the index of all the NAs
b         = rep(1,8)/8                 # moving average coefficient
a         = 1                          # coefficient of the ARMA filter
Flux_i    = filtfilt(b, a, na.omit(f)) #create a forward and reverse ARMA filter
Flux_filt = f                          # make a copy of the full fluxes again
Flux_filt[ind] = Flux_i                # apply the filter where the real data exist

n = 7*48 # set the length of the rolling filter, 48 half hours in day * x days
roll.mad = rollapply(data = Flux_filt,
                     width = n,
                     FUN = mad,
                     partial = TRUE,
                     na.rm = T,
                     fill = NA)  #create a rolling MAD or sd or other
roll.mad[is.na(Flux_filt)] = NA  #make NA values where NAs exist in the real data

ggplot(df)+geom_hline(yintercept = 0)+
  geom_point(aes(ts,LEclean,col='LE'))+
  geom_line(aes(ts,Flux_filt,col='Filter'))+
  geom_line(aes(ts,roll.mad,col='MAD'))+
  scale_y_continuous(limits = c(-100,250))+
  scale_x_datetime(limits = as.POSIXct(flux_dates,format="%F"))+
  scale_color_manual(values=c('yellow','black','red'))
 

 # Now filter the data based on this signal (N) adjust this to tweak how many MADs to be away from the norm

  
N = 5

df$LE.c = ifelse(abs(LEclean - Flux_filt) > (N * roll.mad),NA,LEclean)

ggplot(data = df)+geom_hline(yintercept = 0)+
  geom_point(aes(TIMESTAMP,LEclean,col='uncleaned'))+
  geom_point(aes(TIMESTAMP,LE.c,col='cleaned'))+
  scale_y_continuous(limits=c(-100,250))+
  scale_x_datetime(limits = as.POSIXct(flux_dates,format="%F"))+
  scale_color_manual(values=c('black','red'))
 

# See data with multiple layers of the MAD filter to see if it should be changed


ggplot(data = df)+
  geom_ribbon(aes(x = df$ts,ymax = Flux_filt+roll.mad*6,ymin = Flux_filt-roll.mad*6,fill='6'))+
  geom_ribbon(aes(x = df$ts,ymax = Flux_filt+roll.mad*3,ymin = Flux_filt-roll.mad*3,fill='3'))+
  geom_ribbon(aes(x = df$ts,ymax = Flux_filt+roll.mad*2,ymin = Flux_filt-roll.mad*2,fill='2'))+
  geom_ribbon(aes(x = df$ts,ymax = Flux_filt+roll.mad*1,ymin = Flux_filt-roll.mad*1,fill='1'))+
  geom_point(aes(df$ts,LEclean),col='red')+
  geom_point(aes(df$ts,LE.c),col='black')+
  scale_y_continuous(limits = c(-220, 320))+
  scale_x_datetime(limits = as.POSIXct(flux_dates))


```



### Main Plots - includes .qc, .u, manual and spike cleaning



```{r, warning=FALSE}
ggplot(data = df)+theme_bw()+geom_hline(yintercept = 0)+
  geom_point(aes(ts,LE,col='Filt.'))+
  geom_point(aes(ts,LE.c,col='clean'))+
  scale_y_continuous(expression('LE ('*W~m^-2*')'))+
  scale_color_manual(values = c('black','red'))+
  scale_x_datetime(limits = as.POSIXct(flux_dates))


ggplot(data = df)+theme_bw()+geom_hline(yintercept = 0)+
  geom_point(aes(ts,H,col='Filt.'))+
  geom_point(aes(ts,H.c,col='clean'))+
  scale_y_continuous(expression('H ('*W~m^-2*')'))+
  scale_color_manual(values = c('black','red'))+
  scale_x_datetime(limits = as.POSIXct(flux_dates))

ggplot(data = df)+theme_bw()+geom_hline(yintercept = 0)+
  geom_point(aes(ts,co2_flux,col='Filt.'))+
  geom_point(aes(ts,co2_flux.c,col='clean'))+
  scale_y_continuous (expression('NEE ('*mu*mol~m^-2~s^-1*')'),
                      limits = c(-10,15))+
  scale_color_manual(values = c('black','red'))+
  scale_x_datetime(limits = as.POSIXct(flux_dates))

ggplot(data = df)+theme_bw()+geom_hline(yintercept = 0)+
  geom_point(aes(ts,h2o_flux,col='Filt.'))+
  geom_point(aes(ts,h2o_flux.c,col='clean'))+
  scale_y_continuous (expression('H2O Flux'),
                      limits = c(-10,10))+
  scale_color_manual(values = c('black','red'))+
  scale_x_datetime(limits = as.POSIXct(flux_dates))

```



### Diurnal Fluxes

set hour and month vectors to be able to take the averages - creates new tbl with 
median and standard deviation values averaged over the hour across the month (ie. 
all 11:00's in October are averaged)


```{r, warning=FALSE}
df$hour = as.numeric(format(df$ts,'%H'))
df$month = as.numeric(format(df$ts,'%m'))

diel = df %>% group_by(hour,month) %>% select(co2_flux.c,,LE.c,H.c, h2o_flux.c,hour,month) %>% summarise_all(.funs = c("med" = median, "sd" = sd),na.rm=T)

diel = subset(diel,!is.na(diel$month))
 
 
```



#### NEE


```{r, warning=FALSE}
ggplot(data = diel)+geom_hline(yintercept = 0)+
  geom_line(aes(hour,co2_flux.c_med),lty=2)+
  geom_ribbon(aes(x = hour,y = co2_flux.c_med,
                  ymax = co2_flux.c_med + co2_flux.c_sd,
                  ymin = co2_flux.c_med - co2_flux.c_sd),
              alpha= 0.5)+
  facet_wrap(~month)

levels(diel$month)
 
```


#### H~2~O Flux

```{r, warning=FALSE}
ggplot(data = diel)+geom_hline(yintercept = 0)+
  geom_line(aes(hour,h2o_flux.c_med),lty=2)+
  geom_ribbon(aes(x = hour,y = h2o_flux.c_med,
                  ymax = h2o_flux.c_med + h2o_flux.c_sd,
                  ymin = h2o_flux.c_med - h2o_flux.c_sd),
              alpha= 0.5)+
  facet_wrap(~month)

levels(diel$month)
 
```


#### H

```{r, warning=FALSE}
ggplot(data = diel)+geom_hline(yintercept = 0)+
  geom_line(aes(hour,H.c_med),lty=2)+
  geom_ribbon(aes(x = hour,y = H.c_med,
                  ymax = H.c_med + H.c_sd,
                  ymin = H.c_med - H.c_sd),
              alpha= 0.5)+
  facet_wrap(~month)
 
```



#### LE


```{r, warning=FALSE}
ggplot(data = diel)+geom_hline(yintercept = 0)+
  geom_line(aes(hour,LE.c_med),lty=2)+
  geom_ribbon(aes(x = hour,y = LE.c_med,
                  ymax = LE.c_med + LE.c_sd,
                  ymin = LE.c_med - LE.c_sd),
              alpha= 0.5)+
  facet_wrap(~month)
 
```





#### Post-clean energy balance check 



```{r, warning=FALSE, echo=FALSE}
df$met_EB.c = df$NR_Wm2_Avg.c
df$flux_EB.c = df$H.c + df$LE.c

plot(df$met_EB.c,df$flux_EB.c, abline(0, 1, col= 'blue'),xlim = c(-100,500),ylim = c(-100,500))

summary(lm(df$flux_EB.c ~ df$met_EB.c))
```



#### R^2^ = `r summary(lm(df$flux_EB.c ~ df$met_EB.c))$r.squared`: much better :)



### Save Cleaned Flux Data

```{r, warning=FALSE}
write.csv(x = df,file = 'C:/Users/dtrangmoe/Documents/IQ/IQ Loading & Cleaning/IQ1_2022_Clean.csv',
          row.names = F,quote = F)
```


