---
title: "YKD Year Long Files"
author: "Dani Trangmoe"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r, warning=FALSE}
rm(list = ls())

library(data.table)
library(ggplot2)
library(cowplot)
library(openair)
library(plotrix)
library(signal)
library(svMisc)
library(zoo)
library(stringr)
library(plyr)
library(dplyr)
library(lubridate)
```

# YKD Burned 


Load in entire cleaned met file 
```{r, warning=FALSE}

df1 = fread('C:/Users/dtrangmoe/Documents/YKD Burned/Cleaned Data/YKDBurned_Met_clean.csv')

#create timestamp variable
df1$ts = as.POSIXct(paste(df1$date, df1$time), format="%Y-%m-%d %H:%M", tz="utc")

#check to make sure all duplicated rows are removed
sum(duplicated(df1))

df1 <- df1[!duplicated(df1$ts),]

mindate1 = floor_date(min(df1$ts))
maxdate1 = ceiling_date(max(df1$ts))



```

### Load

Load in entire flux cleaned data
```{r, warning=FALSE}

df2 = fread('C:/Users/dtrangmoe/Documents/YKD Burned/Cleaned Data/YKDBurned_Flux_clean.csv')


sum(duplicated(df2))

df2 <- df2[!duplicated(df2$ts),]

#check to make sure correct number of rows are kept
mindate2 = floor_date(min(df2$ts))
maxdate2 = ceiling_date(max(df2$ts))



```

### Merge
Merge dataframes to inc. cleaned flux and met

```{r, warning=F}


df <- merge(df1, df2, by="ts", suffixes = (c("", ".rm")), all = TRUE)

mindate = floor_date(min(df$ts))
maxdate = ceiling_date(max(df$ts))

# #make sure biomet is identical from each file before removing cols
plot(df$ALB_1_1_1, df$ALB_1_1_1.rm);abline(a = 0, b = 1, col = "red")
plot(df$P_RAIN_1_1_1, df$P_RAIN_1_1_1.rm);abline(a = 0, b = 1, col = "red")
plot(df$PPFD_1_1_1, df$PPFD_1_1_1.rm);abline(a = 0, b = 1, col = "red")

df <- select(df, !ends_with(".rm"))

#check for timestamps that don't end in 00 or 30
minutes <- format(df$ts, "%M")
minutes_vector <- minutes != "00" & minutes != "30"
sum(minutes_vector)

df$ts = round_date(df$ts, "30 minutes")

minutes <- format(df$ts, "%M")
minutes_vector <- minutes != "00" & minutes != "30"
sum(minutes_vector)

#create a timestamp variable every half hour to the full months
ts = seq(from = mindate,to = maxdate,by = 60*30)
ts = as.data.frame(ts)


#merge with the flux data frame to create NAs where data is missing
df = merge(ts,df,by = 'ts',all.x = T)

# 
# # Load in cleaned, merged, tidy file for splitting if possible 
# 
# df=fread('C:/Users/dtrangmoe/Documents/YKD Burned/YKDBurned_Flux_Met_Clean_AmerifluxFormat.csv')
```

### 2019 File

```{r, warning=FALSE}

df19 <- df %>%
  filter(year(ts) %in% c(2019))

plot(df19$ts, df19$co2_flux.c)

# Save df as 2019 file 

write.csv(x = df19,file = 'C:/Users/dtrangmoe/Documents/YKD Burned/Cleaned Data/YKDBurned_Cleaned_Met_Flux_2019_Ameriflux.csv',row.names = F,quote = F)

```

### 2020 File

```{r, warning=FALSE}

df20 <- df %>%
  filter(year(ts) %in% c(2020))

plot(df20$ts, df20$co2_flux.c)

# Save df as 2020 file 

write.csv(x = df20,file = 'C:/Users/dtrangmoe/Documents/YKD Burned/Cleaned Data/YKDBurned_Cleaned_Met_Flux_2020_Ameriflux.csv',row.names = F,quote = F)

```

### 2021 File

```{r, warning=FALSE}

df21 <- df %>%
  filter(year(ts) %in% c(2021))

plot(df21$ts, df21$co2_flux.c)

# Save df as 2021 file 

write.csv(x = df21,file = 'C:/Users/dtrangmoe/Documents/YKD Burned/Cleaned Data/YKDBurned_Cleaned_Met_Flux_2021_Ameriflux.csv',row.names = F,quote = F)

```

### 2022 File

```{r, warning=FALSE}

df22 <- df %>%
  filter(year(ts) %in% c(2022))

plot(df22$ts, df22$co2_flux.c)

# Save df as 2022 file 

write.csv(x = df22,file = 'C:/Users/dtrangmoe/Documents/YKD Burned/Cleaned Data/YKDBurned_Cleaned_Met_Flux_2022_Am.csv',row.names = F,quote = F)

```






# YKD Unburned 

### Load

Load in entire cleaned met file 
```{r, warning=FALSE}

df1 = fread('C:/Users/dtrangmoe/Documents/YKD Unburned/Cleaned Data/YKDUnburned_Met_clean.csv')


#check to make sure all duplicated rows are removed
sum(duplicated(df1))
df1 <- df1[!duplicated(df1$ts),]


#take the min and max date rounding to the nearest full month
mindate1 = floor_date(min(df1$ts))
maxdate1 = ceiling_date(max(df1$ts))



#create a timestamp variable every half hour to the full months
ts = seq(from = mindate1,to = maxdate1,by = 60*30)
ts = as.data.frame(ts)


#merge with the flux data frame to create NAs where data is missing
df = merge(ts,df1,by = 'ts',all.x = T)

mindate1 = floor_date(min(df1$ts))
maxdate1 = ceiling_date(max(df1$ts))

```


Load in entire flux cleaned data
```{r, warning=FALSE}

df2 = fread('C:/Users/dtrangmoe/Documents/YKD Unburned/Cleaned Data/YKDUnburned_Flux_clean.csv')


sum(duplicated(df2))

df2 <- df2[!duplicated(df2$ts),]

#check to make sure corrext number of rows are kept
mindate2 = floor_date(min(df2$ts))
maxdate2 = ceiling_date(max(df2$ts))

```



### Merge
Merge dataframes to inc. cleaned flux and met

```{r, warning=F}


df <- merge(df1, df2, by="ts", suffixes = (c("", ".rm")), all = TRUE)

# #make sure biomet is identical from each file before removing cols
plot(df$ALB_1_1_1, df$ALB_1_1_1.rm);abline(a = 0, b = 1, col = "red")
plot(df$P_RAIN_1_1_1, df$P_RAIN_1_1_1.rm);abline(a = 0, b = 1, col = "red")
plot(df$PPFD_1_1_1, df$PPFD_1_1_1.rm);abline(a = 0, b = 1, col = "red")

df <- select(df, !ends_with(".rm"))

# check to ensure timestamps are only 00 or 30 min.
minutes <- format(df1$ts, "%M")
minutes_vector <- minutes != "00" & minutes != "30"
sum(minutes_vector)

#create a timestamp variable every half hour to the full months
ts = seq(from = mindate1,to = maxdate1,by = 60*30)
ts = as.data.frame(ts)


#merge with the flux data frame to create NAs where data is missing
df = merge(ts,df,by = 'ts',all.x = T)

```

For pre-merged file
```{r, warning=FALSE}
rm(list=ls())

df = fread('C:/Users/dtrangmoe/Documents/YKD Unburned/YKDUnburned_Flux_Met_Clean_AmerifluxFormat.csv')

```


To save off full merged file
```{r, warning=FALSE}

# write.csv(df, 'C:/Users/dtrangmoe/Documents/YKD Unburned/YKDUnburned_Flux_Met_Clean_NotAmeriflux.csv')

```

### 2019 File

```{r, warning=FALSE}

df19 <- df %>%
  filter(year(ts) %in% c(2019))

plot(df19$ts, df19$ch4_flux.c)

# Save df as 2019 file 

write.csv(x = df19,file = 'C:/Users/dtrangmoe/Documents/YKD Unburned/Cleaned Data/YKDUnburned_Cleaned_Met_Flux_2019_Ameriflux.csv',row.names = F,quote = F)

```

### 2020 File

```{r, warning=FALSE}

df20 <- df %>%
  filter(year(ts) %in% c(2020))

plot(df20$ts, df20$co2_flux.c)

# Save df as 2020 file 

write.csv(x = df20,file = 'C:/Users/dtrangmoe/Documents/YKD Unburned/Cleaned Data/YKDUnburned_Cleaned_Met_Flux_2020_Ameriflux.csv',row.names = F,quote = F)

```

### 2021 File

```{r, warning=FALSE}

df21 <- df %>%
  filter(year(ts) %in% c(2021))

plot(df21$ts, df21$co2_flux.c)

# Save df as 2021 file 

write.csv(x = df21,file = 'C:/Users/dtrangmoe/Documents/YKD Unburned/Cleaned Data/YKDUnburned_Cleaned_Met_Flux_2021_Ameriflux.csv',row.names = F,quote = F)

```

### 2022 File

```{r, warning=FALSE}

df22 <- df %>%
  filter(year(ts) %in% c(2022))

plot(df22$ts, df22$co2_flux.c)

# Save df as 2022 file 

write.csv(x = df22,file = 'C:/Users/dtrangmoe/Documents/YKD Unburned/Cleaned Data/YKDUnburned_Cleaned_Met_Flux_2022_Ameriflux.csv',row.names = F,quote = F)

```


## Compare old/new files 

Load into one df
```{r, warning=FASLE}
rm(list = ls())

df_new = fread('C:/Users/dtrangmoe/Documents/YKD Unburned/YKDUnburned_Flux_Met_Clean_AmerifluxFormat.csv')

df_old = fread('C:/Users/dtrangmoe/Documents/YKD Unburned/YKDUnburned_Flux_Met_Clean_NotAAmeriflux.csv')


df_old_renamed <- df_old %>% 
    rename_with(~paste0(., "_old"), everything())

df_old_renamed$ts = df_old_renamed$ts_old


df <- full_join(df_new, df_old_renamed, by = 'ts')

```


Compare
```{r, warning=FASLE}

library(gridExtra)

## CH4 


old <- ggplot(data = df, aes(x = ts, y = ch4_flux.c_old)) + 
  geom_point() +
  ggtitle("Old Data")

new <- ggplot(data = df, aes(x = ts, y = ch4_flux.c)) + 
  geom_point() +
  ggtitle("New Data")

# Arrange the plots side by side
combined_plot <- grid.arrange(new, old, ncol = 2)



## CO2

oldco2 <- ggplot(data = df, aes(x = ts, y = co2_flux.c_old)) + 
  geom_point() +
  ggtitle("Old Data")

newco2 <- ggplot(data = df, aes(x = ts, y = co2_flux.c)) + 
  geom_point() +
  ggtitle("New Data")

# Arrange the plots side by side
combined_plot <- grid.arrange(newco2, oldco2, ncol = 2)



## LE

oldLE <- ggplot(data = df, aes(x = ts, y = LE.c_old)) + 
  geom_point() +
  ggtitle("Old Data")

newLE <- ggplot(data = df, aes(x = ts, y = LE.c)) + 
  geom_point() +
  ggtitle("New Data")

# Arrange the plots side by side
combined_plot <- grid.arrange(newLE, oldLE, ncol = 2)





## H

oldH <- ggplot(data = df, aes(x = ts, y = H.c_old)) + 
  geom_point() +
  ggtitle("Old Data")

newH <- ggplot(data = df, aes(x = ts, y = H.c)) + 
  geom_point() +
  ggtitle("New Data")

# Arrange the plots side by side
combined_plot <- grid.arrange(newH, oldH, ncol = 2)

```
