---
title: "YKDBurned_Cleaning"
author: "Marco Montemayor"
date: "2022-12-12"
output: pdf_document
---

# Loading DF's

Clear Console and add packages

```{r,include= FALSE}
rm(list = ls())

library(data.table)
library(ggplot2)
library(plotrix)
library(signal)
library(svMisc)
library(zoo)
library(stringr)
library(plyr)
library(dplyr)
```

Load in eddypro output and Biomet files

```{r}
fp = 'C:/Permafrost Pathways/YKDBurned/eddypro/EP_full_output'
files = list.files(path = fp,pattern = '*full_output.+csv$',recursive = T,full.names = T)

#load the headers and data into their own lists

h   = lapply(files, fread,skip = 1,nrow = 0)
dat = lapply(files, fread,skip = 3,header = F,na.strings=c('-9999','NA','NaN','NAN'))

#assign the headers to the data

for (i in 1:length(h)) {
  names(dat[[i]]) = names(h[[i]])
}

#make all the lists into one dataframe

df = dat[[1]]
for (i in 2:length(dat)) {
  df = rbind.fill(df,dat[[i]])
}
#create a timestamp from the date and time of full_EP

df$ts = as.POSIXct(x = paste(df$date,df$time,sep = ' '),tz = 'UTC')

#load in the biomet data

fp = 'C:/Permafrost Pathways/YKDBurned/eddypro/EP_biomet'
files = list.files(path = fp,pattern = '*biomet',recursive = T,full.names = T)


#load the headers and data into their own lists

h   = lapply(files, fread,skip = 0,nrow = 0)
dat = lapply(files, fread,skip = 2,header = F,fill = T, na.strings=c('-9999','NA','NaN','NAN'),drop=c('_0_0_1'))

#assign the headers to the data

for (i in 1:length(h)) {
  names(dat[[i]]) = names(h[[i]])
}

#make all the lists into one dataframe

met = dat[[1]]
for (i in 2:length(dat)) {
  met = rbind.fill(met,dat[[i]])
}

#create a timestamp from the date and time

met$ts = as.POSIXct(x = paste(met$date,met$time,sep = ' '),tz = 'UTC')
#merge datasets
df= merge(met,df,by= c('ts','date','time','DOY'),all = T)
```

# Initial Clean

## Energy Balance

combine energy fluxes by met and flux components

```{r}
df$SHF_mean <- mean(c(df$SHF_1_1_1, df$SHF_2_1_1, df$SHF_3_1_1),na.rm = T)
df$met =  (df$LWIN_1_1_1 + df$SWIN_1_1_1) - (df$LWOUT_1_1_1 + df$SWOUT_1_1_1) - df$SHF_mean
df$flux = df$H + df$LE

```

plot shortwave radiation in

```{r}
plot(df$SWIN_1_1_1)
```
plot shortwave radation out

```{r}
plot(df$SWOUT_1_1_1)
```

plot longwave radiation in

```{r}
plot(df$LWIN_1_1_1)
```

plot longwave radiation out

```{r}
plot(df$ts,df$LWOUT_1_1_1,ylim = c(0,800))
``` 
create and plot mismatch variable between met and flux

```{r}
df$mismatch = df$flux/df$met

plot(df$ts,df$mismatch,ylim = c(0,5))
```
plot energy balance
```{r}
plot(df$met,df$flux, xlim = c(-150,650), ylim = c(-150,650), abline(a=0, b=1, col='red') ) 
```
NEED TO REASSESS OR GET RID OF THIS CHUNK ---- removes where the energy balance is off by more than a factor of 10, not sure I like this, mostly removes small fluxes where the factor would have a larger relative mismatch

create new variable _.energy

## EP QC

filter by the eddypro flags and create new variable _.qc

```{r}
Tau.energy  = replace(df$Tau ,abs(df$mismatch)>20,NA)
H.energy    = replace(df$H   ,abs(df$mismatch)>20,NA)
LE.energy   = replace(df$LE  ,abs(df$mismatch)>20,NA)
co2_flux.energy   = replace(df$co2_flux  ,abs(df$mismatch)>20,NA)
ch4_flux.energy = replace(df$ch4_flux,abs(df$mismatch)>20,NA)

Tau.qc      = replace(df$Tau,df$qc_Tau == 2,NA)
co2_flux.qc = replace(df$co2_flux,df$qc_co2_flux == 2,NA)
ch4_flux.qc = replace(df$ch4_flux,df$qc_ch4_flux == 2,NA)
LE.qc       = replace(df$LE,df$qc_LE == 2,NA)
H.qc        = replace(df$H,df$qc_H == 2,NA)
```

## Clear Outliers

look for absolute outliers and manually set some absolute limits to remove crazy data

### Tau

Plot Tau Histogram

```{r}
hist(df$Tau,breaks=100, xlim=c(-1,1))
```

Cut the crazy data and create new variable (Tau.limits)

```{r}
Tau.limits = replace(df$Tau,df$Tau.c > -1,NA)
Tau.limits = replace(df$Tau,df$Tau.c < .5,NA)
```

### NEE

Plot NEE Histogram

```{r}
hist(df$co2_flux,breaks=100, xlim=c(-120,120))
```
```{r}
monthlycleaning = data.frame(month = seq(1,12),
                             minflux = c(-5,-5,-7,-10,-12,-15,-15,-15,-12,-7,-5,-5),
                             maxflux = c(9,10,11,11,11,11,11,11,11,11,10,9))
                             

df=df%>% 
  #select(-c(minflux,maxflux))%>%
  mutate(month=month(ts))%>%
  left_join(monthlycleaning,by=c('month'))
  
```

```{r}
ggplot(df,aes(x=ts))+
  geom_ribbon(aes(ymin= minflux, ymax= maxflux),fill='yellow')+
  geom_point( aes(y=co2_flux))+
  scale_y_continuous(limits= c(-25,25))+
  scale_x_datetime(limits = as.POSIXct(c('2022-4-12','2022-12-31')))
  
```

```{r}
co2_flux.limits = df%>%
  mutate(co2_flux.limits= ifelse(co2_flux >= minflux & co2_flux <= maxflux,
                                 co2_flux,
                                 NA))%>% 
  pull(co2_flux.limits)
plot(co2_flux.limits)
```


### CH4

Plot CH4 Histogram
```{r}
hist(df$ch4_flux,breaks=100)
```

Plot what we might clean

```{r}
plot(df$ts,df$ch4_flux,ylim = c(-2,6.8));abline(h=-.36, col= 'red');abline(h=6, col='red'); abline(h=0,col= 'black')
```

Clean based on graphs, create new variable (ch4_flux.limits), and see cleaned product

```{r}
ch4_flux.limits = replace(df$ch4_flux,df$ch4_flux > 6 | df$ch4_flux < -0.36,NA)
hist(ch4_flux.limits,breaks = 100)
plot(ch4_flux.limits)
```

### H

Plot H Histogram and plot what we might clean

```{r}
hist(df$H,breaks=100)

plot(df$ts,df$H,ylim = c(-250,475));abline(h=-175, col= 'red');abline(h=380, col='red')
```

Clean based on graphs, create new variable (H.limits), and see cleaned product

```{r}
H.limits = replace(df$H, df$H < -175 | df$H > 380,NA)
hist(H.limits,breaks = 100)
plot(H.limits)
```

### LE

Plot LE Histogram

```{r}
hist(df$LE,breaks=100)
```

Plot what we might clean

```{r}
plot(df$ts,df$LE,ylim = c(-350,500));abline(h=-210, col= 'red');abline(h=310, col='red')
```

Clean based on graphs, create new variable (LE.limits), and see cleaned product

```{r}
LE.limits = replace(df$LE, df$LE < -210 | df$LE > 310,NA)
hist(LE.limits)
plot(LE.limits)
```

## USTAR

use night-time only flux values and plot

```{r}
df$nightCO2 = co2_flux.limits
df$nightCO2 = replace(df$nightCO2,df$SWIN_1_1_1 > 10,NA)

plot(df$nightCO2,ylim = c(-20,20))
```

Create a USTAR threshold scatter plot based on the drop off in data

```{r}
Uthreshold=0.05
ggplot(data = df,aes(`u*`,nightCO2))+
  ylab(expression(paste("Flux (g-C", ~CO[2], ~"m",""^"-2","d",""^"-1",")")))+
  geom_point()+xlab("U*")+
  scale_x_continuous(limits = c(0,.6))+
  geom_vline(xintercept = Uthreshold,col='red')

```

pick threshold and filter based on plots above, I liked .05

```{r}
Tau.u  = replace(df$Tau ,df$`u*` < Uthreshold,NA)
H.u    = replace(df$H   ,df$`u*` < Uthreshold,NA)
LE.u   = replace(df$LE  ,df$`u*` < Uthreshold,NA)
co2_flux.u   = replace(df$co2_flux  ,df$`u*` < Uthreshold,NA)
ch4_flux.u = replace(df$ch4_flux,df$`u*` < Uthreshold,NA)
```

## Combine Cleaning

investigate the previous limits and combine all to create a new variable (_clean), plot to see difference

```{r}
co2fluxclean = ifelse(is.na(co2_flux.qc) | is.na(co2_flux.limits) | is.na(co2_flux.u),NA,df$co2_flux)
ch4fluxclean = ifelse(is.na(ch4_flux.qc) | is.na(ch4_flux.limits) | is.na(ch4_flux.u),NA,df$ch4_flux)
Hclean = ifelse(is.na(H.qc) | is.na(H.limits) | is.na(H.u),NA,df$H)
LEclean = ifelse(is.na(LE.qc) | is.na(LE.limits) | is.na(LE.u),NA,df$LE)
Tauclean = ifelse(is.na(Tau.qc) | is.na(Tau.limits) | is.na(Tau.u),NA,df$Tau)

plot(df$ts,co2fluxclean)
plot(df$ts,ch4fluxclean)
plot(df$ts,Hclean)
plot(df$ts,LEclean)
plot(df$ts,Tauclean)

```
# MAD Filter

Now, Spike filtering on half-hourly fluxes. For this type of data, filters based on median rather than std perform better. Use Unsymmetric Distributions and double MAD -MAD=Median Absolute Deviation for more info see link below <https://eurekastatistics.com/using-the-median-absolute-deviation-to-find-outliers/>

## NEE
```{r}
f = co2fluxclean # first make a new flux vector to apply the above filters
# prepare the inputs for a zero-phase (forward and reverse) filter  
ind       = which(complete.cases(f))   # first save the index of all the NAs
b         = rep(1,8)/8                 # moving average coefficient
a         = 1                          # coefficient of the ARMA filter
Flux_i    = filtfilt(b, a, na.omit(f)) #create a forward and reverse ARMA filter
Flux_filt = f                          # make a copy of the full fluxes again
Flux_filt[ind] = Flux_i                # apply the filter where the real data exist

n = 7*48 # set the length of the rolling filter, 48 half hours in day * x days
roll.mad = rollapply(data = Flux_filt,
                     width = n,
                     FUN = mad,
                     partial = TRUE,
                     na.rm = T,
                     fill = NA)  #create a rolling MAD or sd or other
roll.mad[is.na(Flux_filt)] = NA  #make NA values where NAs exist in the real data
```

Graph to see filter and points

```{r}
plot(df$ts,Flux_filt,xlim = as.POSIXct(c('2019-9-1','2022-9-1')),col='red',type = 'l');points(df$ts,df$co2_flux)

plot(df$ts,roll.mad,xlim = as.POSIXct(c('2019-9-1','2022-9-1')),col='red',type = 'l')
```

now filter the data based on this signal

adjust this value (N) to tweak how many MADs to be away from the norm

```{r}
N = 3 
```

Add clean value to dataframe (_.c)

```{r}
df$co2_flux.c = ifelse(abs(co2fluxclean - Flux_filt) > (N * roll.mad),NA,co2fluxclean)
```

Compare cleaned vs. uncleaned

```{r}
plot(df$ts,df$co2_flux,col='red',ylim = c(-20,20));points(df$ts,df$co2_flux.c)
```

See data with multiple layers of the MAD filter to see if it should be changed

```{r}
ggplot(data = df)+
  geom_ribbon(aes(x = ts,ymax = Flux_filt+roll.mad*6,ymin = Flux_filt-roll.mad*6,fill='6'))+
  geom_ribbon(aes(x = ts,ymax = Flux_filt+roll.mad*3,ymin = Flux_filt-roll.mad*3,fill='3'))+
  geom_ribbon(aes(x = ts,ymax = Flux_filt+roll.mad*2,ymin = Flux_filt-roll.mad*2,fill='2'))+
  geom_ribbon(aes(x = ts,ymax = Flux_filt+roll.mad*1,ymin = Flux_filt-roll.mad*1,fill='1'))+
  geom_point(aes(ts,co2fluxclean),col='black')+
  geom_point(aes(ts,co2_flux.c),col='red')+
  scale_y_continuous(limits = c(-15,15))+
scale_x_datetime(limits = as.POSIXct(c('2022-9-21','2022-12-31')))
```
## CH4
```{r}
 #apply the moving window filter
f = ch4fluxclean # first make a new flux vector to apply the above filters

# prepare the inputs for a zero-phase (forward and reverse) filter  
ind       = which(complete.cases(f))   # first save the index of all the NAs
b         = rep(1,8)/8                 # moving average coefficient
a         = 1                          # coefficient of the ARMA filter
Flux_i    = filtfilt(b, a, na.omit(f)) #create a forward and reverse ARMA filter
Flux_filt = f                          # make a copy of the full fluxes again
Flux_filt[ind] = Flux_i                # apply the filter where the real data exist

n = 7*48 # set the length of the rolling filter, 48 half hours in day * x days
roll.mad = rollapply(data = Flux_filt,
                     width = n,
                     FUN = mad,
                     partial = TRUE,
                     na.rm = T,
                     fill = NA)  #create a rolling MAD or sd or other
roll.mad[is.na(Flux_filt)] = NA  #make NA values where NAs exist in the real data
```

adjust this (N) to tweak how many MADs to be away from the norm, CH4 deserves more because of it's nature, then graph

```{r}
N = 6 
df$ch4_flux.c = ifelse(abs(ch4fluxclean - Flux_filt) > (N * roll.mad),NA,ch4fluxclean)

plot(df$ts,roll.mad,xlim = as.POSIXct(c('2019-9-1','2022-9-15')),col='red',type = 'l')

plot(df$ts,Flux_filt,xlim = as.POSIXct(c('2019-9-1','2022-9-15')),col='red',type = 'l');points(df$ts,df$ch4_flux)
```

Add clean value to the dataframe (_.c) and compare cleaned vs. uncleaned


```{r}
df$ch4_flux.c = ifelse(abs(ch4fluxclean - Flux_filt) > (N * roll.mad),NA,ch4fluxclean)

plot(df$ts,ch4fluxclean,col='red');points(df$ts,df$ch4_flux.c);abline(h=0)
```

See data with multiple layers of the MAD filter to see if it should be changed

```{r}
ggplot(data = df)+
  geom_ribbon(aes(x = df$ts,ymax = Flux_filt+roll.mad*9,ymin = Flux_filt-roll.mad*6,fill='9'))+
  geom_ribbon(aes(x = df$ts,ymax = Flux_filt+roll.mad*6,ymin = Flux_filt-roll.mad*3,fill='6'))+
  geom_ribbon(aes(x = df$ts,ymax = Flux_filt+roll.mad*5,ymin = Flux_filt-roll.mad*2,fill='5'))+
  geom_ribbon(aes(x = df$ts,ymax = Flux_filt+roll.mad*4,ymin = Flux_filt-roll.mad*1,fill='4'))+
  geom_point(aes(df$ts,ch4fluxclean),col='black')+
  geom_point(aes(df$ts,ch4_flux.c),col='red')+
  scale_y_continuous(limits = c(-.15,.35))+
  scale_x_datetime(limits = as.POSIXct(c('2022-7-12','2022-9-22')))
```
## H

```{r}
# apply the moving window filter
f = Hclean # first make a new flux vector to apply the above filters

# prepare the inputs for a zero-phase (forward and reverse) filter  
ind       = which(complete.cases(f))   # first save the index of all the NAs
b         = rep(1,8)/8                 # moving average coefficient
a         = 1                          # coefficient of the ARMA filter
Flux_i    = filtfilt(b, a, na.omit(f)) #create a forward and reverse ARMA filter
Flux_filt = f                          # make a copy of the full fluxes again
Flux_filt[ind] = Flux_i                # apply the filter where the real data exist

n = 7*48 # set the length of the rolling filter, 48 half hours in day * x days
roll.mad = rollapply(data = Flux_filt,
                     width = n,
                     FUN = mad,
                     partial = TRUE,
                     na.rm = T,
                     fill = NA)  #create a rolling MAD or sd or other
roll.mad[is.na(Flux_filt)] = NA  #make NA values where NAs exist in the real data

```

Now filter the data based on this signal (N) adjust this to tweak how many MADs to be away from the norm

```{r}
N = 3
```

Add clean value to dataframe (_.c) and Compare Clean vs. Uncleaned

```{r}
df$H.c = ifelse(abs(Hclean - Flux_filt) > (N * roll.mad),NA,Hclean)

plot(df$ts,Hclean,col='red');points(df$ts,df$H.c)
```

See data with multiple layers of the MAD filter to see if it should be changed

```{r}
ggplot(data = df)+
  geom_ribbon(aes(x = df$ts,ymax = Flux_filt+roll.mad*6,ymin = Flux_filt-roll.mad*6,fill='6'))+
  geom_ribbon(aes(x = df$ts,ymax = Flux_filt+roll.mad*3,ymin = Flux_filt-roll.mad*3,fill='3'))+
  geom_ribbon(aes(x = df$ts,ymax = Flux_filt+roll.mad*2,ymin = Flux_filt-roll.mad*2,fill='2'))+
  geom_ribbon(aes(x = df$ts,ymax = Flux_filt+roll.mad*1,ymin = Flux_filt-roll.mad*1,fill='1'))+
  geom_point(aes(df$ts,Hclean),col='black')+
  geom_point(aes(df$ts,H.c),col='red')+
  scale_y_continuous(limits = c(-550,550))+
  scale_x_datetime(limits = as.POSIXct(c('2022-9-1','2022-12-31')))
```

## LE

```{r}
# apply the moving window filter
f = LEclean # first make a new flux vector to apply the above filters

# prepare the inputs for a zero-phase (forward and reverse) filter  
ind       = which(complete.cases(f))   # first save the index of all the NAs
b         = rep(1,8)/8                 # moving average coefficient
a         = 1                          # coefficient of the ARMA filter
Flux_i    = filtfilt(b, a, na.omit(f)) #create a forward and reverse ARMA filter
Flux_filt = f                          # make a copy of the full fluxes again
Flux_filt[ind] = Flux_i                # apply the filter where the real data exist

n = 7*48 # set the length of the rolling filter, 48 half hours in day * x days
roll.mad = rollapply(data = Flux_filt,
                     width = n,
                     FUN = mad,
                     partial = TRUE,
                     na.rm = T,
                     fill = NA)  #create a rolling MAD or sd or other
roll.mad[is.na(Flux_filt)] = NA  #make NA values where NAs exist in the real data

```

Now filter the data based on this signal (N) adjust this to tweak how many MADs to be away from the norm

```{r}
N = 3
```

Add clean value to dataframe (_.c) and compare Cleaned vs. Uncleaned

```{r}
df$LE.c = ifelse(abs(LEclean - Flux_filt) > (N * roll.mad),NA,LEclean)

plot(df$ts,LEclean,col='red');points(df$ts,df$LE.c)
```

See data with multiple layers of the MAD filter to see if it should be changed

```{r}
ggplot(data = df)+
  geom_ribbon(aes(x = df$ts,ymax = Flux_filt+roll.mad*6,ymin = Flux_filt-roll.mad*6,fill='6'))+
  geom_ribbon(aes(x = df$ts,ymax = Flux_filt+roll.mad*3,ymin = Flux_filt-roll.mad*3,fill='3'))+
  geom_ribbon(aes(x = df$ts,ymax = Flux_filt+roll.mad*2,ymin = Flux_filt-roll.mad*2,fill='2'))+
  geom_ribbon(aes(x = df$ts,ymax = Flux_filt+roll.mad*1,ymin = Flux_filt-roll.mad*1,fill='1'))+
  geom_point(aes(df$ts,LEclean),col='black')+
  geom_point(aes(df$ts,LE.c),col='red')+
  scale_y_continuous(limits = c(-550,550))+
  scale_x_datetime(limits = as.POSIXct(c('2022-9-1','2022-12-31')))
```
#Main Plots

Marco's note- During the Fall 22 period, the cleaning code is working extra hard compared to years previous, may need to see if instruments (anemometer specifically) are functioning properly. Cleaned normally, as instructed
```{r}
ggplot(data = df)+theme_bw()+geom_hline(yintercept = 0)+
  geom_point(aes(ts,LE,col='Filt.'))+
  geom_point(aes(ts,LE.c,col='clean'))+
  scale_y_continuous(expression('LE ('*W~m^-2*')'),
                     limits = c(-250,550))+
  scale_color_manual(values = c('black','red'))

ggplot(data = df)+theme_bw()+geom_hline(yintercept = 0)+
  geom_point(aes(ts,H,col='Filt.'))+
  geom_point(aes(ts,H.c,col='clean'))+
  scale_y_continuous(expression('H ('*W~m^-2*')'),
                     limits = c(-250,550))+
  scale_color_manual(values = c('black','red'))

ggplot(data = df)+theme_bw()+geom_hline(yintercept = 0)+
  geom_point(aes(ts,co2_flux,col='Filt.'))+
  geom_point(aes(ts,co2_flux.c,col='clean'))+
  scale_y_continuous(limits = c(-20,15),
                      expression('NEE ('*mu*mol~m^-2~s^-1*')'))+
  scale_color_manual(values = c('black','red'))

ggplot(data = df)+theme_bw()+geom_hline(yintercept = 0)+
  geom_point(aes(ts,ch4_flux,col='Filt.'))+
  geom_point(aes(ts,ch4_flux.c,col='clean'))+
  scale_y_continuous(expression(CH[4]~'flux ('*mu*mol~m^-2~s^-1*')'))+
  scale_color_manual(values = c('black','red'))
```
# Funky Fall Period

Similar to what we see in unburned data set in Dec
```{r}
df$energy <- df$RN_1_1_1 - df$SHF_mean 

ggplot(data = df)+theme_bw()+geom_hline(yintercept = 0)+
  geom_point(aes(ts,energy,col='RN-G'))+
  geom_point(aes(ts,flux,col='H+LE'))+
  scale_y_continuous(limits = c(-110,400))+
  scale_x_datetime(limits = as.POSIXct(c('2022-9-3','2022-12-31'),format="%F"))
```


# Diurnal Fluxes

set hour and month vectors to be able to take the averages

```{r}
df$hour = as.numeric(format(df$ts,'%H'))
df$month = as.numeric(format(df$ts,'%m'))

diel = df %>%
  group_by(hour,month) %>%
  select(co2_flux.c,ch4_flux.c,LE.c,H.c,hour,month) %>%
  summarise_all(.funs = c(median,sd),na.rm=T)

diel = subset(diel,!is.na(diel$month))
```

## NEE

```{r}
ggplot(data = diel)+geom_hline(yintercept = 0)+
  geom_line(aes(hour,co2_flux.c_fn1),lty=2)+
  geom_ribbon(aes(x = hour,y = co2_flux.c_fn1,
                  ymax = co2_flux.c_fn1 + co2_flux.c_fn2,
                  ymin = co2_flux.c_fn1 - co2_flux.c_fn2),
              alpha= 0.5)+
  facet_wrap(~month)
levels(diel$month)
```

## CH4

```{r}
ggplot(data = diel)+geom_hline(yintercept = 0)+
  geom_line(aes(hour,ch4_flux.c_fn1),lty=2)+
  geom_ribbon(aes(x = hour,y = ch4_flux.c_fn1,
                  ymax = ch4_flux.c_fn1 + ch4_flux.c_fn2,
                  ymin = ch4_flux.c_fn1 - ch4_flux.c_fn2),
              alpha= 0.5)+
  facet_wrap(~month)

ggplot(data = diel)+geom_hline(yintercept = 0)+
  geom_line(aes(hour,ch4_flux.c_fn1*43.2),lty=2)+
  geom_ribbon(aes(x = hour,y = ch4_flux.c_fn1*43.2,
                  ymax = ch4_flux.c_fn1*43.2 + ch4_flux.c_fn2*43.2,
                  ymin = ch4_flux.c_fn1*43.2 - ch4_flux.c_fn2*43.2),
              alpha= 0.5)+
  scale_y_continuous(limits = c(-6,6))+
  facet_wrap(~month)
```

## H

```{r}
ggplot(data = diel)+geom_hline(yintercept = 0)+
  geom_line(aes(hour,H.c_fn1),lty=2)+
  geom_ribbon(aes(x = hour,y = H.c_fn1,
                  ymax = H.c_fn1 + H.c_fn2,
                  ymin = H.c_fn1 - H.c_fn2),
              alpha= 0.5)+
  facet_wrap(~month)
```

## LE

```{r}
ggplot(data = diel)+geom_hline(yintercept = 0)+
  geom_line(aes(hour,LE.c_fn1),lty=2)+
  geom_ribbon(aes(x = hour,y = LE.c_fn1,
                  ymax = LE.c_fn1 + LE.c_fn2,
                  ymin = LE.c_fn1 - LE.c_fn2),
              alpha= 0.5)+
  facet_wrap(~month)
```
# Save

```{r}
write.csv(x = df,file = 'C:/Permafrost Pathways/Data/Cleaned/YKDBurned_clean',row.names = F,quote = F)
```

# Monthly Coverage

```{r}
av = df
av$year = format(df$ts,'%Y')
av$month = format(df$ts,'%m')
av$week = format(df$ts,'%W')



plot(av$year)
plot(av$month)
plot(av$week)

av2 = av %>%
  dplyr::group_by(month) %>%
  summarise(co2cov = sum(complete.cases(co2_flux.c)),
            co2raw = sum(complete.cases(co2_flux)),
            ch4cov = sum(complete.cases(ch4_flux.c)),
            ch4raw = sum(complete.cases(ch4_flux)), 
            LEcov = sum(complete.cases(LE.c)),
            LEraw = sum(complete.cases(LE)),
            Hraw = sum(complete.cases(H)),
            Hcov = sum(complete.cases(H.c)),
            co2per = co2cov / n()*100,
            ch4per = ch4cov / n()*100,
            LEper = LEcov / n()*100,
            Hper = Hcov / n()*100,
            co2rawper = co2raw / n()*100,
            ch4rawper = ch4raw / n()*100,
            Hrawper = Hraw / n()*100,
            LErawper = LEraw / n()*100)




```

Subset by percentage clean

```{r}

```

## NEE

```{r}
co2 = ggplot(data = av2)+theme_bw()+ggtitle('CO2 Coverage')+
  geom_bar(aes(month,co2rawper,fill = 'raw'),stat = 'identity', fill = 'red')+
  geom_bar(aes(month,co2per,fill = 'clean'),stat = 'identity', fill = 'black')+
  scale_y_continuous(expand = c(0,0),limits = c(0,105))
co2
```

## CH4

```{r}
ch4 = ggplot(data = av2)+theme_bw()+ggtitle('CH4 Coverage')+
    geom_bar(aes(month,ch4rawper,fill = 'raw'),stat = 'identity', fill = 'red')+
  geom_bar(aes(month,ch4per),stat = 'identity',fill='black')+
  #facet_wrap(~year,nrow = 4)+
  scale_y_continuous(expand = c(0,0),limits = c(0,105))
ch4
```

## H

```{r}
h = ggplot(data = av2)+theme_bw()+ggtitle('H Coverage')+
    geom_bar(aes(month,Hrawper,fill = 'raw'),stat = 'identity', fill = 'red')+
  geom_bar(aes(month,Hper),stat = 'identity',fill='black')+
  #facet_wrap(~year,nrow = 4)+
  scale_y_continuous(expand = c(0,0),limits = c(0,105))
h
```

## LE

```{r}
le = ggplot(data = av2)+theme_bw()+ggtitle('LE Coverage')+
    geom_bar(aes(month,LErawper,fill = 'raw'),stat = 'identity', fill = 'red')+
  geom_bar(aes(month,LEper),stat = 'identity',fill='black')+
  #facet_wrap(~year,nrow = 4)+
  scale_y_continuous(expand = c(0,0),limits = c(0,105))
le
```

# Weekly Coverage

```{r}
av2 =  av %>%
  group_by(week) %>%
  summarise(co2cov = sum(complete.cases(co2_flux.c),na.rm = T),
            co2rawcov = sum(complete.cases(co2_flux),na.rm = T),
            ch4cov = sum(complete.cases(ch4_flux.c),na.rm = T),
            ch4rawcov = sum(complete.cases(ch4_flux),na.rm = T),
            LEcov = sum(complete.cases(LE.c),na.rm = T),
            LErawcov = sum(complete.cases(LE),na.rm = T),
            Hcov = sum(complete.cases(H.c),na.rm = T),
            Hrawcov = sum(complete.cases(H),na.rm = T))
```

## NEE

```{r}
co2cov = ggplot(data = av2)+theme_bw()+ggtitle('CO2 Coverage')+
  geom_bar(aes(week,co2rawcov/336*100),stat = 'identity',fill='red')+
  geom_bar(aes(week,co2cov/336 *100),stat = 'identity',fill='black')+
  #facet_wrap(~year,nrow = 4)+
  scale_y_continuous(expand = c(0,0),limits = c(0,105))
co2cov
```

## CH4

```{r}
ch4 = ggplot(data = av2)+theme_bw()+ggtitle('CH4 Coverage')+
  geom_bar(aes(week,ch4rawcov/336*100),stat = 'identity',fill='red')+
  geom_bar(aes(week,ch4cov/336*100),stat = 'identity',fill='black')+
  #facet_wrap(~year,nrow = 4)+
  scale_y_continuous(expand = c(0,0),limits = c(0,105))
ch4
```

## H

```{r}
h = ggplot(data = av2)+theme_bw()+ggtitle('H Coverage')+
  geom_bar(aes(week,Hrawcov/336*100),stat = 'identity',fill='red')+
  geom_bar(aes(week,Hcov/336*100),stat = 'identity',fill='black')+
  #facet_wrap(~year,nrow = 4)+
  scale_y_continuous(expand = c(0,0),limits = c(0,105))
h
```

## LE

```{r}
le = ggplot(data = av2)+theme_bw()+ggtitle('LE Coverage')+
  geom_bar(aes(week,LErawcov/336*100),stat = 'identity',fill='red')+
  geom_bar(aes(week,LEcov/336*100),stat = 'identity',fill='black')+
  #facet_wrap(~year,nrow = 4)+
  scale_y_continuous(expand = c(0,0),limits = c(0,105))
le
```


