---
title: "Pond Inlet Cleaning"
output:
  pdf_document: default
  html_document: default
    df_print: paged
date: "2024-10-10"
---


# To Do
Make sure all of the timestamps are loaded
Look at roll apply command

# Loading DF's

Clear Console and add packages

# Load 

```{r, warning=FALSE}
rm(list = ls())
Sys.setenv(TZ = "UTC")
knitr::opts_chunk$set(error = TRUE)

library(data.table)
library(ggplot2)
library(cowplot)
library(openair)
library(plotrix)
library(signal)
library(svMisc)
library(zoo)
library(stringr)
library(plyr)
library(dplyr)

# Define file names
file_names = list(
  main_file = "PondMet_AllBiomet.dat",
  file1 = "PondMet_AllBiomet_until2024-09-09-full.dat",
  file2 = "PondMet_AllBiomet_until20230620.dat",
  file3 = "PondMet_AllBiomet_until20240910.dat"
)

# Define columns to exclude
exclude_cols = c(36:38)

# Define NA strings
na_strings <- c("-9999", "NA", "NaN", "NAN", "-7999")

# Define column renaming map
oldtempnames = c("ThermocoupleT_Avg(1)", "ThermocoupleT_Avg(2)", "ThermocoupleT_Avg(3)", "ThermocoupleT_Avg(4)", 
                 "ThermocoupleT_Avg(5)", "ThermocoupleT_Avg(6)", "ThermocoupleT_Avg(7)", "ThermocoupleT_Avg(8)", 
                 "ThermocoupleT_Avg(9)", "SWC_12_36_2_1_1", "SWC_12_36_2_2_1")
newtempnames = c("TS_2_38_2_1_1", "TS_2_38_2_2_1", "TS_2_38_2_3_1", "TS_2_38_2_4_1", "TS_2_38_2_5_1", 
                 "TS_2_38_2_6_1", "TS_2_38_2_7_1", "TS_2_38_2_8_1", "TS_2_38_2_9_1", "SWC_12_36_1_2_1",
                 "SWC_12_36_1_3_1")

# Base path for files
base_path = "C:/Users/klynoe/Documents/pond_inlet/data_downloads/met_202411"  # Update this as needed

# Output path for the merged CSV
output_path = file.path("C:/Users/klynoe/Documents/pond_inlet/R_outputs/pond_inlet_met_merged.csv")

# Threshold timestamp for filtering
timestamp_cutoff <- as.POSIXct("2024-07-26 14:00", format = "%Y-%m-%d %H:%M", tz = "UTC")

#timestamp_cutoff <- as.POSIXct("2024-10-30 14:00", format = "%Y-%m-%d %H:%M", tz = "UTC")

# Function to load and preprocess data
load_data <- function(file_name, exclude_cols = NULL, skip = 4) {
  header <- fread(file.path(base_path, file_name), skip = 1, nrows = 0, na.strings = na_strings)
  data <- fread(file.path(base_path, file_name), skip = skip, header = FALSE, na.strings = na_strings)
  
  setnames(data, names(header))
  return(data)
}

# Load and filter all datasets
df_main <- load_data(file_names$main_file)
dat1 <- load_data(file_names$file1, exclude_cols = exclude_cols)
dat1 <- dat1[as.POSIXct(TIMESTAMP, format = "%Y-%m-%d %H:%M:%S", tz = "UTC") > timestamp_cutoff]

dat2 <- load_data(file_names$file2, exclude_cols = exclude_cols)
dat2 <- dat2[as.POSIXct(TIMESTAMP, format = "%Y-%m-%d %H:%M:%S", tz = "UTC") > timestamp_cutoff]

dat3 <- load_data(file_names$file3, exclude_cols = exclude_cols)
dat3 <- dat3[as.POSIXct(TIMESTAMP, format = "%Y-%m-%d %H:%M:%S", tz = "UTC") > timestamp_cutoff]

# Step 1: Merge all datasets, combining on TIMESTAMP
df_combined <- rbindlist(list(df_main, dat1, dat2, dat3), use.names = TRUE, fill = TRUE)
df_combined <- df_combined[!duplicated(df_combined$TIMESTAMP)] # Remove duplicates

# Step 2: Replace invalid values (-9999, -7999) with NA for consistency
for (col in names(df_combined)) {
  df_combined[[col]] <- fifelse(df_combined[[col]] %in% na_strings, NA, df_combined[[col]])
}


# Step 1: Merge old column data into new columns
for (i in seq_along(oldtempnames)) {
  
  old_col <- oldtempnames[i]
  new_col <- newtempnames[i]
  
  # Check if both columns exist in df_combined
  if (old_col %in% names(df_combined) && new_col %in% names(df_combined)) {
    
    # Merge: Replace NA in new_col with values from old_col if new_col is NA
    df_combined[[new_col]] <- if_else(
      is.na(df_combined[[new_col]]),    # If new_col has NA
      df_combined[[old_col]],           # Replace with values from old_col
      df_combined[[new_col]]            # Otherwise, keep the value in new_col
    )
  } else {
    warning(paste("Column", old_col, "or", new_col, "not found in df_combined"))
    # Print the column names to help debug
    print("Current column names in df_combined:")
    print(names(df_combined))
  }
}

# Step 2: After merging, remove old columns
df_combined[, (oldtempnames) := NULL]
df_combined[, c(2,36:38) := NULL]


# Step 4: Save the cleaned combined data to CSV
#df_combined$TIMESTAMP <- as.character(df_combined$TIMESTAMP)  # Convert TIMESTAMP to character for saving
#fwrite(df_combined, file = output_path, quote = FALSE)
# Convert TIMESTAMP to POSIXct for time series operations
#df_combined$TIMESTAMP <- as.POSIXct(df_combined$TIMESTAMP, format = "%Y-%m-%d %H:%M", tz = "UTC")

# Create a complete sequence of timestamps at 30-minute intervals
tsdf <- data.frame(TIMESTAMP = seq(
  from = min(df_combined$TIMESTAMP),
  to = max(df_combined$TIMESTAMP),
  by = 60*30
))

# Replace specific missing value indicators with NA
df_combined[df_combined == -9999] <- NA
df_combined[df_combined == -7999] <- NA

df = merge(tsdf,df_combined,by = 'TIMESTAMP',all.x = T)
df= df_combined 

summary(df)
```


use for if you want to only look/clean a particular timeperiod

```{r}

#timestamp_cutoff_start <- as.POSIXct("2024-10-30 14:00", format = "%Y-%m-%d %H:%M", tz = "UTC")
#timestamp_cutoff_end <- as.POSIXct("2024-11-01 14:00", format = "%Y-%m-%d %H:%M", tz = "UTC")

#timestamp_cutoff = as.POSIXct("2024-10-30 14:00", format = "%Y-%m-%d %H:%M", tz = "UTC")

#df = df %>%
  #dplyr::filter(TIMESTAMP >= timestamp_cutoff)

```
Creates a variable to input a date range for the plots in the biomet section of
cleaning code. Used to easily change date range for different data sets. 
```{r, warning=FALSE}
biomet_dates <- c('2024-07-25', '2024-12-01')
#biomet_dates <- c('2024-10-30', '2024-12-01')
```


# Air T
```{r, warning=FALSE}
ggplot(data = df)+
  geom_point(aes(TIMESTAMP,TA_2_1_1_1_1),col='black')+
  scale_y_continuous(limits = c(-40,40),
                     expression('Air Temperature ('*Celsius*')'))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates))

#First we need to just convert from Kelvin to degrees C
df$TA_2_1_1_1_1 = ifelse(df$TA_2_1_1_1_1 > 200,df$TA_2_1_1_1_1 - 273.15,df$TA_2_1_1_1_1)

ggplot(data = df)+
  geom_point(aes(TIMESTAMP,TA_2_1_1_1_1),col='black')+
  scale_y_continuous(limits = c(-40,40),
                      expression('Air Temperature ('*Celsius*')'))
```


## Limits
```{r, warning=FALSE}
hist(df$TA_2_1_1_1_1,breaks=100)
plot(df$TIMESTAMP,df$TA_2_1_1_1_1,ylim = c(-50,50));abline(h=-50, col= 'red');abline(h=50, col='red')
TA_2_1_1_1_1.limits = replace(df$TA_2_1_1_1_1, df$TA_2_1_1_1_1 < -50 | df$TA_2_1_1_1_1 > 50,NA)
hist(TA_2_1_1_1_1.limits,breaks=100)
plot(TA_2_1_1_1_1.limits)
```


#Relative Humidity

```{r,warning=FALSE}
ggplot(data = df)+
  geom_point(aes(TIMESTAMP,RH_19_3_1_1_1),col='black')+
  scale_y_continuous(#limits = c(20,100),
                     expression('Relative Humidity ('*percent*')'))
 scale_x_datetime(limits = as.POSIXct(biomet_dates))
```


## Limits
```{r,warning=FALSE}
RH_19_3_1_1_1.limits = df$RH_19_3_1_1_1

RH_19_3_1_1_1.limits = ifelse(df$RH_19_3_1_1_1 > 0 & df$TIMESTAMP <= '2022-9-23',NA, RH_19_3_1_1_1.limits)

df$RH_19_3_1_1_1.c = RH_19_3_1_1_1.limits

ggplot(data = df)+
  geom_point(aes(TIMESTAMP,RH_19_3_1_1_1.c),col='black')+
  scale_y_continuous(limits = c(5,100),
                     expression('Relative Humidity ('*percent*')'))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates))
```

# Barometric Pressure 

```{r,warning=FALSE}
ggplot(data = df)+
  geom_point(aes(TIMESTAMP,PA_4_2_1_1_1),col='black')+
  scale_y_continuous(#limits = c(90000,110000),
                     expression ('Barometric Pressure ('*kPa*')'))
#  scale_x_datetime(limits = as.POSIXct(biomet_dates))

df$PA_4_2_1_1_1 = ifelse(df$PA_4_2_1_1_1 > 97000,df$PA_4_2_1_1_1/1000,df$PA_4_2_1_1_1)

ggplot(data = df)+
  geom_point(aes(TIMESTAMP,PA_4_2_1_1_1),col='black')+
  scale_y_continuous(limits = c(0,200),
                     expression ('Barometric Pressure ('*kPa*')'))


df$PA_4_2_1_1_1 = ifelse(df$PA_4_2_1_1_1 > 150,df$PA_4_2_1_1_1/10,df$PA_4_2_1_1_1)

ggplot(data = df)+
  geom_point(aes(TIMESTAMP,PA_4_2_1_1_1),col='black')+
  scale_y_continuous(limits = c(0,140),
                     expression ('Barometric Pressure ('*kPa*')'))
```


```{r, warning=FALSE}
hist(df$PA_4_2_1_1_1,breaks=100)

ggplot(data = df)+
  geom_point(aes(TIMESTAMP,PA_4_2_1_1_1),col='black')+
  scale_y_continuous(limits = c(90,110),
                     expression ('Barometric Pressure ('*kPa*')'))

PA_4_2_1_1_1.limits = ifelse(df$PA_4_2_1_1_1 > 110 | df$PA_4_2_1_1_1 < 97,NA, df$PA_4_2_1_1_1)

ggplot(data = df)+
  geom_point(aes(TIMESTAMP,PA_4_2_1_1_1.limits),col='black')+
  geom_hline(yintercept = 106,col = 'red')+
  geom_hline(yintercept = 97,col = 'red')+
  scale_y_continuous(limits = c(90,110),
                     expression ('Barometric Pressure ('*kPa*')'))
```
## Rolling MAD
```{r, warning=FALSE}
f = PA_4_2_1_1_1.limits # first make a new flux vector to apply the above filters
# prepare the inputs for a zero-phase (forward and reverse) filter  
ind       = which(complete.cases(f))   # first save the index of all the NAs
b         = rep(1,8)/8                 # moving average coefficient
a         = 1                          # coefficient of the ARMA filter
mad_i    = filtfilt(b, a, na.omit(f)) #create a forward and reverse ARMA filter
mad_filt = f                          # make a copy of the full fluxes again
mad_filt[ind] = mad_i                # apply the filter where the real data exist

n = 7*48 # set the length of the rolling filter, 48 half hours in day * x days
roll.mad = rollapply(data = mad_filt,
                     width = n,
                     FUN = mad,
                     partial = TRUE,
                     na.rm = T,
                     fill = NA)  #create a rolling MAD or sd or other
roll.mad[is.na(mad_filt)] = NA  #make NA values where NAs exist in the real data


ggplot(df)+geom_hline(yintercept = 0)+
  geom_point(aes(TIMESTAMP,PA_4_2_1_1_1.limits,col='Pressure'))+
  geom_line(aes(TIMESTAMP,mad_filt,col='Filter'))+
  geom_line(aes(TIMESTAMP,roll.mad,col='MAD'))+
  scale_y_continuous(limits = c(0,110))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates,format="%F"))+
  scale_color_manual(values=c('yellow','red','black'))
```

```{r, warning=FALSE}
#adjust this value (N) to tweak how many MADs to be away from the norm
N = 3 

#Add clean value to dataframe (_.c)

df$PA_4_2_1_1_1.c = ifelse(abs(PA_4_2_1_1_1.limits - mad_filt) > (N * roll.mad),NA,PA_4_2_1_1_1.limits)

#Compare cleaned vs. uncleaned

ggplot(df)+geom_hline(yintercept = 0)+
  geom_point(aes(TIMESTAMP,PA_4_2_1_1_1,col='Uncleaned'))+
  geom_point(aes(TIMESTAMP,PA_4_2_1_1_1.c,col='Cleaned'))+
  scale_y_continuous(limits = c(90,110))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates,format="%F"))+
  scale_color_manual(values=c('black','red'))
```

```{r, warning=FALSE}
ggplot(data = df)+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*6,ymin = mad_filt-roll.mad*6,fill='6'))+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*3,ymin = mad_filt-roll.mad*3,fill='3'))+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*2,ymin = mad_filt-roll.mad*2,fill='2'))+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*1,ymin = mad_filt-roll.mad*1,fill='1'))+
  geom_point(aes(TIMESTAMP,PA_4_2_1_1_1.limits),col='red')+
  geom_point(aes(TIMESTAMP,PA_4_2_1_1_1.c),col='black')+
  scale_y_continuous(limits = c(80,115))+
scale_x_datetime(limits = as.POSIXct(biomet_dates,format="%F"))
```


#Soil Heat Flux
```{r, warning=FALSE}
ggplot(data = df)+
  geom_point(aes(TIMESTAMP,SHF_6_37_1_1_1,col='SHF 1'))+
  geom_point(aes(TIMESTAMP,SHF_6_37_2_1_1,col='SHF 2'))+
  scale_y_continuous(limits = c(-80,190),
                     expression ('Soil Heat Flux ('*W/m^2*')'))+
  scale_color_manual(values = c('red','black'))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates))
```

## SHF1
```{r, warning=FALSE}
hist(df$SHF_6_37_1_1_1,breaks=100)
plot(df$TIMESTAMP,df$SHF_6_37_1_1_1,ylim = c(-50,200));abline(h=-55, col= 'red');abline(h=190, col='red')
SHF_6_37_1_1_1.limits = replace(df$SHF_6_37_1_1_1, df$SHF_6_37_1_1_1 < -55 | df$SHF_6_37_1_1_1 > 190,NA)
hist(SHF_6_37_1_1_1.limits,breaks=100)
plot(SHF_6_37_1_1_1.limits)
df$SHF_6_37_1_1_1.c = SHF_6_37_1_1_1.limits
```

## SHF2
```{r, warning=FALSE}
hist(df$SHF_6_37_2_1_1,breaks=100)
plot(df$TIMESTAMP,df$SHF_6_37_2_1_1,ylim = c(-80,165));abline(h=-75, col= 'red');abline(h=150, col='red')
SHF_6_37_2_1_1.limits = replace(df$SHF_6_37_2_1_1, df$SHF_6_37_2_1_1 < -75 | df$SHF_6_37_2_1_1 > 150,NA)
hist(SHF_6_37_2_1_1.limits,breaks=100)
plot(SHF_6_37_2_1_1.limits)
df$SHF_6_37_2_1_1.c = SHF_6_37_2_1_1.limits
```

# Snow Depth
```{r, warning=FALSE}
ggplot(data = df)+
  geom_point(aes(TIMESTAMP,SD_10_99_1_1_1),col='black')+
  scale_y_continuous(limits = c(0,.75),
                     expression('Snow Depth ('*m*')'))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates))
```


```{r, warning=FALSE}
hist(df$SD_10_99_1_1_1,breaks=100)
plot(df$TIMESTAMP,df$SD_10_99_1_1_1,ylim = c(-1.5,1));abline(h=0, col= 'red');abline(h=.8, col='red')
SD_10_99_1_1_1.limits=df$SD_10_99_1_1_1

ggplot(data = df)+
  geom_point(aes(TIMESTAMP,SD_10_99_1_1_1.limits),col='black')+
  scale_y_continuous(limits = c(-.25,.75),
                     expression('Snow Depth ('*m*')'))+
  geom_hline(yintercept = .60)+
  scale_x_datetime(limits = as.POSIXct(biomet_dates))

SD_10_99_1_1_1.limits = ifelse(df$SD_10_99_1_1_1 > .60, NA , SD_10_99_1_1_1.limits)

df$SD_10_99_1_1_1.c = SD_10_99_1_1_1.limits 


```

## Rolling MAD
```{r, warning=FALSE}
f = SD_10_99_1_1_1.limits # first make a new flux vector to apply the above filters
# prepare the inputs for a zero-phase (forward and reverse) filter  
ind       = which(complete.cases(f))   # first save the index of all the NAs
b         = rep(1,8)/8                 # moving average coefficient
a         = 1                          # coefficient of the ARMA filter
mad_i    = filtfilt(b, a, na.omit(f)) #create a forward and reverse ARMA filter
mad_filt = f                          # make a copy of the full fluxes again
mad_filt[ind] = mad_i                # apply the filter where the real data exist

n = 7*48 # set the length of the rolling filter, 48 half hours in day * x days
roll.mad = rollapply(data = mad_filt,
                     width = n,
                     FUN = mad,
                     partial = TRUE,
                     na.rm = T,
                     fill = NA)  #create a rolling MAD or sd or other
roll.mad[is.na(mad_filt)] = NA  #make NA values where NAs exist in the real data

```

```{r, warning=FALSE}

ggplot(df)+geom_hline(yintercept = 0)+
  geom_point(aes(TIMESTAMP,SD_10_99_1_1_1.limits,col='Snow Depth'))+
  geom_line(aes(TIMESTAMP,mad_filt,col='Filter'))+
  geom_line(aes(TIMESTAMP,roll.mad,col='MAD'))+
  scale_y_continuous(limits = c(-.1,.8))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates,format="%F"))+
  scale_color_manual(values=c('yellow','red','black'))

```

```{r, warning=FALSE}
#adjust this value (N) to tweak how many MADs to be away from the norm
N = 2

#Add clean value to dataframe (_.c)

df$SD_10_99_1_1_1.c = ifelse(abs(SD_10_99_1_1_1.limits - mad_filt) > (N * roll.mad),NA,SD_10_99_1_1_1.limits)

#Compare cleaned vs. uncleaned

ggplot(df)+geom_hline(yintercept = 0)+
  geom_point(aes(TIMESTAMP,SD_10_99_1_1_1,col='Uncleaned'))+
  geom_point(aes(TIMESTAMP,SD_10_99_1_1_1.c,col='Cleaned'))+
  scale_y_continuous(limits = c(-0.75,1))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates,format="%F"))+
  scale_color_manual(values=c('black','red'))
```


```{r, warning=FALSE}
ggplot(data = df)+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*6,ymin = mad_filt-roll.mad*6,fill='6'))+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*3,ymin = mad_filt-roll.mad*3,fill='3'))+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*2,ymin = mad_filt-roll.mad*2,fill='2'))+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*1,ymin = mad_filt-roll.mad*1,fill='1'))+
  geom_point(aes(TIMESTAMP,SD_10_99_1_1_1.limits),col='red')+
  geom_point(aes(TIMESTAMP,SD_10_99_1_1_1.c),col='black')+
  scale_y_continuous(limits = c(-.25,1))
#scale_x_datetime(limits = as.POSIXct(c('2024-09-26','2024-12-02'),format="%F"))

```


# PAR
```{r, warning=FALSE}
ggplot(data = df)+
  geom_point(aes(TIMESTAMP,PPFD_7_21_1_1_1),col='black')+
  scale_y_continuous(limits = c(-25,2000),
                     expression('PAR ('*mu*mol/m^2/s*')'))
```

```{r, warning=FALSE}
summary(df$PPFD_7_21_1_1_1)
hist(df$PPFD_7_21_1_1_1,breaks=100)
plot(df$TIMESTAMP,df$PPFD_7_21_1_1_1,ylim = c(0,1850));abline(h=1750, col= 'red');abline(h=0, col='red')
PPFD_7_21_1_1_1.limits = replace(df$PPFD_7_21_1_1_1, df$PPFD_7_21_1_1_1 < 0 | df$PPFD_7_21_1_1_1 > 1750,NA)
hist(PPFD_7_21_1_1_1.limits,breaks=100)
plot(PPFD_7_21_1_1_1.limits)
```


### Rolling SD 
(Changed to SD because MAD was cutting good data)
```{r, warning=FALSE}
f = PPFD_7_21_1_1_1.limits # first make a new flux vector to apply the above filters
# prepare the inputs for a zero-phase (forward and reverse) filter  
ind       = which(complete.cases(f))   # first save the index of all the NAs
b         = rep(1,8)/8                 # moving average coefficient
a         = 1                          # coefficient of the ARMA filter
mad_i    = filtfilt(b, a, na.omit(f)) #create a forward and reverse ARMA filter
mad_filt = f                          # make a copy of the full fluxes again
mad_filt[ind] = mad_i                # apply the filter where the real data exist

n = 14*48 # set the length of the rolling filter, 48 half hours in day * x days
roll.mad = rollapply(data = mad_filt,
                     width = n,
                     FUN = sd,
                     partial = TRUE,
                     na.rm = T,
                     fill = NA)  #create a rolling MAD or sd or other
roll.mad[is.na(mad_filt)] = NA  #make NA values where NAs exist in the real data

ggplot(df)+geom_hline(yintercept = 0)+
  geom_point(aes(TIMESTAMP,PPFD_7_21_1_1_1.limits,col='PAR in'))+
  geom_line(aes(TIMESTAMP,mad_filt,col='Filter'))+
  geom_line(aes(TIMESTAMP,roll.mad,col='MAD'))+
  scale_y_continuous(limits = c(-15,1800))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates,format="%F"))+
  scale_color_manual(values=c('yellow','red','black'))

```

```{r, warning=FALSE}
#adjust this value (N) to tweak how many MADs to be away from the norm
N = 6

#Add clean value to dataframe (_.c)

df$PPFD_7_21_1_1_1.c = ifelse(abs(PPFD_7_21_1_1_1.limits - mad_filt) > (N * roll.mad),NA,PPFD_7_21_1_1_1.limits)

#Compare cleaned vs. uncleaned

ggplot(df)+geom_hline(yintercept = 0)+
  geom_point(aes(TIMESTAMP,PPFD_7_21_1_1_1.limits,col='Uncleaned'))+
  geom_point(aes(TIMESTAMP,PPFD_7_21_1_1_1.c,col='Cleaned'))+
  scale_y_continuous(limits = c(0,2000))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates,format="%F"))+
  scale_color_manual(values=c('black','red'))
```

```{r, warning=FALSE}
ggplot(data = df)+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*6,ymin = mad_filt-roll.mad*6,fill='6'))+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*3,ymin = mad_filt-roll.mad*3,fill='3'))+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*2,ymin = mad_filt-roll.mad*2,fill='2'))+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*1,ymin = mad_filt-roll.mad*1,fill='1'))+
  geom_point(aes(TIMESTAMP,PPFD_7_21_1_1_1.limits),col='red')+
  geom_point(aes(TIMESTAMP,PPFD_7_21_1_1_1.c),col='black')+
  scale_y_continuous(limits = c(-500,1300))
```


# PAR Reflected
```{r, warning=FALSE}
ggplot(data = df)+
  geom_point(aes(TIMESTAMP,PPFDR_7_23_1_1_1),col='black')+
  scale_y_continuous(limits = c(-25,400),
                     expression('PAR Reflected ('*mu*mol/m^2/s*')'))
```

```{r, warning=FALSE}
summary(df$PPFDR_7_23_1_1_1)
hist(df$PPFDR_7_23_1_1_1,breaks=100)
plot(df$TIMESTAMP,df$PPFDR_7_23_1_1_1,ylim = c(0,5850));abline(h=1400, col= 'red');abline(h=-1, col='red')
PPFDR_7_23_1_1_1.limits=df$PPFDR_7_23_1_1_1
PPFDR_7_23_1_1_1.limits = ifelse(df$PPFDR_7_23_1_1_1 < -1 | df$PPFDR_7_23_1_1_1 > 600 & df$TIMESTAMP <= '2024-10-31',NA,df$PPFDR_7_23_1_1_1)
hist(PPFDR_7_23_1_1_1.limits,breaks=100)
plot(PPFDR_7_23_1_1_1.limits)
```


### Rolling SD
(Changed to SD because MAD was cutting good data)
```{r, warning=FALSE}
f = PPFDR_7_23_1_1_1.limits # first make a new flux vector to apply the above filters
# prepare the inputs for a zero-phase (forward and reverse) filter  
ind       = which(complete.cases(f))   # first save the index of all the NAs
b         = rep(1,8)/8                 # moving average coefficient
a         = 1                          # coefficient of the ARMA filter
mad_i    = filtfilt(b, a, na.omit(f)) #create a forward and reverse ARMA filter
mad_filt = f                          # make a copy of the full fluxes again
mad_filt[ind] = mad_i                # apply the filter where the real data exist

n = 7*48 # set the length of the rolling filter, 48 half hours in day * x days
roll.mad = rollapply(data = mad_filt,
                     width = n,
                     FUN = sd,
                     partial = TRUE,
                     na.rm = T,
                     fill = NA)  #create a rolling MAD or sd or other
roll.mad[is.na(mad_filt)] = NA  #make NA values where NAs exist in the real data

ggplot(df)+geom_hline(yintercept = 0)+
  geom_point(aes(TIMESTAMP,PPFDR_7_23_1_1_1.limits,col='PAR in'))+
  geom_line(aes(TIMESTAMP,mad_filt,col='Filter'))+
  geom_line(aes(TIMESTAMP,roll.mad,col='MAD'))+
  scale_y_continuous(limits = c(-5,150))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates,format="%F"))+
  scale_color_manual(values=c('yellow','red','black'))

```

```{r, warning=FALSE}
#adjust this value (N) to tweak how many MADs to be away from the norm
N = 5

#Add clean value to dataframe (_.c)

df$PPFDR_7_23_1_1_1.c = ifelse(abs(PPFDR_7_23_1_1_1.limits - mad_filt) > (N * roll.mad),NA,PPFDR_7_23_1_1_1.limits)

#Compare cleaned vs. uncleaned

ggplot(df)+geom_hline(yintercept = 0)+
  geom_point(aes(TIMESTAMP,PPFDR_7_23_1_1_1,col='Uncleaned'))+
  geom_point(aes(TIMESTAMP,PPFDR_7_23_1_1_1.c,col='Cleaned'))+
  scale_y_continuous(limits = c(0,200))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates,format="%F"))+
  scale_color_manual(values=c('black','red'))
```

```{r, warning=FALSE}
ggplot(data = df)+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*6,ymin = mad_filt-roll.mad*6,fill='6'))+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*4,ymin = mad_filt-roll.mad*4,fill='4'))+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*3,ymin = mad_filt-roll.mad*3,fill='3'))+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*1,ymin = mad_filt-roll.mad*1,fill='1'))+
  geom_point(aes(TIMESTAMP,PPFDR_7_23_1_1_1.limits),col='red')+
  geom_point(aes(TIMESTAMP,PPFDR_7_23_1_1_1.c),col='black')+
  scale_y_continuous(limits = c(-500,700))
```

# Net Radiation 
```{r, warning=FALSE}
ggplot(data = df)+
  geom_point(aes(TIMESTAMP, RN_6_5_1_1_1),col='black')+
  scale_y_continuous(limits = c(-125,550),
                     expression('Net Radiation ('*W/m^2*')'))
```

```{r, warning=FALSE}
hist(df$RN_6_5_1_1_1,breaks=100)
plot(df$TIMESTAMP,df$RN_6_5_1_1_1,ylim = c(-400,850));abline(h=835,col= 'red');abline(h=-300, col='red')
RN_6_5_1_1_1.limits = replace(df$RN_6_5_1_1_1, df$RN_6_5_1_1_1 < -300 | df$RN_6_5_1_1_1 > 835,NA)
hist(RN_6_5_1_1_1.limits,breaks=100)
plot(df$TIMESTAMP,RN_6_5_1_1_1.limits)
```
## Rolling SD
```{r, warning=FALSE}
f = RN_6_5_1_1_1.limits # first make a new flux vector to apply the above filters
# prepare the inputs for a zero-phase (forward and reverse) filter  
ind       = which(complete.cases(f))   # first save the index of all the NAs
b         = rep(1,8)/8                 # moving average coefficient
a         = 1                          # coefficient of the ARMA filter
mad_i    = filtfilt(b, a, na.omit(f)) #create a forward and reverse ARMA filter
mad_filt = f                          # make a copy of the full fluxes again
mad_filt[ind] = mad_i                # apply the filter where the real data exist

n = 7*48 # set the length of the rolling filter, 48 half hours in day * x days
roll.mad = rollapply(data = mad_filt,
                     width = n,
                     FUN = sd,
                     partial = TRUE,
                     na.rm = T,
                     fill = NA)  #create a rolling MAD or sd or other
roll.mad[is.na(mad_filt)] = NA  #make NA values where NAs exist in the real data

ggplot(df)+geom_hline(yintercept = 0)+
  geom_point(aes(TIMESTAMP,PPFDR_7_23_1_1_1.limits,col='Net Rad'))+
  geom_line(aes(TIMESTAMP,mad_filt,col='Filter'))+
  geom_line(aes(TIMESTAMP,roll.mad,col='MAD'))+
  scale_y_continuous(limits = c(-5,150))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates,format="%F"))+
  scale_color_manual(values=c('yellow','red','black'))


```


```{r, warning=FALSE}

#adjust this value (N) to tweak how many MADs to be away from the norm
N = 4 

#Add clean value to dataframe (_.c)

df$RN_6_5_1_1_1.c = ifelse(abs(RN_6_5_1_1_1.limits - mad_filt) > (N * roll.mad),NA,RN_6_5_1_1_1.limits)

#Compare cleaned vs. uncleaned

ggplot(df)+geom_hline(yintercept = 0)+
  geom_point(aes(TIMESTAMP,RN_6_5_1_1_1.limits,col='Uncleaned'))+
  geom_point(aes(TIMESTAMP,RN_6_5_1_1_1.c,col='Cleaned'))+
  scale_y_continuous(limits = c(-250,600))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates,format="%F"))+
  scale_color_manual(values=c('black','red'))
```

```{r, warning=FALSE}
ggplot(data = df)+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*6,ymin = mad_filt-roll.mad*6,fill='6'))+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*3,ymin = mad_filt-roll.mad*3,fill='3'))+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*2,ymin = mad_filt-roll.mad*2,fill='2'))+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*1,ymin = mad_filt-roll.mad*1,fill='1'))+
  geom_point(aes(TIMESTAMP,RN_6_5_1_1_1.limits),col='red')+
  geom_point(aes(TIMESTAMP,RN_6_5_1_1_1.c),col='black')+
  scale_y_continuous(limits = c(-500,600))

```

# Shortwave in 
```{r, warning=FALSE}
ggplot(data = df)+
  geom_point(aes(TIMESTAMP,SWIN_6_10_1_1_1))+
  scale_y_continuous(#limits = c(-10,1000),
                     expression('Shortwave In ('*W/m^2*')'))
```

```{r, warning=FALSE}
hist(df$SWIN_6_10_1_1_1,breaks=100)
plot(df$TIMESTAMP,df$SWIN_6_10_1_1_1,ylim = c(0,1000));abline(h=900,col= 'red');abline(h=-1, col='red')
SWIN_6_10_1_1_1.limits <- df$SWIN_6_10_1_1_1
SWIN_6_10_1_1_1.limits[df$SWIN_6_10_1_1_1 < 0] <- 0
hist(SWIN_6_10_1_1_1.limits,breaks=100)
plot(df$TIMESTAMP,SWIN_6_10_1_1_1.limits)
```

## Rolling SD 
```{r, warning=FALSE}
f = SWIN_6_10_1_1_1.limits # first make a new flux vector to apply the above filters
# prepare the inputs for a zero-phase (forward and reverse) filter  
ind       = which(complete.cases(f))   # first save the index of all the NAs
b         = rep(1,8)/8                 # moving average coefficient
a         = 1                          # coefficient of the ARMA filter
mad_i    = filtfilt(b, a, na.omit(f)) #create a forward and reverse ARMA filter
mad_filt = f                          # make a copy of the full fluxes again
mad_filt[ind] = mad_i                # apply the filter where the real data exist

n = 7*48 # set the length of the rolling filter, 48 half hours in day * x days
roll.mad = rollapply(data = mad_filt,
                     width = n,
                     FUN = sd,
                     partial = TRUE,
                     na.rm = T,
                     fill = NA)  #create a rolling MAD or sd or other
roll.mad[is.na(mad_filt)] = NA  #make NA values where NAs exist in the real data


ggplot(df)+geom_hline(yintercept = 0)+
  geom_point(aes(TIMESTAMP,SWIN_6_10_1_1_1.limits,col='Shortwave in'))+
  geom_line(aes(TIMESTAMP,mad_filt,col='Filter'))+
  geom_line(aes(TIMESTAMP,roll.mad,col='MAD'))+
  scale_y_continuous(limits = c(-5,800))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates,format="%F"))+
  scale_color_manual(values=c('yellow','red','black'))

```

```{r, warning=FALSE}
#adjust this value (N) to tweak how many MADs to be away from the norm
N = 4

#Add clean value to dataframe (_.c)

df$SWIN_6_10_1_1_1.c = ifelse(abs(SWIN_6_10_1_1_1.limits - mad_filt) > (N * roll.mad),NA,SWIN_6_10_1_1_1.limits)

#Compare cleaned vs. uncleaned

plot(df$TIMESTAMP,df$SWIN_6_10_1_1_1,col='red',ylim = c(-1,925));points(df$TIMESTAMP,df$SWIN_6_10_1_1_1.c)
```

```{r, warning=FALSE} 
ggplot(data = df)+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*6,ymin = mad_filt-roll.mad*6,fill='6'))+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*3,ymin = mad_filt-roll.mad*3,fill='3'))+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*2,ymin = mad_filt-roll.mad*2,fill='2'))+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*1,ymin = mad_filt-roll.mad*1,fill='1'))+
  geom_point(aes(TIMESTAMP,SWIN_6_10_1_1_1.limits),col='red')+
  geom_point(aes(TIMESTAMP,SWIN_6_10_1_1_1.c),col='black')+
  scale_y_continuous(limits = c(-300,700))
```


# Shortwave out 
```{r, warning=FALSE}
ggplot(data = df)+
  geom_point(aes(TIMESTAMP,SWOUT_6_11_1_1_1))+
  scale_y_continuous(limits = c(-10,150),
                     expression('Shortwave Out ('*W/m^2*')'))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates))
```

```{r, warning=FALSE}
hist(df$SWOUT_6_11_1_1_1,breaks=100)
plot(df$TIMESTAMP,df$SWOUT_6_11_1_1_1,ylim = c(0,800));abline(h=700,col= 'red');abline(h=-1, col='red')
SWOUT_6_11_1_1_1.limits <- df$SWOUT_6_11_1_1_1
SWOUT_6_11_1_1_1.limits[df$SWOUT_6_11_1_1_1 < 0] <- 0
hist(SWOUT_6_11_1_1_1.limits,breaks=100)
plot(df$TIMESTAMP,SWOUT_6_11_1_1_1.limits)
```


### Rolling MAD

```{r, warning=FALSE}
f = SWOUT_6_11_1_1_1.limits # first make a new flux vector to apply the above filters
# prepare the inputs for a zero-phase (forward and reverse) filter  
ind       = which(complete.cases(f))   # first save the index of all the NAs
b         = rep(1,8)/8                 # moving average coefficient
a         = 1                          # coefficient of the ARMA filter
mad_i    = filtfilt(b, a, na.omit(f)) #create a forward and reverse ARMA filter
mad_filt = f                          # make a copy of the full fluxes again
mad_filt[ind] = mad_i                # apply the filter where the real data exist

n = 7*48 # set the length of the rolling filter, 48 half hours in day * x days
roll.mad = rollapply(data = mad_filt,
                     width = n,
                     FUN = sd,
                     partial = TRUE,
                     na.rm = T,
                     fill = NA)  #create a rolling MAD or sd or other
roll.mad[is.na(mad_filt)] = NA  #make NA values where NAs exist in the real data

ggplot(df)+geom_hline(yintercept = 0)+
  geom_point(aes(TIMESTAMP,SWOUT_6_11_1_1_1.limits,col='Shortwave out'))+
  geom_line(aes(TIMESTAMP,mad_filt,col='Filter'))+
  geom_line(aes(TIMESTAMP,roll.mad,col='MAD'))+
  scale_y_continuous(limits = c(-5,100))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates,format="%F"))+
  scale_color_manual(values=c('yellow','red','black'))


```

```{r, warning=FALSE}
#adjust this value (N) to tweak how many MADs to be away from the norm
N = 5

#Add clean value to dataframe (_.c)

df$SWOUT_6_11_1_1_1.c = ifelse(abs(SWOUT_6_11_1_1_1.limits - mad_filt) > (N * roll.mad),NA,SWOUT_6_11_1_1_1.limits)

#Compare cleaned vs. uncleaned

plot(df$TIMESTAMP,df$SWOUT_6_11_1_1_1,col='red',ylim = c(0,110));points(df$TIMESTAMP,df$SWOUT_6_11_1_1_1.c)
```

```{r, warning=FALSE}
ggplot(data = df)+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*6,ymin = mad_filt-roll.mad*6,fill='6'))+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*4,ymin = mad_filt-roll.mad*4,fill='4'))+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*3,ymin = mad_filt-roll.mad*3,fill='3'))+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*1,ymin = mad_filt-roll.mad*1,fill='1'))+
  geom_point(aes(TIMESTAMP,SWOUT_6_11_1_1_1.limits),col='red')+
  geom_point(aes(TIMESTAMP,SWOUT_6_11_1_1_1.c),col='black')+
  scale_y_continuous(limits = c(-200,300))
```


# Albedo 
```{r, warning=FALSE}
albedo = df$SWOUT_6_11_1_1_1.c / df$SWIN_6_10_1_1_1.c

ggplot(data = df)+
  geom_point(aes(TIMESTAMP,albedo))+
  scale_y_continuous(limits = c(-1,2),
                     expression('Albedo'))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates))

albedo.limits = replace(albedo, albedo < .05 | albedo > 1,NA)


ggplot(data = df)+
  geom_point(aes(TIMESTAMP,albedo.limits))+
  scale_y_continuous(limits = c(-.5,1.5),
                     expression('Albedo'))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates))


```

```{r, warning=FALSE}
f = albedo.limits # first make a new flux vector to apply the above filters
# prepare the inputs for a zero-phase (forward and reverse) filter  
ind       = which(complete.cases(f))   # first save the index of all the NAs
b         = rep(1,8)/8                 # moving average coefficient
a         = 1                          # coefficient of the ARMA filter
mad_i    = filtfilt(b, a, na.omit(f)) #create a forward and reverse ARMA filter
mad_filt = f                          # make a copy of the full fluxes again
mad_filt[ind] = mad_i                # apply the filter where the real data exist

n = 7*48 # set the length of the rolling filter, 48 half hours in day * x days
roll.mad = rollapply(data = mad_filt,
                     width = n,
                     FUN = mad,
                     partial = TRUE,
                     na.rm = T,
                     fill = NA)  #create a rolling MAD or sd or other
roll.mad[is.na(mad_filt)] = NA  #make NA values where NAs exist in the real data

ggplot(df)+geom_hline(yintercept = 0)+
  geom_point(aes(TIMESTAMP,albedo.limits,col='Albedo'))+
  geom_line(aes(TIMESTAMP,mad_filt,col='Filter'))+
  geom_line(aes(TIMESTAMP,roll.mad,col='MAD'))+
  scale_y_continuous(limits = c(0,1))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates,format="%F"))+
  scale_color_manual(values=c('black','yellow','red'))
```


```{r, warning=FALSE}
#adjust this value (N) to tweak how many MADs to be away from the norm
N = 5

#Add clean value to dataframe (_.c)

df$ALB_1_1_1.c = ifelse(abs(albedo.limits - mad_filt) > (N * roll.mad),NA,albedo.limits)

#Compare cleaned vs. uncleaned


ggplot(df)+geom_hline(yintercept = 0)+
  geom_point(aes(TIMESTAMP,albedo.limits,col='Uncleaned'))+
  geom_point(aes(TIMESTAMP,df$ALB_1_1_1.c,col='Cleaned'))+
  scale_y_continuous(limits = c(0,1))+
  scale_color_manual(values=c('black','red'))   #scale_x_datetime(limits=as.POSIXct(c('2024-07-25','2024-12-01'),format="%F"))+
 


```

# Longwave In 
```{r, warning=FALSE}
ggplot(data = df)+
  geom_point(aes(TIMESTAMP,LWIN_6_14_1_1_1))+
  scale_y_continuous(limits = c(50,500),
                     expression('Longwave In ('*W/m^2*')'))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates))

```

```{r, warning=FALSE}
hist(df$LWIN_6_14_1_1_1,breaks=100)
plot(df$TIMESTAMP,df$LWIN_6_14_1_1_1,ylim = c(80,750));abline(h=450, col= 'red');abline(h=90, col='red')
LWIN_6_14_1_1_1.limits = replace(df$LWIN_6_14_1_1_1, df$LWIN_6_14_1_1_1 < 80 | df$LWIN_6_14_1_1_1 > 450,NA)
hist(LWIN_6_14_1_1_1.limits,breaks=100)

ggplot(data = df)+
  geom_point(aes(TIMESTAMP,LWIN_6_14_1_1_1.limits))+
  scale_y_continuous(limits = c(50,550),
                     expression('Longwave In ('*W/m^2*')'))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates))

df$LWIN_6_14_1_1_1.c = LWIN_6_14_1_1_1.limits
```


# Longwave out 
```{r, warning=FALSE}
ggplot(data = df)+
  geom_point(aes(TIMESTAMP,LWOUT_6_15_1_1_1))+
  scale_y_continuous(limits = c(100,500),
                     expression('Longwave Out ('*W/m^2*')'))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates))
```

```{r, warning=FALSE}
hist(df$LWOUT_6_15_1_1_1,breaks=100)
plot(df$TIMESTAMP,df$LWOUT_6_15_1_1_1,ylim = c(80,750));abline(h=550, col= 'red');abline(h=85, col='red')
LWOUT_6_15_1_1_1.limits = replace(df$LWOUT_6_15_1_1_1, df$LWOUT_6_15_1_1_1 < 85 | df$LWOUT_6_15_1_1_1 > 550,NA)
hist(LWOUT_6_15_1_1_1.limits,breaks=100)
plot(LWOUT_6_15_1_1_1.limits)
df$LWOUT_6_15_1_1_1.c = LWOUT_6_15_1_1_1.limits
```


# Convert Soil Temps in Kelvin to Celcius
```{r, warning=FALSE}

ts_columns <- names(df)[grepl("TS", names(df))]

for (col in ts_columns) {
  df[[col]] <- ifelse(df[[col]] > 150, df[[col]] - 273.15, df[[col]])
}

```

# 10-30 cm Therm

```{r, warning=FALSE}
ggplot(data = df)+ theme_bw()+ geom_hline(yintercept = 0)+
  geom_line(aes(TIMESTAMP, TS_2_38_1_1_1, col = '10 cm'))+
    geom_line(aes(TIMESTAMP, TS_2_38_1_2_1, col = '20 cm'))+
  geom_line(aes(TIMESTAMP, TS_2_38_1_3_1, col = '30 cm'))+
  geom_hline(yintercept = 0)+
  scale_y_continuous(limits = c(-5,10),
                     expression('Soil T ('*degree*C*')'))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates))
``` 



# Surface Therm 

```{r, warning=FALSE}
ggplot(data = df)+ theme_bw()+ geom_hline(yintercept = 0)+
  geom_line(aes(TIMESTAMP, TS_2_38_2_1_1, col = 'Surface'))+
  geom_hline(yintercept = 0)+
  scale_y_continuous(limits = c(-8,15),
                     expression('Soil T ('*degree*C*')'))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates))+
  scale_x_datetime(limits = as.POSIXct(c('2024-09-22','2024-09-24'),format="%F"))
```



```{r, warning=FALSE}
ggplot(data = df)+ theme_bw()+ geom_hline(yintercept = 0)+
  geom_point(aes(TIMESTAMP, TS_2_38_2_1_1, col = 'Surface'))+
  scale_y_continuous(limits = c(-8,15),
                     expression('Therms Soil T ('*C*')'))
  
TS_2_38_2_1_1.limits = df$TS_2_38_2_1_1



```

## Rolling MAD 
```{r, warning=FALSE}
f = TS_2_38_2_1_1.limits # first make a new flux vector to apply the above filters
# prepare the inputs for a zero-phase (forward and reverse) filter  
ind       = which(complete.cases(f))   # first save the index of all the NAs
b         = rep(1,8)/8                 # moving average coefficient
a         = 1                          # coefficient of the ARMA filter
mad_i    = filtfilt(b, a, na.omit(f)) #create a forward and reverse ARMA filter
mad_filt = f                          # make a copy of the full fluxes again
mad_filt[ind] = mad_i                # apply the filter where the real data exist

n = 7*48 # set the length of the rolling filter, 48 half hours in day * x days
roll.mad = rollapply(data = mad_filt,
                     width = n,
                     FUN = mad,
                     partial = TRUE,
                     na.rm = T,
                     fill = NA)  #create a rolling MAD or sd or other
roll.mad[is.na(mad_filt)] = NA  #make NA values where NAs exist in the real data


ggplot(df)+geom_hline(yintercept = 0)+
  geom_point(aes(TIMESTAMP,TS_2_38_2_1_1.limits,col='Soil T'))+
  geom_line(aes(TIMESTAMP,mad_filt,col='Filter'))+
  geom_line(aes(TIMESTAMP,roll.mad,col='MAD'))+
  scale_y_continuous(limits = c(-8,15))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates,format="%F"))+
  scale_color_manual(values=c('yellow','red','black'))
```

```{r, warning=FALSE}
#adjust this value (N) to tweak how many MADs to be away from the norm
N = 20

#Add clean value to dataframe (_.c)

df$TS_2_38_2_1_1.c = ifelse(abs(TS_2_38_2_1_1.limits - mad_filt) > (N * roll.mad),NA,TS_2_38_2_1_1.limits)

#Compare cleaned vs. uncleaned

ggplot(df)+geom_hline(yintercept = 0)+
  geom_point(aes(TIMESTAMP,TS_2_38_2_1_1.limits,col='Uncleaned'))+
  geom_point(aes(TIMESTAMP,df$TS_2_38_2_1_1.c,col='Cleaned'))+
  scale_y_continuous(limits = c(-10,15))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates,format="%F"))+
  scale_color_manual(values=c('black','red'))

```

```{r, warning=FALSE}

ggplot(data = df)+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*6,ymin = mad_filt-roll.mad*6,fill='6'))+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*3,ymin = mad_filt-roll.mad*3,fill='3'))+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*2,ymin = mad_filt-roll.mad*2,fill='2'))+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*1,ymin = mad_filt-roll.mad*1,fill='1'))+
  geom_point(aes(TIMESTAMP,TS_2_38_2_1_1.limits),col='red')+
  geom_point(aes(TIMESTAMP,TS_2_38_2_1_1.c),col='black')+
  scale_y_continuous(limits = c(-15,30))
```


#5 Cm depth Therm

```{r, warning=FALSE}

ggplot(data = df)+ theme_bw()+ geom_hline(yintercept = 0)+
  geom_line(aes(TIMESTAMP, TS_2_38_2_2_1, col = '10 cm'))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates))

TS_2_38_2_2_1.limits = df$TS_2_38_2_2_1

df$TS_2_38_2_2_1.c = TS_2_38_2_2_1.limits

ggplot(data = df)+ theme_bw()+ geom_hline(yintercept = 0)+
  geom_line(aes(TIMESTAMP, TS_2_38_2_2_1.c, col = '10 cm'))
#+
 # scale_x_datetime(limits = as.POSIXct(c("2024-07-25",'2024-12-01')))

plot(df$TS_2_38_2_2_1.c)
```
## Rolling MAD

```{r, warning=FALSE}
f = TS_2_38_2_2_1.limits # first make a new flux vector to apply the above filters
# prepare the inputs for a zero-phase (forward and reverse) filter  
ind       = which(complete.cases(f))   # first save the index of all the NAs
b         = rep(1,8)/8                 # moving average coefficient
a         = 1                          # coefficient of the ARMA filter
mad_i    = filtfilt(b, a, na.omit(f)) #create a forward and reverse ARMA filter
mad_filt = f                          # make a copy of the full fluxes again
mad_filt[ind] = mad_i                # apply the filter where the real data exist

n = 7*48 # set the length of the rolling filter, 48 half hours in day * x days
roll.mad = rollapply(data = mad_filt,
                     width = n,
                     FUN = mad,
                     partial = TRUE,
                     na.rm = T,
                     fill = NA)  #create a rolling MAD or sd or other
roll.mad[is.na(mad_filt)] = NA  #make NA values where NAs exist in the real data


ggplot(df)+geom_hline(yintercept = 0)+
  geom_point(aes(TIMESTAMP,TS_2_38_2_2_1.limits,col='Soil T'))+
  geom_line(aes(TIMESTAMP,mad_filt,col='Filter'))+
  geom_line(aes(TIMESTAMP,roll.mad,col='MAD'))+
  scale_y_continuous(limits = c(-5,15))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates,format="%F"))+
  scale_color_manual(values=c('yellow','red','black'))
```


```{r, warning=FALSE}
#adjust this value (N) to tweak how many MADs to be away from the norm
N = 3

#Add clean value to dataframe (_.c)

df$TS_2_38_2_2_1.c = ifelse(abs(TS_2_38_2_2_1.limits - mad_filt) > (N * roll.mad),NA,TS_2_38_2_2_1.limits)

#Compare cleaned vs. uncleaned

ggplot(df)+geom_hline(yintercept = 0)+
  geom_point(aes(TIMESTAMP,TS_2_38_2_2_1.limits,col='Uncleaned'))+
  geom_point(aes(TIMESTAMP,df$TS_2_38_2_2_1.c,col='Cleaned'))+
  scale_y_continuous(limits = c(-10,15))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates,format="%F"))+
  scale_color_manual(values=c('black','red'))

```


```{r, warning=FALSE}

ggplot(data = df)+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*6,ymin = mad_filt-roll.mad*6,fill='6'))+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*3,ymin = mad_filt-roll.mad*3,fill='3'))+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*2,ymin = mad_filt-roll.mad*2,fill='2'))+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*1,ymin = mad_filt-roll.mad*1,fill='1'))+
  geom_point(aes(TIMESTAMP,TS_2_38_2_2_1.limits),col='red')+
  geom_point(aes(TIMESTAMP,TS_2_38_2_2_1.c),col='black')+
  scale_y_continuous(limits = c(-15,30))
```


# 10 cm Therm

```{r, warning=FALSE}
ggplot(data = df)+ theme_bw()+ geom_hline(yintercept = 0)+
  geom_line(aes(TIMESTAMP, TS_2_38_2_3_1, col = '10 cm'))+
  scale_y_continuous(limits = c(-15,20),
                     expression('Therms Soil T ('*C*')'))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates))


ggplot(data = df)+ theme_bw()+ geom_hline(yintercept = 0)+
  geom_point(aes(TIMESTAMP, TS_2_38_2_3_1, col = '10 cm'))+
  scale_y_continuous(limits = c(-15,15),
                     expression('Therms Soil T ('*C*')'))
  
TS_2_38_2_3_1.limits = df$TS_2_38_2_3_1


ggplot(data = df)+ theme_bw()+ geom_hline(yintercept = 0)+
  geom_point(aes(TIMESTAMP, TS_2_38_2_3_1.limits, col = '10 cm'))+
  scale_y_continuous(limits = c(-15,15),
                     expression('Therms Soil T ('*C*')'))
  

```
## Rolling MAD 
```{r, warning=FALSE}
f = TS_2_38_2_3_1.limits # first make a new flux vector to apply the above filters
# prepare the inputs for a zero-phase (forward and reverse) filter  
ind       = which(complete.cases(f))   # first save the index of all the NAs
b         = rep(1,8)/8                 # moving average coefficient
a         = 1                          # coefficient of the ARMA filter
mad_i    = filtfilt(b, a, na.omit(f)) #create a forward and reverse ARMA filter
mad_filt = f                          # make a copy of the full fluxes again
mad_filt[ind] = mad_i                # apply the filter where the real data exist

n = 7*48 # set the length of the rolling filter, 48 half hours in day * x days
roll.mad = rollapply(data = mad_filt,
                     width = n,
                     FUN = mad,
                     partial = TRUE,
                     na.rm = T,
                     fill = NA)  #create a rolling MAD or sd or other
roll.mad[is.na(mad_filt)] = NA  #make NA values where NAs exist in the real data


ggplot(df)+geom_hline(yintercept = 0)+
  geom_point(aes(TIMESTAMP,TS_2_38_2_3_1.limits,col='Soil T'))+
  geom_line(aes(TIMESTAMP,mad_filt,col='Filter'))+
  geom_line(aes(TIMESTAMP,roll.mad,col='MAD'))+
  scale_y_continuous(limits = c(-15,20))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates,format="%F"))+
  scale_color_manual(values=c('yellow','red','black'))

```

```{r, warning=FALSE}
#adjust this value (N) to tweak how many MADs to be away from the norm
N = 3

#Add clean value to dataframe (_.c)

df$TS_2_38_2_3_1.c = ifelse(abs(TS_2_38_2_3_1.limits - mad_filt) > (N * roll.mad),NA,TS_2_38_2_3_1.limits)

#Compare cleaned vs. uncleaned

ggplot(data = df)+geom_hline(yintercept = 0)+
  geom_point(aes(TIMESTAMP,TS_2_38_2_3_1,col='uncleaned'))+
  geom_point(aes(TIMESTAMP,TS_2_38_2_3_1.c,col='cleaned'))+
  scale_y_continuous(limits=c(-15,20))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates,format="%F"))+
  scale_color_manual(values=c('black','red'))



```

```{r, warning=FALSE}

ggplot(data = df)+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*6,ymin = mad_filt-roll.mad*6,fill='6'))+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*3,ymin = mad_filt-roll.mad*3,fill='3'))+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*2,ymin = mad_filt-roll.mad*2,fill='2'))+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*1,ymin = mad_filt-roll.mad*1,fill='1'))+
  geom_point(aes(TIMESTAMP,TS_2_38_2_3_1),col='red')+
  geom_point(aes(TIMESTAMP,TS_2_38_2_3_1.c),col='black')+
  scale_y_continuous(limits = c(-10,15))
```

# 20 cm depth Therm

```{r, warning=FALSE}
ggplot(data = df)+ theme_bw()+ geom_hline(yintercept = 0)+
  geom_line(aes(TIMESTAMP, TS_2_38_2_4_1, col = '20 Cm'))+
  scale_y_continuous(limits = c(-5,10),
                     expression('Therms Soil T ('*C*')'))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates))


TS_2_38_2_4_1.limits = replace(df$TS_2_38_2_4_1, df$TS_2_38_2_4_1 < 15 | df$TS_2_38_2_4_1.limits > -15,NA)

ggplot(data = df)+ theme_bw()+ geom_hline(yintercept = 0)+
  geom_point(aes(TIMESTAMP, TS_2_38_2_4_1, col = '20 cm'))+
  scale_y_continuous(limits = c(-5,10),
                     expression('Therms Soil T ('*C*')'))



```


## Rolling MAD 
```{r, warning=FALSE}
f = TS_2_38_2_4_1.limits # first make a new flux vector to apply the above filters
# prepare the inputs for a zero-phase (forward and reverse) filter  
ind       = which(complete.cases(f))   # first save the index of all the NAs
b         = rep(1,8)/8                 # moving average coefficient
a         = 1                          # coefficient of the ARMA filter
mad_i    = filtfilt(b, a, na.omit(f)) #create a forward and reverse ARMA filter
mad_filt = f                          # make a copy of the full fluxes again
mad_filt[ind] = mad_i                # apply the filter where the real data exist

n = 7*48 # set the length of the rolling filter, 48 half hours in day * x days
roll.mad = rollapply(data = mad_filt,
                     width = n,
                     FUN = mad,
                     partial = TRUE,
                     na.rm = T,
                     fill = NA)  #create a rolling MAD or sd or other
roll.mad[is.na(mad_filt)] = NA  #make NA values where NAs exist in the real data


ggplot(df)+geom_hline(yintercept = 0)+
  geom_point(aes(TIMESTAMP,TS_2_38_2_4_1.limits,col='20 cm Soil T'))+
  geom_line(aes(TIMESTAMP,mad_filt,col='Filter'))+
  geom_line(aes(TIMESTAMP,roll.mad,col='MAD'))+
  scale_y_continuous(limits = c(-5,10))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates,format="%F"))+
  scale_color_manual(values=c('yellow','red','black'))

```

```{r, warning=FALSE}
#adjust this value (N) to tweak how many MADs to be away from the norm
N = 3

#Add clean value to dataframe (_.c)

df$TS_2_38_2_4_1.c = ifelse(abs(TS_2_38_2_4_1.limits - mad_filt) > (N * roll.mad),NA,TS_2_38_2_4_1.limits)

#Compare cleaned vs. uncleaned

ggplot(data = df)+geom_hline(yintercept = 0)+
  geom_point(aes(TIMESTAMP,TS_2_38_2_4_1,col='uncleaned'))+
  geom_point(aes(TIMESTAMP,TS_2_38_2_4_1.c,col='cleaned'))+
  scale_y_continuous(limits=c(-5,10))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates,format="%F"))+
  scale_color_manual(values=c('black','red'))

```

```{r, warning=FALSE}

ggplot(data = df)+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*6,ymin = mad_filt-roll.mad*6,fill='6'))+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*3,ymin = mad_filt-roll.mad*3,fill='3'))+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*2,ymin = mad_filt-roll.mad*2,fill='2'))+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*1,ymin = mad_filt-roll.mad*1,fill='1'))+
  geom_point(aes(TIMESTAMP,TS_2_38_2_4_1),col='red')+
  geom_point(aes(TIMESTAMP,TS_2_38_2_4_1.c),col='black')+
  scale_y_continuous(limits = c(-5,10))
```

# 30 cm depth Therm

```{r, warning=FALSE}
ggplot(data = df)+ theme_bw()+ geom_hline(yintercept = 0)+
  geom_line(aes(TIMESTAMP, TS_2_38_2_5_1, col = '30 Cm'))+
  scale_y_continuous(limits = c(-10,8.5),
                     expression('Therms Soil T ('*C*')'))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates))

TS_2_38_2_5_1.limits = df$TS_2_38_2_5_1

ggplot(data = df)+ theme_bw()+ geom_hline(yintercept = 0)+
  geom_point(aes(TIMESTAMP, TS_2_38_2_5_1))+
  scale_y_continuous(limits = c(-5,5),
                     expression('Therms Soil T ('*C*')'))


```
## Rolling MAD 
```{r, warning=FALSE}
f = TS_2_38_2_5_1.limits # first make a new flux vector to apply the above filters
# prepare the inputs for a zero-phase (forward and reverse) filter  
ind       = which(complete.cases(f))   # first save the index of all the NAs
b         = rep(1,8)/8                 # moving average coefficient
a         = 1                          # coefficient of the ARMA filter
mad_i    = filtfilt(b, a, na.omit(f)) #create a forward and reverse ARMA filter
mad_filt = f                          # make a copy of the full fluxes again
mad_filt[ind] = mad_i                # apply the filter where the real data exist

n = 7*48 # set the length of the rolling filter, 48 half hours in day * x days
roll.mad = rollapply(data = mad_filt,
                     width = n,
                     FUN = mad,
                     partial = TRUE,
                     na.rm = T,
                     fill = NA)  #create a rolling MAD or sd or other
roll.mad[is.na(mad_filt)] = NA  #make NA values where NAs exist in the real data


ggplot(df)+geom_hline(yintercept = 0)+
  geom_point(aes(TIMESTAMP,TS_2_38_2_5_1.limits,col='30 cm Soil T'))+
  geom_line(aes(TIMESTAMP,mad_filt,col='Filter'))+
  geom_line(aes(TIMESTAMP,roll.mad,col='MAD'))+
  scale_y_continuous(limits = c(-10,5))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates,format="%F"))+
  scale_color_manual(values=c('yellow','red','black'))
```

```{r, warning=FALSE}
#adjust this value (N) to tweak how many MADs to be away from the norm
N = 2

#Add clean value to dataframe (_.c)

df$TS_2_38_2_5_1.c = ifelse(abs(TS_2_38_2_5_1.limits - mad_filt) > (N * roll.mad),NA,TS_2_38_2_5_1.limits)

#Compare cleaned vs. uncleaned

ggplot(data = df)+geom_hline(yintercept = 0)+
  geom_point(aes(TIMESTAMP,TS_2_38_2_5_1,col='uncleaned'))+
  geom_point(aes(TIMESTAMP,TS_2_38_2_5_1.c,col='cleaned'))+
  scale_y_continuous(limits=c(-10,5))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates,format="%F"))+
  scale_color_manual(values=c('black','red'))

```

```{r, warning=FALSE}

ggplot(data = df)+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*6,ymin = mad_filt-roll.mad*6,fill='6'))+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*3,ymin = mad_filt-roll.mad*3,fill='3'))+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*2,ymin = mad_filt-roll.mad*2,fill='2'))+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*1,ymin = mad_filt-roll.mad*1,fill='1'))+
  geom_point(aes(TIMESTAMP,TS_2_38_2_5_1.limits),col='red')+
  geom_point(aes(TIMESTAMP,TS_2_38_2_5_1.c),col='black')+
  scale_y_continuous(limits = c(-8,5))
```


# 40 cm depth Therm
```{r, warning=FALSE}
ggplot(data = df)+ theme_bw()+ geom_hline(yintercept = 0)+
  geom_line(aes(TIMESTAMP, TS_2_38_2_6_1, col = '40 Cm'))+
  scale_y_continuous(limits = c(-1,5),
                     expression('Therms Soil T ('*C*')'))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates))

TS_2_38_2_6_1.limits = df$TS_2_38_2_6_1

```


## Rolling MAD 
```{r, warning=FALSE}
f = TS_2_38_2_6_1.limits # first make a new flux vector to apply the above filters
# prepare the inputs for a zero-phase (forward and reverse) filter  
ind       = which(complete.cases(f))   # first save the index of all the NAs
b         = rep(1,8)/8                 # moving average coefficient
a         = 1                          # coefficient of the ARMA filter
mad_i    = filtfilt(b, a, na.omit(f)) #create a forward and reverse ARMA filter
mad_filt = f                          # make a copy of the full fluxes again
mad_filt[ind] = mad_i                # apply the filter where the real data exist

n = 7*48 # set the length of the rolling filter, 48 half hours in day * x days
roll.mad = rollapply(data = mad_filt,
                     width = n,
                     FUN = mad,
                     partial = TRUE,
                     na.rm = T,
                     fill = NA)  #create a rolling MAD or sd or other
roll.mad[is.na(mad_filt)] = NA  #make NA values where NAs exist in the real data


ggplot(df)+geom_hline(yintercept = 0)+
  geom_point(aes(TIMESTAMP,TS_2_38_2_6_1.limits,col='40 cm Soil T'))+
  geom_line(aes(TIMESTAMP,mad_filt,col='Filter'))+
  geom_line(aes(TIMESTAMP,roll.mad,col='MAD'))+
  scale_y_continuous(limits = c(-1,5))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates,format="%F"))+
  scale_color_manual(values=c('yellow','red','black'))

```

```{r, warning=FALSE}
#adjust this value (N) to tweak how many MADs to be away from the norm
N = 3

#Add clean value to dataframe (_.c)

df$TS_2_38_2_6_1.c = ifelse(abs(TS_2_38_2_6_1.limits - mad_filt) > (N * roll.mad),NA,TS_2_38_2_6_1.limits)

#Compare cleaned vs. uncleaned

ggplot(data = df)+geom_hline(yintercept = 0)+
  geom_point(aes(TIMESTAMP,TS_2_38_2_6_1,col='uncleaned'))+
  geom_point(aes(TIMESTAMP,TS_2_38_2_6_1.c,col='cleaned'))+
  scale_y_continuous(limits=c(-8,5))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates,format="%F"))+
  scale_color_manual(values=c('black','red'))
```

```{r, warning=FALSE}

ggplot(data = df)+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*6,ymin = mad_filt-roll.mad*6,fill='6'))+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*3,ymin = mad_filt-roll.mad*3,fill='3'))+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*2,ymin = mad_filt-roll.mad*2,fill='2'))+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*1,ymin = mad_filt-roll.mad*1,fill='1'))+
  geom_point(aes(TIMESTAMP,TS_2_38_2_6_1.limits),col='red')+
  geom_point(aes(TIMESTAMP,TS_2_38_2_6_1.c),col='black')+
  scale_y_continuous(limits = c(-2,5))

```
# 50 cm depth Therm

```{r, warning=FALSE}
ggplot(data = df)+ theme_bw()+ geom_hline(yintercept = 0)+
  geom_line(aes(TIMESTAMP, TS_2_38_2_7_1, col = '50 Cm'))+
  scale_y_continuous(limits = c(-1,5),
                     expression('Therms Soil T ('*K*')'))
  scale_x_datetime(limits = as.POSIXct(biomet_dates))

TS_2_38_2_7_1.limits = df$TS_2_38_2_7_1


```


## Rolling MAD 
```{r, warning=FALSE}
f = TS_2_38_2_7_1.limits # first make a new flux vector to apply the above filters
# prepare the inputs for a zero-phase (forward and reverse) filter  
ind       = which(complete.cases(f))   # first save the index of all the NAs
b         = rep(1,8)/8                 # moving average coefficient
a         = 1                          # coefficient of the ARMA filter
mad_i    = filtfilt(b, a, na.omit(f)) #create a forward and reverse ARMA filter
mad_filt = f                          # make a copy of the full fluxes again
mad_filt[ind] = mad_i                # apply the filter where the real data exist

n = 7*48 # set the length of the rolling filter, 48 half hours in day * x days
roll.mad = rollapply(data = mad_filt,
                     width = n,
                     FUN = mad,
                     partial = TRUE,
                     na.rm = T,
                     fill = NA)  #create a rolling MAD or sd or other
roll.mad[is.na(mad_filt)] = NA  #make NA values where NAs exist in the real data

ggplot(df)+geom_hline(yintercept = 0)+
  geom_point(aes(TIMESTAMP,TS_2_38_2_7_1.limits,col='50 cm Soil T'))+
  geom_line(aes(TIMESTAMP,mad_filt,col='Filter'))+
  geom_line(aes(TIMESTAMP,roll.mad,col='MAD'))+
  scale_y_continuous(limits = c(-1,5))+
 # scale_x_datetime(limits = as.POSIXct(biomet_dates,format="%F"))+
  scale_color_manual(values=c('yellow','red','black'))
```

```{r, warning=FALSE}
#adjust this value (N) to tweak how many MADs to be away from the norm
N = 3

#Add clean value to dataframe (_.c)

df$TS_2_38_2_7_1.c = ifelse(abs(TS_2_38_2_7_1.limits - mad_filt) > (N * roll.mad),NA,TS_2_38_2_7_1.limits)

#Compare cleaned vs. uncleaned

ggplot(data = df)+geom_hline(yintercept = 0)+
  geom_point(aes(TIMESTAMP,TS_2_38_2_7_1,col='uncleaned'))+
  geom_point(aes(TIMESTAMP,TS_2_38_2_7_1.c,col='cleaned'))+
  scale_y_continuous(limits=c(-1,5))+
#  scale_x_datetime(limits = as.POSIXct(biomet_dates,format="%F"))+
  scale_color_manual(values=c('black','red'))
```

```{r, warning=FALSE}

ggplot(data = df)+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*6,ymin = mad_filt-roll.mad*6,fill='6'))+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*3,ymin = mad_filt-roll.mad*3,fill='3'))+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*2,ymin = mad_filt-roll.mad*2,fill='2'))+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*1,ymin = mad_filt-roll.mad*1,fill='1'))+
  geom_point(aes(TIMESTAMP,TS_2_38_2_7_1.limits),col='red')+
  geom_point(aes(TIMESTAMP,TS_2_38_2_7_1.c),col='black')+
  scale_y_continuous(limits = c(-5,5))

```


# 60 cm depth Therm
```{r, warning=FALSE}
ggplot(data = df)+ theme_bw()+ geom_hline(yintercept = 0)+
  geom_line(aes(TIMESTAMP, TS_2_38_2_8_1, col = '60 Cm'))+
  scale_y_continuous(limits = c(-1,3),
                     expression('Therms Soil T ('*K*')'))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates))

TS_2_38_2_8_1.limits = df$TS_2_38_2_8_1


```
## Rolling MAD 
```{r, warning=FALSE}
f = TS_2_38_2_8_1.limits # first make a new flux vector to apply the above filters
# prepare the inputs for a zero-phase (forward and reverse) filter  
ind       = which(complete.cases(f))   # first save the index of all the NAs
b         = rep(1,8)/8                 # moving average coefficient
a         = 1                          # coefficient of the ARMA filter
mad_i    = filtfilt(b, a, na.omit(f)) #create a forward and reverse ARMA filter
mad_filt = f                          # make a copy of the full fluxes again
mad_filt[ind] = mad_i                # apply the filter where the real data exist

n = 7*48 # set the length of the rolling filter, 48 half hours in day * x days
roll.mad = rollapply(data = mad_filt,
                     width = n,
                     FUN = mad,
                     partial = TRUE,
                     na.rm = T,
                     fill = NA)  #create a rolling MAD or sd or other
roll.mad[is.na(mad_filt)] = NA  #make NA values where NAs exist in the real data

ggplot(df)+geom_hline(yintercept = 0)+
  geom_point(aes(TIMESTAMP,TS_2_38_2_8_1.limits,col='60 cm Soil T'))+
  geom_line(aes(TIMESTAMP,mad_filt,col='Filter'))+
  geom_line(aes(TIMESTAMP,roll.mad,col='MAD'))+
  scale_y_continuous(limits = c(-1,5))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates,format="%F"))+
  scale_color_manual(values=c('yellow','red','black'))
```

```{r, warning=FALSE}
#adjust this value (N) to tweak how many MADs to be away from the norm
N = 3

#Add clean value to dataframe (_.c)

df$TS_2_38_2_8_1.c = ifelse(abs(TS_2_38_2_8_1.limits - mad_filt) > (N * roll.mad),NA,TS_2_38_2_8_1.limits)

#Compare cleaned vs. uncleaned

ggplot(data = df)+geom_hline(yintercept = 0)+
  geom_point(aes(TIMESTAMP,TS_2_38_2_8_1,col='uncleaned'))+
  geom_point(aes(TIMESTAMP,TS_2_38_2_8_1.c,col='cleaned'))+
  scale_y_continuous(limits=c(-1,5))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates,format="%F"))+
  scale_color_manual(values=c('black','red'))
```

```{r, warning=FALSE}

ggplot(data = df)+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*6,ymin = mad_filt-roll.mad*6,fill='6'))+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*3,ymin = mad_filt-roll.mad*3,fill='3'))+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*2,ymin = mad_filt-roll.mad*2,fill='2'))+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*1,ymin = mad_filt-roll.mad*1,fill='1'))+
  geom_point(aes(TIMESTAMP,TS_2_38_2_8_1.limits),col='red')+
  geom_point(aes(TIMESTAMP,TS_2_38_2_8_1.c),col='black')+
  scale_y_continuous(limits = c(-5,5))
```


#  70 cm depth Therm
```{r, warning=FALSE}
ggplot(data = df)+ theme_bw()+ geom_hline(yintercept = 0)+
  geom_line(aes(TIMESTAMP, TS_2_38_2_9_1, col = '70 Cm'))+
  scale_y_continuous(limits = c(-3,3),
                     expression('Therms Soil T ('*K*')'))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates))

TS_2_38_2_9_1.limits = df$TS_2_38_2_9_1


```
## Rolling MAD 
```{r, warning=FALSE}
f = TS_2_38_2_9_1.limits # first make a new flux vector to apply the above filters
# prepare the inputs for a zero-phase (forward and reverse) filter  
ind       = which(complete.cases(f))   # first save the index of all the NAs
b         = rep(1,8)/8                 # moving average coefficient
a         = 1                          # coefficient of the ARMA filter
mad_i    = filtfilt(b, a, na.omit(f)) #create a forward and reverse ARMA filter
mad_filt = f                          # make a copy of the full fluxes again
mad_filt[ind] = mad_i                # apply the filter where the real data exist

n = 7*48 # set the length of the rolling filter, 48 half hours in day * x days
roll.mad = rollapply(data = mad_filt,
                     width = n,
                     FUN = mad,
                     partial = TRUE,
                     na.rm = T,
                     fill = NA)  #create a rolling MAD or sd or other
roll.mad[is.na(mad_filt)] = NA  #make NA values where NAs exist in the real data

ggplot(df)+geom_hline(yintercept = 0)+
  geom_point(aes(TIMESTAMP,TS_2_38_2_9_1.limits,col='70 cm Soil T'))+
  geom_line(aes(TIMESTAMP,mad_filt,col='Filter'))+
  geom_line(aes(TIMESTAMP,roll.mad,col='MAD'))+
  scale_y_continuous(limits = c(-3,3))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates,format="%F"))+
  scale_color_manual(values=c('yellow','red','black'))
```

```{r, warning=FALSE}
#adjust this value (N) to tweak how many MADs to be away from the norm
N = 3

#Add clean value to dataframe (_.c)

df$TS_2_38_2_9_1.c = ifelse(abs(TS_2_38_2_9_1.limits - mad_filt) > (N * roll.mad),NA,TS_2_38_2_9_1.limits)

#Compare cleaned vs. uncleaned

ggplot(data = df)+geom_hline(yintercept = 0)+
  geom_point(aes(TIMESTAMP,TS_2_38_2_9_1,col='uncleaned'))+
  geom_point(aes(TIMESTAMP,TS_2_38_2_9_1.c,col='cleaned'))+
  scale_y_continuous(limits=c(-3,3))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates,format="%F"))+
  scale_color_manual(values=c('black','red'))
```

```{r, warning=FALSE}

ggplot(data = df)+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*6,ymin = mad_filt-roll.mad*6,fill='6'))+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*3,ymin = mad_filt-roll.mad*3,fill='3'))+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*2,ymin = mad_filt-roll.mad*2,fill='2'))+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*1,ymin = mad_filt-roll.mad*1,fill='1'))+
  geom_point(aes(TIMESTAMP,TS_2_38_2_9_1.limits),col='red')+
  geom_point(aes(TIMESTAMP,TS_2_38_2_9_1.c),col='black')+
  scale_y_continuous(limits = c(-5,5))
```




# All soil therms
```{r, warning=FALSE}
ggplot(data = df)+ theme_bw()+
  geom_hline(yintercept = 0)+
  geom_line(aes(TIMESTAMP,TS_2_38_2_1_1.c,color='Surface'))+
  geom_line(aes(TIMESTAMP,TS_2_38_2_2_1.c,color='5 cm'))+
  geom_line(aes(TIMESTAMP,TS_2_38_2_3_1.c,color='10 cm'))+
  geom_line(aes(TIMESTAMP,TS_2_38_2_4_1.c,color='20 cm'))+  
  geom_line(aes(TIMESTAMP,TS_2_38_2_5_1.c,color='30 cm'))+
  geom_line(aes(TIMESTAMP,TS_2_38_2_6_1.c,color='40 cm'))+
  geom_line(aes(TIMESTAMP,TS_2_38_2_7_1.c,color='50 cm'))+
  geom_line(aes(TIMESTAMP,TS_2_38_2_8_1.c,color='60 cm'))+
  geom_line(aes(TIMESTAMP,TS_2_38_2_9_1.c,color='70 cm'))
 
```




# Volumetric Water Content
```{r, warning=FALSE}
ggplot(data = df)+
  geom_point(aes(TIMESTAMP, SWC_12_36_1_1_1*100,col='SWC 1'))+
  geom_point(aes(TIMESTAMP, SWC_12_36_1_2_1*100,col='SWC 2'))+
  geom_point(aes(TIMESTAMP, SWC_12_36_1_3_1*100,col='SWC 3'))+
  scale_y_continuous(limits = c(0,100),
                     expression('% VWC'))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates))
```

# Save

```{r, warning=FALSE}
write.csv(x = df,file = 'C:/Users/klynoe/Documents/pond_inlet/R_outputs/pondinlet_met_clean_202411.csv',row.names = F,quote = F)
```







