---
title: "CH4/CO2 Merging Churchill"
author: "Dani Trangmoe"
output: html_document
date: "`r Sys.Date()`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load packages

```{r, warning=FALSE}
rm(list = ls())

library(data.table)
library(ggplot2)
library(cowplot)
library(openair)
library(plotrix)
library(signal)
library(svMisc)
library(zoo)
library(stringr)
library(plyr)
library(dplyr)
library(lubridate)
```


# Nov. 23

### Load file - co2 and methane

```{r, warning=FALSE}

#load in the full output flux data ##################
fp = 'C:/Users/dtrangmoe/Documents/Churchill/Processed Nov 23 - CO2 and Methane'
files = list.files(path = fp,pattern = '*full_output.+csv$',recursive = T,full.names = T)

#load the headers and data into their own lists
h   = lapply(files, fread,skip = 1,nrow = 0)
dat = lapply(files, fread,skip = 3,header = F,na.strings=c('-9999'))

ls()


#assign the headers to the data
for (i in 1:length(h)) {
  names(dat[[i]]) = names(h[[i]])
}

df = dat[[1]] 

# #make all the lists into one dataframe - only for more than one file
# for (i in 2:length(dat)) {
#  df = rbind.fill(df,dat[[i]])
# }

#create a timestamp from the date and time
df$ts = as.POSIXct(x = paste(df$date,df$time,sep = ' '),tz = 'UTC')

#take the min and max date rounding to the nearest full month
## create NAs for beginning & end of partial months: add unit='months'
mindate = floor_date(min(df$ts))
maxdate = ceiling_date(max(df$ts))

#create a timestamp variable every half hour
ts = seq(from = mindate,to = maxdate,by = 60*30)
ts = as.data.frame(ts)


#merge with the flux data frame to create NAs where data is missing
df = merge(ts,df,by = 'ts',all.x = T)


#save off flux data
write.csv(df, 'C:/Users/dtrangmoe/Documents/Churchill/ChurchillFlux_Nov23_CO2_CH4_merged.csv',row.names = F)


```



### Load file - methane only

```{r, warning=FALSE}

#load in the full output flux data ##################
fp = 'C:/Users/dtrangmoe/Documents/Churchill/Processed Late Nov 23 - Methane Only'
files = list.files(path = fp,pattern = '*full_output.+csv$',recursive = T,full.names = T)

#load the headers and data into their own lists
h   = lapply(files, fread,skip = 1,nrow = 0)
dat = lapply(files, fread,skip = 3,header = F,na.strings=c('-9999'))

ls()


#assign the headers to the data
for (i in 1:length(h)) {
  names(dat[[i]]) = names(h[[i]])
}

df = dat[[1]] 

# #make all the lists into one dataframe - only for more than one file
# for (i in 2:length(dat)) {
#  df = rbind.fill(df,dat[[i]])
# }

#create a timestamp from the date and time
df$ts = as.POSIXct(x = paste(df$date,df$time,sep = ' '),tz = 'UTC')


#create a timestamp variable every half hour, creating full month - uses min and max from co2 and ch4 df
ts = seq(from = mindate,to = maxdate,by = 60*30)
ts = as.data.frame(ts)


#merge with the flux data frame to create NAs where data is missing
df = merge(ts,df,by = 'ts',all.x = T)


#save off flux data
write.csv(df, 'C:/Users/dtrangmoe/Documents/Churchill/ChurchillFlux_LateNov23_CH4only_merged.csv',row.names = F)


```

### Merge

Merge two files to include co2 and methane data when available, and include only methane otherwise

```{r, warning=FALSE}

df_both = fread('C:/Users/dtrangmoe/Documents/Churchill/ChurchillFlux_Nov23_CO2_CH4_merged.csv')

df_ch4 = fread('C:/Users/dtrangmoe/Documents/Churchill/ChurchillFlux_LateNov23_CH4only_merged.csv')

df = full_join(df_both, df_ch4, by = 'ts', suffix=c('', '.ch4'))

#plot to show ch4 data consistent between data frames, and some gaps are present in 'both' data
ggplot(df)+
  geom_point(aes(ts,ch4_flux.ch4, col = 'CH4'))+
  geom_point(aes(ts,ch4_flux, col = 'Both'))

ch4_columns <- names(df)[grep("\\.ch4$", names(df))]


## scans all rows in df, and if co2 is not available data in the "both" columns of the data frame is replaced by corresponding data from "ch4" data frame

for(i in 1:length(ch4_columns)) {

  col_to_reference = ch4_columns[i]
  col_to_replace = sub(".ch4$", "", ch4_columns[i])

  for (j in 1:nrow(df)) {
    if (is.na(df[j,co2_flux])) {

      df[j, col_to_replace] <- df[j, ..col_to_reference]

    }
  }
}


ggplot(df)+
  geom_point(aes(ts,ch4_flux.ch4, col = 'CH4'))+
  geom_point(aes(ts,ch4_flux, col = 'Both'))

# creates logical vector indicating with columns to keep, then removes all others (removes duplicates)

df_cols_to_keep <- df[, !names(df) %in% ch4_columns]
df = subset(df, select = df_cols_to_keep)

write.csv(df, 'C:/Users/dtrangmoe/Documents/Churchill/ChurchillFlux_Nov23_merged.csv',row.names = F)

rm(list = ls())

```








# Dec 23

### Load file - co2 and methane

```{r, warning=FALSE}

rm(list = ls())


#load in the full output flux data ##################
fp = 'C:/Users/dtrangmoe/Documents/Churchill/Processed Dec 23 - CO2 and Methane'
files = list.files(path = fp,pattern = '*full_output.+csv$',recursive = T,full.names = T)

#load the headers and data into their own lists
h   = lapply(files, fread,skip = 1,nrow = 0)
dat = lapply(files, fread,skip = 3,header = F,na.strings=c('-9999'))

ls()


#assign the headers to the data
for (i in 1:length(h)) {
  names(dat[[i]]) = names(h[[i]])
}

df = dat[[1]] 

# #make all the lists into one dataframe - only for more than one file
# for (i in 2:length(dat)) {
#  df = rbind.fill(df,dat[[i]])
# }

#create a timestamp from the date and time
df$ts = as.POSIXct(x = paste(df$date,df$time,sep = ' '),tz = 'UTC')

#take the min and max date rounding to the nearest full month
## create NAs for beginning & end of partial months: add unit='months'
mindate = floor_date(min(df$ts))
maxdate = ceiling_date(max(df$ts))

#create a timestamp variable every half hour
ts = seq(from = mindate,to = maxdate,by = 60*30)
ts = as.data.frame(ts)


#merge with the flux data frame to create NAs where data is missing
df = merge(ts,df,by = 'ts',all.x = T)


#save off flux data
write.csv(df, 'C:/Users/dtrangmoe/Documents/Churchill/ChurchillFlux_Dec23_CO2_CH4_merged.csv',row.names = F)


```



### Load file - methane only

```{r, warning=FALSE}

#load in the full output flux data ##################
fp = 'C:/Users/dtrangmoe/Documents/Churchill/Processed Dec 23 - Methane Only'
files = list.files(path = fp,pattern = '*full_output.+csv$',recursive = T,full.names = T)

#load the headers and data into their own lists
h   = lapply(files, fread,skip = 1,nrow = 0)
dat = lapply(files, fread,skip = 3,header = F,na.strings=c('-9999'))

ls()


#assign the headers to the data
for (i in 1:length(h)) {
  names(dat[[i]]) = names(h[[i]])
}

df = dat[[1]] 

# #make all the lists into one dataframe - only for more than one file
# for (i in 2:length(dat)) {
#  df = rbind.fill(df,dat[[i]])
# }

#create a timestamp from the date and time
df$ts = as.POSIXct(x = paste(df$date,df$time,sep = ' '),tz = 'UTC')

#take the min and max date rounding to the nearest full month
## create NAs for beginning & end of partial months: add unit='months'
mindate = floor_date(min(df$ts))
maxdate = ceiling_date(max(df$ts))

#create a timestamp variable every half hour
ts = seq(from = mindate,to = maxdate,by = 60*30)
ts = as.data.frame(ts)


#merge with the flux data frame to create NAs where data is missing
df = merge(ts,df,by = 'ts',all.x = T)


#save off flux data
write.csv(df, 'C:/Users/dtrangmoe/Documents/Churchill/ChurchillFlux_Dec23_CH4only_merged.csv',row.names = F)

```


### Merge

Merge two files to include co2 and methane data when available, and include only methane otherwise

```{r, warning=FALSE}

df_both = fread('C:/Users/dtrangmoe/Documents/Churchill/ChurchillFlux_Dec23_CO2_CH4_merged.csv')

df_ch4 = fread('C:/Users/dtrangmoe/Documents/Churchill/ChurchillFlux_Dec23_CH4only_merged.csv')


df = full_join(df_both, df_ch4, by = 'ts', suffix=c('', '.ch4'))

#plot to show ch4 data consistent between data frames, and some gaps are present in 'both' data
ggplot(df)+
  geom_point(aes(ts,ch4_flux.ch4, col = 'CH4'))+
  geom_point(aes(ts,ch4_flux, col = 'Both'))

ggplot(df)+
  geom_point(aes(ts,ch4_flux, col = 'Both'))+
  geom_point(aes(ts,ch4_flux.ch4, col = 'CH4'))

ch4_columns <- names(df)[grep("\\.ch4$", names(df))]


## scans all rows in df, and if co2 is not available data in the "both" columns of the data frame is replaced by corresponding data from "ch4" data frame

for(i in 1:length(ch4_columns)) {

  col_to_reference = ch4_columns[i]
  col_to_replace = sub(".ch4$", "", ch4_columns[i])

  for (j in 1:nrow(df)) {
    if (is.na(df[j,co2_flux])) {

      df[j, col_to_replace] <- df[j, ..col_to_reference]

    }
  }
}


ggplot(df)+
  geom_point(aes(ts,ch4_flux.ch4, col = 'CH4'))+
  geom_point(aes(ts,ch4_flux, col = 'Both'))

# creates logical vector indicating with columns to keep, then removes all others (removes duplicates)

df_cols_to_keep <- df[, !names(df) %in% ch4_columns]
df = subset(df, select = df_cols_to_keep)

write.csv(df, 'C:/Users/dtrangmoe/Documents/Churchill/ChurchillFlux_Dec23_merged.csv',row.names = F)

rm(list = ls())

```



# Combine

```{r, warning=FALSE}
df_nov = fread('C:/Users/dtrangmoe/Documents/Churchill/ChurchillFlux_Nov23_merged.csv')

df_dec = fread('C:/Users/dtrangmoe/Documents/Churchill/ChurchillFlux_Dec23_merged.csv')

df = bind_rows(df_nov, df_dec)

write.csv(df, 'C:/Users/dtrangmoe/Documents/Churchill/ChurchillFlux_NovDec23_merged.csv',row.names = F)

```



# Jan 24

### Load file - co2 and methane

```{r, warning=FALSE}

rm(list = ls())


#load in the full output flux data ##################
fp = 'C:/Users/dtrangmoe/Documents/Churchill/Processed Jan 24 - CO2 and Methane'
files = list.files(path = fp,pattern = '*full_output.+csv$',recursive = T,full.names = T)

#load the headers and data into their own lists
h   = lapply(files, fread,skip = 1,nrow = 0)
dat = lapply(files, fread,skip = 3,header = F,na.strings=c('-9999'))

ls()


#assign the headers to the data
for (i in 1:length(h)) {
  names(dat[[i]]) = names(h[[i]])
}

df = dat[[1]] 

# #make all the lists into one dataframe - only for more than one file
# for (i in 2:length(dat)) {
#  df = rbind.fill(df,dat[[i]])
# }

#create a timestamp from the date and time
df$ts = as.POSIXct(x = paste(df$date,df$time,sep = ' '),tz = 'UTC')

#take the min and max date rounding to the nearest full month
## create NAs for beginning & end of partial months: add unit='months'
mindate = floor_date(min(df$ts))
maxdate = ceiling_date(max(df$ts))

#create a timestamp variable every half hour
ts = seq(from = mindate,to = maxdate,by = 60*30)
ts = as.data.frame(ts)


#merge with the flux data frame to create NAs where data is missing
df = merge(ts,df,by = 'ts',all.x = T)


#save off flux data
write.csv(df, 'C:/Users/dtrangmoe/Documents/Churchill/ChurchillFlux_Jan24_CO2_CH4_merged.csv',row.names = F)


```



### Load file - methane only

```{r, warning=FALSE}

#load in the full output flux data ##################
fp = 'C:/Users/dtrangmoe/Documents/Churchill/Processed Jan 24 - Methane Only'
files = list.files(path = fp,pattern = '*full_output.+csv$',recursive = T,full.names = T)

#load the headers and data into their own lists
h   = lapply(files, fread,skip = 1,nrow = 0)
dat = lapply(files, fread,skip = 3,header = F,na.strings=c('-9999'))

ls()


#assign the headers to the data
for (i in 1:length(h)) {
  names(dat[[i]]) = names(h[[i]])
}

df = dat[[1]] 

# #make all the lists into one dataframe - only for more than one file
# for (i in 2:length(dat)) {
#  df = rbind.fill(df,dat[[i]])
# }

#create a timestamp from the date and time
df$ts = as.POSIXct(x = paste(df$date,df$time,sep = ' '),tz = 'UTC')

#take the min and max date rounding to the nearest full month
## create NAs for beginning & end of partial months: add unit='months'
mindate = floor_date(min(df$ts))
maxdate = ceiling_date(max(df$ts))

#create a timestamp variable every half hour
ts = seq(from = mindate,to = maxdate,by = 60*30)
ts = as.data.frame(ts)


#merge with the flux data frame to create NAs where data is missing
df = merge(ts,df,by = 'ts',all.x = T)


#save off flux data
write.csv(df, 'C:/Users/dtrangmoe/Documents/Churchill/ChurchillFlux_Jan24_CH4only_merged.csv',row.names = F)

```


### Merge

Merge two files to include co2 and methane data when available, and include only methane otherwise

```{r, warning=FALSE}

df_both = fread('C:/Users/dtrangmoe/Documents/Churchill/ChurchillFlux_Jan24_CO2_CH4_merged.csv')

df_ch4 = fread('C:/Users/dtrangmoe/Documents/Churchill/ChurchillFlux_Jan24_CH4only_merged.csv')


df = full_join(df_both, df_ch4, by = 'ts', suffix=c('', '.ch4'))

#plot to show ch4 data consistent between data frames, and check if gaps are present in 'both' data
ggplot(df)+
  geom_point(aes(ts,ch4_flux.ch4, col = 'CH4'))+
  geom_point(aes(ts,ch4_flux, col = 'Both'))

ggplot(df)+
  geom_point(aes(ts,ch4_flux, col = 'Both'))+
  geom_point(aes(ts,ch4_flux.ch4, col = 'CH4'))

plot(df$ch4_flux, df$ch4_flux.ch4)

ch4_columns <- names(df)[grep("\\.ch4$", names(df))]


## scans all rows in df, and if co2 is not available data in the "both" columns of the data frame is replaced by corresponding data from "ch4" data frame

for(i in 1:length(ch4_columns)) {

  col_to_reference = ch4_columns[i]
  col_to_replace = sub(".ch4$", "", ch4_columns[i])

  for (j in 1:nrow(df)) {
    if (is.na(df[j,co2_flux])) {

      df[j, col_to_replace] <- df[j, ..col_to_reference]

    }
  }
}

# not that necessary for this month
ggplot(df)+
  geom_point(aes(ts,ch4_flux.ch4, col = 'CH4'))+
  geom_point(aes(ts,ch4_flux, col = 'Both'))

# creates logical vector indicating with columns to keep, then removes all others (removes duplicates)

df_cols_to_keep <- df[, !names(df) %in% ch4_columns]
df = subset(df, select = df_cols_to_keep)

write.csv(df, 'C:/Users/dtrangmoe/Documents/Churchill/ChurchillFlux_Jan24_merged.csv',row.names = F)

rm(list = ls())

```



# Feb 24

### Load file - co2 and methane

```{r, warning=FALSE}

rm(list = ls())


#load in the full output flux data ##################
fp = 'C:/Users/dtrangmoe/Documents/Churchill/Processed Feb 24 - CO2 and Methane'
files = list.files(path = fp,pattern = '*full_output.+csv$',recursive = T,full.names = T)

#load the headers and data into their own lists
h   = lapply(files, fread,skip = 1,nrow = 0)
dat = lapply(files, fread,skip = 3,header = F,na.strings=c('-9999'))

ls()


#assign the headers to the data
for (i in 1:length(h)) {
  names(dat[[i]]) = names(h[[i]])
}

df = dat[[1]] 

# #make all the lists into one dataframe - only for more than one file
# for (i in 2:length(dat)) {
#  df = rbind.fill(df,dat[[i]])
# }

#create a timestamp from the date and time
df$ts = as.POSIXct(x = paste(df$date,df$time,sep = ' '),tz = 'UTC')

#take the min and max date rounding to the nearest full month
## create NAs for beginning & end of partial months: add unit='months'
mindate = floor_date(min(df$ts))
maxdate = ceiling_date(max(df$ts))

#create a timestamp variable every half hour
ts = seq(from = mindate,to = maxdate,by = 60*30)
ts = as.data.frame(ts)


#merge with the flux data frame to create NAs where data is missing
df = merge(ts,df,by = 'ts',all.x = T)


#save off flux data
write.csv(df, 'C:/Users/dtrangmoe/Documents/Churchill/ChurchillFlux_Jan24_CO2_CH4_merged.csv',row.names = F)


```



### Load file - methane only

```{r, warning=FALSE}

#load in the full output flux data ##################
fp = 'C:/Users/dtrangmoe/Documents/Churchill/Processed Feb 24 - Methane Only'
files = list.files(path = fp,pattern = '*full_output.+csv$',recursive = T,full.names = T)

#load the headers and data into their own lists
h   = lapply(files, fread,skip = 1,nrow = 0)
dat = lapply(files, fread,skip = 3,header = F,na.strings=c('-9999'))

ls()


#assign the headers to the data
for (i in 1:length(h)) {
  names(dat[[i]]) = names(h[[i]])
}

df = dat[[1]] 

# #make all the lists into one dataframe - only for more than one file
# for (i in 2:length(dat)) {
#  df = rbind.fill(df,dat[[i]])
# }

#create a timestamp from the date and time
df$ts = as.POSIXct(x = paste(df$date,df$time,sep = ' '),tz = 'UTC')

#take the min and max date rounding to the nearest full month
## create NAs for beginning & end of partial months: add unit='months'
mindate = floor_date(min(df$ts))
maxdate = ceiling_date(max(df$ts))

#create a timestamp variable every half hour
ts = seq(from = mindate,to = maxdate,by = 60*30)
ts = as.data.frame(ts)


#merge with the flux data frame to create NAs where data is missing
df = merge(ts,df,by = 'ts',all.x = T)


#save off flux data
write.csv(df, 'C:/Users/dtrangmoe/Documents/Churchill/ChurchillFlux_Feb24_CH4only_merged.csv',row.names = F)

```


### Merge

Merge two files to include co2 and methane data when available, and include only methane otherwise

```{r, warning=FALSE}

df_both = fread('C:/Users/dtrangmoe/Documents/Churchill/ChurchillFlux_Feb24_CO2_CH4_merged.csv')

df_ch4 = fread('C:/Users/dtrangmoe/Documents/Churchill/ChurchillFlux_Feb24_CH4only_merged.csv')


df = full_join(df_both, df_ch4, by = 'ts', suffix=c('', '.ch4'))

#plot to show ch4 data consistent between data frames, and check if gaps are present in 'both' data
ggplot(df)+
  geom_point(aes(ts,ch4_flux.ch4, col = 'CH4'))+
  geom_point(aes(ts,ch4_flux, col = 'Both'))

ggplot(df)+
  geom_point(aes(ts,ch4_flux, col = 'Both'))+
  geom_point(aes(ts,ch4_flux.ch4, col = 'CH4'))

plot(df$ch4_flux, df$ch4_flux.ch4)

ch4_columns <- names(df)[grep("\\.ch4$", names(df))]


## scans all rows in df, and if co2 is not available data in the "both" columns of the data frame is replaced by corresponding data from "ch4" data frame

for(i in 1:length(ch4_columns)) {

  col_to_reference = ch4_columns[i]
  col_to_replace = sub(".ch4$", "", ch4_columns[i])

  for (j in 1:nrow(df)) {
    if (is.na(df[j,co2_flux])) {

      df[j, col_to_replace] <- df[j, ..col_to_reference]

    }
  }
}

# not that necessary for this month
ggplot(df)+
  geom_point(aes(ts,ch4_flux.ch4, col = 'CH4'))+
  geom_point(aes(ts,ch4_flux, col = 'Both'))

# creates logical vector indicating with columns to keep, then removes all others (removes duplicates)

df_cols_to_keep <- df[, !names(df) %in% ch4_columns]
df = subset(df, select = df_cols_to_keep)

write.csv(df, 'C:/Users/dtrangmoe/Documents/Churchill/ChurchillFlux_Feb24_merged.csv',row.names = F)

rm(list = ls())

```



# Mar 24

### Load file - co2 and methane

```{r, warning=FALSE}

rm(list = ls())


#load in the full output flux data ##################
fp = 'C:/Users/dtrangmoe/Documents/Churchill/Processed Mar 24 - CO2 and Methane'
files = list.files(path = fp,pattern = '*full_output.+csv$',recursive = T,full.names = T)

#load the headers and data into their own lists
h   = lapply(files, fread,skip = 1,nrow = 0)
dat = lapply(files, fread,skip = 3,header = F,na.strings=c('-9999'))

ls()


#assign the headers to the data
for (i in 1:length(h)) {
  names(dat[[i]]) = names(h[[i]])
}

df = dat[[1]] 

# #make all the lists into one dataframe - only for more than one file
# for (i in 2:length(dat)) {
#  df = rbind.fill(df,dat[[i]])
# }

#create a timestamp from the date and time
df$ts = as.POSIXct(x = paste(df$date,df$time,sep = ' '),tz = 'UTC')

#take the min and max date rounding to the nearest full month
## create NAs for beginning & end of partial months: add unit='months'
mindate = floor_date(min(df$ts))
maxdate = ceiling_date(max(df$ts))

#create a timestamp variable every half hour
ts = seq(from = mindate,to = maxdate,by = 60*30)
ts = as.data.frame(ts)


#merge with the flux data frame to create NAs where data is missing
df = merge(ts,df,by = 'ts',all.x = T)


#save off flux data
write.csv(df, 'C:/Users/dtrangmoe/Documents/Churchill/ChurchillFlux_Mar24_CO2_CH4_merged.csv',row.names = F)


```



### Load file - methane only

```{r, warning=FALSE}

#load in the full output flux data ##################
fp = 'C:/Users/dtrangmoe/Documents/Churchill/Processed Mar 24 - Methane Only'
files = list.files(path = fp,pattern = '*full_output.+csv$',recursive = T,full.names = T)

#load the headers and data into their own lists
h   = lapply(files, fread,skip = 1,nrow = 0)
dat = lapply(files, fread,skip = 3,header = F,na.strings=c('-9999'))

ls()


#assign the headers to the data
for (i in 1:length(h)) {
  names(dat[[i]]) = names(h[[i]])
}

df = dat[[1]] 

# #make all the lists into one dataframe - only for more than one file
# for (i in 2:length(dat)) {
#  df = rbind.fill(df,dat[[i]])
# }

#create a timestamp from the date and time
df$ts = as.POSIXct(x = paste(df$date,df$time,sep = ' '),tz = 'UTC')

#take the min and max date rounding to the nearest full month
## create NAs for beginning & end of partial months: add unit='months'
mindate = floor_date(min(df$ts))
maxdate = ceiling_date(max(df$ts))

#create a timestamp variable every half hour
ts = seq(from = mindate,to = maxdate,by = 60*30)
ts = as.data.frame(ts)


#merge with the flux data frame to create NAs where data is missing
df = merge(ts,df,by = 'ts',all.x = T)


#save off flux data
write.csv(df, 'C:/Users/dtrangmoe/Documents/Churchill/ChurchillFlux_Mar24_CH4only_merged.csv',row.names = F)

```


### Merge

Merge two files to include co2 and methane data when available, and include only methane otherwise

```{r, warning=FALSE}

df_both = fread('C:/Users/dtrangmoe/Documents/Churchill/ChurchillFlux_Mar24_CO2_CH4_merged.csv')

df_ch4 = fread('C:/Users/dtrangmoe/Documents/Churchill/ChurchillFlux_Mar24_CH4only_merged.csv')


df = full_join(df_both, df_ch4, by = 'ts', suffix=c('', '.ch4'))

#plot to show ch4 data consistent between data frames, and check if gaps are present in 'both' data
ggplot(df)+
  geom_point(aes(ts,ch4_flux.ch4, col = 'CH4'))+
  geom_point(aes(ts,ch4_flux, col = 'Both'))

ggplot(df)+
  geom_point(aes(ts,ch4_flux, col = 'Both'))+
  geom_point(aes(ts,ch4_flux.ch4, col = 'CH4'))

plot(df$ch4_flux, df$ch4_flux.ch4)

ch4_columns <- names(df)[grep("\\.ch4$", names(df))]


## scans all rows in df, and if co2 is not available data in the "both" columns of the data frame is replaced by corresponding data from "ch4" data frame

for(i in 1:length(ch4_columns)) {

  col_to_reference = ch4_columns[i]
  col_to_replace = sub(".ch4$", "", ch4_columns[i])

  for (j in 1:nrow(df)) {
    if (is.na(df[j,co2_flux])) {

      df[j, col_to_replace] <- df[j, ..col_to_reference]

    }
  }
}

# not that necessary for this month
ggplot(df)+
  geom_point(aes(ts,ch4_flux.ch4, col = 'CH4'))+
  geom_point(aes(ts,ch4_flux, col = 'Both'))

# creates logical vector indicating with columns to keep, then removes all others (removes duplicates)

df_cols_to_keep <- df[, !names(df) %in% ch4_columns]
df = subset(df, select = df_cols_to_keep)

write.csv(df, 'C:/Users/dtrangmoe/Documents/Churchill/ChurchillFlux_Mar24_merged.csv',row.names = F)

rm(list = ls())

```
