---
title: "Churchill Model Runs"
output: pdf_document
date: "2024-02-15"
---

# Load Packages
```{r}
rm(list = ls())

library(data.table)
library(ggplot2)
library(cowplot)
library(openair)
library(plotrix)
library(signal)
library(svMisc)
library(zoo)
library(stringr)
library(plyr)
library(dplyr)
library(lubridate)
library(tidyverse)
library(RColorBrewer)
library(tidyr)
library(ppcor)
```
# Load DF's 
```{r}
h1 = fread('G:/My Drive/Permafrost Pathways/Towers/Churchill/Data/CA_CF3.csv', nrows = 1, skip = 0)
dat1 = fread('G:/My Drive/Permafrost Pathways/Towers/Churchill/Data/CA_CF3.csv',skip = 1, header = FALSE, na.strings=c('-9999','NA','NaN','NAN'))

h2 = fread('G:/My Drive/Permafrost Pathways/Towers/Churchill/Data/AMF_CA-CF2_BASE_HH_2-5.csv',nrows=1,skip=2)
dat2 = fread ('G:/My Drive/Permafrost Pathways/Towers/Churchill/Data/AMF_CA-CF2_BASE_HH_2-5.csv',skip = 3,header = FALSE, na.strings=c('-9999','NA','NaN','NAN'))

h3 = fread('G:/My Drive/Permafrost Pathways/Towers/Churchill/Data/AMF_CA-CF1_BASE_HH_2-5.csv',nrows=1,skip=2)
dat3 = fread ('G:/My Drive/Permafrost Pathways/Towers/Churchill/Data/AMF_CA-CF1_BASE_HH_2-5.csv',skip = 3,header = FALSE, na.strings=c('-9999','NA','NaN','NAN'))

names(dat1) = names(h1)
names(dat2) = names(h2)
names(dat3) = names(h3)

CF3= dat1
CF2 = dat2
CF1 = dat3
```

# Timestamps
```{r}

#CF2

CF2$ts = as.character(CF2$TIMESTAMP_START)

CF2$year = substr(CF2$ts,1,4)
CF2$month = substr(CF2$ts,5,6)
CF2$day = substr(CF2$ts,7,8)
CF2$hour = substr(CF2$ts,9,10)
CF2$min = substr(CF2$ts,11,12)



CF2$ts = as.POSIXct(paste(CF2$year,CF2$month,CF2$day,CF2$hour,CF2$min,sep = ''),
                    format = '%Y%m%d%H%M',
                    tz = "America/Belize"	
                    )

CF2$date = as.POSIXct(paste(CF2$year,CF2$month,CF2$day,sep = ''),
                      format = '%Y%m%d')
#CF1

CF1$ts = as.character(CF1$TIMESTAMP_START)

CF1$year = substr(CF1$ts,1,4)
CF1$month = substr(CF1$ts,5,6)
CF1$day = substr(CF1$ts,7,8)
CF1$hour = substr(CF1$ts,9,10)
CF1$min = substr(CF1$ts,11,12)



CF1$ts = as.POSIXct(paste(CF1$year,CF1$month,CF1$day,CF1$hour,CF1$min,sep = ''),
                    format = '%Y%m%d%H%M',
                    tz = "America/Belize"	
                    )

CF1$date = as.POSIXct(paste(CF1$year,CF1$month,CF1$day,sep = ''),
                      format = '%Y%m%d')

#CF3

CF3$ts = as.character(CF3$TIMESTAMP_START)

CF3$year = substr(CF3$ts,1,4)
CF3$month = substr(CF3$ts,5,6)
CF3$day = substr(CF3$ts,7,8)
CF3$hour = substr(CF3$ts,9,10)
CF3$min = substr(CF3$ts,11,12)



CF3$ts = as.POSIXct(paste(CF3$year,CF3$month,CF3$day,CF3$hour,CF3$min,sep = ''),
                    format = '%Y%m%d%H%M',
                    tz = "America/Belize"	
                    )


CF3$date = as.POSIXct(paste(CF3$year,CF3$month,CF3$day,sep = ''),
                      format = '%Y%m%d')


```

## Variable names CF3
```{r,warning = FALSE}

#Removing TS_1_1_1, TS_2_1_1, and TS_2_2_1 (choosing to use therm data, not CS655's)
#Changing TS_3 and TS_4 into TS_2 and TS_1 
#Changing TS_2_1_1 and TS_2_2_1 into TS_3_0_1 & TS_3_05_1

CF3 <- CF3 %>% dplyr::select(-TS_1_1_1)
CF3 <- CF3 %>% dplyr::select(-TS_2_1_1)
CF3 <- CF3 %>% dplyr::select(-TS_2_2_1)


#Open water therms
names(CF3)[names(CF3) == "TS_3_1_1"] <- "TS_2_0_1"
names(CF3)[names(CF3) == "TS_3_2_1"] <- "TS_2_05_1"
names(CF3)[names(CF3) == "TS_3_3_1"] <- "TS_2_1_1"
names(CF3)[names(CF3) == "TS_3_4_1"] <- "TS_2_2_1"
names(CF3)[names(CF3) == "TS_3_5_1"] <- "TS_2_3_1"
names(CF3)[names(CF3) == "TS_3_6_1"] <- "TS_2_4_1"
names(CF3)[names(CF3) == "TS_3_7_1"] <- "TS_2_5_1"
names(CF3)[names(CF3) == "TS_3_8_1"] <- "TS_2_6_1"
names(CF3)[names(CF3) == "TS_3_9_1"] <- "TS_2_7_1"
names(CF3)[names(CF3) == "TS_3_10_1"] <- "TS_2_8_1"
names(CF3)[names(CF3) == "TS_3_11_1"] <- "TS_2_9_1"
names(CF3)[names(CF3) == "TS_3_12_1"] <- "TS_2_10_1"

names(CF3)[names(CF3) == "TS_4_1_1"] <- "TS_1_0_1"
names(CF3)[names(CF3) == "TS_4_2_1"] <- "TS_1_05_1"
names(CF3)[names(CF3) == "TS_4_3_1"] <- "TS_1_1_1"
names(CF3)[names(CF3) == "TS_4_4_1"] <- "TS_1_2_1"
names(CF3)[names(CF3) == "TS_4_5_1"] <- "TS_1_3_1"
names(CF3)[names(CF3) == "TS_4_6_1"] <- "TS_1_4_1"
names(CF3)[names(CF3) == "TS_4_7_1"] <- "TS_1_5_1"
names(CF3)[names(CF3) == "TS_4_8_1"] <- "TS_1_6_1"
names(CF3)[names(CF3) == "TS_4_9_1"] <- "TS_1_7_1"
names(CF3)[names(CF3) == "TS_4_10_1"] <- "TS_1_8_1"
names(CF3)[names(CF3) == "TS_4_11_1"] <- "TS_1_9_1"
names(CF3)[names(CF3) == "TS_4_12_1"] <- "TS_1_10_1"


```
## Merge
```{r}

#Merge
merged_df = rbind.fill(CF1,CF2,CF3)

merged_df$DOY = yday(merged_df$date)

merged_df$year = substr(merged_df$date,1,4)


```

# Daily Average
```{r}

avg = timeAverage(
  merged_df,
  avg.time = 'day',
  data.thresh = 40,
  statistic = 'mean',
  fill = TRUE
)


df = timeAverage(
  CF3,
  avg.time = 'day',
  data.thresh = 40,
  statistic = 'mean',
  fill = TRUE
)


```
## time separations 
```{r}
avg$year = substr(avg$date,1,4)
avg$year <- factor(avg$year)

avg$DOY = yday(avg$date)
avg$DOY <- as.numeric(avg$DOY)

df$year = substr(df$date,1,4)
df$year <- factor(df$year)

df$DOY = yday(df$date)
df$DOY <- as.numeric(df$DOY)

df$month = as.numeric(format(df$ts,'%m'))


```


# Raster Column (Not going to work right now because I removed the date column)
format is |Date|SoilT|SoilDepth|
```{r}

dfnew = df
dfnew$TS_2_0_1 = dfnew$TS_2_05_1


ras <- dfnew[,c('date',
            'TS_2_0_1', 
            'TS_2_1_1', 
            'TS_2_2_1', 
            'TS_2_3_1',
            'TS_2_4_1',
            'TS_2_5_1', 
            'TS_2_6_1', 
            'TS_2_7_1', 
            'TS_2_8_1',
            'TS_2_9_1')]


# Reshape the data into long format
ras <- ras %>%
  pivot_longer(
    cols = -date, 
    names_to = "SoilDepth",
    values_to = "SoilTemperature",
    names_pattern = "TS_2_(\\d+)_1" 
  ) %>%
  mutate(SoilDepth = as.numeric(gsub("TS_2_", "", SoilDepth)) * 10) 

# Extract Date from column
ras$date <- as.Date(ras$date)

ras <- ras %>%
  filter(date >= as.Date("2023-01-01") & date <= as.Date("2023-12-31"))
# Select and reorder columns
ras <- ras %>%
  dplyr::select(date, SoilDepth, SoilTemperature)


library(viridis)

ggplot(ras, aes(x = date, y = SoilDepth, fill = SoilTemperature)) +
  geom_raster(interpolate = TRUE)+
  scale_fill_viridis(option = "turbo") +  
  labs(x = "Date", y = "Soil Depth", fill = "Soil Temperature") +
  scale_y_reverse() +  # Invert the y-axis
  theme_minimal()

ras_plot = ggplot(ras, aes(x = date, y = SoilDepth, fill = SoilTemperature))+
  geom_raster(interpolate = TRUE) +
  scale_fill_viridis(option = "turbo") +  
  labs(x = "Date", y = "Soil Depth (cm)", fill = "Soil Temperature") +
  scale_x_date(expand = expansion(c(0, 0.00413))) + 
  scale_y_reverse(expand = expansion(c(0, 0))) +  # Invert the y-axis
  theme(
    axis.text.x = element_text(size = 16),   
    axis.text.y = element_text(size = 16),  
    axis.title.y = element_text(size = 18), 
    axis.title.x = element_text(size = 18),
    legend.title = element_text(size = 18), 
    legend.text = element_text(size = 14),
    legend.key.size = unit(1.5, "cm"),
  )

ras_plot

ggsave('C:/Permafrost Pathways/ras_plot.png', ras_plot, width = 9, height = 4.5)
```
removing date bc of conflict with ts column 
```{r}

df <- df %>% select(-date)
```
# Graphs
## multi-year annual plot (rough)
```{r,warning = FALSE}

ggplot(data = avg)+theme_bw()+
  geom_point(aes(DOY,FCH4,color = year))+
  geom_hline(yintercept = 0)+
  scale_x_continuous(limits = c(110,340))+
  scale_y_continuous (expression('CH4 Flux ('*n*mol~m^-2~s^-1*')'),
                      limits = c(-10,150))+
  labs(color='Year')
```
# Met Timeseries
```{r}
#Soil T
st5 = ggplot(data = df)+theme_bw()+
  geom_point(aes(ts,FCH4),color = "salmon",pch=20,size = 2,alpha=0.75)+
  geom_line(aes(x = ts, y = TS_2_05_1*5), color = '#087d94',size = .6) + 
  geom_smooth(aes(x = ts, y = FCH4), color = "salmon", method = 'loess',span = 0.09,size = .7)+  
  geom_hline(yintercept = 0)+
  scale_y_continuous (expression('CH'[4]~'Flux ('*n*mol~m^-2~s^-1*')'),
                      limits = c(-70,100),
  sec.axis = sec_axis(~./5, name = "Soil Temperature 5cm (°C)")
  ) +
  scale_x_datetime(limits = as.POSIXct(c('2023-01-1', '2023-12-31')))+
  labs(x = NULL)+
  theme(
    axis.text.x = element_text(size = 16),   
    axis.text.y = element_text(size = 16),  
    axis.title.y = element_text(size = 18) 
  )
st5
#SWC
swc = ggplot(data = df)+theme_bw()+
  geom_point(aes(ts,FCH4),color = "salmon",pch=20,size = 2,alpha=0.75)+
  geom_line(aes(x = ts, y = SWC_2_1_1), color = '#087d94',size = .6) + 
  geom_smooth(aes(x = ts, y = FCH4), color = "salmon", method = 'loess',span = 0.09,size = .7)+  
  geom_hline(yintercept = 0)+
  scale_y_continuous (expression('CH'[4]~'Flux ('*n*mol~m^-2~s^-1*')'),
                      limits = c(-5,100),
  sec.axis = sec_axis(~., name = "Volumetric Water Content (%)")
  ) +
  scale_x_datetime(limits = as.POSIXct(c('2023-01-1', '2023-12-31')))+
  labs(x = NULL)+
  theme(
    axis.text.x = element_text(size = 16),   
    axis.text.y = element_text(size = 16),  
    axis.title.y = element_text(size = 18) 
  )

#Rain
rain = ggplot(data = df)+theme_bw()+
  geom_point(aes(ts,FCH4),color = "salmon",pch=20,size = 2,alpha=0.75)+
  geom_smooth(aes(x = ts, y = FCH4), color = "salmon", method = 'loess',span = 0.09,size = .7)+  
  geom_bar(aes(x = ts, y = P * 48 * 2), stat = "identity", fill = '#087d94', alpha = 0.8) +
  geom_hline(yintercept = 0)+
  scale_y_continuous (expression('CH'[4]~'Flux ('*n*mol~m^-2~s^-1*')'),
                      limits = c(-5,100),
  sec.axis = sec_axis(~./2, name = "Precip (mm)")
  )+
  scale_x_datetime(limits = as.POSIXct(c('2023-01-1', '2023-12-31')))+
  labs(x = NULL)+
  theme(
    axis.text.x = element_text(size = 16),   
    axis.text.y = element_text(size = 16),  
    axis.title.y = element_text(size = 18) 
  )

#GPP
GPP = ggplot(data = df)+theme_bw()+
  geom_point(aes(ts,FCH4),color = "salmon",pch=20,size = 2,alpha=0.75)+
  geom_smooth(aes(x = ts, y = FCH4), color = "salmon", method = 'loess',span = 0.09,size = .7)+  
  geom_line(aes(x = ts, y = GPP_F*30), color = '#087d94',size = .6) + 
  geom_hline(yintercept = 0)+
  scale_y_continuous (expression('CH'[4]~'Flux ('*n*mol~m^-2~s^-1*')'),
                      limits = c(-5,100),
  sec.axis = sec_axis(~./30, name = 'GPP ('*u*mol~m^-2~s^-1*')')
  )+
  scale_x_datetime(limits = as.POSIXct(c('2023-01-1', '2023-12-31')))+
  labs(x = NULL) +
  theme(
    axis.text.x = element_text(size = 16),   
    axis.text.y = element_text(size = 16),  
    axis.title.y = element_text(size = 18) 
  )
  

GPP
combined_plot <- plot_grid(st5, swc, GPP, ncol = 1)
print(combined_plot)

ggsave('C:/Permafrost Pathways/combined_plot.png', combined_plot, width = 16, height = 12)
```


# NA DF
```{r}

NAdf <- na.omit(df[, c("ts","FCH4", "TS_2_05_1", "SWC_2_1_1", "GPP_F")])
```



# Model Runs

## LM Runs 0, 5, 10 cm
```{r}
#0 cm (R-squared 0.73)
TS0logCH4 = lm(log10(FCH4+5)~TS_1_0_1,data = df)
summary((TS0logCH4))


#5cm (R-squared 0.76) with NAdf and non-NAdf, all is the same
TS5logCH4 = lm(log10(FCH4+5)~TS_2_05_1,data = NAdf)
summary((TS5logCH4))


TS5logCH4 = lm(log10(FCH4+5)~TS_2_05_1,data = df)
summary((TS5logCH4))



#5cm (R-squared 0.72)
TS10logCH4 = lm(log10(FCH4+5)~TS_2_1_1,data = df)
summary((TS10logCH4))

#TA (R-squared 0.72)
TAlogCH4 = lm(log10(FCH4+5)~TA,data = df)
summary((TAlogCH4))


```

## Trendline 0 cm
```{r}
# Define the exponential trend function
exponential_trend_0 <- function(x) {
  10^(1.20111 + 0.04328664 * x) - 5
}

# Determine the number of rows in your original dataframe df
num_rows_df <- nrow(df)

# Create the new dataframe with the same number of rows as df, removing NA values
new_data <- data.frame(TS_1_0_1 = seq(min(na.omit(df$TS_1_0_1)), max(na.omit(df$TS_1_0_1)), length.out = num_rows_df))
new_data$predicted <- exponential_trend_0(new_data$TS_1_0_1)


#na.omit(df$TS_2_05_1) removes NA values from the TS_2_05_1 column of your dataframe df, returning a vector containing only the non-NA values.

#min() and max() functions are then applied to this vector to calculate the minimum and maximum values of TS_2_05_1 while ignoring NA values.

#The length.out argument in seq() ensures that the sequence has the same length as the filtered TS_2_05_1 values, thus addressing the issue of mismatched row numbers.
```
## 0 cm hysteresis graph
```{r}


cm_0 = ggplot(data = df) +
  theme_bw() +
  geom_point(aes(x = TS_1_0_1, y = FCH4, fill = month), pch = 21, size = 5, alpha = 0.75) +
  geom_hline(yintercept = 0) +
  geom_line(aes(x = TS_1_0_1, y = exponential_trend_0(TS_1_0_1)), color = "black", size = 1.45) +
 scale_y_continuous(expression('CH'[4]~'Flux (' * n * mol ~ m^-2 ~ s^-1 * ')'),
                     limits = c(-8, 150)) +
  scale_x_continuous(expression('Surface Temperature (°C)'),
                     limits = c(-15, 20)) +
  labs(color = 'DOY') +
  theme(legend.position = "none")+
  scale_fill_gradientn(colours = (brewer.pal(9, 'GnBu')))+
  theme(
    axis.text.x = element_text(size = 20),   
    axis.text.y = element_text(size = 20),  
    axis.title.y = element_text(size = 22),  
    axis.title.x = element_text(size = 22),
  )
cm_0
```
## Trendline 5 cm
```{r}
# Define the exponential trend function
exponential_trend_5 <- function(x) {
  10^(1.155294 + 0.0502205 * x) - 5
}

# Determine the number of rows in your original dataframe df
num_rows_df <- nrow(df)

# Create the new dataframe with the same number of rows as df, removing NA values
new_data <- data.frame(TS_2_05_1 = seq(min(na.omit(df$TS_2_05_1)), max(na.omit(df$TS_2_05_1)), length.out = num_rows_df))
new_data$predicted <- exponential_trend_5(new_data$TS_2_05_1)


#na.omit(df$TS_2_05_1) removes NA values from the TS_2_05_1 column of your dataframe df, returning a vector containing only the non-NA values.

#min() and max() functions are then applied to this vector to calculate the minimum and maximum values of TS_2_05_1 while ignoring NA values.

#The length.out argument in seq() ensures that the sequence has the same length as the filtered TS_2_05_1 values, thus addressing the issue of mismatched row numbers.
```
## 5 cm hysteresis graph
```{r}


cm_5 = ggplot(data = df) +
  theme_bw() +
  geom_point(aes(x = TS_2_05_1, y = FCH4, fill = month), pch = 21, size = 5, alpha = 0.75) +
  geom_hline(yintercept = 0) +
  geom_line(aes(x = TS_2_05_1, y = exponential_trend_5(TS_2_05_1)), color = "black", size = 1.45) +
 scale_y_continuous(expression('CH'[4]~'Flux (' * n * mol ~ m^-2 ~ s^-1 * ')'),
                     limits = c(-8, 150)) +
  scale_x_continuous(expression('Temperature 5 cm (°C)'),
                     limits = c(-15, 18)) +
  labs(color = 'DOY') +
  theme(legend.position = "none")+
  scale_fill_gradientn(colours = brewer.pal(9, 'GnBu'))+
  theme(
    axis.text.x = element_text(size = 20),   
    axis.text.y = element_text(size = 20),  
    axis.title.y = element_text(size = 22),  
    axis.title.x = element_text(size = 22),
  )
cm_5
```


## Trendline 10 cm
```{r}
# Define the exponential trend function
exponential_trend_10 <- function(x) {
  10^(1.172676 + 0.05492273 * x) - 5
}

# Determine the number of rows in your original dataframe df
num_rows_df <- nrow(df)

# Create the new dataframe with the same number of rows as df, removing NA values
new_data <- data.frame(TS_2_1_1 = seq(min(na.omit(df$TS_2_1_1)), max(na.omit(df$TS_2_1_1)), length.out = num_rows_df))
new_data$predicted <- exponential_trend_10(new_data$TS_2_1_1)


#na.omit(df$TS_2_05_1) removes NA values from the TS_2_05_1 column of your dataframe df, returning a vector containing only the non-NA values.

#min() and max() functions are then applied to this vector to calculate the minimum and maximum values of TS_2_05_1 while ignoring NA values.

#The length.out argument in seq() ensures that the sequence has the same length as the filtered TS_2_05_1 values, thus addressing the issue of mismatched row numbers.
```
## 10 cm hysteresis graph
```{r}


cm_10 = ggplot(data = df) +
  theme_bw() +
  geom_point(aes(x = TS_2_1_1, y = FCH4, fill = month), pch = 21, size = 5, alpha = 0.75) +
  geom_hline(yintercept = 0) +
  geom_line(aes(x = TS_2_1_1, y = exponential_trend_10(TS_2_1_1)), color = "black", size = 1.45) +
  scale_y_continuous(expression('CH'[4]~'Flux (' * n * mol ~ m^-2 ~ s^-1 * ')'),
                     limits = c(-8, 150)) +
  scale_x_continuous(expression(' Temperature 10 cm(°C)'),
                     limits = c(-15, 16)) +
  labs(color = 'DOY') +
  theme(legend.position = "none")+
  scale_fill_gradientn(colours = (brewer.pal(9, 'GnBu')))+
  theme(
    axis.text.x = element_text(size = 20),   
    axis.text.y = element_text(size = 20),  
    axis.title.y = element_text(size = 22),  
    axis.title.x = element_text(size = 22),
  )
cm_10
```

```{r}
hyst_plot <- plot_grid(cm_0, cm_5, cm_10, ncol = 1)

print(hyst_plot)


ggsave('C:/Permafrost Pathways/hyst_plot.png', hyst_plot, width = 16, height = 12)
```

## Residual Analysis (ST5)

```{r}

# NEED TO USE NA df for same variable lengths
TS5logCH4_residuals <- residuals(TS5logCH4)
# TS5 and VWC
TS5_VWC = lm(SWC_2_1_1~TS_2_05_1, data = NAdf)

TS5_VWC_residuals <- residuals(TS5_VWC)

PCOR_TS5_VWC <- lm(TS5logCH4_residuals ~ TS5_VWC_residuals)
summary(PCOR_TS5_VWC)
# TS5 and GPP
TS5_GPP = lm(GPP_F~TS_2_05_1, data = NAdf)

TS5_GPP_residuals <- residuals(TS5_GPP)

PCOR_TS5_GPP <- lm(TS5logCH4_residuals ~ TS5_GPP_residuals)
summary(PCOR_TS5_GPP)

hist(PCOR_TS5_GPP$residuals)
shapiro.test(PCOR_TS5_GPP$residuals)

plot(TS5logCH4_residuals,TS5_GPP_residuals)
```
#Re-insert residuals
#Spring Analysis
```{r}
# add log10(FCH4+5) residuals to NAdf data frame
NAdf$TS5logCH4_residuals = TS5logCH4_residuals

#create new NAdf for spring period only
spring = subset(NAdf, NAdf$ts >= '2023-5-3' & NAdf$ts <= '2023-6-14')

#summarize and visualize df
summary(spring$TS5logCH4_residuals)
hist(spring$TS5logCH4_residuals)

#re-insert residuals with correct formula 10^residuals +5
spring$regresid = (10^spring$TS5logCH4_residuals) +5 
hist(spring$regresid)
summary(spring$regresid)

# change units to mgC /day
spring$regresid_daily_mgc = spring$regresid*60*60*24/(10^6)*12
sum(spring$regresid_daily_mgc)

```

### p RESIDUAL
```{r}
# Model residuals with P
P_FCH4_residuals <- lm(TS5logCH4_residuals ~ LAGGED_P, data = NAdf)
summary(P_FCH4_residuals)
```






## LM 5 model
```{r, warning=FALSE}

# Extract the predicted log10(FCH4 + 5) values from the model
predicted_FCH4 <- predict(TS5logCH4)

# Exponentiate the predicted log10(FCH4 + 5) values to obtain predicted FCH4 values
p_FCH4 <- 10^predicted_FCH4 - 5

# Plot the predicted FCH4 values against the actual FCH4 values
plot(p_FCH4, pch = 16, col = "blue", xlab = "Actual FCH4", ylab = "Predicted FCH4", main = "Predicted vs Actual FCH4")




# Extract the subset of observations used for fitting the model
df_subset <- df[!is.na(df$TS_2_05_1), ]

# Predict CH4 values for the subset of observations
predicted_FCH4_subset <- 10^predict(TS5logCH4, newdata = df_subset) - 5

# Add the predicted CH4 values to your dataframe df_subset
df_subset$Predicted_CH4 <- predicted_FCH4_subset

# Merge the predicted CH4 values back to the original dataframe df
df <- merge(df, df_subset[, c("ts", "Predicted_CH4")], by = "ts", all.x = TRUE)

# Check the structure of your dataframe to confirm that the new column has been added
str(df)


plot(df$FCH4,df$Predicted_CH4)


ggplot(data = df) +
  theme_bw() +
  geom_point(aes(x = ts, y = FCH4, color = "Observed CH4"), alpha = 0.5) +
  geom_smooth(aes(x = ts, y = FCH4, color = "Observed CH4"), method = 'loess',span = 0.25)+
  geom_point(aes(x = ts, y = Predicted_CH4, color = "Predicted CH4"), alpha = 0.5) +
  geom_smooth(aes(x = ts, y = Predicted_CH4, color = "Predicted CH4"), method = 'loess',span = 0.25)+
  geom_hline(yintercept = 0) +
  scale_y_continuous(expression('CH4 Flux (' * n * mol ~ m^-2 ~ s^-1 * ')'), limits = c(-6, 135)) +
  scale_x_datetime(limits = as.POSIXct(c('2022-08-6', '2023-12-31'))) +
  labs(color = "CH4 Values") +
  scale_color_manual(values = c("Observed CH4" = "salmon", "Predicted CH4" = "blue")) +
  guides(color = guide_legend(title = "CH4 Values"))


ggplot(data = df) +
  theme_bw() +
  geom_point(aes(x = TS_2_05_1, y = FCH4, fill = month), pch = 21, size = 3, alpha = 0.75) +
  geom_hline(yintercept = 0) +
  geom_line(aes(x = TS_2_05_1, y = exponential_trend_5(TS_2_05_1)), color = "black", size = 1.3) +
  scale_y_continuous(expression('CH4 Flux (' * n * mol ~ m^-2 ~ s^-1 * ')'),
                     limits = c(-8, 150)) +
  scale_x_continuous(expression('Temperature 5 cm (°C)'),
                     limits = c(-15, 20)) +
  labs(color = 'DOY') +
  scale_fill_gradientn(colours = brewer.pal(9, 'Reds'))


ggplot(data = df) +
  theme_bw() +
  geom_point(aes(x = TS_2_1_1, y = FCH4, fill = month), pch = 21, size = 3, alpha = 0.75) +
  geom_hline(yintercept = 0) +
  geom_line(aes(x = TS_2_05_1, y = exponential_trend_5(TS_2_05_1)), color = "black", size = 1.3) +
  scale_y_continuous(expression('CH4 Flux (' * n * mol ~ m^-2 ~ s^-1 * ')'),
                     limits = c(-8, 150)) +
  scale_x_continuous(expression('Temperature 5 cm (°C)'),
                     limits = c(-15, 20)) +
  labs(color = 'DOY') +
  scale_fill_gradientn(colours = brewer.pal(9, 'Reds'))

ggplot(data = df) +
  theme_bw() +
  geom_point(aes(x = TS_1_0_1, y = FCH4, fill = month), pch = 21, size = 3, alpha = 0.75) +
  geom_hline(yintercept = 0) +
  geom_line(aes(x = TS_2_05_1, y = exponential_trend_5(TS_2_05_1)), color = "black", size = 1.3) +
  scale_y_continuous(expression('CH4 Flux (' * n * mol ~ m^-2 ~ s^-1 * ')'),
                     limits = c(-8, 150)) +
  scale_x_continuous(expression('Temperature 5 cm (°C)'),
                     limits = c(-15, 20)) +
  labs(color = 'DOY') +
  scale_fill_gradientn(colours = brewer.pal(9, 'Reds'))
```




## LM Runs GPP


```{r}
# Consider using ifelse statement for when there is real CO2 data available to have the more accurate data product

#GPP_DT (R-squared 0.66)
GPP_DTCH4 = lm(FCH4~GPP_DT,data = df)
summary((GPP_DTCH4))

#GPP_F (R-squared 0.76) (feels sketch using this bc gap-filled)
GPP_FCH4 = lm(FCH4~GPP_F,data = df)
summary((GPP_FCH4))



```



## Time lag 
```{r}
#Rain
ccf(df$P,df$FCH4, na.action = na.pass)
#Soil T
ccf(df$TS_2_05_1,df$FCH4, na.action = na.pass)
#VWC
ccf(df$SWC_2_1_1,df$FCH4, na.action = na.pass)
#GPP
ccf(df$GPP_F,df$FCH4, na.action = na.pass)

```



## Seasons breakdown 
Our onset of melt is DOY 126, theirs is 166
Our onset and their onset of fall is similar (DOY 305-315)
```{r}

```




# seasonal change
Fall (260-320) split down the middle with pre and post freeze
Spring (113-153) melt is: 123-132 few different endings
```{r,warning = FALSE}
ggplot(data = avg) +
  theme_bw() +
  geom_line(aes(x = ts, y = G_1_1_1), color = 'red') +  
  geom_line(aes(x = ts, y = TA*10), color = 'blue') +  
  geom_line(aes(x = ts, y = PPFD_OUT/10), color = 'green') +
  geom_line(aes(x = ts, y = D_SNOW), color = 'pink') +
  geom_vline(xintercept = as.POSIXct('2023-5-12'), linetype = 'dotdash')+
  geom_vline(xintercept = as.POSIXct('2023-5-3'), linetype = 'dotdash')+
  geom_hline(yintercept = 0) +
  scale_y_continuous(
    name = expression('CH4 Flux (' * n * mol ~ m^-2 ~ s^-1 * ')'),
    limits = c(-50, 200))+
  scale_x_datetime(limits = as.POSIXct(c('2023-4-20', '2023-6-16')))
 

ggplot(data = avg) +
  theme_bw() +
  geom_point(aes(x = ts, y = FCH4), color = 'salmon') +
  geom_line(aes(x = ts, y = TS_2_05_1*4), color = 'blue') +  
  geom_hline(yintercept = 0) +
  scale_y_continuous(
    name = expression('CH4 Flux (' * n * mol ~ m^-2 ~ s^-1 * ')'),
    limits = c(-50, 95),
    sec.axis = sec_axis(~./4, name = "Soil Temperature 10cm (°C)")
  ) +
  scale_x_datetime(limits = as.POSIXct(c('2022-09-17', '2022-11-16')))


ggplot(data = df) +
  theme_bw() +
  geom_point(aes(x = ts, y = FCH4), color = 'salmon') +
  geom_smooth(aes(x = ts, y = FCH4, color = "FCH4"), method = 'loess',span = 0.15)+
  geom_line(aes(x = ts, y = TS_2_05_1*4), color = 'blue') +  
  geom_vline(xintercept = as.POSIXct('2023-6-23'), linetype = 'dotted')+
  geom_hline(yintercept = 0) +
  scale_y_continuous(
    name = expression('CH4 Flux (' * n * mol ~ m^-2 ~ s^-1 * ')'),
    limits = c(-20, 95),
    sec.axis = sec_axis(~./4, name = "Soil Temperature 10cm (°C)")
  ) +
  scale_x_datetime(limits = as.POSIXct(c('2023-05-1', '2023-6-30')))
```
# Spring differences 
```{r,warning=FALSE}
ggplot(data = df) +
  theme_bw() +
  geom_point(aes(x = ts, y = FCH4_F*1000), color = 'salmon') +
  geom_point(aes(x = ts, y = Predicted_CH4), color = '#00BFC4') +
  geom_line(aes(x = ts, y = TS_2_05_1*5), color = 'blue') +  
  geom_line(aes(x = ts, y = TS_2_1_1*5), color = 'darkgreen') + 
  geom_line(aes(x = ts, y = TS_2_2_1*5), color = 'orange') + 
  geom_line(aes(x = ts, y = TS_2_3_1*5), color = 'red') + 
  geom_smooth(aes(x = ts, y = FCH4, color = "FCH4"), method = 'loess',span = 0.115)+
  geom_smooth(aes(x = ts, y = Predicted_CH4, color = "Log 5 CH4"), method = 'loess',span = 0.115)+
  geom_vline(xintercept = as.POSIXct('2023-4-23'))+
  geom_vline(xintercept = as.POSIXct('2023-5-12'), linetype = 'longdash')+
  geom_vline(xintercept = as.POSIXct('2023-5-3'), linetype = 'longdash')+
  geom_vline(xintercept = as.POSIXct('2023-6-15'))+
  geom_hline(yintercept = 0) +
  scale_y_continuous(
    name = expression('CH4 Flux (' * n * mol ~ m^-2 ~ s^-1 * ')'),
    limits = c(-25, 95),
    sec.axis = sec_axis(~./5, name = "Soil Temperature 10cm (°C)")
  ) +
  scale_x_datetime(limits = as.POSIXct(c('2023-04-11', '2023-7-14')))

```
# Winter comparison
```{r}
ggplot(data = df) +
  theme_bw() +
  geom_point(aes(x = ts, y = FCH4_F*1000), color = 'salmon') +
  geom_point(aes(x = ts, y = Predicted_CH4), color = '#00BFC4') +
  geom_smooth(aes(x = ts, y = FCH4, color = "FCH4"), method = 'loess',span = 0.115)+
  geom_smooth(aes(x = ts, y = Predicted_CH4, color = "Log 5 CH4"), method = 'loess',span = 0.115)+
  geom_vline(xintercept = as.POSIXct('2023-4-23'))+
  geom_vline(xintercept = as.POSIXct('2023-5-12'), linetype = 'longdash')+
  geom_vline(xintercept = as.POSIXct('2023-5-3'), linetype = 'longdash')+
  geom_vline(xintercept = as.POSIXct('2023-6-15'))+
  geom_vline(xintercept = as.POSIXct('2023-6-23'), linetype = 'dotted')+
  geom_hline(yintercept = 0) +
  scale_y_continuous(
    name = expression('CH4 Flux (' * n * mol ~ m^-2 ~ s^-1 * ')'),
    limits = c(-25, 15),
    sec.axis = sec_axis(~./5, name = "Soil Temperature 10cm (°C)")
  ) +
  scale_x_datetime(limits = as.POSIXct(c('2023-01-1', '2023-4-30')))
```

# Spring pulse removed model

```{r}
#create new variable removing spring pulse in DF
df$FCH4_no_spring = df$FCH4
df$FCH4_no_spring = ifelse(df$ts >= '2023-5-3' & df$ts <= '2023-6-14' ,NA, df$FCH4_no_spring)

#linear model with no spring (R^2 = 0.80)
no_spring_TS5logCH4 = lm(log10(FCH4_no_spring+5)~TS_2_05_1,data = df)
summary(no_spring_TS5logCH4)
```


## Separations and plots
Spring will start at the onset of melt (5/3 DOY 124)
```{r}

df23 = df

df23 <- df23 %>%
  filter(ts >= as.POSIXct("2023-01-01") & ts <= as.POSIXct("2023-12-31"))


df23 <- df23 %>%
  mutate(
      season = case_when(
      (DOY >= 260 & DOY <= 320) ~ 'Zero Curtain', # 61 days
      (DOY >= 124 & DOY <= 166) ~ 'Initial Thaw', # 43 days
      (DOY >= 167 & DOY <= 259) ~ 'Growing Season', # 93 days
      (DOY >= 321 | DOY <= 123) ~ 'Frozen', # 168 days    #Math is weird here
      TRUE ~ NA_character_
    )
  ) %>%
  filter(year == 2023)
    

seconds_in_a_day <- 86400  # 24 hours * 60 minutes * 60 seconds

seasonal_cumulative <- df23 %>%
  group_by(season) %>%
  summarize(
    cumulative_FCH_F = sum((FCH4_F), na.rm = TRUE)*1000*0.01604*seconds_in_a_day/1e6,
    cumulative_Predicted_CH4 = sum(Predicted_CH4, na.rm = TRUE)*0.01604*seconds_in_a_day/1e6
  )

print(seasonal_cumulative)

# these values are now in g/m^-2,day^-1
```

```{r}

# Reshape the data for plotting
days_in_season <- data.frame(
  season = c("Zero Curtain", "Initial Thaw", "Growing Season", "Frozen"),
  days = c(61, 43, 93, 168)
)

seasonal_cumulative_long <- seasonal_cumulative %>%
  pivot_longer(
    cols = c(cumulative_FCH_F, cumulative_Predicted_CH4), 
    names_to = "Data", 
    values_to = "cumulative_value"
  ) %>%
  mutate(
    Data = recode(
      Data,
      "cumulative_FCH_F" = "Gap-Filled",
      "cumulative_Predicted_CH4" = "Soil T Model"
    )
  )%>%
  left_join(days_in_season, by = "season") %>%
  mutate(
    cumulative_value_per_season = cumulative_value * days
  )



# Create the bar chart
# Daily 
daily_bar = ggplot(seasonal_cumulative_long, aes(x = season, y = cumulative_value, fill = Data)) + theme_bw()+
  geom_hline(yintercept = 0)+
  geom_bar(stat = "identity", position = "dodge") +
  labs(
    x = "Season", 
    y = expression('Cumulative Daily Flux (g CH'[4] ~ m^-2 ~ day^-1))
daily_bar

ggsave('C:/Permafrost Pathways/daily_bar.png', daily_bar, width = 8, height = 5)

#Season
seasonal_bar = ggplot(seasonal_cumulative_long, aes(x = season, y = cumulative_value_per_season, fill = Data)) + theme_bw()+
  geom_hline(yintercept = 0)+
  geom_bar(stat = "identity", position = "dodge") +
  labs(
    x = "Season", 
    y = expression('Cumulative Seasonal Flux (g CH'[4] ~ m^-2 ~ season^-1))
seasonal_bar

ggsave('C:/Permafrost Pathways/seasonal_bar.png', seasonal_bar, width = 8, height = 5)

```

```{r}


```












