---
title: "Churchill CO2 Data Analysis"
author: "Dani Trangmoe"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# add root directory here for github
```

Notes:






```{r, include=FALSE}
rm(list = ls())

library(data.table)
library(ggplot2)
library(cowplot)
library(openair)
library(plotrix)
library(signal)
library(svMisc)
library(zoo)
library(stringr)
library(plyr)
library(viridis)
library(lubridate)
library(tidyverse)
library(gridExtra)
library(plotly)
library(RColorBrewer)
library(pracma)
```


To-Do:

Link files to Google Drive

Differentiate temp. controlled peak and non-temperature controlled

Make plots show up in script




# Load data
```{r}

df = fread('C:/Users/dtrangmoe/Documents/Churchill/Churchill_Merged_CF1_CF3.csv',na.strings = c('-9999','NA','NaN','NAN','-7999'))

#needs continuous day variable
df_avg = fread('C:/Users/dtrangmoe/Documents/Churchill/Churchill_Merged_Avg_CF1_CF3.csv',na.strings = c('-9999','NA','NaN','NAN','-7999'))


```

#### Create yearly dataframes, timestamp

```{r}
#create TIMESTAMP variable that is = to TIMESTAMP_END

df$TIMESTAMP = df$TIMESTAMP_END

year_df <- function(df, year) {
  df %>%
    filter(format(day, "%Y") == as.character(year)) %>%
    mutate(DOY = yday(day))
}


#Creates data frames of each year containing the daily averages of each value- useful for focusing on one year at a time

df_avg$day <- as.POSIXct(df_avg$day, format = "%Y-%m-%d")


df_avg_2007 <- year_df(df_avg, 2007)
df_avg_2008 <- year_df(df_avg, 2008)
df_avg_2022 <- year_df(df_avg, 2022)
df_avg_2023 <- year_df(df_avg, 2023)

df_2023 <- year_df(df, 2023)


```


### Date ranges for plots

Adjust dates here!

```{r}
dates_07 = c('2007-06-19','2007-10-07')

dates_08 = c('2008-06-19','2008-10-07')

dates_22 = c('2022-08-10','2022-12-01')

dates_23 = c('2023-01-01','2023-12-01')
```



# Gap Filling Plots

Shows gap in flux data and compares gap filled and non-gap filled data

```{r}

#Uses Half-Hourly data

ggplot(data = df_2023)+
  geom_hline(yintercept = 0)+
  geom_point(aes(TIMESTAMP,FC_F,col='Gapfilled'))+
  geom_point(aes(TIMESTAMP,FC,col='Original'))+
  scale_y_continuous(limits=c(-6,6))+
  scale_x_datetime(limits = as.POSIXct(dates_23,format="%F"))+
  labs(y = "CO2 Flux", x = "Time") +
  scale_color_manual(values=c('red','black'))+
  geom_vline(xintercept = as.POSIXct("07-05-2023"))


# Uses daily averages

ggplot(data = df_avg_2023)+geom_hline(yintercept = 0)+
  geom_point(aes(day,FC_F,col='Gapfilled'))+
  geom_point(aes(day,FC,col='Original'))+
  scale_y_continuous(limits=c(-2.5,2.5))+
  scale_x_datetime(limits = as.POSIXct(dates_23,format="%F"))+
  scale_color_manual(values=c('red','black'))

```



# Definition of Seasons

Uses ratio of par in/out, soil heat flux data, snow depth, air temp to identify seasonal periods

```{r}

# last period of the growing season is senescence, analyze with growing season


#need key here on graph

ggplot(data = df_avg_2023) +
  theme_bw() +
  geom_line(aes(x = DOY, y = TS_1_2_1), color = 'red') +
  geom_line(aes(x = DOY, y = TA), color = 'blue') +
  geom_line(aes(x = DOY, y = (PPFD_OUT*20) / PPFD_IN), color = 'green') +
  geom_line(aes(x = DOY, y = D_SNOW/2), color = 'purple') +
  geom_line(aes(x = DOY, y = (FC_F*15)), color = 'black') +
  scale_y_continuous(name = expression('Biomet Vars & FC'), limits = ) +
  geom_vline(xintercept = 112)+
  geom_vline(xintercept = 135)+
  geom_vline(xintercept = 295)+
  geom_vline(xintercept = 325)+
  scale_x_discrete(limits = c(0, 366))


# Defines seasons in 2023 dataframes using a column of character values

# Daily Average dataframe

df_avg_2023 <- df_avg_2023 %>%
  mutate(
      season = case_when(
      (DOY >= 295 & DOY <= 325) ~ 'Zero curtain',
      (DOY >= 113 & DOY <= 135) ~ 'Snow Melt',
      (DOY >= 136 & DOY <= 294) ~ 'Growing Season',
      (DOY >= 326 | DOY <= 112) ~ 'Winter',
      TRUE ~ NA_character_
    )
  )
    
seasonal_cumulative <- df_avg_2023 %>%
  group_by(season) %>%
  summarize(
    cumulative_FC_F = sum(FC_F, na.rm = TRUE)
  )

print(seasonal_cumulative)

# # Returns:
# 1 Growing Season          -22.9 
# 2 Snow Melt                 3.83
# 3 Winter                    4.39
# 4 Zero curtain              2.90


# Half-Hourly dataframe 

df_2023 <- df_2023 %>%
  mutate(
      season = case_when(
      (DOY >= 295 & DOY <= 325) ~ 'Zero curtain',
      (DOY >= 113 & DOY <= 135) ~ 'Snow Melt',
      (DOY >= 136 & DOY <= 294) ~ 'Growing Season',
      (DOY >= 326 | DOY <= 112) ~ 'Winter',
      TRUE ~ NA_character_
    )
  )


seasonal_cumulative2 <- df_2023 %>%
  group_by(season) %>%
  summarize(
    cumulative_FC_F = sum(FC_F, na.rm = TRUE)
  )

print(seasonal_cumulative2)

# # Returns:
# 1 Growing Season          -1098
# 2 Snow Melt                 184
# 3 Winter                    210
# 4 Zero curtain              139

```




# 2023 Seasonal Integrals


## NEE

Finds the net CO2 exchange of each season as defined above
```{r}

seasonal_integrals <- function(df) {
  
  # Calculate integral (sum) for each season
  integrals <- df %>%
    group_by(season) %>%
    summarise(integral_value = round(sum(FC_F, na.rm = TRUE), 2)) %>%
    ungroup() %>%
    arrange(season)
  
  return(integrals)
}

seasonal_integrals_2023 <- seasonal_integrals(df_avg_2023)

ggplot(seasonal_integrals_2023, aes(x = season, y = integral_value)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(
    x = "Season",
    y = "Net CO2 Flux",
    title = "2023 CO2 Flux by season"
  ) +
  theme_minimal()+
  geom_text(aes(label = integral_value), vjust = 1, colour = "black")



# Bar graph showing growing season vs. year round analysis



```

### Growing Season vs. Full Year

Compares the NEE of growing-season only site and our year round data

```{r}



```



## GPP

Finds the net GPP of each season

```{r}

seasonal_integrals <- function(df) {
  
  # Calculate integral (sum) for each season
  integrals <- df %>%
    group_by(season) %>% summarise(integral_value = round(sum(GPP_F, na.rm = TRUE), 2)) %>%
    ungroup() %>%
    arrange(season)
  
  return(integrals)
}

seasonal_integrals_2023 <- seasonal_integrals(df_avg_2023)

ggplot(seasonal_integrals_2023, aes(x = season, y = integral_value)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(
    x = "Season",
    y = "Net GPP",
    title = "2023 GPP by season"
  ) +
  theme_minimal()+
  geom_text(aes(label = integral_value), vjust = 1, colour = "magenta")



# Bar graph showing growing season vs. year round analysis



```





## RECO
```{r}

seasonal_integrals <- function(df) {
  
  # Calculate integral (sum) for each season
  integrals <- df %>%
    group_by(season) %>%
    summarise(integral_value = round(sum(RECO, na.rm = TRUE), 2)) %>%
    ungroup() %>%
    arrange(season)
  
  return(integrals)
}

seasonal_integrals_2023 <- seasonal_integrals(df_avg_2023)

ggplot(seasonal_integrals_2023, aes(x = season, y = integral_value)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(
    x = "Season",
    y = "Net ER",
    title = "2023 ER by season"
  ) +
  theme_minimal()+
  geom_text(aes(label = integral_value), vjust = 1, colour = "orange")



# Bar graph showing growing season vs. year round analysis



```



# Year long Integrals

Gets net emissions from given yr
could change this to use half-hourly data? 
could create function here instead of copy/paste in future


#### 2007
```{r}

df_avg_2007 <- df_avg %>%
  subset(format(day, "%Y") == "2007") %>%
  mutate(day_as_POSIXct = as.POSIXct(day)) %>%
  mutate(DOY = as.numeric(format(day_as_POSIXct, "%j"))) %>%
  subset(select = -c(day_as_POSIXct)) %>%
  mutate(FC_F_no_NAs = ifelse(is.na(FC_F), 0, FC_F)) %>%
  mutate(cumulative = cumtrapz(DOY, FC_F_no_NAs))


trapz(df_avg_2007$DOY, df_avg_2007$FC_F_no_NAs)
#returns 10.71887
                           
ggplot(data = df_avg_2007, aes(x=DOY, y=cumulative))+
  geom_point()+
  scale_x_continuous(lim = c(160, 290))+
  geom_hline(yintercept=0, col="blue")+
  scale_y_continuous(expression('Cumulative NEE ('*m*mol~m^-2~s^-1*')'))

```


#### 2008
```{r}

df_avg_2008 <- df_avg %>%
  subset(format(day, "%Y") == "2008") %>%
  mutate(day_as_POSIXct = as.POSIXct(day)) %>%
  mutate(DOY = as.numeric(format(day_as_POSIXct, "%j"))) %>%
  subset(select = -c(day_as_POSIXct)) %>%
  mutate(FC_F_no_NAs = ifelse(is.na(FC_F), 0, FC_F)) %>%
  mutate(cumulative = cumtrapz(DOY, FC_F_no_NAs))

trapz(df_avg_2008$DOY, df_avg_2008$FC_F_no_NAs)
#returns 46.96865

ggplot(data = df_avg_2008, aes(x=DOY, y=cumulative))+
  geom_point()+
  scale_x_continuous(lim = c(160, 290))+
  geom_hline(yintercept=0, col="blue")+
  scale_y_continuous(expression('Cumulative NEE ('*m*mol~m^-2~s^-1*')'))

```


#### 2022
```{r}
#incomplete year - need continuous day var in avg df

df_avg_2022 <- df_avg %>%
  subset(format(day, "%Y") == "2022") %>%
  mutate(day_as_POSIXct = as.POSIXct(day)) %>%
  mutate(DOY = as.numeric(format(day_as_POSIXct, "%j"))) %>%
  subset(select = -c(day_as_POSIXct)) %>%
  mutate(FC_F_no_NAs = ifelse(is.na(FC_F), 0, FC_F)) %>%
  mutate(cumulative = cumtrapz(DOY, FC_F_no_NAs))

trapz(df_avg_2022$DOY, df_avg_2022$FC_F_no_NAs)
#returns -17.67401

ggplot(data = df_avg_2022, aes(x=DOY, y=cumulative))+
  geom_point()+
  scale_x_continuous(lim = c(160, 290))+
  geom_hline(yintercept=0, col="blue")+
  scale_y_continuous(expression('Cumulative NEE ('*m*mol~m^-2~s^-1*')'))

```


#### 2023

Add GPP and RECO plots here?

```{r}

df_avg_2023 <- df_avg_2023 %>%
  subset(format(day, "%Y") == "2023") %>%
  mutate(day_as_POSIXct = as.POSIXct(day)) %>%
  mutate(DOY = as.numeric(format(day_as_POSIXct, "%j"))) %>%
  subset(select = -c(day_as_POSIXct)) %>%
  mutate(FC_F_no_NAs = ifelse(is.na(FC_F), 0, FC_F)) %>%
  mutate(cumulative = cumtrapz(DOY, FC_F_no_NAs))

trapz(df_avg_2023$DOY, df_avg_2023$FC_F)
#returns -11.81368

ggplot(data = df_avg_2023, aes(x=DOY, y=cumulative, color = season))+
  geom_point()+
  scale_x_continuous(lim = c(0, 365))+
  geom_hline(yintercept=0, col="black")+ 
  scale_y_continuous(expression('Cumulative NEE ('*m*mol~m^-2~s^-1*')'))
  

```



### GPP & ER

```{r}

ggplot(data = df_avg_2007, aes(x=DOY))+
  geom_point(aes(y = GPP_F, color = "GPP")) +
  geom_point(aes(y = RECO, color = "ER")) +
  geom_hline(yintercept=0, col="black")+
  scale_y_continuous(expression('CO'[2] * '('*m*mol~m^-2~s^-1*')'))+ labs(title = "2007 GPP & ER")

ggplot(data = df_avg_2008, aes(x=DOY))+
  geom_point(aes(y = GPP_F, color = "GPP")) +
  geom_point(aes(y = RECO, color = "ER")) +
  geom_hline(yintercept=0, col="black")+
  scale_y_continuous(expression('CO'[2] * '('*m*mol~m^-2~s^-1*')'))+ labs(title = "2008 GPP & ER")

ggplot(data = df_avg_2022, aes(x=DOY))+
  geom_point(aes(y = GPP_F, color = "GPP")) +
  geom_point(aes(y = RECO, color = "ER")) +
  geom_hline(yintercept=0, col="black")+
  scale_y_continuous(expression('CO'[2] * '('*m*mol~m^-2~s^-1*')'))+ labs(title = "2022 GPP & ER")

ggplot(data = df_avg_2023, aes(x=DOY))+
  geom_point(aes(y = GPP_F, color = "GPP")) +
  geom_point(aes(y = RECO, color = "ER")) +
  geom_hline(yintercept=0, col="black")+
  scale_y_continuous(expression('CO'[2] * '('*m*mol~m^-2~s^-1*')'))+ labs(title = "2023 GPP & ER")

```




# Analysis of Controls

## Energy Balance
```{r}

energy_balance <- function(df) {
  
  # Create the plot
  df$Met <- df$NETRAD
  
  df$Flux <- df$LE + df$H
  
  plot <- ggplot(data = df, aes(x = Met, y = Flux))+ 
    geom_point()+
    geom_abline(slope=1, intercept=0, colour = "red")+
  scale_x_continuous(lim = c(-100, 600))+
  scale_y_continuous(lim = c(-100, 600))
  
  return(plot)
}

eb07 <- energy_balance(df_avg_2007)
eb08 <- energy_balance(df_avg_2008)
eb22 <- energy_balance(df_avg_2022)
eb23 <- energy_balance(df_avg_2023)

grid.arrange(eb07, eb08, eb22, eb23, nrow=2, ncol=2)



```



## Biomet variable plots

Used to figure out what data is included for each year, not for analysis

``` {r, warning=FALSE}

ggplot(df, aes_string(x = "TIMESTAMP_END", y = "FC_F"))+
    theme_bw()+
    geom_point()+
    scale_x_datetime(name = 'Date')+
    scale_y_continuous(name = CO2)

#only soil heat flux in CF3 dataset
ggplot(df, aes_string(x = "TIMESTAMP_END", y = "G_1_1_1"))+
    theme_bw()+
    geom_point()+
  geom_vline(aes(xintercept= as.POSIXct("2023-05-14")))+
    scale_x_datetime(name = 'Date')+
    scale_y_continuous(name = 'SHF1')

#only snow depth in CF3 dataset
ggplot(df, aes_string(x = "TIMESTAMP_END", y = "D_SNOW"))+
    theme_bw()+
    geom_point() +
  geom_vline(aes(xintercept= as.POSIXct("2023-05-14")))+
    scale_x_datetime(name = 'Date')+
    scale_y_continuous(name = 'Snow Depth')

ggplot(df, aes_string(x = "TIMESTAMP_END", y = "TA"))+
    theme_bw()+
    geom_point() +
  geom_vline(aes(xintercept= as.POSIXct("2023-05-14")))+
  geom_vline(aes(xintercept= as.POSIXct("2023-04-10")))+
    scale_x_datetime(name = 'Date')+
    scale_y_continuous(name = 'Air Temp')

# only CACF3 data here
ggplot(df, aes_string(x = "TIMESTAMP_END", y = "ALB"))+
    theme_bw()+
    geom_point() +
  geom_vline(aes(xintercept= as.POSIXct("2023-05-14")))+
    scale_x_datetime(name = 'Date')+
    scale_y_continuous(name = 'Albedo')

ggplot(df, aes_string(x = "TIMESTAMP_END", y = "TS_2_4_1"))+
    theme_bw()+
    geom_point() +
  geom_vline(aes(xintercept= as.POSIXct("2023-05-14")))+
    scale_x_datetime(name = 'Date')+
    scale_y_continuous(name = 'Random Soil Temp, CF3')


# Only CF1 soil temps

ggplot(df, aes_string(x = "TIMESTAMP_END", y = "TS_F_MDS_1"))+
    theme_bw()+
    geom_point() +
    scale_x_datetime(as.POSIXct(c('01-01-2007','12-31-2008'))+
    scale_y_continuous(name = 'Random Soil Temp, CF1')
    

ggplot(df, aes_string(x = "TIMESTAMP_END", y = "TS_F_MDS_2"))+
    theme_bw()+
    geom_point() +
  geom_vline(aes(xintercept= as.POSIXct("2023-05-14")))+
    scale_x_datetime(name = 'Date')+
    scale_y_continuous(name = 'Random Soil Temp, CF1')

ggplot(df, aes_string(x = "TIMESTAMP_END", y = "TS_F_MDS_2"))+
    theme_bw()+
    geom_point() +
  geom_vline(aes(xintercept= as.POSIXct("2023-05-14")))+
    scale_x_datetime(name = 'Date')+
    scale_y_continuous(name = 'Random Soil Temp, CF1')


```


## Month=color plots 

```{r}

#Creates a month variable in the 2023 dataframe

df_avg_2023$month = as.numeric(as.yearmon(df_avg_2023$day))


#Plots two variables against each other with the color representing the time of year 

ggplot(data=df_avg_2023)+
  geom_point(aes(x=TS_2_0_1, y=GPP_F, col = month))+
  scale_x_continuous(limits = c(0, 25))


```


## Soil Temp

2023

Plots both soil profiles and net CO2 flux together

```{r}

co2_23 <- ggplot(data = df, aes(x = TIMESTAMP, y = FC_F)) +
  scale_y_continuous(limits=c(-5, 5))+
  geom_point()+
  ggtitle("2023")+
  scale_x_datetime(limits = as.POSIXct(dates_23))


soil23_1 <- ggplot(data = df)+ theme_bw()+
  geom_hline(yintercept = 0)+
  geom_line(aes(TIMESTAMP,TS_1_0_1))+
  geom_line(aes(TIMESTAMP,TS_1_05_1))+
  geom_line(aes(TIMESTAMP,TS_1_1_1))+
  geom_line(aes(TIMESTAMP,TS_1_2_1))+  
  geom_line(aes(TIMESTAMP,TS_1_3_1))+
  geom_line(aes(TIMESTAMP,TS_1_4_1))+
  geom_line(aes(TIMESTAMP,TS_1_5_1))+
  geom_line(aes(TIMESTAMP,TS_1_6_1))+
  geom_line(aes(TIMESTAMP,TS_1_7_1))+
  geom_line(aes(TIMESTAMP,TS_1_8_1))+
  geom_line(aes(TIMESTAMP,TS_1_9_1))+
  geom_line(aes(TIMESTAMP,TS_1_10_1))+
  scale_x_datetime(limits=as.POSIXct(dates_23))


soil23_2 <- ggplot(data = df)+
  theme_bw()+
  geom_hline(yintercept = 0)+
  geom_line(aes(TIMESTAMP,TS_2_0_1))+
  geom_line(aes(TIMESTAMP,TS_2_05_1))+
  geom_line(aes(TIMESTAMP,TS_2_1_1))+
  geom_line(aes(TIMESTAMP,TS_2_2_1))+  
  geom_line(aes(TIMESTAMP,TS_2_3_1))+
  geom_line(aes(TIMESTAMP,TS_2_4_1))+
  geom_line(aes(TIMESTAMP,TS_2_5_1))+
  geom_line(aes(TIMESTAMP,TS_2_6_1))+
  geom_line(aes(TIMESTAMP,TS_2_7_1))+
  geom_line(aes(TIMESTAMP,TS_2_8_1))+
  geom_line(aes(TIMESTAMP,TS_2_9_1))+
  geom_line(aes(TIMESTAMP,TS_2_10_1))+
  scale_x_datetime(limits=as.POSIXct(dates_23))


# Arrange the plots side by side
grid.arrange(co2_23, soil23_1, soil23_2)

```


2007/2008
```{r}

co2_07 <- ggplot(data = df, aes(x = TIMESTAMP, y = FC_F)) + 
  geom_point() +
  ggtitle("2007")+
  scale_x_datetime(limits = as.POSIXct(dates_07))

co2_08 <- ggplot(data = df, aes(x = TIMESTAMP, y = FC_F)) + 
  geom_point() +
  ggtitle("2008")+
  scale_x_datetime(limits = as.POSIXct(dates_08))

soil07 <- ggplot(data = df)+ theme_bw()+
  geom_hline(yintercept = 0)+
  geom_line(aes(TIMESTAMP,TS_F_MDS_1))+
  geom_line(aes(TIMESTAMP,TS_F_MDS_2))+
  geom_line(aes(TIMESTAMP,TS_F_MDS_3))+
  geom_line(aes(TIMESTAMP,TS_F_MDS_4))+  
  geom_line(aes(TIMESTAMP,TS_F_MDS_5))+
  geom_line(aes(TIMESTAMP,TS_F_MDS_6))+
  scale_x_datetime(limits=as.POSIXct(dates_07))+
  scale_y_continuous(limits=c(-5, 20))

soil08 <- ggplot(data = df)+ theme_bw()+
  geom_hline(yintercept = 0)+
  geom_line(aes(TIMESTAMP,TS_F_MDS_1))+
  geom_line(aes(TIMESTAMP,TS_F_MDS_2))+
  geom_line(aes(TIMESTAMP,TS_F_MDS_3))+
  geom_line(aes(TIMESTAMP,TS_F_MDS_4))+  
  geom_line(aes(TIMESTAMP,TS_F_MDS_5))+
  geom_line(aes(TIMESTAMP,TS_F_MDS_6))+
  scale_x_datetime(limits=as.POSIXct(dates_08))+
  scale_y_continuous(limits=c(-5, 20))

# Arrange the plots side by side
grid.arrange(co2_07, co2_08, soil07, soil08, nrow=2, ncol = 2)

rm(co2_07, co2_08, soil07, soil08)
```



##CO2/NR Side by Side

2022/2023
```{r}

co2_22 <- ggplot(data = df, aes(x = TIMESTAMP, y = FC_F)) + 
  geom_point() +
  ggtitle("2022")+
  scale_x_datetime(limits = as.POSIXct(dates_22))

co2_23 <- ggplot(data = df, aes(x = TIMESTAMP, y = FC_F)) + 
  geom_point() +
  ggtitle("2023")+
  scale_x_datetime(limits = as.POSIXct(dates_23))

rn_22 <- ggplot(data = df, aes(x = TIMESTAMP, y = NETRAD)) + 
  geom_point() +
  scale_x_datetime(limits = as.POSIXct(dates_22))+
  scale_y_continuous(limits = c(-10, 1000))

rn_23 <- ggplot(data = df, aes(x = TIMESTAMP, y = NETRAD)) + 
  geom_point() +
  scale_x_datetime(limits = as.POSIXct(dates_23))+
  scale_y_continuous(limits = c(-10, 1000))

grid.arrange(co2_22, co2_23, rn_22, rn_23, nrow=2, ncol=2)

rm(co2_22, co2_23, rn_22, rn_23)

```

2007/2008
```{r}

co2_07 <- ggplot(data = df, aes(x = TIMESTAMP, y = FC_F)) + 
  geom_point() +
  ggtitle("2007")+
  scale_x_datetime(limits = as.POSIXct(dates_07))

co2_08 <- ggplot(data = df, aes(x = TIMESTAMP, y = FC_F)) + 
  geom_point() +
  ggtitle("2008")+
  scale_x_datetime(limits = as.POSIXct(dates_08))

## check units on VPD for different datasets
vpd_07 <- ggplot(data = df, aes(x = TIMESTAMP, y = VPD)) + 
  geom_point() +
  scale_x_datetime(limits = as.POSIXct(dates_07))+
  scale_y_continuous(limits = c(-10, 50))

vpd_08 <- ggplot(data = df, aes(x = TIMESTAMP, y = VPD)) + 
  geom_point() +
  scale_x_datetime(limits = as.POSIXct(dates_08))+
  scale_y_continuous(limits = c(-10, 50))

rn_07 <- ggplot(data = df, aes(x = TIMESTAMP, y = NETRAD)) + 
  geom_point() +
  scale_x_datetime(limits = as.POSIXct(dates_07))+
  scale_y_continuous(limits = c(-10, 1000))

rn_08 <- ggplot(data = df, aes(x = TIMESTAMP, y = NETRAD)) + 
  geom_point() +
  scale_x_datetime(limits = as.POSIXct(dates_08))+
  scale_y_continuous(limits = c(-10, 1000))

grid.arrange(co2_07, co2_08, vpd_07, vpd_08, rn_07, rn_08, nrow=3, ncol=2)

rm(co2_07, co2_08, vpd_07, vpd_08, rn_07, rn_08)

```



##CO2/Air Temp Side by Side

2022/2023
```{r}

co2_22 <- ggplot(data = df, aes(x = TIMESTAMP, y = FC_F)) + 
  geom_point() +
  ggtitle("2022")+
  scale_x_datetime(limits = as.POSIXct(dates_22))

co2_23 <- ggplot(data = df, aes(x = TIMESTAMP, y = FC_F)) + 
  geom_point() +
  ggtitle("2023")+
  scale_x_datetime(limits = as.POSIXct(dates_23))

ta_22 <- ggplot(data = df, aes(x = TIMESTAMP, y = TA)) + 
  geom_point() +
  scale_x_datetime(limits = as.POSIXct(dates_22))+
  scale_y_continuous(limits = c(-25, 40))

ta_23 <- ggplot(data = df, aes(x = TIMESTAMP, y = TA)) + 
  geom_point() +
  scale_x_datetime(limits = as.POSIXct(dates_23))+
  scale_y_continuous(limits = c(-25, 40))

grid.arrange(co2_22, co2_23, ta_22, ta_23, nrow=2, ncol=2)

rm(co2_22, co2_23, ta_22, ta_23)

## add partitioned data here
```

### July 2023 peak

Focused plots on the peak in FC_F in July 2023

```{r}

# gapfilled data causes peak here? compare with non-gapfilled data


peak_plot <- function(y_var, df = df_2023, vline_date = "2023-07-02") {
  # Convert y_var to symbol
  y_var <- sym(y_var)
  
  # Fixed start and end dates
  start_date <- "2023-06-20"
  end_date <- "2023-07-10"
  
  # Create the plot
  plot <- ggplot(data = df, aes(x = TIMESTAMP, y = !!y_var)) + 
    geom_point() +
    scale_x_datetime(limits = as.POSIXct(c(start_date, end_date))) +
    geom_vline(xintercept = as.POSIXct(vline_date))
  
  return(plot)
}

co2peak_23 <- peak_plot("FC_F")
GPPpeak_23 <- peak_plot("GPP_F")
RECOpeak_23 <- peak_plot("RECO")
TApeak_23 <- peak_plot("TA")

grid.arrange(co2peak_23, RECOpeak_23, GPPpeak_23, TApeak_23, nrow=2, ncol=2)


ggplot(data = df_avg_2023)+
  geom_point(aes(x=day, y=FC))+
  geom_point(aes(x=day, y=FC_F, color = "blue"))+


```



2007/2008
```{r}

co2_07 <- ggplot(data = df, aes(x = TIMESTAMP, y = FC_F)) + 
  geom_point() +
  ggtitle("2007")+
  scale_x_datetime(limits = as.POSIXct(dates_07))

co2_08 <- ggplot(data = df, aes(x = TIMESTAMP, y = FC_F)) + 
  geom_point() +
  ggtitle("2008")+
  scale_x_datetime(limits = as.POSIXct(dates_08))

ta_07 <- ggplot(data = df, aes(x = TIMESTAMP, y = TA)) + 
  geom_point() +
  scale_x_datetime(limits = as.POSIXct(dates_07))+
  scale_y_continuous(limits = c(-25, 40))

ta_08 <- ggplot(data = df, aes(x = TIMESTAMP, y = TA)) + 
  geom_point() +
  scale_x_datetime(limits = as.POSIXct(dates_08))+
  scale_y_continuous(limits = c(-25, 40))

grid.arrange(co2_07, co2_08, ta_07, ta_08, nrow=2, ncol=2)

rm(co2_07, co2_08, ta_07, ta_08)

```



# Monthly Averages of Biomet

doesn't work yet!

``` {r}

df <- df %>%
  mutate(year = year(TIMESTAMP_END),
         month = month(TIMESTAMP_END, label = TRUE))

# Group by year and month, then calculate the monthly average TEMP and P
monthly_summary <- df %>%
  group_by(year, month) %>%
  summarize(avg_air_temp = mean(TA, na.rm = TRUE),
            avg_precip = mean(P, na.rm = TRUE), avg_soil_temp = mean(TS_1_05_1, na.rm = TRUE)) %>%
  ungroup()

# Print the monthly summary
print(monthly_summary)

```


