---
title: "Churchill CO2 Data Analysis"
author: "Dani Trangmoe"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# add root directory here for github
```

Notes:






```{r, include=FALSE}
rm(list = ls())

library(data.table)
library(ggplot2)
library(cowplot)
library(openair)
library(plotrix)
library(signal)
library(svMisc)
library(zoo)
library(stringr)
library(plyr)
library(viridis)
library(lubridate)
library(tidyverse)
library(gridExtra)
library(plotly)
library(RColorBrewer)
library(pracma)
```




# Load data
```{r}

df = fread('C:/Users/dtrangmoe/Documents/Churchill/Churchill_Merged_CF1_CF3.csv',na.strings = c('-9999','NA','NaN','NAN','-7999'))

#needs continuous day variable
df_avg = fread('C:/Users/dtrangmoe/Documents/Churchill/Churchill_Merged_Avg_CF1_CF3.csv',na.strings = c('-9999','NA','NaN','NAN','-7999'))


```

#### Create yearly dataframes, timestamp

```{r}
#create TIMESTAMP variable that is = to TIMESTAMP_END

df$TIMESTAMP = df$TIMESTAMP_END

year_df <- function(df, year) {
  df %>%
    filter(format(day, "%Y") == as.character(year)) %>%
    mutate(DOY = yday(day))
}


#Creates data frames of each year containing the daily averages of each value- useful for focusing on one year at a time

df_avg$day <- as.POSIXct(df_avg$day, format = "%Y-%m-%d")

df_avg_2022 <- year_df(df_avg, 2022)
df_avg_2023 <- year_df(df_avg, 2023)

df_2023 <- year_df(df, 2023)


```


### Date ranges for plots

Adjust dates here!

```{r}

dates_23 = c('2023-01-01','2023-12-01')

snowmelt23 = c('2023-04-23','2023-05-15')
```


### GPP & ER Plots

```{r}

ggplot(data = df_2023, aes(x=DOY))+
  geom_point(aes(y = GPP_F, color = "GPP")) +
  geom_point(aes(y = RECO, color = "ER")) +
  geom_hline(yintercept=0, col="black")+
  scale_y_continuous(expression('CO'[2] * '('*m*mol~m^-2~s^-1*')'))+ labs(title = "2023 GPP & ER")

```


#### Gap Filling Plot

Shows gap in flux data and compares gap filled and non-gap filled data

```{r}

#Uses Half-Hourly data

ggplot(data = df_2023)+
  geom_hline(yintercept = 0)+
  geom_point(aes(TIMESTAMP,FC_F,col='Gapfilled'))+
  geom_point(aes(TIMESTAMP,FC,col='Original'))+
  scale_y_continuous(limits=c(-7,6))+
  scale_x_datetime(limits = as.POSIXct(dates_23,format="%F"))+
  labs(y = "CO2 Flux", x = "Time") +
  scale_color_manual(values=c('red','black'))+
  geom_vline(xintercept = as.POSIXct("2023-07-05"))


```



# Definition of Seasons

Uses ratio of par in/out, soil heat flux data, snow depth, air temp to identify seasonal periods

```{r}

# last period of the growing season is senescence, analyze with growing season


#need key here on graph

ggplot(data = df_avg_2023) +
  theme_bw() +
  geom_line(aes(x = DOY, y = TS_1_2_1), color = 'red') +
  geom_line(aes(x = DOY, y = TA), color = 'blue') +
  geom_line(aes(x = DOY, y = (PPFD_OUT*20) / PPFD_IN), color = 'green') +
  geom_line(aes(x = DOY, y = D_SNOW/2), color = 'purple') +
  geom_line(aes(x = DOY, y = (FC_F*15)), color = 'black') +
  scale_y_continuous(name = expression('Biomet Vars & FC'), limits = ) +
  geom_vline(xintercept = 112)+
  geom_vline(xintercept = 135)+
  geom_vline(xintercept = 295)+
  geom_vline(xintercept = 325)+
  scale_x_discrete(limits = c(0, 366))


# Defines seasons in 2023 dataframes using a column of character values

# Daily Average dataframe

df_avg_2023 <- df_avg_2023 %>%
  mutate(
      season = case_when(
      (DOY >= 295 & DOY <= 325) ~ 'Zero curtain',
      (DOY >= 113 & DOY <= 135) ~ 'Snow Melt',
      (DOY >= 136 & DOY <= 294) ~ 'Growing Season',
      (DOY >= 326 | DOY <= 112) ~ 'Winter',
      TRUE ~ NA_character_
    )
  )
    
seasonal_cumulative <- df_avg_2023 %>%
  group_by(season) %>%
  summarize(
    cumulative_FC_F = sum(FC_F, na.rm = TRUE)
  )

print(seasonal_cumulative)

# # Returns:
# 1 Growing Season          -22.9 
# 2 Snow Melt                 3.83
# 3 Winter                    4.39
# 4 Zero curtain              2.90


# Half-Hourly dataframe 

df_2023 <- df_2023 %>%
  mutate(
      season = case_when(
      (DOY >= 295 & DOY <= 325) ~ 'Zero curtain',
      (DOY >= 113 & DOY <= 135) ~ 'Snow Melt',
      (DOY >= 136 & DOY <= 294) ~ 'Growing Season',
      (DOY >= 326 | DOY <= 112) ~ 'Winter',
      TRUE ~ NA_character_
    )
  )


seasonal_cumulative2 <- df_2023 %>%
  group_by(season) %>%
  summarize(
    cumulative_FC_F = sum(FC_F, na.rm = TRUE)
  )

print(seasonal_cumulative2)

# # Returns:
# 1 Growing Season          -1098
# 2 Snow Melt                 184
# 3 Winter                    210
# 4 Zero curtain              139

```


# Isolate nighttime data

```{r}

ggplot(data=df_2023)+
  geom_point(aes(x=TIMESTAMP, y=NETRAD))
  
```


# Year-Long Budget 

#### Methane

```{r}

df_avg_2023 <- df_avg_2023 %>%
  subset(format(day, "%Y") == "2023") %>%
  mutate(day_as_POSIXct = as.POSIXct(day)) %>%
  mutate(DOY = as.numeric(format(day_as_POSIXct, "%j"))) %>%
  subset(select = -c(day_as_POSIXct)) %>%
  mutate(FCH4_F_no_NAs = ifelse(is.na(FCH4_F), 0, FCH4_F)) %>%
  mutate(cumulativeCH4 = cumtrapz(DOY, FCH4_F_no_NAs))

trapz(df_avg_2023$DOY, df_avg_2023$FCH4_F)
#returns 8.03157

ggplot(data = df_avg_2023, aes(x=DOY, y=cumulativeCH4, color = season))+
  geom_point()+
  scale_x_continuous(lim = c(0, 365))+
  geom_hline(yintercept=0, col="black")+ 
  scale_y_continuous(expression('Cumulative CH4 ('*m*mol~m^-2~s^-1*')'))
  

```

#### NEE


```{r}

df_avg_2023 <- df_avg_2023 %>%
  subset(format(day, "%Y") == "2023") %>%
  mutate(day_as_POSIXct = as.POSIXct(day)) %>%
  mutate(DOY = as.numeric(format(day_as_POSIXct, "%j"))) %>%
  subset(select = -c(day_as_POSIXct)) %>%
  mutate(FC_F_no_NAs = ifelse(is.na(FC_F), 0, FC_F)) %>%
  mutate(cumulative = cumtrapz(DOY, FC_F_no_NAs))

trapz(df_avg_2023$DOY, df_avg_2023$FC_F)
#returns -11.81368

ggplot(data = df_avg_2023, aes(x=DOY, y=cumulative, color = season))+
  geom_point()+
  scale_x_continuous(lim = c(0, 365))+
  geom_hline(yintercept=0, col="black")+ 
  scale_y_continuous(expression('Cumulative NEE ('*m*mol~m^-2~s^-1*')'))
  

```


# Seasonal Integrals

Use half-hourly data to calculate net co2 budgets by season


## NEE

Finds the net CO2 exchange of each season as defined above
```{r}

seasonal_integrals <- function(df) {
  
  # Calculate integral (sum) for each season
  integrals <- df %>%
    group_by(season) %>%
    summarise(integral_value = round(sum(FC_F, na.rm = TRUE), 2)) %>%
    ungroup() %>%
    arrange(season)
  
  return(integrals)
}

seasonal_integrals_2023 <- seasonal_integrals(df_2023)

ggplot(seasonal_integrals_2023, aes(x = season, y = integral_value)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(
    x = "Season",
    y = "Net CO2 Flux",
    title = "2023 CO2 Flux by season"
  ) +
  theme_minimal()+
  geom_text(aes(label = integral_value), vjust = 1, colour = "orange")



# Bar graph showing growing season vs. year round analysis



```

### Growing Season vs. Full Year

Compares the NEE of growing-season only site and our year round data

```{r}



```


## GPP

Finds the net GPP of each season

```{r}

seasonal_integrals <- function(df) {
  
  # Calculate integral (sum) for each season
  integrals <- df %>%
    group_by(season) %>% summarise(integral_value = round(sum(GPP_F, na.rm = TRUE), 2)) %>%
    ungroup() %>%
    arrange(season)
  
  return(integrals)
}

seasonal_integrals_2023 <- seasonal_integrals(df_2023)

ggplot(seasonal_integrals_2023, aes(x = season, y = integral_value)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(
    x = "Season",
    y = "Net GPP",
    title = "2023 GPP by season"
  ) +
  theme_minimal()+
  geom_text(aes(label = integral_value), vjust = 1, colour = "orange")



# Bar graph showing growing season vs. year round analysis



```



## RECO
```{r}

seasonal_integrals <- function(df) {
  
  # Calculate integral (sum) for each season
  integrals <- df %>%
    group_by(season) %>%
    summarise(integral_value = round(sum(RECO, na.rm = TRUE), 2)) %>%
    ungroup() %>%
    arrange(season)
  
  return(integrals)
}

seasonal_integrals_2023 <- seasonal_integrals(df_2023)

ggplot(seasonal_integrals_2023, aes(x = season, y = integral_value)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(
    x = "Season",
    y = "Net ER",
    title = "2023 ER by season"
  ) +
  theme_minimal()+
  geom_text(aes(label = integral_value), vjust = 1, colour = "orange")



# Bar graph showing growing season vs. year round analysis



```


## Methane
```{r}

seasonal_integrals <- function(df) {
  
  # Calculate integral (sum) for each season
  integrals <- df %>%
    group_by(season) %>%
    summarise(integral_value = round(sum(FCH4_F, na.rm = TRUE), 2)) %>%
    ungroup() %>%
    arrange(season)
  
  return(integrals)
}

seasonal_integrals_2023 <- seasonal_integrals(df_2023)

ggplot(seasonal_integrals_2023, aes(x = season, y = integral_value)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(
    x = "Season",
    y = "Net CH4 Flux",
    title = "2023 CH4 Flux by season"
  ) +
  theme_minimal()+
  geom_text(aes(label = integral_value), vjust = 1, colour = "orange")

```


# Snowmelt peak analysis

```{r}

## Shows non-temperature correlated peak in CO2 Flux data during snowmelt

ggplot(data = df_2023) +
  theme_bw() +
  geom_point(aes(x = TIMESTAMP, y = FC_F), color = 'black') +
  geom_point(aes(x = TIMESTAMP, y = RECO), color = 'blue') +
  geom_point(aes(x = TIMESTAMP, y = GPP_F), color = 'green') +
  geom_line(aes(x = TIMESTAMP, y = TS_2_05_1), color = 'deeppink2') +  
  geom_hline(yintercept = 0) +
  scale_y_continuous(
    name = expression('CO2 Data'),
    limits = c(-7, 5),
    sec.axis = sec_axis(~./4, name = "5cm Soil Temp")
    ) +
  scale_x_datetime(limits = as.POSIXct(c('2023-05-05', '2023-05-20')))

```


# Analysis of Controls

## Energy Balance
```{r}

energy_balance <- function(df) {
  
  # Create the plot
  df$Met <- df$NETRAD
  
  df$Flux <- df$LE + df$H
  
  plot <- ggplot(data = df, aes(x = Met, y = Flux))+ 
    geom_point()+
    geom_abline(slope=1, intercept=0, colour = "red")+
  scale_x_continuous(lim = c(-100, 600))+
  scale_y_continuous(lim = c(-100, 600))
  
  return(plot)
}

eb07 <- energy_balance(df_avg_2007)
eb08 <- energy_balance(df_avg_2008)
eb22 <- energy_balance(df_avg_2022)
eb23 <- energy_balance(df_avg_2023)

grid.arrange(eb07, eb08, eb22, eb23, nrow=2, ncol=2)



```



## Temperature Relationship 

```{r}

#Creates a month variable in the 2023 dataframe

df_2023$month = as.numeric(as.yearmon(df_2023$day))

#Plots flux variables vs. 5cm soil temp to visualize temperature/co2 flux relationship

ggplot(data=df_2023)+
  geom_point(aes(x=TS_1_05_1, y=FC, col = season))+
  labs(
    x = "Soil Temp (C)",
    y = "NEE",
    title = "NEE vs. Soil Temp"
  ) 

ggplot(data=df_2023)+
  geom_point(aes(x=TS_1_05_1, y=GPP_F, col = season))+
  labs(
    x = "Soil Temp",
    y = "GPP",
    title = "GPP vs. Soil Temp"
  ) 

ggplot(data=df_2023)+
  geom_point(aes(x=TS_1_05_1, y=RECO, col = season))+
  labs(
    x = "Soil Temp",
    y = "Respiration",
    title = "Respiraton vs. Soil Temp"
  ) 

ggplot(data=df_avg_2023)+
  geom_point(aes(x=TS_1_05_1, y=RECO, col = season)) +
  labs(
    x = "Soil Temp",
    y = "Respiration",
    title = "Respiraton vs. Soil Temp"
  ) 

```


## Soil Temp

2023

Plots both soil profiles and net CO2 flux together

```{r}

co2_23 <- ggplot(data = df, aes(x = TIMESTAMP, y = FC_F)) +
  scale_y_continuous(limits=c(-5, 5))+
  geom_point()+
  ggtitle("2023")+
  scale_x_datetime(limits = as.POSIXct(dates_23))


soil23_1 <- ggplot(data = df)+ theme_bw()+
  geom_hline(yintercept = 0)+
  geom_line(aes(TIMESTAMP,TS_1_0_1))+
  geom_line(aes(TIMESTAMP,TS_1_05_1))+
  geom_line(aes(TIMESTAMP,TS_1_1_1))+
  geom_line(aes(TIMESTAMP,TS_1_2_1))+  
  geom_line(aes(TIMESTAMP,TS_1_3_1))+
  geom_line(aes(TIMESTAMP,TS_1_4_1))+
  geom_line(aes(TIMESTAMP,TS_1_5_1))+
  geom_line(aes(TIMESTAMP,TS_1_6_1))+
  geom_line(aes(TIMESTAMP,TS_1_7_1))+
  geom_line(aes(TIMESTAMP,TS_1_8_1))+
  geom_line(aes(TIMESTAMP,TS_1_9_1))+
  geom_line(aes(TIMESTAMP,TS_1_10_1))+
  scale_x_datetime(limits=as.POSIXct(dates_23))


soil23_2 <- ggplot(data = df)+
  theme_bw()+
  geom_hline(yintercept = 0)+
  geom_line(aes(TIMESTAMP,TS_2_0_1))+
  geom_line(aes(TIMESTAMP,TS_2_05_1))+
  geom_line(aes(TIMESTAMP,TS_2_1_1))+
  geom_line(aes(TIMESTAMP,TS_2_2_1))+  
  geom_line(aes(TIMESTAMP,TS_2_3_1))+
  geom_line(aes(TIMESTAMP,TS_2_4_1))+
  geom_line(aes(TIMESTAMP,TS_2_5_1))+
  geom_line(aes(TIMESTAMP,TS_2_6_1))+
  geom_line(aes(TIMESTAMP,TS_2_7_1))+
  geom_line(aes(TIMESTAMP,TS_2_8_1))+
  geom_line(aes(TIMESTAMP,TS_2_9_1))+
  geom_line(aes(TIMESTAMP,TS_2_10_1))+
  scale_x_datetime(limits=as.POSIXct(dates_23))


# Arrange the plots side by side
grid.arrange(co2_23, soil23_1, soil23_2)

## Shows non-temperature correlated peak in CO2 Flux data during snowmelt

ggplot(data = df_2023) +
  theme_bw() +
  geom_point(aes(x = TIMESTAMP, y = FC), color = 'darkgreen') +
  geom_line(aes(x = TIMESTAMP, y = TS_2_05_1), color = 'deeppink2') +  
  geom_hline(yintercept = 0) +
  scale_y_continuous(
    name = expression('CO2 Flux'),
    limits = c(-7, 5),
    sec.axis = sec_axis(~./4, name = "5cm Soil Temp")
    ) +
  scale_x_datetime(limits = as.POSIXct(c('2023-05-01', '2023-05-20')))

```

