---
title: "Churchill CO2 Data Analysis"
author: "Dani Trangmoe"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# add root directory here for github
```

Notes:

```{r, include=FALSE}
rm(list = ls())

library(data.table)
library(ggplot2)
library(cowplot)
library(openair)
library(plotrix)
library(signal)
library(svMisc)
library(zoo)
library(stringr)
library(plyr)
library(viridis)
library(lubridate)
library(tidyverse)
library(gridExtra)
library(plotly)
library(RColorBrewer)
library(pracma)
library(cowplot)
```

# Load data

```{r}

df = fread('C:/Users/dtrangmoe/Documents/Churchill/Churchill_Merged_CF1_CF3.csv',na.strings = c('-9999','NA','NaN','NAN','-7999'))

#needs continuous day variable
df_avg = fread('C:/Users/dtrangmoe/Documents/Churchill/Churchill_Merged_Avg_CF1_CF3.csv',na.strings = c('-9999','NA','NaN','NAN','-7999'))


```

#### Create yearly dataframes, timestamp

```{r}
#create TIMESTAMP variable that is = to TIMESTAMP_END

year_df <- function(df, year) {
  df %>%
    filter(format(day, "%Y") == as.character(year)) %>%
    mutate(DOY = yday(day))
}


#Creates data frames of each year containing the daily averages of each value- useful for focusing on one year at a time

df_avg$day <- as.POSIXct(df_avg$day, format = "%Y-%m-%d")

df_avg_2022 <- year_df(df_avg, 2022)
df_avg_2023 <- year_df(df_avg, 2023)

df_2023 <- year_df(df, 2023)


```


### Timeseries plot


Plot 1 on ameriflux poster; timeseries of GPP, ER, NEE, and CH4

```{r}


ggplot(data = df_avg_2023, aes(x=day))+
  theme_bw()+
  geom_point(aes(y = -GPP_F*60*60*24*(1/1000000)*12, color = "GPP"))+
  geom_point(aes(y = RECO*60*60*24*(1/1000000)*12, color = "Respiration")) +
  geom_line(aes(y = FC_F*60*60*24*(1/1000000)*12, color = "NEE"))+
  geom_line(aes(y = FCH4_F*60*60*24*(1/1000000)*12*13, color = "CH4"))+
  geom_hline(yintercept=0, col="black")+
  scale_y_continuous(expression('CO'[2]*' Flux (g C'~m^-2~d^-1*')'),
  sec.axis = sec_axis(~ . /13, name = expression('CH'[4]*' Flux (g C'~m^-2~d^-1*')')))+
  scale_color_manual(name = " ",
            values = c("GPP" = "navy", 
                      "Respiration" = "turquoise3", 
                      "NEE" = "salmon", 
                      "CH4" = "mediumorchid"),
            breaks = c("GPP", "Respiration", "NEE", "CH4"))

```



#### Gap Filling Plot

Shows gap in flux data and compares gap filled and non-gap filled data

```{r}

#Uses Half-Hourly data

ggplot(data = df_2023)+
  geom_hline(yintercept = 0)+
  geom_point(aes(TIMESTAMP,FC_F,col='Gapfilled'))+
  geom_point(aes(TIMESTAMP,FC,col='Original'))+
  scale_y_continuous(limits=c(-7,6))+
  scale_x_datetime(limits = as.POSIXct(c('2023-01-01','2023-12-01'),format="%F"))+
  labs(y = "CO2 Flux ", x = "Time") +
  scale_color_manual(values=c('red','black'))+
  geom_vline(xintercept = as.POSIXct("2023-07-05"))


```


#### Net C Budget

Plot 2 in Ameriflux poster

_no_NAs is used for other years of data where NAs are present in gapfilled data

```{r}
#Creates numeric timestamp with the unit of minutes to integrate over half-hourly data

df_2023 <- df_2023 %>%
  mutate(time_minutes = as.numeric(difftime(TIMESTAMP, min(TIMESTAMP), units = "mins")))

# Units start as micromoles of CO2/(m^2s), converted to Grams of C/m^2/minute, integrated over minutes to get Grams of C/m^2

# Net CO2 Flux
df_2023 <- df_2023 %>%
  mutate(FC_F_no_NAs = ifelse(is.na(FC_F), 0, FC_F * 60 * (1/1000000) * 12))

net_CO2 <- trapz(df_2023$time_minutes, df_2023$FC_F_no_NAs)

# Units start as micromoles of CH4/(m^2s), converted to Grams of C/m^2/minute, integrated over minutes to get Grams of C/m^2

#Net CH4 Flux
df_2023 <- df_2023 %>%
  mutate(FCH4_F_no_NAs = ifelse(is.na(FCH4_F), 0, FCH4_F*60*(1/1000000)*12))


net_CH4 <- trapz(df_2023$time_minutes, df_2023$FCH4_F_no_NAs)

## Test for Sum/Integral match up- could change to sum for easier math
# net_CH4_sum <- sum(df_2023$FCH4_F_no_NAs)

## Marco uses g CH4 not g C, gets a value of ~11 for CH4 in 2023

# Used IPCC Sixth Assessment Report (AR6) global warming potentials, 100 year time period - could use paper gwp* or delta equation for future analysis

net_CH4_CO2e <- net_CH4*27.2
sum = net_CO2+net_CH4


#Dataframe created to generate bar graph
net_wp_2023 <- data.frame(
  Category = c("CO2", "CH4", "Total"),
  Value = c(round(net_CO2, 2), round(net_CH4, 2), round(sum, 2) 
))

#Plot here

ggplot(net_wp_2023, aes(x = Category, y = Value)) +
  theme_bw()+
  geom_bar(stat = "identity", position = "dodge", fill = "turquoise3") +
  geom_hline(yintercept=0, colour = "black")+
  labs(
    x = "",
    y = expression("Net Carbon Flux (g C"~m^-2~y^-1*")")) +
  geom_label(aes(label = Value), vjust = ifelse(net_wp_2023$Value >= 0, -0.7, 1.5), colour = "black", fill ="white")+
  scale_y_continuous(limits=c(-15, 12))


```



# Definition of Seasons

Plots ratio of par in/out, soil heat flux data, snow depth, air temp to identify seasonal trends

```{r}

ggplot(data = df_avg_2023) +
  theme_bw() +
  geom_line(aes(x = DOY, y = TS_1_2_1), color = 'red') +
  geom_line(aes(x = DOY, y = TA), color = 'darkgreen') +
  geom_line(aes(x = DOY, y = (PPFD_OUT*500) / PPFD_IN), color = 'green') +
  ## Lower values = more green
  geom_line(aes(x = DOY, y = D_SNOW/2), color = 'purple') +
  geom_line(aes(x = DOY, y = (FC_F*15)), color = 'darkblue') +
  geom_line(aes(x = DOY, y = 0, color = 'black')) +
  scale_y_continuous(name = expression('Biomet Vars & FC'), limits = c(-30,20)) +
  geom_vline(xintercept = 124)+ #end of winter
  geom_vline(xintercept = 162)+ #end of snowmelt
  geom_vline(xintercept = 248)+ #end of growing season
  geom_vline(xintercept = 294)+ #end of Fall Senescence
  scale_x_continuous(limits = c(0, 366))

```



####Split Plots

Plot 5 on Ameriflux poster

Definition of seasons: 3+ days of FC_F>0 for growing season, and 3+ days of air temperature <0 for winter. Gaps are senescence and spring

```{r}

df_avg_2023$day <- as.POSIXct(df_avg_2023$day)


## CO2 Flux and Soil/Air Temp
tempplotco2 <- ggplot(data = df_avg_2023) +
  theme_bw() +
  geom_hline(yintercept=0, colour = "black")+
  geom_line(aes(x = day, y = TS_1_05_1/15, colour = "5cm Soil Temperature")) +
  geom_line(aes(x = day, y = TA/15, colour = "Air Temperature")) +
  geom_point(aes(x = day, y = FC_F*60*60*24*(1/1000000)*12, colour = "NEE"))+
  scale_x_datetime(name = expression(""))+
  scale_y_continuous(
  name = expression("NEE (g C"~m^-2~d^-1~")"),
  sec.axis = sec_axis(~ . * 15, name = expression("Temperature ("*degree*"C)"))) +
  scale_color_manual(
    name = "",
    values = c( "NEE" = "turquoise3", "5cm Soil Temperature" = "darkblue", "Air Temperature" = "salmon"),
  breaks = c("NEE", "5cm Soil Temperature", "Air Temperature"))+
  geom_vline(xintercept = as.POSIXct("2023-05-05"))+ #end of winter, DOY 125
  geom_vline(xintercept =  as.POSIXct("2023-06-12"))+ #end of snowmelt, DOY 163
  geom_vline(xintercept =  as.POSIXct("2023-09-06"))+ #end of growing season, DOY 249
  geom_vline(xintercept =  as.POSIXct("2023-10-22"))

#tempplotco2

tempplotch4 <- ggplot(data = df_avg_2023) +
  theme_bw() +
  geom_hline(yintercept=0, colour = "black")+
  geom_line(aes(x = day, y = TS_1_05_1/100, colour = "5cm Soil Temperature")) +
  geom_line(aes(x = day, y = TA/100, colour = "Air Temperature")) +
  geom_point(aes(x = day, y = FCH4_F*60*60*24*(1/1000000)*12, colour = "Methane Flux"))+
  scale_x_datetime(name = expression(""))+
  scale_y_continuous(
  name = expression('Methane Flux (g C'~m^-2~d^-1*')'),
  sec.axis = sec_axis(~ . * 50, name = expression("Temperature ("*degree*"C)"))) +
  scale_color_manual(
    name = "",
    values = c( "Methane Flux" = "turquoise3", "5cm Soil Temperature" = "darkblue", "Air Temperature" = "salmon"),
  breaks = c("Methane Flux", "5cm Soil Temperature", "Air Temperature"))+
  geom_vline(xintercept = as.POSIXct("2023-05-05"))+ #end of winter, DOY 125
  geom_vline(xintercept =  as.POSIXct("2023-06-12"))+ #end of snowmelt, DOY 163
  geom_vline(xintercept =  as.POSIXct("2023-09-06"))+ #end of growing season, DOY 249
  geom_vline(xintercept =  as.POSIXct("2023-10-22"))

#tempplotch4


## CO2 flux and PAR ratio
parplot <- ggplot(data = df_avg_2023) +
  theme_bw() +
  geom_hline(yintercept=0, colour = "black")+
  geom_line(aes(x = day, y = (PPFD_OUT) / PPFD_IN, colour = "PAR Out/PAR In")) +
  #geom_line(aes(x = day, y = D_SNOW/15, colour = "Snow Depth")) +
  geom_point(aes(x = day, y = FC_F*60*60*24*(1/1000000)*12, colour = "NEE"))+
  scale_x_datetime(name = expression(""))+
  scale_y_continuous(
  name = expression("NEE (g C"~m^-2~d^-1~")"),
  sec.axis = sec_axis(~ . * 1, name = expression("PAR Out/PAR In"))) +
  scale_color_manual(
    name = "",
    values = c("PAR Out/PAR In" = "salmon", "Snow Depth" = "darkblue", "NEE" = "turquoise3"))+
  geom_vline(xintercept = as.POSIXct("2023-05-05"))+ #end of winter, DOY 125
  geom_vline(xintercept =  as.POSIXct("2023-06-12"))+ #end of snowmelt, DOY 163
  geom_vline(xintercept =  as.POSIXct("2023-09-06"))+ #end of growing season, DOY 249
  geom_vline(xintercept =  as.POSIXct("2023-10-22"))

#parplot



shfplot <- ggplot(data = df_avg_2023) +
  theme_bw() +
  geom_hline(yintercept=0, colour = "black")+
  geom_line(aes(x = day, y = G_1_1_1/45, colour = "Soil Heat Flux")) +
  geom_point(aes(x = day, y = FC_F*60*60*24*(1/1000000)*12, colour = "NEE"))+
  scale_x_datetime(name = expression(""))+
  scale_y_continuous(
  name = expression("NEE (g C"~m^-2~d^-1~")"),
  sec.axis = sec_axis(~ . * 45, name = expression("Soil Heat Flux (W"~m^-2~")"))) +
  scale_color_manual(
    name = "",
    values = c("Soil Heat Flux" =  "salmon", "NEE" = "turquoise3"))+
  geom_vline(xintercept = as.POSIXct("2023-05-05"))+ #end of winter, DOY 125
  geom_vline(xintercept =  as.POSIXct("2023-06-12"))+ #end of snowmelt, DOY 163
  geom_vline(xintercept =  as.POSIXct("2023-09-06"))+ #end of growing season, DOY 249
  geom_vline(xintercept =  as.POSIXct("2023-10-22"))

#shfplot


#grid.arrange(tempplotco2, tempplotch4, parplot, shfplot, nrow=4, ncol=1)

plot_row <- plot_grid(tempplotco2, tempplotch4, parplot, shfplot, nrow=4, align = 'v' )

plot_row




```



#### Add Seasons to Dataframes

``` {r}

# Definition of seasons in the daily average dataframe 

df_avg_2023 <- df_avg_2023 %>%
  mutate(
      season = case_when(
      (DOY >= 249 & DOY <= 294) ~ 'Fall Senescence',
      (DOY >= 125 & DOY <= 162) ~ 'Snow Melt',
      (DOY >= 163 & DOY <= 248) ~ 'Growing Season',
      (DOY >= 295 | DOY <= 124) ~ 'Winter',
      TRUE ~ NA_character_
    )
  )


# Definition of seasons in the half-hourly dataframe 

df_2023 <- df_2023 %>%
  mutate(
      season = case_when(
      (DOY >= 249 & DOY <= 294) ~ 'Fall Senescence',
      (DOY >= 125 & DOY <= 162) ~ 'Snow Melt',
      (DOY >= 163 & DOY <= 248) ~ 'Growing Season',
      (DOY >= 295 | DOY <= 124) ~ 'Winter',
      TRUE ~ NA_character_
    )
  )

```


# Seasonal Correlations

correlation between variables in growing season

```{r}

df_growing_avg_2023 <- filter(df_avg_2023, season == "Growing Season")

cor(df_growing_avg_2023$FC_F, df_growing_avg_2023$TA)


```


# Cumulative Emissions Plot

Shows NEE and Methane flux accumulation of C over the year, with colors representing different seasons

#### NEE

```{r}

# Units start as Micromoles of CO2/(m^2s), converted to g C/m^2


# Creates column in dataframe that is in the correct units, without NAs
df_avg_2023 <- df_avg_2023 %>%
  subset(format(day, "%Y") == "2023") %>%
  mutate(day_as_POSIXct = as.POSIXct(day)) %>%
  mutate(DOY = as.numeric(format(day_as_POSIXct, "%j"))) %>%
  subset(select = -c(day_as_POSIXct)) %>%
  mutate(FC_F_no_NAs = ifelse(is.na(FC_F), 0, FC_F*60*60*24*(1/1000000)*12)) %>%
  mutate(cumulative = cumtrapz(DOY, FC_F_no_NAs))


# Calculates numeric sum of CO2 Flux in 2023
trapz(df_avg_2023$DOY, df_avg_2023$FC_F_no_NAs)
#returns -12.24842 grams of C/m2


## why is the sum here not the same as in the budget plot?? look into later


# Plots cumulative CO2 Flux for the year of 2023
ggplot(data = df_avg_2023, aes(x=DOY, y=cumulative, color = season))+
  geom_point()+
  scale_x_continuous(lim = c(0, 365))+
  geom_hline(yintercept=0, col="black")+ 
  scale_y_continuous(expression('Cumulative CO2 Emissions (g C/m^2)'))
  

```

#### Methane

```{r}

# For unit adjustment: 
#   Units start as micromoles of CH4/(m^2s), converted to Grams of C/m^2

df_avg_2023 <- df_avg_2023 %>%
  subset(format(day, "%Y") == "2023") %>%
  mutate(day_as_POSIXct = as.POSIXct(day)) %>%
  mutate(DOY = as.numeric(format(day_as_POSIXct, "%j"))) %>%
  subset(select = -c(day_as_POSIXct)) %>%
  mutate(FCH4_F_no_NAs = ifelse(is.na(FCH4_F), 0, FCH4_F)) %>%
  mutate(cumulativeCH4 = 
           cumtrapz(DOY, FCH4_F_no_NAs*60*30*(1/1000000)*12))

trapz(df_avg_2023$DOY, df_avg_2023$FCH4_F*60*30*(1/1000000)*12)
#returns 0.1734819

# Also doesn't align with earlier budget

ggplot(data = df_avg_2023, aes(x=DOY, y=cumulativeCH4, color = season))+
  geom_point()+
  scale_x_continuous(lim = c(0, 365))+
  geom_hline(yintercept=0, col="black")+ 
  scale_y_continuous(expression('Cumulative CH4 Emissions (mg of C)'))
  

```

# Seasonal Budgets

Use half-hourly data to calculate net co2 budgets by season Average rate per day

To separate graph for daily rate; use geom_violin

## NEE

Plot 3 in Ameriflux poster

Finds the net CO2 exchange of each season as defined above

```{r}

seasonal_integrals <- function(df) {
  
  # Calculate integral (sum) for each season
  integrals <- df %>%
    group_by(season) %>%
    summarise(integral_value = sum(FC_F, na.rm = TRUE)) %>%
    ungroup() %>%
    arrange(season)
  
  
  # Changes units from  Micromoles of CO2/((m^2)s) to Grams of C/m^2, and rounds
    integrals$integral_value = 
      round(integrals$integral_value*60*30*(1/1000000)*12, 2)
  
  return(integrals)
}

seasonal_integrals_2023 <- seasonal_integrals(df_2023)

#reorders seasons to timeline order
seasonal_integrals_2023$season <- factor(seasonal_integrals_2023$season, levels = c("Snow Melt", "Growing Season", "Fall Senescence", "Winter"))

ggplot(seasonal_integrals_2023, aes(x = season, y = integral_value)) +
  theme_bw()+
  geom_hline(yintercept=0, colour="black")+
  geom_bar(stat = "identity", position = "dodge", fill = "turquoise3") +
  labs(
    x = " ",
    y = expression("Net CO"[2] * " Flux (g C m"^-2*")"),
    title = expression("Net CO"[2] * " Flux by Season")
  ) +
  geom_label(aes(label = integral_value), vjust = ifelse(seasonal_integrals_2023$integral_value >= 0, -0.7, 1.5), colour = "black", fill ="white")+
  scale_y_continuous(limits=c(-53, 23))
 



# Bar graph showing growing season vs. year round analysis
# Change GPP to negative to show dynamics in budget




```

## GPP

Finds the net GPP of each season

```{r}

seasonal_integrals <- function(df) {
  
  # Calculate integral (sum) for each season
  integrals <- df %>%
    group_by(season) %>% 
    summarise(integral_value = sum(GPP_F, na.rm = TRUE)) %>%
    ungroup() %>%
    arrange(season)
  
    
# Changes units from  Micromoles of CO2/(m^2s) to Grams of C/m^2, makes GPP a negative value, and rounds
  
    integrals$integral_value = 
      round(integrals$integral_value*-60*30*(1/1000000)*12, 2)
  
  return(integrals)
}

seasonal_integrals_2023 <- seasonal_integrals(df_2023)

ggplot(seasonal_integrals_2023, aes(x = season, y = integral_value)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(
    x = "Season",
    y = "Net GPP (Grams of Carbon/m^2)",
    title = "2023 GPP by season"
  ) +
  theme_minimal()+
  geom_text(aes(label = integral_value), vjust = 1, colour = "orange")


```

## RECO

```{r}

seasonal_integrals <- function(df) {
  
  # Calculate integral (sum) for each season
  integrals <- df %>%
    group_by(season) %>%
    summarise(integral_value = sum(RECO, na.rm = TRUE)) %>%
    ungroup() %>%
    arrange(season)
  
    
  # Changes units from  Micromoles of CO2/(m^2s) to Grams of C/m^2, and rounds
    integrals$integral_value = 
      round(integrals$integral_value*60*30*(1/1000000)*12, 2)
  
  return(integrals)
}

seasonal_integrals_2023 <- seasonal_integrals(df_2023)

ggplot(seasonal_integrals_2023, aes(x = season, y = integral_value)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(
    x = "Season",
    y = "Net ER (Grams of Carbon/m^2)",
    title = "2023 Ecosystem Respiration by season"
  ) +
  theme_minimal()+
  geom_text(aes(label = integral_value), vjust = 1, colour = "orange")



# Bar graph showing growing season vs. year round analysis



```

## Methane

Plot 4 on Ameriflux Poster


```{r}

seasonal_integrals <- function(df) {
  
  # Calculate integral (sum) for each season
  integrals <- df %>%
    group_by(season) %>%
    summarise(integral_value = sum(FCH4_F, na.rm = TRUE)) %>%
    ungroup() %>%
    arrange(season)
  
    
  # Changes units from mmol of CH4/(m^2s) to grams of C/m^2, and rounds
    integrals$integral_value = 
      round(integrals$integral_value*60*30*(1/1000000)*12, 2)
  
  return(integrals)
}

seasonal_integrals_2023 <- seasonal_integrals(df_2023)

#reorders seasons to timeline order
seasonal_integrals_2023$season <- factor(seasonal_integrals_2023$season, levels = c("Snow Melt", "Growing Season", "Fall Senescence", "Winter"))

ggplot(seasonal_integrals_2023, aes(x = season, y = integral_value)) +
  theme_bw()+
  geom_hline(yintercept=0, colour="black")+
  geom_bar(stat = "identity", position = "dodge", fill = "turquoise3") +
  labs(
    x = "",
    y = expression("Net CH"[4] * " Flux (g C m"^-2*")"),
    title = expression("Net CH"[4] * " Flux by Season")
  ) +
  geom_label(aes(label = integral_value), vjust = ifelse(seasonal_integrals_2023$integral_value >= 0, -0.7, 1.5), colour = "black", fill ="white")+
  scale_y_continuous(limits=c(0, 6.1))

```


# Snowmelt peak analysis

```{r}

## Shows non-temperature correlated peak in CO2 Flux data during snowmelt

## Very useful paper on this: https://doi.org/10.1002/2016GL071220


## May 15: DOY 135


ggplot(data = df_avg_2023) +
  theme_bw() +
  geom_point(aes(x = day, y = FC), color = 'black') +
  # geom_point(aes(x = day, y = FC_night), color = 'deeppink2') +
  geom_point(aes(x = day, y = GPP_F), color = 'green') +
  geom_point(aes(x = day, y = FCH4_F*12), color = 'orange') +
  geom_point(aes(x = day, y = RECO), color = 'purple') +
  geom_line(aes(x = day, y = TS_2_05_1/3), color = 'blue') + 
  # geom_line(aes(x= day, y= TA*(1/20)), color="purple")+
  # geom_point(aes(x=day, y = G_1_1_1*(1/50)), color = "grey")+
  geom_hline(yintercept = 0) +
  scale_y_continuous(
    name = expression('CO2 Data'),
    limits = c(-7, 5),
    sec.axis = sec_axis(~./4, name = "5cm Soil Temp")
    ) +
  scale_x_datetime(limits = as.POSIXct(c('2023-05-05', '2023-07-30')))+
  scale_y_continuous(limits = c(-2.5, 6))

```

# Soil temp heat map (in progress)

## Create dataframe

```{r}

# Create new data frame for plot; one column is timestamp, one is soil temp depth, and one is numeric temperature value; 12 soil depths over two profiles in data set

#Creates numeric vector of the correct length with all of the soil temperature measurement depths in cm, repeated once for each row of data collected

# # To view all soil temperature variables in dataset
# print(grep("^TS_1", names(df), value = TRUE))

#Uses depth values in cm for easy coercion to numeric later
ts_columns <- rep(c("0", "10", "20", "30", "40", "50", "60", "70", "80", "90", "100"), nrow(df_2023))

#Picks columns to move into new dataframe; 5 cm lost to make geom_raster work, could linearly interpolate or use geom_tile later?
df_soiltemp = select(df_2023, TIMESTAMP, grep("^TS_1", names(df), value = TRUE), -TS_1_05_1) 

#Changes column names to line up with numeric depth values
colnames(df_soiltemp) = c("Time", "10", "0", "20", "30", "40", "50", "60", "70", "80", "90", "100")

# Uses linear interpolation to fill NAs in data to create smooth plot
for (col in c("10", "0", "20", "30", "40", "50", "60", "70", "80", "90", "100")) {
  df_soiltemp[[col]] <- na.approx(df_soiltemp[[col]])
}

#repeats every row of the dataframe 11 times
df_soiltemp <- df_soiltemp %>%
  slice(rep(1:n(), each = 11)) %>%
  bind_cols(ts_columns) 

names(df_soiltemp)[13] <- "Depth"

#creates empty temp variable to fill with temp values
df_soiltemp$Temperature = NA


#Move corresponding temperature values into the temperature column, them remove unneccesary columns
df_soiltemp <- df_soiltemp %>%
  rowwise() %>%
  mutate(Temperature = ifelse(Depth %in% colnames(df_soiltemp), get(Depth), NA)) %>%
  ungroup() %>%
  select(-c("10", "0", "20", "30", "40", "50", "60", "70", "80", "90", "100"))

df_soiltemp$Depth = as.numeric(df_soiltemp$Depth)

summary(df_soiltemp)

```

## Create Plot 

```{r}
pal = c('red','orange','yellow','cyan','lightblue','blue','purple','violet')
pal = c('violet','violet','purple','blue','lightblue','cyan','green','yellow','orange','red','red')


soiltemp <- ggplot()+
  theme_bw()+
  geom_raster(data = df_soiltemp, interpolate = TRUE)+
  aes(x=Time, y=-Depth, fill= Temperature)+
#  scale_fill_viridis_c()+
  scale_fill_gradient2(low = c('pink','violet','purple','blue'),mid = 'cyan',high = c('green','yellow','orange','red'),midpoint = 0,limits = c(-15,20),oob = scales::squish)+
  # scale_fill_gradientn('Temp.',
  #                      na.value = 'transparent',
  #                      colours = pal, # 
  #                      #trans = 'log',
  #                      limits = c(-15,20),
  #                   #   labels = c("Good","Poor"),
  #                     # breaks = c(0,3.5),
  #                      oob = scales::squish)+ #out of bounds, squishes everything into scale 
  # add manual color scale, 0 is tight cyan color, cool negative colors and warm positive colors
  scale_y_continuous(name = "Depth (cm)",
    # trans = "reverse",  # Reverses the direction of the axis
    breaks = seq(0, -100, by = -10),  # Sets breaks for each 10 cm
    labels = seq(0, 100, by = 10) )

soiltemp

hist(df_soiltemp$Temperature)
#Stop temp scale at 20, make 20+ its own color to help with skew
  

```


#  Temperature Relationship

Plots 6 and 7 for Ameriflux poster

```{r}

#Creates a month variable in the 2023 dataframe

df_2023$month = as.numeric(as.yearmon(df_2023$day))

#Plots flux variables vs. 5cm soil temp to visualize temperature/co2 flux relationship

#RECO vs. soil temp; Not that useful because temperature was used to partition data

ggplot(data=df_2023)+
  geom_point(aes(x=TS_1_05_1, y=RECO, col = day))+
  labs(
    x = "Soil Temp",
    y = "Respiration",
    title = "Respiraton vs. Soil Temp"
  )

## Temp relationship plots with half hourly data

# FC_night vs. soil temp; used to estimate RECO without temp correlation or gap filling

ggplot(data=df_2023)+
  theme_bw()+
  geom_hline(yintercept = 0)+
  geom_vline(xintercept = 0)+
  geom_point(aes(x=TS_1_05_1, y=FC_night, col = DOY))+
scale_color_gradient(low = "navy", high = "salmon")+
  labs(
    x = expression("5cm Soil Temperature ("*degree*"C)"),
    y = expression("Half-hourly nighttime CO"[2] * " Flux ("*mu*mol~m^-2~s^-1*")"),
    title = expression("Nighttime CO"[2] * " Flux vs. Soil Temperature")
  )+
  scale_x_continuous(limits=c(-15,25))+
  scale_y_continuous(limits=c(-0.5,2.5))


#Methane vs. soil temp

ggplot(data=df_2023)+
  geom_vline(xintercept=0)+
  theme_bw()+
  geom_point(aes(x=TS_1_05_1, y=FCH4*(1/1000), col = DOY))+
scale_color_gradient(low = "navy", high = "salmon")+
  labs(
    x = expression("5cm Soil Temperature ("*degree*"C)"),
    y = expression("Half-hourly CH"[4] * " Flux ("*mu*mol~m^-2~s^-1*")"),
    title = expression("CH"[4] * " Flux vs. Soil Temperature")
  )+
  scale_x_continuous(limits = c(-15, 30))+
  scale_y_continuous(limits = c(-0.04, .150))




## Temp relationship plots with daily avg data

# FC_night vs. soil temp; used to estimate RECO without temp correlation or gap filling

ggplot(data=df_avg_2023)+
  theme_bw()+
  geom_hline(yintercept = 0)+
  geom_vline(xintercept = 0)+
  geom_point(aes(x=TS_1_05_1, y=FC_night, col = DOY))+
scale_color_gradient(low = "navy", high = "salmon")+
  labs(
    x = expression("5cm Soil Temperature ("*degree*"C)"),
    y = expression("Daily Average nighttime CO"[2] * " Flux ("*mu*mol~m^-2~s^-1*")"),
    title = expression("Nighttime CO"[2] * " Flux vs. Soil Temperature")
  )+
  scale_x_continuous(limits=c(-15,18))+
  scale_y_continuous(limits=c(-0.5,2.1))


#Methane vs. soil temp

ggplot(data=df_avg_2023)+
  geom_vline(xintercept=0)+
  theme_bw()+
  geom_point(aes(x=TS_1_05_1, y=FCH4*(1/1000), col = DOY))+
scale_color_gradient(low = "navy", high = "salmon")+
  labs(
    x = expression("5cm Soil Temperature ("*degree*"C)"),
    y = expression("Daily Average CH"[4] * " Flux ("*mu*mol~m^-2~s^-1*")"),
    title = expression("CH"[4] * " Flux vs. Soil Temperature")
  )+
  scale_x_continuous(limits = c(-15, 20))+
  scale_y_continuous(limits = c(-0.03, .10))

```



#### Exponential - doesn't work yet

# Daily average values are less noisy, better for analysis
```{r}

ta_fc <- lm(log10(RECO) ~ TS_1_05_1, data = df_avg_2023)
  
ta_fc$residuals
ta_fc$rank
ta_fc$df.residual

anova(ta_fc)
summary(ta_fc)

plot(ta_fc)



plot(df_avg_2023$TS_1_05_1, log10(df_avg_2023$RECO))
abline(ta_fc)

#skewed residuals: model isn't working well
hist(ta_fc$residuals)

#   ggplot(data=data)+
#   theme_bw()+
#   geom_hline(yintercept = 0)+
#   geom_vline(xintercept = 0)+
#   geom_line(aes_string(y = fit), x=x_var, color = "black") +
#   geom_point(aes(x=x_var, y=y_var, col = DOY))+
# scale_color_gradient(low = "navy", high = "salmon")
# 
# 
# 
# ggplot(data=df_2023)+
#   theme_bw()+
#   geom_hline(yintercept = 0)+
#   geom_vline(xintercept = 0)+
#   geom_line(aes_string(y = fit), x=TS_1_05_1, color = "black") +
#   geom_point(aes(x=TS_1_05_1, y=FC_night, col = DOY))+
# scale_color_gradient(low = "navy", high = "salmon")+
#   labs(
#     x = expression("5cm Soil Temperature ("*degree*"C)"),
#     y = expression("Half-hourly Nighttime CO"[2] * " Flux"),
#     title = expression("Nighttime CO"[2] * " Flux vs. Soil Temperature")
#   )+
#   scale_x_continuous(limits=c(-15,18))+
#   scale_y_continuous(limits=c(-0.5,4))

```