---
title: "IQ2 Met & Flux Cleaning Script"
output:
  pdf_document: default
  html_document: default
date: "`r Sys.Date()`"
---




```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, dev="png")
knitr::opts_chunk$set(error = TRUE)
```



## IQ2 Biomet Data Cleaning


#### Designed to clean biomet variables collected at the Iqaluit 2 site. 

#### Uses original variable names as created by datalogger, not FluxNet 
#### standardized biomet names. 





Clear console and add packages
```{r, warning=FALSE, echo=FALSE}
rm(list = ls())

library(data.table)
library(ggplot2)
library(cowplot)
library(openair)
library(plotrix)
library(signal)
library(svMisc)
library(zoo)
library(stringr)
library(plyr)
library(dplyr)
library(viridis)
library(lubridate)
```


To load tidy, uncleaned biomet data as created by IQ loading script 
```{r, warning=FALSE}
df = fread('C:/Users/klynoe/Documents/iqaluit_2/met/IQtundra2_met.dat',skip=4, header = F
           , na.strings = c('-9999','NA','NaN','NAN','-7999'))

h = fread('C:/Users/klynoe/Documents/iqaluit_2/met/IQtundra2_met.dat',skip=1, nrows = 0 ,
          na.strings = c('-9999','NA','NaN','NAN','-7999'))

names(df) = names(h)
```

Creates a variable to input a date range for the plots in the biomet section of
cleaning code. Used to easily change date range for different data sets. 
```{r, warning=FALSE}
biomet_dates <- c('2024-03-01', '2024-07-30')
```

Converts biomet variable names for easier programming 
```{r, warning=FALSE}
colnames(df)[which(names(df) == 'SHFP_Avg(1)')] <- 'SHFP_Avg_1'
colnames(df)[which(names(df) == 'SHFP_Avg(2)')] <- 'SHFP_Avg_2'
colnames(df)[which(names(df) == 'SHFP_Avg(3)')] <- 'SHFP_Avg_3'


colnames(df)[which(names(df) == 'Temp_C_Avg(1)')] <- 'Temp_C_Avg_1'
colnames(df)[which(names(df) == 'Temp_C_Avg(2)')] <- 'Temp_C_Avg_2'
colnames(df)[which(names(df) == 'Temp_C_Avg(3)')] <- 'Temp_C_Avg_3'
colnames(df)[which(names(df) == 'Temp_C_Avg(4)')] <- 'Temp_C_Avg_4'
colnames(df)[which(names(df) == 'Temp_C_Avg(5)')] <- 'Temp_C_Avg_5'
colnames(df)[which(names(df) == 'Temp_C_Avg(6)')] <- 'Temp_C_Avg_6'
```



## Biomet cleaning Script 

#### Air Temp

Doesn't clean anything right how- looks fine
```{r, warning=FALSE}
ggplot(data = df)+
  geom_point(aes(TIMESTAMP,AirTC_Avg),col='black')+
  scale_y_continuous(limits = c(-30,20),
                     expression('Air Temperature ('*Celsius*')'))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates,format="%F"))

hist(df$AirTC_Avg,breaks=100)

AirTC.limits = df$AirTC_Avg
df$AirTC_Avg.c = AirTC.limits

```


#### Relative Humidity

Doesn't clean anything right how- looks fine
```{r, warning=FALSE}
ggplot(data = df)+
  geom_point(aes(TIMESTAMP,RH_Avg),col='black')+
  scale_y_continuous(limits = c(20,110),
                     expression('Relative Humidity ('*percent*')'))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates,format="%F"))



RH.limits = df$RH_Avg

df$RH_Avg.c = RH.limits

```



#### Soil Heat Flux

Plots all three values 
```{r, warning=FALSE}
ggplot(data = df)+
  geom_point(aes(TIMESTAMP,SHFP_Avg_1,col='SHF 1'))+
  geom_point(aes(TIMESTAMP,SHFP_Avg_2,col='SHF 2'))+
  geom_point(aes(TIMESTAMP,SHFP_Avg_3,col='SHF 3'))+
  scale_y_continuous(limits = c(-60,100),
                     expression ('Soil Heat Flux ('*W/m^2*')'))+
  scale_color_manual(values = c('red','black', 'blue'))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates,format="%F"))
```


SHF1 - does nothing, looks fine
```{r, warning=FALSE}
hist(df$SHFP_Avg_1,breaks=100)
plot(df$TIMESTAMP,df$SHFP_Avg_1,ylim = c(-40,110))

df$SHFP_Avg_1.c = df$SHFP_Avg_1
```

SHF2 - does nothing, looks fine
```{r, warning=FALSE}
hist(df$SHFP_Avg_2,breaks=100)
plot(df$TIMESTAMP,df$SHFP_Avg_2,ylim = c(-80,165))

df$SHFP_Avg_2.c = df$SHFP_Avg_2
```

SHF3 - does nothing, looks fine 
```{r, warning=FALSE}
hist(df$SHFP_Avg_3,breaks=100)
plot(df$TIMESTAMP,df$SHFP_Avg_3,ylim = c(-80,165))

df$SHFP_Avg_3.c = df$SHFP_Avg_3
```



#### PAR in 

Initial Cleaning with Limits - doesn't do anything
```{r, warning=FALSE}
ggplot(data = df)+
  geom_point(aes(TIMESTAMP,PPFDu_Avg),col='black')+
  scale_y_continuous(limits = c(-200, 2000),
                     expression('PAR ('*mu*mol/m^2/s*')'))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates,format="%F"))


hist(df$PPFDu_Avg,breaks=100)

ggplot(data = df)+geom_hline(yintercept = 0)+
  geom_point(aes(x=TIMESTAMP,y=PPFDu_Avg))+
  geom_hline(yintercept = 0, col="red")+
  scale_y_continuous(limits = c(-200, 1800))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates,format="%F"))

PPFD.limits = replace(df$PPFDu_Avg, df$PPFDu_Avg < 0,NA)


hist(PPFD.limits,breaks=100)

```

Rolling SD 
```{r, warning=FALSE}
f = PPFD.limits # first make a new flux vector to apply the above filters
# prepare the inputs for a zero-phase (forward and reverse) filter  
ind       = which(complete.cases(f))   # first save the index of all the NAs
b         = rep(1,8)/8                 # moving average coefficient
a         = 1                          # coefficient of the ARMA filter
mad_i    = filtfilt(b, a, na.omit(f)) # create a forward and reverse ARMA filter
mad_filt = f                          # make a copy of the full fluxes again
mad_filt[ind] = mad_i                # apply the filter where the real data exist

n = 14*48 # set the length of the rolling filter, 48 half hours in day * x days
roll.mad = rollapply(data = mad_filt,
                     width = n,
                     FUN = sd,
                     partial = TRUE,
                     na.rm = T,
                     fill = NA)  #create a rolling MAD or sd or other
roll.mad[is.na(mad_filt)] = NA  #make NA values where NAs exist in the real data

ggplot(df)+geom_hline(yintercept = 0)+
  geom_point(aes(TIMESTAMP,PPFD.limits,col='PAR in'))+
  geom_line(aes(TIMESTAMP,mad_filt,col='Filter'))+
  geom_line(aes(TIMESTAMP,roll.mad,col='MAD'))+
  scale_y_continuous(limits = c(-15,1800))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates,format="%F"))+
  scale_color_manual(values=c('yellow','red','black'))



#adjust this value (N) to tweak how many MADs to be away from the norm (4 default)
N = 4

#Add clean value to dataframe (_.c)

df$PPFDu_Avg.c = ifelse(abs(PPFD.limits - mad_filt) > (N * roll.mad),NA,PPFD.limits)

#Compare cleaned vs. uncleaned

ggplot(df)+geom_hline(yintercept = 0)+
  geom_point(aes(TIMESTAMP,PPFD.limits,col='Uncleaned'))+
  geom_point(aes(TIMESTAMP,PPFDu_Avg.c,col='Cleaned'))+
  scale_y_continuous(limits = c(0,2000))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates,format="%F"))+
  scale_color_manual(values=c('black','red'))


# plot range of different N vals

ggplot(data = df)+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*6,ymin = mad_filt-roll.mad*6,fill='6'))+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*3,ymin = mad_filt-roll.mad*3,fill='3'))+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*2,ymin = mad_filt-roll.mad*2,fill='2'))+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*1,ymin = mad_filt-roll.mad*1,fill='1'))+
  geom_point(aes(TIMESTAMP,PPFD.limits),col='red')+
  geom_point(aes(TIMESTAMP,PPFDu_Avg.c),col='black')+
  scale_y_continuous(limits = c(-500,1800))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates,format="%F"))

```



#### Net Radiation

No initial cleaning- looks fine
```{r, warning=FALSE, echo=FALSE}
ggplot(data = df)+
  geom_point(aes(TIMESTAMP, Rn_Avg),col='black')+
  scale_y_continuous(limits = c(-125,950),
                     expression('Net Radiation ('*W/m^2*')'))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates,format="%F"))

RN.limits= df$Rn_Avg
```

Rolling SD
```{r, warning=FALSE}
f = RN.limits # first make a new flux vector to apply the above filters
# prepare the inputs for a zero-phase (forward and reverse) filter  
ind       = which(complete.cases(f))   # first save the index of all the NAs
b         = rep(1,8)/8                 # moving average coefficient
a         = 1                          # coefficient of the ARMA filter
mad_i    = filtfilt(b, a, na.omit(f)) #create a forward and reverse ARMA filter
mad_filt = f                          # make a copy of the full fluxes again
mad_filt[ind] = mad_i                # apply the filter where the real data exist

n = 7*48 # set the length of the rolling filter, 48 half hours in day * x days
roll.mad = rollapply(data = mad_filt,
                     width = n,
                     FUN = sd,
                     partial = TRUE,
                     na.rm = T,
                     fill = NA)  #create a rolling MAD or sd or other
roll.mad[is.na(mad_filt)] = NA  #make NA values where NAs exist in the real data




#adjust this value (N) to tweak how many MADs to be away from the norm
N = 3 

#Add clean value to dataframe (_.c)  (change these lines for new site)

df$Rn_Avg.c = ifelse(abs(RN.limits - mad_filt) > (N * roll.mad),NA,RN.limits)


#Compare cleaned vs. uncleaned

ggplot(df)+geom_hline(yintercept = 0)+
  geom_point(aes(TIMESTAMP,RN.limits,col='Uncleaned'))+
  geom_point(aes(TIMESTAMP,Rn_Avg.c,col='Cleaned'))+
  scale_y_continuous(limits = c(-150,500))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates,format="%F"))+
  scale_color_manual(values=c('black','red'))
 

 
ggplot(data = df)+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*6,ymin = mad_filt-roll.mad*6,fill='6'))+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*3,ymin = mad_filt-roll.mad*3,fill='3'))+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*2,ymin = mad_filt-roll.mad*2,fill='2'))+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*1,ymin = mad_filt-roll.mad*1,fill='1'))+
  geom_point(aes(TIMESTAMP,RN.limits),col='red')+
  geom_point(aes(TIMESTAMP, Rn_Avg.c),col='black')+
  scale_y_continuous(limits = c(-500,600))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates,format="%F"))
 
```



#### Shortwave Out (Energy going up)

Initial Cleaning with Limits 
```{r, warning=FALSE}

ggplot(data = df)+
  geom_point(aes(TIMESTAMP,Su_Avg))+
  scale_y_continuous(limits = c(-10,250),
                     expression('Shortwave Out ('*W/m^2*')'))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates,format="%F"))
 
 
hist(df$Su_Avg,breaks=100)

ggplot(data = df)+geom_hline(yintercept = 0)+
  geom_point(aes(x=TIMESTAMP,y=Su_Avg))+
  geom_hline(yintercept = 0, col="red")+
  scale_y_continuous(limits = c(-20, 250))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates,format="%F"))

SWOUT.limits = replace(df$Su_Avg, df$Su_Avg < 0,NA)


hist(SWOUT.limits,breaks=100)
plot(df$TIMESTAMP,SWOUT.limits)
```


Rolling SD
```{r, warning=FALSE}
f = SWOUT.limits # first make a new flux vector to apply the above filters
# prepare the inputs for a zero-phase (forward and reverse) filter  
ind       = which(complete.cases(f))   # first save the index of all the NAs
b         = rep(1,8)/8                 # moving average coefficient
a         = 1                          # coefficient of the ARMA filter
mad_i    = filtfilt(b, a, na.omit(f)) #create a forward and reverse ARMA filter
mad_filt = f                          # make a copy of the full fluxes again
mad_filt[ind] = mad_i                # apply the filter where the real data exist

n = 7*48 # set the length of the rolling filter, 48 half hours in day * x days
roll.mad = rollapply(data = mad_filt,
                     width = n,
                     FUN = sd,
                     partial = TRUE,
                     na.rm = T,
                     fill = NA)  #create a rolling MAD or sd or other
roll.mad[is.na(mad_filt)] = NA  #make NA values where NAs exist in the real data


ggplot(df)+geom_hline(yintercept = 0)+
  geom_point(aes(TIMESTAMP,SWOUT.limits,col='Shortwave out'))+
  geom_line(aes(TIMESTAMP,mad_filt,col='Filter'))+
  geom_line(aes(TIMESTAMP,roll.mad,col='MAD'))+
  scale_y_continuous(limits = c(-5,750))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates,format="%F"))+
  scale_color_manual(values=c('yellow','red','black'))

 

 
#adjust this value (N) to tweak how many MADs to be away from the norm
N = 4

#Add clean value to dataframe (_.c)

df$Su_Avg.c = ifelse(abs(SWOUT.limits - mad_filt) > (N * roll.mad),NA,SWOUT.limits)


#Compare cleaned vs. uncleaned

plot(df$TIMESTAMP,df$Su_Avg,col='red',ylim = c(-1,750));points(df$TIMESTAMP,df$Su_Avg.c)
 

  
ggplot(data = df)+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*6,ymin = mad_filt-roll.mad*6,fill='6'))+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*3,ymin = mad_filt-roll.mad*3,fill='3'))+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*2,ymin = mad_filt-roll.mad*2,fill='2'))+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*1,ymin = mad_filt-roll.mad*1,fill='1'))+
  geom_point(aes(TIMESTAMP,SWOUT.limits),col='red')+
  geom_point(aes(TIMESTAMP,Su_Avg.c),col='black')+
  scale_y_continuous(limits = c(-200,780))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates,format="%F"))
 
```



#### Shortwave In (Energy going down)

Initial Cleaning with Limits 
```{r, warning=FALSE}
ggplot(data = df)+
  geom_point(aes(TIMESTAMP,Sd_Avg))+
  scale_y_continuous(limits = c(-10,700),
                     expression('Shortwave In ('*W/m^2*')'))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates,format="%F"))
 

 
hist(df$Sd_Avg,breaks=100)

ggplot(data = df)+geom_hline(yintercept = 0)+
  geom_point(aes(x=TIMESTAMP,y=Sd_Avg))+
  geom_hline(yintercept = 0, col="red")+
  scale_y_continuous(limits = c(-10, 700))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates,format="%F"))

SWIN.limits = replace(df$Sd_Avg, df$Sd_Avg < 0,NA)


hist(SWIN.limits,breaks=100)
plot(df$TIMESTAMP,SWIN.limits)

```


Rolling SD (left in for future use, doesn't do anything)
```{r, warning=FALSE}
f = SWIN.limits # first make a new flux vector to apply the above filters
# prepare the inputs for a zero-phase (forward and reverse) filter  
ind       = which(complete.cases(f))   # first save the index of all the NAs
b         = rep(1,8)/8                 # moving average coefficient
a         = 1                          # coefficient of the ARMA filter
mad_i    = filtfilt(b, a, na.omit(f)) #create a forward and reverse ARMA filter
mad_filt = f                          # make a copy of the full fluxes again
mad_filt[ind] = mad_i                # apply the filter where the real data exist

n = 7*48 # set the length of the rolling filter, 48 half hours in day * x days
roll.mad = rollapply(data = mad_filt,
                     width = n,
                     FUN = sd,
                     partial = TRUE,
                     na.rm = T,
                     fill = NA)  #create a rolling MAD or sd or other
roll.mad[is.na(mad_filt)] = NA  #make NA values where NAs exist in the real data

ggplot(df)+geom_hline(yintercept = 0)+
  geom_point(aes(TIMESTAMP,SWIN.limits,col='Shortwave out'))+
  geom_line(aes(TIMESTAMP,mad_filt,col='Filter'))+
  geom_line(aes(TIMESTAMP,roll.mad,col='MAD'))+
  scale_y_continuous(limits = c(-5,800))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates,format="%F"))+
  scale_color_manual(values=c('yellow','red','black'))


 

 
#adjust this value (N) to tweak how many MADs to be away from the norm
N = 5

#Add clean value to dataframe (_.c)

df$Sd_Avg.c = ifelse(abs(SWIN.limits - mad_filt) > (N * roll.mad),NA,SWIN.limits)

#Compare cleaned vs. uncleaned

plot(df$TIMESTAMP,df$Sd_Avg,col='red',ylim = c(0,800));points(df$TIMESTAMP,df$Sd_Avg.c)
 

 
ggplot(data = df)+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*6,ymin = mad_filt-roll.mad*6,fill='6'))+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*4,ymin = mad_filt-roll.mad*4,fill='4'))+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*3,ymin = mad_filt-roll.mad*3,fill='3'))+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*1,ymin = mad_filt-roll.mad*1,fill='1'))+
  geom_point(aes(TIMESTAMP,SWIN.limits),col='red')+
  geom_point(aes(TIMESTAMP,Sd_Avg.c),col='black')+
  scale_y_continuous(limits = c(-600, 800))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates,format="%F"))
```


#### Albedo 

Creation of variable and initial cleaning with limits 
```{r, warning=FALSE}
albedo = df$Su_Avg.c / df$Sd_Avg.c



ggplot(data = df)+
  geom_point(aes(TIMESTAMP,albedo))+
  scale_y_continuous(limits = c(-0.5, 20),
                     expression('Albedo'))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates,format="%F"))

albedo.limits = replace(albedo, albedo < .05 | albedo > 1,NA)


ggplot(data = df)+
  geom_point(aes(TIMESTAMP,albedo.limits))+
  scale_y_continuous(limits = c(-.5,1.5),
                     expression('Albedo'))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates,format="%F"))
```


Rolling MAD
```{r, warning=FALSE}
f = albedo.limits # first make a new flux vector to apply the above filters
# prepare the inputs for a zero-phase (forward and reverse) filter  
ind       = which(complete.cases(f))   # first save the index of all the NAs
b         = rep(1,8)/8                 # moving average coefficient
a         = 1                          # coefficient of the ARMA filter
mad_i    = filtfilt(b, a, na.omit(f)) #create a forward and reverse ARMA filter
mad_filt = f                          # make a copy of the full fluxes again
mad_filt[ind] = mad_i                # apply the filter where the real data exist

n = 7*48 # set the length of the rolling filter, 48 half hours in day * x days
roll.mad = rollapply(data = mad_filt,
                     width = n,
                     FUN = mad,
                     partial = TRUE,
                     na.rm = T,
                     fill = NA)  #create a rolling MAD or sd or other
roll.mad[is.na(mad_filt)] = NA  #make NA values where NAs exist in the real data

ggplot(df)+geom_hline(yintercept = 0)+
  geom_point(aes(TIMESTAMP,albedo.limits,col='Albedo'))+
  geom_line(aes(TIMESTAMP,mad_filt,col='Filter'))+
  geom_line(aes(TIMESTAMP,roll.mad,col='MAD'))+
  scale_y_continuous(limits = c(0,1))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates,format="%F"))+
  scale_color_manual(values=c('black','yellow','red'))
 


 
#adjust this value (N) to tweak how many MADs to be away from the norm
N = 3
#Add clean value to dataframe (_.c)

df$albedo.c = ifelse(abs(albedo.limits - mad_filt) > (N * roll.mad),NA,albedo.limits)

#Compare cleaned vs. uncleaned


ggplot(df)+geom_hline(yintercept = 0)+
  geom_point(aes(TIMESTAMP,albedo.limits,col='Uncleaned'))+
  geom_point(aes(TIMESTAMP,df$albedo.c,col='Cleaned'))+
  scale_y_continuous(limits = c(0,1))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates,format="%F"))+
  scale_color_manual(values=c('black','red'))
```



#### Longwave In

Looks fine, doesn't do anything 
```{r, warning=FALSE}
ggplot(data = df)+
  geom_point(aes(TIMESTAMP,long_dn_corr_Avg))+
  scale_y_continuous(limits = c(100,400),
                     expression('Longwave In ('*W/m^2*')'))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates,format="%F"))
 

df$long_dn_corr_Avg.c = df$long_dn_corr_Avg
```


#### Longwave Out 

Looks fine, doesn't do anything
```{r, warning=FALSE}
ggplot(data = df)+
  geom_point(aes(TIMESTAMP,long_up_corr_Avg))+
  scale_y_continuous(limits = c(200,450),
                     expression('Longwave Out ('*W/m^2*')'))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates,format="%F"))


df$long_up_corr_Avg.c = df$long_up_corr_Avg
```




#### Net SW Avg

No initial cleaning
```{r, warning=FALSE}
ggplot(data = df)+
  geom_point(aes(TIMESTAMP,Rs_net_Avg))+
  scale_y_continuous(limits = c(-20, 600),
                     expression('SW net ('*W/m^2*')'))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates,format="%F"))


Rs_net.limits = df$Rs_net_Avg
```

Rolling SD (doesn't do anything, left for future use)
```{r, warning=FALSE}
f = Rs_net.limits # first make a new flux vector to apply the above filters
# prepare the inputs for a zero-phase (forward and reverse) filter  
ind       = which(complete.cases(f))   # first save the index of all the NAs
b         = rep(1,8)/8                 # moving average coefficient
a         = 1                          # coefficient of the ARMA filter
mad_i    = filtfilt(b, a, na.omit(f)) #create a forward and reverse ARMA filter
mad_filt = f                          # make a copy of the full fluxes again
mad_filt[ind] = mad_i                # apply the filter where the real data exist

n = 7*48 # set the length of the rolling filter, 48 half hours in day * x days
roll.mad = rollapply(data = mad_filt,
                     width = n,
                     FUN = sd,
                     partial = TRUE,
                     na.rm = T,
                     fill = NA)  #create a rolling MAD or sd or other
roll.mad[is.na(mad_filt)] = NA  #make NA values where NAs exist in the real data

ggplot(df)+geom_hline(yintercept = 0)+
  geom_point(aes(TIMESTAMP,Rs_net.limits,col='Net SW'))+
  geom_line(aes(TIMESTAMP,mad_filt,col='Filter'))+
  geom_line(aes(TIMESTAMP,roll.mad,col='MAD'))+
  scale_y_continuous(limits = c(-5,600))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates,format="%F"))+
  scale_color_manual(values=c('yellow','red','black'))


 

 
#adjust this value (N) to tweak how many MADs to be away from the norm
N = 5

#Add clean value to dataframe (_.c)

df$Rs_net_Avg.c = ifelse(abs(Rs_net.limits - mad_filt) > (N * roll.mad),NA,Rs_net.limits)

#Compare cleaned vs. uncleaned

plot(df$TIMESTAMP,df$Rs_net_Avg,col='red',ylim = c(0,800));points(df$TIMESTAMP,df$Rs_net_Avg.c)
 

 
ggplot(data = df)+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*6,ymin = mad_filt-roll.mad*6,fill='6'))+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*4,ymin = mad_filt-roll.mad*4,fill='4'))+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*3,ymin = mad_filt-roll.mad*3,fill='3'))+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*1,ymin = mad_filt-roll.mad*1,fill='1'))+
  geom_point(aes(TIMESTAMP,Rs_net.limits),col='red')+
  geom_point(aes(TIMESTAMP,Rs_net_Avg.c),col='black')+
  scale_y_continuous(limits = c(-600, 800))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates,format="%F"))
```


#### Net LW Avg

Doesn't do anything
```{r, warning=FALSE}
ggplot(data = df)+
  geom_point(aes(TIMESTAMP,Rl_net_Avg))+
  scale_y_continuous(limits = c(-20, 20),
                     expression('LW net ('*W/m^2*')'))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates,format="%F"))


Rl_net.limits = df$Rl_net_Avg
```

Rolling SD (doesn't do anything, left for future use)
```{r, warning=FALSE}
f = Rl_net.limits # first make a new flux vector to apply the above filters
# prepare the inputs for a zero-phase (forward and reverse) filter  
ind       = which(complete.cases(f))   # first save the index of all the NAs
b         = rep(1,8)/8                 # moving average coefficient
a         = 1                          # coefficient of the ARMA filter
mad_i    = filtfilt(b, a, na.omit(f)) #create a forward and reverse ARMA filter
mad_filt = f                          # make a copy of the full fluxes again
mad_filt[ind] = mad_i                # apply the filter where the real data exist

n = 7*48 # set the length of the rolling filter, 48 half hours in day * x days
roll.mad = rollapply(data = mad_filt,
                     width = n,
                     FUN = sd,
                     partial = TRUE,
                     na.rm = T,
                     fill = NA)  #create a rolling MAD or sd or other
roll.mad[is.na(mad_filt)] = NA  #make NA values where NAs exist in the real data

ggplot(df)+geom_hline(yintercept = 0)+
  geom_point(aes(TIMESTAMP,Rl_net.limits,col='Net SW'))+
  geom_line(aes(TIMESTAMP,mad_filt,col='Filter'))+
  geom_line(aes(TIMESTAMP,roll.mad,col='MAD'))+
  scale_y_continuous(limits = c(-5,600))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates,format="%F"))+
  scale_color_manual(values=c('yellow','red','black'))


 

 
#adjust this value (N) to tweak how many MADs to be away from the norm
N = 5

#Add clean value to dataframe (_.c)

df$Rl_net_Avg.c = ifelse(abs(Rl_net.limits - mad_filt) > (N * roll.mad),NA,Rl_net.limits)

#Compare cleaned vs. uncleaned

plot(df$TIMESTAMP,df$Rl_net_Avg,col='red',ylim = c(0,800));points(df$TIMESTAMP,df$Rs_net_Avg.c)
 

 
ggplot(data = df)+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*6,ymin = mad_filt-roll.mad*6,fill='6'))+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*4,ymin = mad_filt-roll.mad*4,fill='4'))+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*3,ymin = mad_filt-roll.mad*3,fill='3'))+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*1,ymin = mad_filt-roll.mad*1,fill='1'))+
  geom_point(aes(TIMESTAMP,Rl_net.limits),col='red')+
  geom_point(aes(TIMESTAMP,Rl_net_Avg.c),col='black')+
  scale_y_continuous(limits = c(-400, 300))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates,format="%F"))
```




#### Rain 

Looks fine, doesn't do anything
```{r, warning=FALSE}
ggplot(data = df)+
  geom_point(aes(TIMESTAMP, Rain_mm_Tot),col='black')+
  scale_y_continuous(limits = c(-1,5),
                     expression('Rain ('*mm*')'))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates,format="%F"))

df$Rain_mm_Tot.c = df$Rain_mm_Tot
```




#### Temp 1

Looks fine, doesn't do anything
```{r, warning=FALSE}

ggplot(data = df)+
  geom_point(aes(TIMESTAMP, Temp_C_Avg_1))+
  scale_y_continuous(limits = c(-12, 20),
                     expression('Temp 1 Avg ('*C*')'))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates,format="%F"))

df$Temp_C_Avg_1.c = df$Temp_C_Avg_1

```


#### Temp 2

Looks fine, doesn't do anything
```{r, warning=FALSE}

ggplot(data = df)+
  geom_point(aes(TIMESTAMP, Temp_C_Avg_2))+
  scale_y_continuous(limits = c(-10, 14),
                     expression('Temp 2 Avg ('*C*')'))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates,format="%F"))

df$Temp_C_Avg_2.c = df$Temp_C_Avg_2

```


#### Temp 3

Looks fine, doesn't do anything
```{r, warning=FALSE}

ggplot(data = df)+
  geom_point(aes(TIMESTAMP, Temp_C_Avg_3))+
  scale_y_continuous(limits = c(-10, 11),
                     expression('Temp 3 Avg ('*C*')'))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates,format="%F"))

df$Temp_C_Avg_3.c = df$Temp_C_Avg_3

```

#### Temp 4

Looks fine, doesn't do anything
```{r, warning=FALSE}

ggplot(data = df)+
  geom_point(aes(TIMESTAMP, Temp_C_Avg_4))+
  scale_y_continuous(limits = c(-12, 27),
                     expression('Temp 4 Avg ('*C*')'))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates,format="%F"))

df$Temp_C_Avg_4.c = df$Temp_C_Avg_4

```


#### Temp 5

Looks fine, doesn't do anything
```{r, warning=FALSE}

ggplot(data = df)+
  geom_point(aes(TIMESTAMP, Temp_C_Avg_5))+
  scale_y_continuous(limits = c(-10, 25),
                     expression('Temp 5 Avg ('*C*')'))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates,format="%F"))

df$Temp_C_Avg_5.c = df$Temp_C_Avg_5

```


#### Temp 6

Cleaning w/ limits
```{r, warning=FALSE}

ggplot(data = df)+
  geom_point(aes(TIMESTAMP, Temp_C_Avg_6))+
  geom_hline(aes(yintercept=6, col = 'red'))+
  scale_y_continuous(limits = c(-20,25),
                     expression('Temp 6 Avg ('*C*')'))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates,format="%F"))


Temp_C_Avg_6.limits = replace(df$Temp_C_Avg_6,df$Temp_C_Avg_6 > 6,NA)

df$Temp_C_Avg_6.c = Temp_C_Avg_6.limits

ggplot(data = df)+
  geom_point(aes(TIMESTAMP, Temp_C_Avg_6, col = 'uncleaned'))+
  geom_point(aes(TIMESTAMP, Temp_C_Avg_6.c, col = 'cleaned'))+
  scale_y_continuous(limits = c(-18,25),
                     expression('Temp 6 Avg ('*C*')'))+scale_color_manual(values=c('black','red'))
  scale_x_datetime(limits = as.POSIXct(biomet_dates,format="%F"))

```



### Soil meaurements

#### EC columns

```{r, warning=FALSE}

plot_grid(
plot(df$TIMESTAMP, df$EC_5cm),
plot(df$TIMESTAMP, df$EC_10cm),
plot(df$TIMESTAMP, df$EC_20cm),
plot(df$TIMESTAMP, df$EC_30cm),
plot(df$TIMESTAMP, df$EC_40cm),
plot(df$TIMESTAMP, df$EC_50cm)
)
```



#### 5 cm

##### VWC 5cm 

```{r, warning=FALSE}
ggplot(data = df)+
  geom_point(aes(TIMESTAMP, VWC_5cm*100,col='5 cm'))+ # convert to percentage 
  scale_y_continuous(limits = c(0,60),
                     expression('% VWC'))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates,format="%F"))


VWC_5cm.limits = df$VWC_5cm

VWC_5cm.limits = ifelse(df$VWC_5cm == 0,NA, VWC_5cm.limits)

df$VWC_5cm.c = VWC_5cm.limits

ggplot(data = df)+
  geom_point(aes(TIMESTAMP, VWC_5cm.c*100,col='5 cm'))+ # convert to percentage 
  scale_y_continuous(limits = c(0,60),
                     expression('% VWC'))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates,format="%F"))
```

##### Perm 5cm 

```{r, warning=FALSE}
ggplot(data = df)+
  geom_point(aes(TIMESTAMP, Perm_5cm ,col='5 cm'))+ 
  scale_y_continuous(limits = c(0,45),
                     expression('Perm'))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates,format="%F"))


Perm_5cm.limits = df$Perm_5cm

Perm_5cm.limits = ifelse(df$Perm_5cm == 0,NA, Perm_5cm.limits)

df$Perm_5cm.c = Perm_5cm.limits

ggplot(data = df)+
  geom_point(aes(TIMESTAMP, Perm_5cm.c,col='5 cm'))+ 
  scale_y_continuous(limits = c(0,45),
                     expression('Perm'))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates,format="%F"))
```


Plot perm/VWC w/rain to explain peaks in data
```{r, warning=FALSE}
ggplot(data = df)+
  geom_point(aes(TIMESTAMP, VWC_5cm.c*100,col='WVC 5 cm'))+ # convert to percentage
  geom_point(aes(TIMESTAMP, Perm_5cm.c, col='Perm 5cm'))+
  geom_point(aes(TIMESTAMP, Rain_mm_Tot.c, col='Rain'))+
  scale_y_continuous(limits = c(0,60), expression("% VWC, Rain (mm), Perm")) +
  scale_x_datetime(limits = as.POSIXct(biomet_dates,format="%F"))
```
  
  
##### Soil temp 5cm 

```{r, warning=FALSE}

ggplot(data = df)+ theme_bw()+ geom_hline(yintercept = 0)+
  geom_point(aes(TIMESTAMP, TC_5cm, col = '5cm'))+
  scale_y_continuous(limits = c(-10, 16),
                     expression('5 cm Soil T ('*C*')'))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates))

TC_5cm.limits = df$TC_5cm

TC_5cm.limits = ifelse(df$TC_5cm == 0 & df$TIMESTAMP >= '2023-08-14' & df$TIMESTAMP <= '2023-09-01' ,NA, TC_5cm.limits)

## Check to see values are removed
ggplot(data = df)+ theme_bw()+ geom_hline(yintercept = 0)+
  geom_line(aes(TIMESTAMP, TC_5cm.limits, col = '5cm'))+
  scale_y_continuous(limits = c(-10, 16),
                     expression('5 cm Soil T ('*C*')'))+
  scale_x_datetime(limits = as.POSIXct(c('2023-08-14','2023-09-01')))

ggplot(data = df)+ theme_bw()+ geom_hline(yintercept = 0)+
  geom_line(aes(TIMESTAMP, TC_5cm, col = '5cm'))+
  scale_y_continuous(limits = c(-10, 16),
                     expression('5 cm Soil T ('*C*')'))+
  scale_x_datetime(limits = as.POSIXct(c('2023-10-16', '2023-10-23')))


TC_5cm.limits = ifelse(df$TC_5cm == 0 & df$TIMESTAMP >= '2023-10-16' & df$TIMESTAMP <= '2023-10-23' ,NA, TC_5cm.limits)

## Check to see values are removed
ggplot(data = df)+ theme_bw()+ geom_hline(yintercept = 0)+
  geom_line(aes(TIMESTAMP, TC_5cm.limits, col = '5cm'))+
  scale_y_continuous(limits = c(-10, 16),
                     expression('5 cm Soil T ('*C*')'))+
  scale_x_datetime(limits = as.POSIXct(c('2023-10-16', '2023-10-23')))
```


Rolling MAD

```{r}
f = TC_5cm.limits # first make a new flux vector to apply the above filters
# prepare the inputs for a zero-phase (forward and reverse) filter  
ind       = which(complete.cases(f))   # first save the index of all the NAs
b         = rep(1,8)/8                 # moving average coefficient
a         = 1                          # coefficient of the ARMA filter
mad_i    = filtfilt(b, a, na.omit(f)) #create a forward and reverse ARMA filter
mad_filt = f                          # make a copy of the full fluxes again
mad_filt[ind] = mad_i                # apply the filter where the real data exist

n = 7*48 # set the length of the rolling filter, 48 half hours in day * x days
roll.mad = rollapply(data = mad_filt,
                     width = n,
                     FUN = mad,
                     partial = TRUE,
                     na.rm = T,
                     fill = NA)  #create a rolling MAD or sd or other
roll.mad[is.na(mad_filt)] = NA  #make NA values where NAs exist in the real data

ggplot(df)+geom_hline(yintercept = 0)+
  geom_point(aes(TIMESTAMP,TC_5cm.limits,col='Hummock 90 cm Soil T'))+
  geom_line(aes(TIMESTAMP,mad_filt,col='Filter'))+
  geom_line(aes(TIMESTAMP,roll.mad,col='MAD'))+
  scale_y_continuous(limits = c(-18,16))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates,format="%F"))+
  scale_color_manual(values=c('yellow','black','red'))



#adjust this value (N) to tweak how many MADs to be away from the norm
N = 3

#Add clean value to dataframe (_.c)

df$TC_5cm.c = ifelse(abs(TC_5cm.limits - mad_filt) > (N * roll.mad),NA,TC_5cm.limits)

#Compare cleaned vs. uncleaned

ggplot(data = df)+geom_hline(yintercept = 0)+
  geom_point(aes(TIMESTAMP,TC_5cm,col='uncleaned'))+
  geom_point(aes(TIMESTAMP,TC_5cm.c,col='cleaned'))+
  scale_y_continuous(limits=c(-18,18))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates,format="%F"))+
  scale_color_manual(values=c('black','red'))



ggplot(data = df)+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*6,ymin = mad_filt-roll.mad*6,fill='6'))+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*3,ymin = mad_filt-roll.mad*3,fill='3'))+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*2,ymin = mad_filt-roll.mad*2,fill='2'))+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*1,ymin = mad_filt-roll.mad*1,fill='1'))+
  geom_point(aes(TIMESTAMP,TC_5cm),col='red')+
  geom_point(aes(TIMESTAMP,TC_5cm.c),col='black')+
  scale_y_continuous(limits = c(-25,25))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates,format="%F"))

```



#### 10 cm

##### VWC 10cm 

```{r, warning=FALSE}
ggplot(data = df)+
  geom_point(aes(TIMESTAMP, VWC_10cm*100,col='10 cm'))+ # convert to percentage 
  scale_y_continuous(limits = c(0,55),
                     expression('% VWC'))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates,format="%F"))

ggplot(data = df)+
  geom_point(aes(TIMESTAMP, VWC_10cm*100,col='10 cm'))+ 
  scale_y_continuous(limits = c(0,4),
                     expression('% VWC'))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates))

VWC_10cm.limits = df$VWC_10cm

VWC_10cm.limits = ifelse(df$VWC_10cm == 0 & df$TIMESTAMP <= '2023-10-24' ,NA, VWC_10cm.limits)

df$VWC_10cm.c = VWC_10cm.limits

# Check to see if values are removed

ggplot(data = df)+
  geom_point(aes(TIMESTAMP, VWC_10cm.c*100,col='10 cm'))+ # convert to percentage
  scale_y_continuous(limits = c(0,55),
                     expression('% VWC'))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates,format="%F"))
```

##### Perm 10cm 

```{r, warning=FALSE}
ggplot(data = df)+
  geom_point(aes(TIMESTAMP, Perm_10cm ,col='10 cm'))+ 
  scale_y_continuous(limits = c(0,100),
                     expression('Perm'))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates,format="%F"))

Perm_10cm.limits = df$Perm_10cm

Perm_10cm.limits = ifelse(df$Perm_10cm == 0 & df$TIMESTAMP <= '2023-10-24' ,NA, Perm_10cm.limits)

df$Perm_10cm.c = Perm_10cm.limits

ggplot(data = df)+
  geom_point(aes(TIMESTAMP, Perm_10cm.c,col='10 cm'))+ 
  scale_y_continuous(limits = c(0,50),
                     expression('Perm'))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates,format="%F"))
```



##### Soil temp 10cm 

```{r, warning=FALSE}
ggplot(data = df)+ theme_bw()+ geom_hline(yintercept = 0)+
  geom_line(aes(TIMESTAMP, TC_10cm, col = '10cm'))+
  scale_y_continuous(limits = c(-10,16),
                     expression('10 cm Soil T ('*C*')'))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates,format="%F"))

TC_10cm.limits = df$TC_10cm


## Limits- removes a few zeros 

# Removes early zeros
ggplot(data = df)+ theme_bw()+ geom_hline(yintercept = 0)+
  geom_line(aes(TIMESTAMP, TC_10cm, col = '10cm'))+
  scale_y_continuous(limits = c(-10, 16),
                     expression('10 cm Soil T ('*C*')'))+
  scale_x_datetime(limits = as.POSIXct(c('2023-08-14','2023-10-01')))


TC_10cm.limits = ifelse(df$TC_10cm == 0 & df$TIMESTAMP <= '2023-10-01' ,NA, TC_10cm.limits)

# Check to see values are removed
ggplot(data = df)+ theme_bw()+ geom_hline(yintercept = 0)+
  geom_line(aes(TIMESTAMP, TC_10cm.limits, col = '10cm'))+
  scale_y_continuous(limits = c(-10, 16),
                     expression('10 cm Soil T ('*C*')'))+
  scale_x_datetime(limits = as.POSIXct(c('2023-08-14','2023-10-01')))

# finds & removes later zeroes 
ggplot(data = df)+ theme_bw()+ geom_hline(yintercept = 0)+
  geom_line(aes(TIMESTAMP, TC_10cm, col = '10cm'))+
  scale_y_continuous(limits = c(-1, 6),
                     expression('10 cm Soil T ('*C*')'))+
  scale_x_datetime(limits = as.POSIXct(c('2023-10-18', '2023-10-23')))


TC_10cm.limits = ifelse(df$TC_10cm == 0 & df$TIMESTAMP >= '2023-10-18' & df$TIMESTAMP <= '2023-10-23' ,NA, TC_10cm.limits)

# Check to see values are removed
ggplot(data = df)+ theme_bw()+ geom_hline(yintercept = 0)+
  geom_line(aes(TIMESTAMP, TC_10cm.limits, col = '10cm'))+
  scale_y_continuous(limits = c(-10, 16),
                     expression('10 cm Soil T ('*C*')'))+
  scale_x_datetime(limits = as.POSIXct(c('2023-10-09', '2023-10-23')))
```



Rolling MAD 

```{r}

f = TC_10cm.limits # first make a new flux vector to apply the above filters
# prepare the inputs for a zero-phase (forward and reverse) filter  
ind       = which(complete.cases(f))   # first save the index of all the NAs
b         = rep(1,8)/8                 # moving average coefficient
a         = 1                          # coefficient of the ARMA filter
mad_i    = filtfilt(b, a, na.omit(f)) #create a forward and reverse ARMA filter
mad_filt = f                          # make a copy of the full fluxes again
mad_filt[ind] = mad_i                # apply the filter where the real data exist

n = 7*48 # set the length of the rolling filter, 48 half hours in day * x days
roll.mad = rollapply(data = mad_filt,
                     width = n,
                     FUN = mad,
                     partial = TRUE,
                     na.rm = T,
                     fill = NA)  #create a rolling MAD or sd or other
roll.mad[is.na(mad_filt)] = NA  #make NA values where NAs exist in the real data

ggplot(df)+geom_hline(yintercept = 0)+
  geom_point(aes(TIMESTAMP,TC_10cm.limits,col='Hummock 90 cm Soil T'))+
  geom_line(aes(TIMESTAMP,mad_filt,col='Filter'))+
  geom_line(aes(TIMESTAMP,roll.mad,col='MAD'))+
  scale_y_continuous(limits = c(-18,16))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates,format="%F"))+
  scale_color_manual(values=c('yellow','black','red'))





#adjust this value (N) to tweak how many MADs to be away from the norm
N = 6

#Add clean value to dataframe (_.c)

df$TC_10cm.c = ifelse(abs(TC_10cm.limits - mad_filt) > (N * roll.mad),NA,TC_10cm.limits)

#Compare cleaned vs. uncleaned

ggplot(data = df)+geom_hline(yintercept = 0)+
  geom_point(aes(TIMESTAMP,TC_10cm,col='uncleaned'))+
  geom_point(aes(TIMESTAMP,TC_10cm.c,col='cleaned'))+
  scale_y_continuous(limits=c(-18,18))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates,format="%F"))+
  scale_color_manual(values=c('black','red'))



ggplot(data = df)+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*6,ymin = mad_filt-roll.mad*6,fill='6'))+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*3,ymin = mad_filt-roll.mad*3,fill='3'))+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*2,ymin = mad_filt-roll.mad*2,fill='2'))+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*1,ymin = mad_filt-roll.mad*1,fill='1'))+
  geom_point(aes(TIMESTAMP,TC_10cm),col='red')+
  geom_point(aes(TIMESTAMP,TC_10cm.c),col='black')+
  scale_y_continuous(limits = c(-25,18))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates,format="%F"))

# plot showing zeros getting removed by rolling MAD
ggplot(data = df)+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*6,ymin = mad_filt-roll.mad*6,fill='6'))+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*3,ymin = mad_filt-roll.mad*3,fill='3'))+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*2,ymin = mad_filt-roll.mad*2,fill='2'))+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*1,ymin = mad_filt-roll.mad*1,fill='1'))+
  geom_point(aes(TIMESTAMP,TC_10cm),col='red')+
  geom_point(aes(TIMESTAMP,TC_10cm.c),col='black')+
  scale_y_continuous(limits = c(-25,18))
```





#### 20 cm

##### VWC 20cm 

```{r, warning=FALSE}
ggplot(data = df)+
  geom_point(aes(TIMESTAMP, VWC_20cm*100,col='20 cm'))+ # convert to percentage 
  scale_y_continuous(limits = c(0,50),
                     expression('% VWC'))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates,format="%F"))

VWC_20cm.limits = df$VWC_20cm

VWC_20cm.limits = ifelse(df$VWC_20cm == 0 ,NA, VWC_20cm.limits)

df$VWC_20cm.c = VWC_20cm.limits

# Check to see if values are removed

ggplot(data = df)+
  geom_point(aes(TIMESTAMP, VWC_20cm.c*100,col='20 cm'))+ # convert to percentage
  scale_y_continuous(limits = c(0,50),
                     expression('% VWC'))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates,format="%F"))
```

##### Perm 20cm 

```{r, warning=FALSE}
ggplot(data = df)+
  geom_point(aes(TIMESTAMP, Perm_20cm ,col='20 cm'))+ 
  scale_y_continuous(limits = c(0,35),
                     expression('Perm'))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates,format="%F"))

Perm_20cm.limits = df$Perm_20cm

Perm_20cm.limits = ifelse(df$Perm_20cm == 0 & df$TIMESTAMP <= '2023-10-24' ,NA, Perm_20cm.limits)

df$Perm_20cm.c = Perm_20cm.limits

#check to see if values are removed
ggplot(data = df)+
  geom_point(aes(TIMESTAMP, Perm_20cm.c,col='20 cm'))+ 
  scale_y_continuous(limits = c(0,35),
                     expression('Perm'))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates,format="%F"))
```


##### Soil temp 20cm 

```{r, warning=FALSE}
ggplot(data = df)+ theme_bw()+ geom_hline(yintercept = 0)+
  geom_line(aes(TIMESTAMP, TC_20cm, col = '20cm'))+
  scale_y_continuous(limits = c(-10,16),
                     expression('20 cm Soil T ('*C*')'))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates,format="%F"))

TC_20cm.limits = df$TC_20cm

## Limits- removes a few zeros 

# Removes early zeros
ggplot(data = df)+ theme_bw()+ geom_hline(yintercept = 0)+
  geom_line(aes(TIMESTAMP, TC_20cm, col = '20cm'))+
  scale_y_continuous(limits = c(-10, 16),
                     expression('20 cm Soil T ('*C*')'))+
  scale_x_datetime(limits = as.POSIXct(c('2023-08-14','2023-10-01')))


TC_20cm.limits = ifelse(df$TC_20cm == 0 & df$TIMESTAMP <= '2023-10-01' ,NA, TC_20cm.limits)

# Check to see values are removed
ggplot(data = df)+ theme_bw()+ geom_hline(yintercept = 0)+
  geom_line(aes(TIMESTAMP, TC_20cm.limits, col = '20cm'))+
  scale_y_continuous(limits = c(-10, 16),
                     expression('20 cm Soil T ('*C*')'))+
  scale_x_datetime(limits = as.POSIXct(c('2023-08-14','2023-10-01')))


# looks for later zeroes
ggplot(data = df)+ theme_bw()+ geom_hline(yintercept = 0)+
  geom_line(aes(TIMESTAMP, TC_20cm, col = '20cm'))+
  scale_y_continuous(limits = c(-1, 1),
                     expression('20 cm Soil T ('*C*')'))+
  scale_x_datetime(limits = as.POSIXct(c('2023-10-18', '2023-10-23')))
TC_10cm.limits = ifelse(df$TC_10cm == 0 & df$TIMESTAMP >= '2023-10-18' & df$TIMESTAMP <= '2023-10-23' ,NA, TC_10cm.limits)

# Check to see values are removed
ggplot(data = df)+ theme_bw()+ geom_hline(yintercept = 0)+
  geom_line(aes(TIMESTAMP, TC_10cm.limits, col = '10cm'))+
  scale_y_continuous(limits = c(-10, 16),
                     expression('10 cm Soil T ('*C*')'))+
  scale_x_datetime(limits = as.POSIXct(c('2023-10-18', '2023-10-23')))

```


Rolling MAD

```{r}

f = TC_20cm.limits # first make a new flux vector to apply the above filters
# prepare the inputs for a zero-phase (forward and reverse) filter  
ind       = which(complete.cases(f))   # first save the index of all the NAs
b         = rep(1,8)/8                 # moving average coefficient
a         = 1                          # coefficient of the ARMA filter
mad_i    = filtfilt(b, a, na.omit(f)) #create a forward and reverse ARMA filter
mad_filt = f                          # make a copy of the full fluxes again
mad_filt[ind] = mad_i                # apply the filter where the real data exist

n = 7*48 # set the length of the rolling filter, 48 half hours in day * x days
roll.mad = rollapply(data = mad_filt,
                     width = n,
                     FUN = mad,
                     partial = TRUE,
                     na.rm = T,
                     fill = NA)  #create a rolling MAD or sd or other
roll.mad[is.na(mad_filt)] = NA  #make NA values where NAs exist in the real data

ggplot(df)+geom_hline(yintercept = 0)+
  geom_point(aes(TIMESTAMP,TC_20cm.limits,col='Hummock 90 cm Soil T'))+
  geom_line(aes(TIMESTAMP,mad_filt,col='Filter'))+
  geom_line(aes(TIMESTAMP,roll.mad,col='MAD'))+
  scale_y_continuous(limits = c(-18,16))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates,format="%F"))+
  scale_color_manual(values=c('yellow','black','red'))





#adjust this value (N) to tweak how many MADs to be away from the norm
N = 6

#Add clean value to dataframe (_.c)

df$TC_20cm.c = ifelse(abs(TC_20cm.limits - mad_filt) > (N * roll.mad),NA,TC_20cm.limits)

#Compare cleaned vs. uncleaned

ggplot(data = df)+geom_hline(yintercept = 0)+
  geom_point(aes(TIMESTAMP,TC_20cm,col='uncleaned'))+
  geom_point(aes(TIMESTAMP,TC_20cm.c,col='cleaned'))+
  scale_y_continuous(limits=c(-18,18))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates,format="%F"))+
  scale_color_manual(values=c('black','red'))



ggplot(data = df)+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*6,ymin = mad_filt-roll.mad*6,fill='6'))+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*3,ymin = mad_filt-roll.mad*3,fill='3'))+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*2,ymin = mad_filt-roll.mad*2,fill='2'))+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*1,ymin = mad_filt-roll.mad*1,fill='1'))+
  geom_point(aes(TIMESTAMP,TC_20cm),col='red')+
  geom_point(aes(TIMESTAMP,TC_20cm.c),col='black')+
  scale_y_continuous(limits = c(-20,15))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates,format="%F"))

```




#### 30 cm

##### VWC 30cm 

```{r, warning=FALSE}
ggplot(data = df)+
  geom_point(aes(TIMESTAMP, VWC_30cm*100,col='30 cm'))+ # convert to percentage 
  scale_y_continuous(limits = c(0,100),
                     expression('% VWC'))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates,format="%F"))

VWC_30cm.limits = df$VWC_30cm

VWC_30cm.limits = ifelse(df$VWC_30cm == 0 ,NA, VWC_30cm.limits)

df$VWC_30cm.c = VWC_30cm.limits

# Check to see if values are removed

ggplot(data = df)+
  geom_point(aes(TIMESTAMP, VWC_30cm.c*100,col='30 cm'))+ # convert to percentage
  scale_y_continuous(limits = c(0,100),
                     expression('% VWC'))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates))
```

##### Perm 30cm 

```{r, warning=FALSE}
ggplot(data = df)+
  geom_point(aes(TIMESTAMP, Perm_30cm ,col='30 cm'))+ 
  scale_y_continuous(limits = c(0,100),
                     expression('Perm'))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates))

Perm_30cm.limits = df$Perm_30cm

Perm_30cm.limits = ifelse(df$Perm_30cm == 0,NA, Perm_30cm.limits)

df$Perm_30cm.c = Perm_30cm.limits
```

##### Soil temp 30cm 

```{r, warning=FALSE}
ggplot(data = df)+ theme_bw()+ geom_hline(yintercept = 0)+
  geom_line(aes(TIMESTAMP, TC_30cm, col = '30cm'))+
  scale_y_continuous(limits = c(-10,16),
                     expression('30 cm Soil T ('*C*')'))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates))

TC_30cm.limits = df$TC_30cm


## Limits- removes a few zeros 

```



Rolling MAD 

```{r}
f = TC_30cm.limits # first make a new flux vector to apply the above filters
# prepare the inputs for a zero-phase (forward and reverse) filter  
ind       = which(complete.cases(f))   # first save the index of all the NAs
b         = rep(1,8)/8                 # moving average coefficient
a         = 1                          # coefficient of the ARMA filter
mad_i    = filtfilt(b, a, na.omit(f)) #create a forward and reverse ARMA filter
mad_filt = f                          # make a copy of the full fluxes again
mad_filt[ind] = mad_i                # apply the filter where the real data exist

n = 7*48 # set the length of the rolling filter, 48 half hours in day * x days
roll.mad = rollapply(data = mad_filt,
                     width = n,
                     FUN = mad,
                     partial = TRUE,
                     na.rm = T,
                     fill = NA)  #create a rolling MAD or sd or other
roll.mad[is.na(mad_filt)] = NA  #make NA values where NAs exist in the real data

ggplot(df)+geom_hline(yintercept = 0)+
  geom_point(aes(TIMESTAMP,TC_30cm.limits,col='Soil T 30 cm'))+
  geom_line(aes(TIMESTAMP,mad_filt,col='Filter'))+
  geom_line(aes(TIMESTAMP,roll.mad,col='MAD'))+
  scale_y_continuous(limits = c(-15,10))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates,format="%F"))+
  scale_color_manual(values=c('yellow','black','red'))





#adjust this value (N) to tweak how many MADs to be away from the norm
N = 6

#Add clean value to dataframe (_.c)

df$TC_30cm.c = ifelse(abs(TC_30cm.limits - mad_filt) > (N * roll.mad),NA,TC_30cm.limits)

#Compare cleaned vs. uncleaned

ggplot(data = df)+geom_hline(yintercept = 0)+
  geom_point(aes(TIMESTAMP,TC_30cm,col='uncleaned'))+
  geom_point(aes(TIMESTAMP,TC_30cm.c,col='cleaned'))+
  scale_y_continuous(limits=c(-15,10))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates,format="%F"))+
  scale_color_manual(values=c('black','red'))



ggplot(data = df)+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*6,ymin = mad_filt-roll.mad*6,fill='6'))+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*3,ymin = mad_filt-roll.mad*3,fill='3'))+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*2,ymin = mad_filt-roll.mad*2,fill='2'))+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*1,ymin = mad_filt-roll.mad*1,fill='1'))+
  geom_point(aes(TIMESTAMP,TC_30cm),col='red')+
  geom_point(aes(TIMESTAMP,TC_30cm.c),col='black')+
  scale_y_continuous(limits = c(-15, 15))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates,format="%F"))

```





#### 40 cm

##### VWC 40cm 

```{r, warning=FALSE}
ggplot(data = df)+
  geom_point(aes(TIMESTAMP, VWC_40cm*100,col='40 cm'))+ # convert to percentage 
  scale_y_continuous(limits = c(0,50),
                     expression('% VWC'))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates))

VWC_40cm.limits = df$VWC_40cm

VWC_40cm.limits = ifelse(df$VWC_40cm == 0 ,NA, VWC_40cm.limits)

df$VWC_40cm.c = VWC_40cm.limits

# Check to see if values are removed

ggplot(data = df)+
  geom_point(aes(TIMESTAMP, VWC_40cm.c*100,col='40 cm'))+ # convert to percentage
  scale_y_continuous(limits = c(0,50),
                     expression('% VWC'))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates))


```

##### Perm 40cm 

```{r, warning=FALSE}
ggplot(data = df)+
  geom_point(aes(TIMESTAMP, Perm_40cm ,col='40 cm'))+ 
  scale_y_continuous(limits = c(0,40),
                     expression('Perm'))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates))

Perm_40cm.limits = df$Perm_40cm

Perm_40cm.limits = ifelse(df$Perm_40cm == 0,NA, Perm_40cm.limits)

df$Perm_40cm.c = Perm_40cm.limits

#check to see if values are removed
ggplot(data = df)+
  geom_point(aes(TIMESTAMP, Perm_40cm.c,col='40 cm'))+ 
  scale_y_continuous(limits = c(0,40),
                     expression('Perm'))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates))


```

##### Soil temp 40cm 

```{r, warning=FALSE}
ggplot(data = df)+ theme_bw()+ geom_hline(yintercept = 0)+
  geom_line(aes(TIMESTAMP, TC_40cm, col = '40cm'))+
  scale_y_continuous(limits = c(-10,16),
                     expression('40 cm Soil T ('*C*')'))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates))

TC_40cm.limits = df$TC_40cm



## Limits- removes a few zeros 

# Removes early zeros


```


Rolling MAD 
```{r}

f = TC_40cm.limits # first make a new flux vector to apply the above filters
# prepare the inputs for a zero-phase (forward and reverse) filter  
ind       = which(complete.cases(f))   # first save the index of all the NAs
b         = rep(1,8)/8                 # moving average coefficient
a         = 1                          # coefficient of the ARMA filter
mad_i    = filtfilt(b, a, na.omit(f)) #create a forward and reverse ARMA filter
mad_filt = f                          # make a copy of the full fluxes again
mad_filt[ind] = mad_i                # apply the filter where the real data exist

n = 7*48 # set the length of the rolling filter, 48 half hours in day * x days
roll.mad = rollapply(data = mad_filt,
                     width = n,
                     FUN = mad,
                     partial = TRUE,
                     na.rm = T,
                     fill = NA)  #create a rolling MAD or sd or other
roll.mad[is.na(mad_filt)] = NA  #make NA values where NAs exist in the real data

ggplot(df)+geom_hline(yintercept = 0)+
  geom_point(aes(TIMESTAMP,TC_40cm.limits,col='Soil T 40 cm'))+
  geom_line(aes(TIMESTAMP,mad_filt,col='Filter'))+
  geom_line(aes(TIMESTAMP,roll.mad,col='MAD'))+
  scale_y_continuous(limits = c(-14,10))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates,format="%F"))+
  scale_color_manual(values=c('yellow','black','red'))





#adjust this value (N) to tweak how many MADs to be away from the norm
N = 6

#Add clean value to dataframe (_.c)

df$TC_40cm.c = ifelse(abs(TC_40cm.limits - mad_filt) > (N * roll.mad),NA,TC_40cm.limits)

#Compare cleaned vs. uncleaned

ggplot(data = df)+geom_hline(yintercept = 0)+
  geom_point(aes(TIMESTAMP,TC_40cm,col='uncleaned'))+
  geom_point(aes(TIMESTAMP,TC_40cm.c,col='cleaned'))+
  scale_y_continuous(limits=c(-14, 10))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates,format="%F"))+
  scale_color_manual(values=c('black','red'))



ggplot(data = df)+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*6,ymin = mad_filt-roll.mad*6,fill='6'))+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*3,ymin = mad_filt-roll.mad*3,fill='3'))+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*2,ymin = mad_filt-roll.mad*2,fill='2'))+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*1,ymin = mad_filt-roll.mad*1,fill='1'))+
  geom_point(aes(TIMESTAMP,TC_40cm),col='red')+
  geom_point(aes(TIMESTAMP,TC_40cm.c),col='black')+
  scale_y_continuous(limits = c(-14,15))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates,format="%F"))


```




#### 50 cm

##### VWC 50cm 

```{r, warning=FALSE}
ggplot(data = df)+
  geom_point(aes(TIMESTAMP, VWC_50cm*100,col='50 cm'))+ # convert to percentage 
  scale_y_continuous(limits = c(0,45),
                     expression('% VWC'))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates))

VWC_50cm.limits = df$VWC_50cm

VWC_50cm.limits = ifelse(df$VWC_50cm == 0 ,NA, VWC_50cm.limits)

df$VWC_50cm.c = VWC_50cm.limits

# Check to see if values are removed

ggplot(data = df)+
  geom_point(aes(TIMESTAMP, VWC_50cm.c*100,col='50 cm'))+ # convert to percentage
  scale_y_continuous(limits = c(0,45),
                     expression('% VWC'))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates))
```

##### Perm 50cm 

```{r, warning=FALSE}
ggplot(data = df)+
  geom_point(aes(TIMESTAMP, Perm_50cm ,col='50 cm'))+ 
  scale_y_continuous(limits = c(0,30),
                     expression('Perm'))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates))

Perm_50cm.limits = df$Perm_50cm

Perm_50cm.limits = ifelse(df$Perm_50cm == 0,NA, Perm_50cm.limits)

df$Perm_50cm.c = Perm_50cm.limits

#check to see if values are removed
ggplot(data = df)+
  geom_point(aes(TIMESTAMP, Perm_50cm.c,col='50 cm'))+ 
  scale_y_continuous(limits = c(0,30),
                     expression('Perm'))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates))
```

##### Soil temp 50cm 

```{r, warning=FALSE}
ggplot(data = df)+ theme_bw()+ geom_hline(yintercept = 0)+
  geom_line(aes(TIMESTAMP, TC_50cm, col = '50cm'))+
  scale_y_continuous(limits = c(-15,16),
                     expression('50 cm Soil T ('*C*')'))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates,format="%F"))

TC_50cm.limits = df$TC_50cm



## Limits- removes a few zeros 

# Removes early zeros


```



Rolling MAD - removing too much good data?

```{r}
f = TC_50cm.limits # first make a new flux vector to apply the above filters
# prepare the inputs for a zero-phase (forward and reverse) filter  
ind       = which(complete.cases(f))   # first save the index of all the NAs
b         = rep(1,8)/8                 # moving average coefficient
a         = 1                          # coefficient of the ARMA filter
mad_i    = filtfilt(b, a, na.omit(f)) #create a forward and reverse ARMA filter
mad_filt = f                          # make a copy of the full fluxes again
mad_filt[ind] = mad_i                # apply the filter where the real data exist

n = 7*48 # set the length of the rolling filter, 48 half hours in day * x days
roll.mad = rollapply(data = mad_filt,
                     width = n,
                     FUN = mad,
                     partial = TRUE,
                     na.rm = T,
                     fill = NA)  #create a rolling MAD or sd or other
roll.mad[is.na(mad_filt)] = NA  #make NA values where NAs exist in the real data

ggplot(df)+geom_hline(yintercept = 0)+
  geom_point(aes(TIMESTAMP,TC_50cm.limits,col='Soil T 50 cm'))+
  geom_line(aes(TIMESTAMP,mad_filt,col='Filter'))+
  geom_line(aes(TIMESTAMP,roll.mad,col='MAD'))+
  scale_y_continuous(limits = c(-13,16))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates,format="%F"))+
  scale_color_manual(values=c('yellow','black','red'))





#adjust this value (N) to tweak how many MADs to be away from the norm
N = 6

#Add clean value to dataframe (_.c)

df$TC_50cm.c = ifelse(abs(TC_50cm.limits - mad_filt) > (N * roll.mad),NA,TC_50cm.limits)

#Compare cleaned vs. uncleaned

ggplot(data = df)+geom_hline(yintercept = 0)+
  geom_point(aes(TIMESTAMP,TC_50cm,col='uncleaned'))+
  geom_point(aes(TIMESTAMP,TC_50cm.c,col='cleaned'))+
  scale_y_continuous(limits=c(-13,10))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates,format="%F"))+
  scale_color_manual(values=c('black','red'))



ggplot(data = df)+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*6,ymin = mad_filt-roll.mad*6,fill='6'))+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*3,ymin = mad_filt-roll.mad*3,fill='3'))+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*2,ymin = mad_filt-roll.mad*2,fill='2'))+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*1,ymin = mad_filt-roll.mad*1,fill='1'))+
  geom_point(aes(TIMESTAMP,TC_50cm),col='red')+
  geom_point(aes(TIMESTAMP,TC_50cm.c),col='black')+
  scale_y_continuous(limits = c(-13,15))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates,format="%F"))

```



To save cleaned biomet file
```{r, warning=FALSE}
write.csv(x = df,file = 'C:/Users/klynoe/Documents/iqaluit_2/R_outputs/met/cleaned_met/IQ2biomet_cleaned.csv',row.names = F,quote = F)
```

Save individual month
```{r , warning=FALSE}
# Define the base file path
base_path = "C:/Users/klynoe/Documents/iqaluit_2/R_outputs/met/cleaned_met/"

# Nest the data and prepare for saving
data_nested = df %>%
  mutate(TIMESTAMP = as.POSIXct(TIMESTAMP, format = "%Y-%m-%d %H:%M")) %>%
  mutate(year_month = format(TIMESTAMP, "%Y%m")) %>%
  group_by(year_month) %>%
  nest() %>%
  ungroup() %>%  # Important to prevent errors with grouped data
  mutate(file_path = paste0(base_path, year_month, ".csv"))

# Iterate over each nested data frame within data_nested$data
for (i in seq_along(data_nested$data)) {
  
  # Convert TIMESTAMP to character format for each nested data frame
  data_nested$data[[i]]$TIMESTAMP_1 = as.character(data_nested$data[[i]]$TIMESTAMP)
  
  # Extract year, month, day, hour, and minute from TIMESTAMP
  year <- format(data_nested$data[[i]]$TIMESTAMP, '%Y')
  month <- format(data_nested$data[[i]]$TIMESTAMP, '%m')
  day <- format(data_nested$data[[i]]$TIMESTAMP, '%d')
  hour <- format(data_nested$data[[i]]$TIMESTAMP, '%H')
  minute <- format(data_nested$data[[i]]$TIMESTAMP, '%M')
  
  
  date <- paste(year, month, day, sep = '-')
  time <- paste(hour, minute, sep = ':')
  timestamp <- paste(date, time, sep = ' ')
  
  # Store the final timestamp in the nested data frame
  data_nested$data[[i]]$timestamp_formatted <- timestamp
}

# Write each nested data frame to the specified file path, adding the units row
walk2(
  .x = data_nested$data, 
  .y = data_nested$file_path, 
  ~ {
    # Ensure the nested data frame has the same column names and types as units_row
    .x[] <- lapply(.x, as.character)  # Convert all columns to character
    
  
    # Write to CSV
    write.csv(.x, .y, row.names = FALSE)
  }
)

```
