---
title: "Iqaluit flux cleaning"
author: "Kaj"
date: "2024-11-18"
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(error = TRUE)
```

## IQ2 Flux Data Cleaning


Designed to clean EddyPro output variables collected at th Iqaluit 2 site,using cleaned biomet data and merged EddyPro output files created by IQ loading script 

Uses original biomet variable names as created by datalogger, not FluxNet standardized biomet names. 





Clear console and add packages

```{r, warning=FALSE, echo=FALSE}
rm(list = ls())

library(data.table)
library(ggplot2)
library(cowplot)
library(openair)
library(plotrix)
library(signal)
library(svMisc)
library(zoo)
library(stringr)
library(plyr)
library(dplyr)
library(viridis)
library(lubridate)
```


Loads cleaned biomet file created above and EddyPro flux data 
```{r, warning=FALSE}
met = fread('C:/Users/klynoe/Documents/iqaluit_2/R_outputs/met/cleaned_met/IQ2biomet_cleaned.csv')

df = fread('C:/Users/klynoe/Documents/iqaluit_2/R_outputs/flux/IQ2_fluxes_merged_24.csv')

df$TIMESTAMP = df$ts

df= merge(df,met,by='TIMESTAMP',all = T, suffixes = c(".flux", ".met"))

rm(met)
```


Creates a variable to input a date range for the plots in the flux section
```{r, warning=FALSE}
flux_dates <- c('2024-03-01', '2024-09-30')
```


## Initial Clean 

Initial Enegry Balance Analysis
```{r, warning=FALSE}
df$shf = (df$SHFP_Avg_1.c + df$SHFP_Avg_2.c + df$SHFP_Avg_3.c)/3

df$met_EB = (df$long_dn_corr_Avg.c + df$Sd_Avg.c) - (df$long_up_corr_Avg.c + df$Su_Avg.c) + df$shf
df$flux_EB = df$H + df$LE


plot(df$TIMESTAMP,df$Su_Avg.c)
plot(df$TIMESTAMP,df$Sd_Avg.c)
plot(df$TIMESTAMP,df$long_up_corr_Avg.c)
plot(df$TIMESTAMP,df$long_dn_corr_Avg.c)
plot(df$TIMESTAMP, df$met_EB)
plot(df$TIMESTAMP, df$flux_EB)


ggplot(data = df)+
  geom_point(aes(TIMESTAMP,H,col='H'))+
  geom_point(aes(TIMESTAMP,LE,col='LE'))+
  scale_x_datetime(limits = as.POSIXct(flux_dates,format="%F"))

ggplot(data = df,aes(met_EB,flux_EB))+
  geom_point()


plot(df$met_EB,df$flux_EB, abline(0, 1, col= 'blue'),xlim = c(-300,500),ylim = c(-300,500))

```


Statistical analysis of energy balance 


```{r, warning=FALSE, echo=FALSE}
summary(lm(df$flux_EB ~ df$met_EB))
```

Filter by EddyPro quality flags to remove 2's
```{r, warning=FALSE}
Tau.qc      = replace(df$Tau,df$qc_Tau == 2,NA)
co2_flux.qc = replace(df$co2_flux,df$qc_co2_flux == 2,NA)
ch4_flux.qc = replace(df$ch4_flux,df$qc_ch4_flux == 2,NA)
h2o_flux.qc = replace(df$h2o_flux,df$qc_h2o_flux == 2,NA)
LE.qc       = replace(df$LE,df$qc_LE == 2,NA)
H.qc        = replace(df$H,df$qc_H == 2,NA)
```

#### Tau

Looks fine, didn't clean anything
```{r, warning=FALSE}
plot(df$TIMESTAMP, df$Tau)
hist(df$Tau,breaks=100)

Tau.limits = df$Tau
```

#### NEE/CO~2~ Flux

Initial Cleaning w/ Limits
```{r, warning=FALSE}
hist(df$co2_flux,breaks=100)

upper_lim = 10
lower_lim = -12

ggplot(data = df)+geom_hline(yintercept = 0)+
  geom_point(aes(x=ts,y=co2_flux))+
  geom_hline(yintercept = upper_lim, col="red")+
  geom_hline(yintercept = lower_lim, col="red")+
  scale_y_continuous(limits = c(-20,20))+
  scale_x_datetime(limits = as.POSIXct(flux_dates,format="%F"))

 

co2_flux.limits = replace(df$co2_flux,df$co2_flux > upper_lim | df$co2$flux < lower_lim,NA)

hist(co2_flux.limits,breaks=100)
plot(df$TIMESTAMP, co2_flux.limits)
```


#### H~2~O Flux

Initial Cleaning w/ Limits
```{r, warning=FALSE}
hist(df$h2o_flux,breaks=100)

plot(df$ts,df$h2o_flux, abline(h=-2, col= 'red')); abline(h=0,col= 'black')
 

h2o_flux.limits = replace(df$h2o_flux,df$h2o_flux < -1,NA)
hist(h2o_flux.limits,breaks=100)
plot(df$TIMESTAMP, h2o_flux.limits)
```
#### CH~4~ Flux 


Initial Cleaning w/ Limits
```{r, warning=FALSE}
hist(df$ch4_flux,breaks=100)

plot(df$ts,df$ch4_flux); abline(h=0,col= 'black'); abline(h=-0.03, col='red')


# Clean based on graphs, create new variable (ch4_flux.limits), and see cleaned product

ch4_flux.limits = df$ch4_flux
ch4_flux.limits = replace(df$ch4_flux, df$ch4_flux < -0.03, NA)

hist(ch4_flux.limits,breaks = 100)


ggplot(data = df)+geom_hline(yintercept = 0)+
  geom_point(aes(x=ts,y=ch4_flux),col = 'red')+
  geom_point(aes(x=ts,y=ch4_flux.limits),col = 'black')+
  scale_y_continuous(limits = c(-0.05, 0.05))+
  scale_x_datetime(limits = as.POSIXct(flux_dates,format="%F"))
 
```
#### H

Initial Cleaning w/ Limits
```{r, warning=FALSE}
hist(df$H,breaks=100)

plot(df$ts,df$H,ylim = c(-250,250));abline(h=-150, col= 'red')
 

# Clean based on graphs, create new variable (H.limits), and see cleaned product

  
H.limits = replace(df$H, df$H < -150,NA)
hist(H.limits,breaks = 100)

ggplot(data = df)+geom_hline(yintercept = 0)+
  geom_point(aes(x=ts,y=H),col = 'red')+
  geom_point(aes(x=ts,y=H.limits),col = 'black')+
  scale_y_continuous(limits = c(-250,250))+
  scale_x_datetime(limits = as.POSIXct(flux_dates,format="%F"))
```

#### LE


Initial Cleaning w/ limits
```{r, warning=FALSE}
hist(df$LE,breaks=100)

plot(df$ts,df$LE,ylim = c(-160, 150));abline(h=-50, col= 'red')
 

# Clean based on graphs, create new variable (H.limits), and see cleaned product

  
LE.limits = replace(df$LE, df$LE < -50,NA)
hist(LE.limits)

ggplot(data = df)+geom_hline(yintercept = 0)+
  geom_point(aes(x=ts,y=LE),col = 'red')+
  geom_point(aes(x=ts,y=LE.limits),col = 'black')+
  scale_y_continuous(limits = c(-200,150))+
  scale_x_datetime(limits = as.POSIXct(flux_dates,format="%F"))
```

#### USTAR - friction velocity (turbulence)

Hard to detect legitamate fluxes without enough turbulence- used to filter out these values
```{r, warning=FALSE}
df$nightCO2 = co2_flux.limits
df$nightCO2 = replace(df$nightCO2,df$Sd_Avg.c > 10,NA)


ggplot(data = df, aes(x=ts, y=nightCO2))+
  geom_point()+
  scale_y_continuous(limits = c(-3,5))+
  scale_x_datetime(limits = as.POSIXct(flux_dates,format="%F"))


Uthreshold=0.06
ggplot(data = df,aes(`u*`,nightCO2))+
  ylab(expression(paste("Flux (g-C", ~CO[2], ~"m",""^"-2","d",""^"-1",")")))+
  geom_point()+xlab("U*")+
  scale_x_continuous(limits = c(0,1))+
  geom_vline(xintercept = Uthreshold,col='red')
```

Create U* flag to flag low turbulence data

```{r, warning=FALSE}
df$u_flag = ifelse(df$`u*` < Uthreshold,1,0)
```



## Combine Cleaning

Investigate the previous limits and combine all to create a new variable (clean), plot to see difference

```{r, warning=FALSE}
co2fluxclean = ifelse(is.na(co2_flux.qc) | is.na(co2_flux.limits),NA,df$co2_flux)
ch4fluxclean = ifelse(is.na(ch4_flux.qc) | is.na(ch4_flux.limits),NA,df$ch4_flux)
Hclean = ifelse(is.na(H.qc) | is.na(H.limits),NA,df$H)
LEclean = ifelse(is.na(LE.qc) | is.na(LE.limits),NA,df$LE)
Tauclean = ifelse(is.na(Tau.qc) | is.na(Tau.limits),NA,df$Tau)
h2ofluxclean = ifelse(is.na(h2o_flux.qc) | is.na(h2o_flux.limits),NA,df$h2o_flux)

```

Plot results of cleaning up to this point

``` {r, warning=FALSE}
# CO2
ggplot(data = df)+geom_hline(yintercept = 0)+
  geom_point(aes(x=ts,y=co2_flux),col = 'red')+
  geom_point(aes(x=ts,y=co2fluxclean),col = 'black')+
  scale_y_continuous(limits = c(-10,15))+
  scale_x_datetime(limits = as.POSIXct(flux_dates,format="%F"))

#H2O
ggplot(data = df)+geom_hline(yintercept = 0)+
  geom_point(aes(x=ts,y=h2o_flux),col = 'red')+
  geom_point(aes(x=ts,y=h2ofluxclean),col = 'black')+
  scale_y_continuous(limits = c(-5,3))+
  scale_x_datetime(limits = as.POSIXct(flux_dates,format="%F"))

#H
ggplot(data = df)+geom_hline(yintercept = 0)+
  geom_point(aes(x=ts,y=H),col = 'red')+
  geom_point(aes(x=ts,y=Hclean),col = 'black')+
  scale_y_continuous(limits = c(-225,225))+
  scale_x_datetime(limits = as.POSIXct(flux_dates,format="%F"))

#LE
ggplot(data = df)+geom_hline(yintercept = 0)+
  geom_point(aes(x=ts,y=LE),col = 'red')+
  geom_point(aes(x=ts,y=LEclean),col = 'black')+
  scale_y_continuous(limits = c(-150,125))+
  scale_x_datetime(limits = as.POSIXct(flux_dates,format="%F"))

#Tau
ggplot(data = df)+geom_hline(yintercept = 0)+
  geom_point(aes(x=ts,y=Tau),col = 'red')+
  geom_point(aes(x=ts,y=Tauclean),col = 'black')+
  scale_y_continuous(limits = c(-1.5,0.3))+
  scale_x_datetime(limits = as.POSIXct(flux_dates,format="%F"))
```

### MAD Filters 

#### NEE


```{r, warning=FALSE}
f = co2fluxclean # first make a new flux vector to apply the above filters
# prepare the inputs for a zero-phase (forward and reverse) filter  
ind       = which(complete.cases(f))   # first save the index of all the NAs
b         = rep(1,8)/8                 # moving average coefficient
a         = 1                          # coefficient of the ARMA filter
Flux_i    = filtfilt(b, a, na.omit(f)) #create a forward and reverse ARMA filter
Flux_filt = f                          # make a copy of the full fluxes again
Flux_filt[ind] = Flux_i                # apply the filter where the real data exist

n = 7*48 # set the length of the rolling filter, 48 half hours in day * x days
roll.mad = rollapply(data = Flux_filt,
                     width = n,
                     FUN = mad,
                     partial = TRUE,
                     na.rm = T,
                     fill = NA)  #create a rolling MAD or sd or other
roll.mad[is.na(Flux_filt)] = NA  #make NA values where NAs exist in the real data

ggplot(df)+geom_hline(yintercept = 0)+
  geom_point(aes(ts,co2fluxclean,col='CO2 flux'))+
  geom_line(aes(ts,Flux_filt,col='Filter'))+
  geom_line(aes(ts,roll.mad,col='MAD'))+
  scale_y_continuous(limits = c(-7, 7))+
  scale_x_datetime(limits = as.POSIXct(flux_dates,format="%F"))+
  scale_color_manual(values=c('black','yellow','red'))
 

#  now filter the data based on this signal

  
#adjust this value (N) to tweak how many MADs to be away from the norm
N = 3 

#Add clean value to dataframe (_.c)

df$co2_flux.c = ifelse(abs(co2fluxclean - Flux_filt) > (N * roll.mad),NA,co2fluxclean)


  

ggplot(data = df)+theme_bw()+geom_hline(yintercept = 0)+
  geom_point(aes(ts,co2_flux))+
  scale_x_datetime(limits = as.POSIXct(flux_dates,format="%F"))+
  scale_y_continuous (expression('NEE ('*mu*mol~m^-2~s^-1*')'),
                      limits = c(-10,15))

 

# See data with multiple layers of the MAD filter to see if it should be changed

  
ggplot(data = df)+
  geom_ribbon(aes(x = ts,ymax = Flux_filt+roll.mad*6,ymin = Flux_filt-roll.mad*6,fill='6'))+
  geom_ribbon(aes(x = ts,ymax = Flux_filt+roll.mad*3,ymin = Flux_filt-roll.mad*3,fill='3'))+
  geom_ribbon(aes(x = ts,ymax = Flux_filt+roll.mad*2,ymin = Flux_filt-roll.mad*2,fill='2'))+
  geom_ribbon(aes(x = ts,ymax = Flux_filt+roll.mad*1,ymin = Flux_filt-roll.mad*1,fill='1'))+
  geom_point(aes(ts,co2fluxclean),col='red')+
  geom_point(aes(ts,co2_flux.c),col='black')+
  scale_y_continuous(limits = c(-15, 15))
ggplot(data = df)+
  geom_ribbon(aes(x = ts,ymax = Flux_filt+roll.mad*6,ymin = Flux_filt-roll.mad*6,fill='6'))+
  geom_ribbon(aes(x = ts,ymax = Flux_filt+roll.mad*3,ymin = Flux_filt-roll.mad*3,fill='3'))+
  geom_ribbon(aes(x = ts,ymax = Flux_filt+roll.mad*2,ymin = Flux_filt-roll.mad*2,fill='2'))+
  geom_ribbon(aes(x = ts,ymax = Flux_filt+roll.mad*1,ymin = Flux_filt-roll.mad*1,fill='1'))+
  geom_point(aes(ts,co2fluxclean),col='red')+
  geom_point(aes(ts,co2_flux.c),col='black')+
  scale_y_continuous(limits = c(-6, 6))
 
```
#### H~2~O Flux


```{r, warning=FALSE}
f = h2ofluxclean # first make a new flux vector to apply the above filters
# prepare the inputs for a zero-phase (forward and reverse) filter  
ind       = which(complete.cases(f))   # first save the index of all the NAs
b         = rep(1,8)/8                 # moving average coefficient
a         = 1                          # coefficient of the ARMA filter
Flux_i    = filtfilt(b, a, na.omit(f)) #create a forward and reverse ARMA filter
Flux_filt = f                          # make a copy of the full fluxes again
Flux_filt[ind] = Flux_i                # apply the filter where the real data exist

n = 7*48 # set the length of the rolling filter, 48 half hours in day * x days
roll.mad = rollapply(data = Flux_filt,
                     width = n,
                     FUN = mad,
                     partial = TRUE,
                     na.rm = T,
                     fill = NA)  #create a rolling MAD or sd or other
roll.mad[is.na(Flux_filt)] = NA  #make NA values where NAs exist in the real data

ggplot(df)+geom_hline(yintercept = 0)+
  geom_point(aes(ts,h2ofluxclean,col='h2o flux'))+
  geom_line(aes(ts,Flux_filt,col='Filter'))+
  geom_line(aes(ts,roll.mad,col='MAD'))+
  scale_y_continuous(limits = c(-7, 7))+
  scale_x_datetime(limits = as.POSIXct(flux_dates,format="%F"))+
  scale_color_manual(values=c('black','yellow','red'))
 

#  now filter the data based on this signal

  
#adjust this value (N) to tweak how many MADs to be away from the norm
N = 4

#Add clean value to dataframe (_.c)

df$h2o_flux.c = ifelse(abs(h2ofluxclean - Flux_filt) > (N * roll.mad),NA,h2ofluxclean)


  

ggplot(data = df)+theme_bw()+geom_hline(yintercept = 0)+
  geom_point(aes(ts,h2o_flux))+
  scale_x_datetime(limits = as.POSIXct(flux_dates,format="%F"))+
  scale_y_continuous (expression('NEE ('*mu*mol~m^-2~s^-1*')'),
                      limits = c(-10,15))

 

# See data with multiple layers of the MAD filter to see if it should be changed

  
ggplot(data = df)+
  geom_ribbon(aes(x = ts,ymax = Flux_filt+roll.mad*6,ymin = Flux_filt-roll.mad*6,fill='6'))+
  geom_ribbon(aes(x = ts,ymax = Flux_filt+roll.mad*3,ymin = Flux_filt-roll.mad*3,fill='3'))+
  geom_ribbon(aes(x = ts,ymax = Flux_filt+roll.mad*2,ymin = Flux_filt-roll.mad*2,fill='2'))+
  geom_ribbon(aes(x = ts,ymax = Flux_filt+roll.mad*1,ymin = Flux_filt-roll.mad*1,fill='1'))+
  geom_point(aes(ts,h2ofluxclean),col='red')+
  geom_point(aes(ts,h2o_flux.c),col='black')+
  scale_y_continuous(limits = c(-5, 5))+
  scale_x_datetime(limits = as.POSIXct(flux_dates,format="%F"))

 
```

#### CH~4~



```{r, warning=FALSE}
#apply the moving window filter
f = ch4fluxclean # first make a new flux vector to apply the above filters

# prepare the inputs for a zero-phase (forward and reverse) filter  
ind       = which(complete.cases(f))   # first save the index of all the NAs
b         = rep(1,8)/8                 # moving average coefficient
a         = 1                          # coefficient of the ARMA filter
Flux_i    = filtfilt(b, a, na.omit(f)) #create a forward and reverse ARMA filter
Flux_filt = f                          # make a copy of the full fluxes again
Flux_filt[ind] = Flux_i                # apply the filter where the real data exist

n = 7*48 # set the length of the rolling filter, 48 half hours in day * x days
roll.mad = rollapply(data = Flux_filt,
                     width = n,
                     FUN = mad,
                     partial = TRUE,
                     na.rm = T,
                     fill = NA)  #create a rolling MAD or sd or other
roll.mad[is.na(Flux_filt)] = NA  #make NA values where NAs exist in the real data

ggplot(df)+geom_hline(yintercept = 0)+
  geom_point(aes(ts,ch4fluxclean,col='CH4 flux'))+
  geom_line(aes(ts,Flux_filt,col='Filter'))+
  geom_line(aes(ts,roll.mad,col='MAD'))+
  scale_y_continuous(limits = c(-0.05,0.03))+
  scale_x_datetime(limits = as.POSIXct(flux_dates,format="%F"))+
  scale_color_manual(values=c('black','yellow','red'))
 

# adjust this (N) to tweak how many MADs to be away from the norm, CH4 deserves more because
# of it's nature, add clean value to the dataframe (_.c) and compare cleaned vs. uncleaned


  
N = 6 

df$ch4_flux.c = ifelse(abs(ch4fluxclean - Flux_filt) > (N * roll.mad),NA,ch4fluxclean)

ggplot(data = df)+geom_hline(yintercept = 0)+
  geom_point(aes(TIMESTAMP,ch4_flux,col='uncleaned'))+
  geom_point(aes(TIMESTAMP,ch4_flux.c,col='cleaned'))+
  scale_y_continuous(limits = c(-0.05,0.05))+
  scale_x_datetime(limits = as.POSIXct(flux_dates,format="%F"))+
  scale_color_manual(values=c('black','red'))
 

# See data with multiple layers of the MAD filter to see if it should be changed


CH4Filter = ggplot(data = df)+geom_hline(yintercept = 0)+
  geom_point(aes(df$ts,ch4fluxclean),col='red')+
  geom_point(aes(df$ts,ch4_flux.c),col='black')+
  scale_y_continuous(limits = c(-0.05,0.03))+
  scale_x_datetime(limits = as.POSIXct(flux_dates,format="%F"))


# RSSI- recieved signal strength indicator
CH4RSSI = ggplot(data = df)+geom_hline(yintercept = 0)+
  geom_line(aes(x=ts,y=rssi_77_mean))+
  scale_y_continuous(limits = c(-1,80))+
  scale_x_datetime(limits = as.POSIXct(flux_dates,format="%F"))



CH4MOLE = ggplot(data = df)+geom_hline(yintercept = 0)+
  geom_point(aes(x=ts,y=ch4_mole_fraction))+
  scale_y_continuous(limits = c(1.9,2.1))+
  scale_x_datetime(limits = as.POSIXct(flux_dates,format="%F"))


CH4_FALLSOILTCOMP = plot_grid(CH4Filter,CH4RSSI,CH4MOLE,nrow=3,align = 'v')
CH4_FALLSOILTCOMP
```

#### H

```{r, warning=FALSE}
# apply the moving window filter
f = Hclean # first make a new flux vector to apply the above filters

# prepare the inputs for a zero-phase (forward and reverse) filter  
ind       = which(complete.cases(f))   # first save the index of all the NAs
b         = rep(1,8)/8                 # moving average coefficient
a         = 1                          # coefficient of the ARMA filter
Flux_i    = filtfilt(b, a, na.omit(f)) #create a forward and reverse ARMA filter
Flux_filt = f                          # make a copy of the full fluxes again
Flux_filt[ind] = Flux_i                # apply the filter where the real data exist

n = 7*48 # set the length of the rolling filter, 48 half hours in day * x days
roll.mad = rollapply(data = Flux_filt,
                     width = n,
                     FUN = mad,
                     partial = TRUE,
                     na.rm = T,
                     fill = NA)  #create a rolling MAD or sd or other
roll.mad[is.na(Flux_filt)] = NA  #make NA values where NAs exist in the real data

ggplot(df)+geom_hline(yintercept = 0)+
  geom_point(aes(ts,Hclean,col='H'))+
  geom_line(aes(ts,Flux_filt,col='Filter'))+
  geom_line(aes(ts,roll.mad,col='MAD'))+
  scale_y_continuous(limits = c(-125,250))+
  scale_x_datetime(limits = as.POSIXct(flux_dates,format="%F"))+
  scale_color_manual(values=c('yellow','black','red'))
 

# Now filter the data based on this signal (N) adjust this to tweak how many MADs to be away from the norm, add clean value to dataframe (_.c) and Compare Clean vs. Uncleaned

  
N = 4

df$H.c = ifelse(abs(Hclean - Flux_filt) > (N * roll.mad),NA,Hclean)

ggplot(data = df)+geom_hline(yintercept = 0)+
  geom_point(aes(TIMESTAMP,Hclean,col='uncleaned'))+
  geom_point(aes(TIMESTAMP,H.c,col='cleaned'))+
  scale_y_continuous(limits=c(-150,350))+
  scale_x_datetime(limits = as.POSIXct(flux_dates,format="%F"))+
  scale_color_manual(values=c('black','red'))
 

# See data with multiple layers of the MAD filter to see if it should be changed

  
ggplot(data = df)+
  geom_ribbon(aes(x = df$ts,ymax = Flux_filt+roll.mad*6,ymin = Flux_filt-roll.mad*6,fill='6'))+
  geom_ribbon(aes(x = df$ts,ymax = Flux_filt+roll.mad*3,ymin = Flux_filt-roll.mad*3,fill='3'))+
  geom_ribbon(aes(x = df$ts,ymax = Flux_filt+roll.mad*2,ymin = Flux_filt-roll.mad*2,fill='2'))+
  geom_ribbon(aes(x = df$ts,ymax = Flux_filt+roll.mad*1,ymin = Flux_filt-roll.mad*1,fill='1'))+
  geom_point(aes(df$ts,Hclean),col='red')+
  geom_point(aes(df$ts,H.c),col='black')+
  scale_y_continuous(limits = c(-350,400))+
  scale_x_datetime(limits = as.POSIXct(flux_dates, format="%F"))
 
```

#### LE


```{r, warning=FALSE}
# apply the moving window filter
f = LEclean # first make a new flux vector to apply the above filters

# prepare the inputs for a zero-phase (forward and reverse) filter  
ind       = which(complete.cases(f))   # first save the index of all the NAs
b         = rep(1,8)/8                 # moving average coefficient
a         = 1                          # coefficient of the ARMA filter
Flux_i    = filtfilt(b, a, na.omit(f)) #create a forward and reverse ARMA filter
Flux_filt = f                          # make a copy of the full fluxes again
Flux_filt[ind] = Flux_i                # apply the filter where the real data exist

n = 7*48 # set the length of the rolling filter, 48 half hours in day * x days
roll.mad = rollapply(data = Flux_filt,
                     width = n,
                     FUN = mad,
                     partial = TRUE,
                     na.rm = T,
                     fill = NA)  #create a rolling MAD or sd or other
roll.mad[is.na(Flux_filt)] = NA  #make NA values where NAs exist in the real data

ggplot(df)+geom_hline(yintercept = 0)+
  geom_point(aes(ts,LEclean,col='LE'))+
  geom_line(aes(ts,Flux_filt,col='Filter'))+
  geom_line(aes(ts,roll.mad,col='MAD'))+
  scale_y_continuous(limits = c(-50,150))+
  scale_x_datetime(limits = as.POSIXct(flux_dates,format="%F"))+
  scale_color_manual(values=c('yellow','black','red'))
 

 # Now filter the data based on this signal (N) adjust this to tweak how many MADs to be away from the norm

  
N = 4

df$LE.c = ifelse(abs(LEclean - Flux_filt) > (N * roll.mad),NA,LEclean)

ggplot(data = df)+geom_hline(yintercept = 0)+
  geom_point(aes(TIMESTAMP,LEclean,col='uncleaned'))+
  geom_point(aes(TIMESTAMP,LE.c,col='cleaned'))+
  scale_y_continuous(limits=c(-50,150))+
  scale_x_datetime(limits = as.POSIXct(flux_dates,format="%F"))+
  scale_color_manual(values=c('black','red'))
 

# See data with multiple layers of the MAD filter to see if it should be changed


ggplot(data = df)+
  geom_ribbon(aes(x = df$ts,ymax = Flux_filt+roll.mad*6,ymin = Flux_filt-roll.mad*6,fill='6'))+
  geom_ribbon(aes(x = df$ts,ymax = Flux_filt+roll.mad*3,ymin = Flux_filt-roll.mad*3,fill='3'))+
  geom_ribbon(aes(x = df$ts,ymax = Flux_filt+roll.mad*2,ymin = Flux_filt-roll.mad*2,fill='2'))+
  geom_ribbon(aes(x = df$ts,ymax = Flux_filt+roll.mad*1,ymin = Flux_filt-roll.mad*1,fill='1'))+
  geom_point(aes(df$ts,LEclean),col='red')+
  geom_point(aes(df$ts,LE.c),col='black')+
  scale_y_continuous(limits = c(-150, 200))

ggplot(data = df)+
  geom_ribbon(aes(x = df$ts,ymax = Flux_filt+roll.mad*6,ymin = Flux_filt-roll.mad*6,fill='6'))+
  geom_ribbon(aes(x = df$ts,ymax = Flux_filt+roll.mad*3,ymin = Flux_filt-roll.mad*3,fill='3'))+
  geom_ribbon(aes(x = df$ts,ymax = Flux_filt+roll.mad*2,ymin = Flux_filt-roll.mad*2,fill='2'))+
  geom_ribbon(aes(x = df$ts,ymax = Flux_filt+roll.mad*1,ymin = Flux_filt-roll.mad*1,fill='1'))+
  geom_point(aes(df$ts,LEclean),col='red')+
  geom_point(aes(df$ts,LE.c),col='black')+
  scale_y_continuous(limits = c(-60, 75))

```

### Main Plots

includes .qc, .u, manual and spike cleaning



```{r, warning=FALSE}
ggplot(data = df)+theme_bw()+geom_hline(yintercept = 0)+
  geom_point(aes(ts,LE,col='Filt.'))+
  geom_point(aes(ts,LE.c,col='clean'))+
  scale_y_continuous(expression('LE ('*W~m^-2*')'))+
  scale_color_manual(values = c('black','red'))+
  scale_x_datetime(limits = as.POSIXct(flux_dates,format="%F"))
  

ggplot(data = df)+theme_bw()+geom_hline(yintercept = 0)+
  geom_point(aes(ts,H,col='Filt.'))+
  geom_point(aes(ts,H.c,col='clean'))+
  scale_y_continuous(expression('H ('*W~m^-2*')'))+
  scale_color_manual(values = c('black','red'))+
  scale_x_datetime(limits = as.POSIXct(flux_dates,format="%F"))

ggplot(data = df)+theme_bw()+geom_hline(yintercept = 0)+
  geom_point(aes(ts,co2_flux,col='Filt.'))+
  geom_point(aes(ts,co2_flux.c,col='clean'))+
  scale_y_continuous (expression('NEE ('*mu*mol~m^-2~s^-1*')'),
                      limits = c(-10,15))+
  scale_color_manual(values = c('black','red'))+
  scale_x_datetime(limits = as.POSIXct(flux_dates,format="%F"))


ggplot(data = df)+theme_bw()+geom_hline(yintercept = 0)+
  geom_point(aes(ts,h2o_flux,col='Filt.'))+
  geom_point(aes(ts,h2o_flux.c,col='clean'))+
  scale_y_continuous (expression('H2O Flux'),
                      limits = c(-4,3))+
  scale_color_manual(values = c('black','red'))+
  scale_x_datetime(limits = as.POSIXct(flux_dates,format="%F"))

ggplot(data = df)+theme_bw()+geom_hline(yintercept = 0)+
  geom_point(aes(ts,ch4_flux*43.2,col='Filt.'))+
  geom_point(aes(ts,ch4_flux.c*43.2,col='clean'))+
  scale_y_continuous(expression(CH[4]~'flux ('*mu*mol~m^-2~s^-1*')'),
                     limits = c(-2,2))+
  scale_color_manual(values = c('black','red'))+
  scale_x_datetime(limits = as.POSIXct(flux_dates,format="%F"))

```

## Diurnal Fluxes

set hour and month vectors to be able to take the averages - creates new tbl with 
median and standard deviation values averaged over the hour across the month (ie. 
all 11:00's in October are averaged)


```{r, warning=FALSE}
df$hour = as.numeric(format(df$ts,'%H'))
df$month = as.numeric(format(df$ts,'%m'))

diel = df %>%
  group_by(hour,month) %>%
  select(co2_flux.c,ch4_flux.c,LE.c,H.c,h2o_flux.c,hour,month) %>%
  summarise_all(.funs = c("med" = median, "sd" = sd),na.rm=T)

diel = subset(diel,!is.na(diel$month))
#diel = filter(diel, month != 11) # removes only null values in November 
 
```



#### NEE


```{r, warning=FALSE}
ggplot(data = diel)+geom_hline(yintercept = 0)+
  geom_line(aes(hour,co2_flux.c_med),lty=2)+
  geom_ribbon(aes(x = hour,y = co2_flux.c_med,
                  ymax = co2_flux.c_med + co2_flux.c_sd,
                  ymin = co2_flux.c_med - co2_flux.c_sd),
              alpha= 0.5)+
  facet_wrap(~month, nrow=2, ncol=2)

levels(diel$month)
 
```
#### H~2~O


```{r, warning=FALSE}
ggplot(data = diel)+geom_hline(yintercept = 0)+
  geom_line(aes(hour,h2o_flux.c_med),lty=2)+
  geom_ribbon(aes(x = hour,y = h2o_flux.c_med,
                  ymax = h2o_flux.c_med + h2o_flux.c_sd,
                  ymin = h2o_flux.c_med - h2o_flux.c_sd),
              alpha= 0.5)+
  facet_wrap(~month, nrow=2, ncol=2)

levels(diel$month)
 
```
#### CH~4~

```{r, warning=FALSE}
ggplot(data = diel)+geom_hline(yintercept = 0)+
  geom_line(aes(hour,ch4_flux.c_med),lty=2)+
  geom_ribbon(aes(x = hour,y = ch4_flux.c_med,
                  ymax = ch4_flux.c_med + ch4_flux.c_sd,
                  ymin = ch4_flux.c_med - ch4_flux.c_sd),
              alpha= 0.5)+
  facet_wrap(~month,  nrow=2, ncol=2)

ggplot(data = diel)+geom_hline(yintercept = 0)+
  geom_line(aes(hour,ch4_flux.c_med*43.2),lty=2)+
  geom_ribbon(aes(x = hour,y = ch4_flux.c_med*43.2,
                  ymax = ch4_flux.c_med*43.2 + ch4_flux.c_sd*43.2,
                  ymin = ch4_flux.c_med*43.2 - ch4_flux.c_sd*43.2),
              alpha= 0.5)+
  scale_y_continuous(limits = c(-0.5, 0.5))+
  facet_wrap(~month, nrow=2, ncol=2)
```
#### H

```{r, warning=FALSE}
ggplot(data = diel)+geom_hline(yintercept = 0)+
  geom_line(aes(hour,H.c_med),lty=2)+
  geom_ribbon(aes(x = hour,y = H.c_med,
                  ymax = H.c_med + H.c_sd,
                  ymin = H.c_med - H.c_sd),
              alpha= 0.5)+
  facet_wrap(~month,  nrow=2, ncol=2)
 
```

#### LE


```{r, warning=FALSE}
ggplot(data = diel)+geom_hline(yintercept = 0)+
  geom_line(aes(hour,LE.c_med),lty=2)+
  geom_ribbon(aes(x = hour,y = LE.c_med,
                  ymax = LE.c_med + LE.c_sd,
                  ymin = LE.c_med - LE.c_sd),
              alpha= 0.5)+
  facet_wrap(~month,  nrow=2, ncol=2)
 
```
## Save Cleaned Flux Data

```{r, warning=FALSE}
write.csv(x = df,file = 'C:/Users/klynoe/Documents/iqaluit_2/R_outputs/flux/IQ2_24_Clean.csv',
          row.names = F,quote = F)
```

Save individual month
```{r , warning=FALSE}
# Define the base file path
base_path = "C:/Users/klynoe/Documents/iqaluit_2/R_outputs/flux/cleaned_flux/"

# Nest the data and prepare for saving
data_nested = df %>%
  mutate(TIMESTAMP = as.POSIXct(TIMESTAMP, format = "%Y-%m-%d %H:%M")) %>%
  mutate(year_month = format(TIMESTAMP, "%Y%m")) %>%
  group_by(year_month) %>%
  nest() %>%
  ungroup() %>%  # Important to prevent errors with grouped data
  mutate(file_path = paste0(base_path, year_month, ".csv"))

# Iterate over each nested data frame within data_nested$data
for (i in seq_along(data_nested$data)) {
  
  # Convert TIMESTAMP to character format for each nested data frame
  data_nested$data[[i]]$TIMESTAMP_1 = as.character(data_nested$data[[i]]$TIMESTAMP)
  
  # Extract year, month, day, hour, and minute from TIMESTAMP
  year <- format(data_nested$data[[i]]$TIMESTAMP, '%Y')
  month <- format(data_nested$data[[i]]$TIMESTAMP, '%m')
  day <- format(data_nested$data[[i]]$TIMESTAMP, '%d')
  hour <- format(data_nested$data[[i]]$TIMESTAMP, '%H')
  minute <- format(data_nested$data[[i]]$TIMESTAMP, '%M')
  
  
  date <- paste(year, month, day, sep = '-')
  time <- paste(hour, minute, sep = ':')
  timestamp <- paste(date, time, sep = ' ')
  
  # Store the final timestamp in the nested data frame
  data_nested$data[[i]]$timestamp_formatted <- timestamp
}

# Write each nested data frame to the specified file path, adding the units row
walk2(
  .x = data_nested$data, 
  .y = data_nested$file_path, 
  ~ {
    # Ensure the nested data frame has the same column names and types as units_row
    .x[] <- lapply(.x, as.character)  # Convert all columns to character
    
  
    # Write to CSV
    write.csv(.x, .y, row.names = FALSE)
  }
)

```

#### Post-clean energy balance check 



```{r, warning=FALSE, echo=FALSE}
df$shf = (df$SHFP_Avg_1.c + df$SHFP_Avg_2.c + df$SHFP_Avg_3.c)/3

df$met_EB.c = (df$long_dn_corr_Avg.c + df$Sd_Avg.c) - (df$long_up_corr_Avg.c + df$Su_Avg.c) + df$shf

df$flux_EB.c = df$H.c + df$LE.c

plot(df$met_EB.c,df$flux_EB.c, abline(0, 1, col= 'blue'),xlim = c(-200,500),ylim = c(-200,500))

summary(lm(df$flux_EB.c ~ df$met_EB.c))
```
#### R^2^ = `r summary(lm(df$flux_EB.c ~ df$met_EB.c))$r.squared`




