---
title: "YKDUnburned_met_cleaning"
author: "Marco Montemayor"
date: "2/3/2023"
output: pdf_document
---
# Load 
```{r}
rm(list = ls())

library(data.table)
library(ggplot2)
library(plotrix)
library(signal)
library(svMisc)
library(zoo)
library(stringr)
library(plyr)
library(dplyr)

#load in the biomet data

fp = 'C:/Permafrost Pathways/YKDBurned/eddypro/EP_biomet'
#files = list.files(path = fp,pattern = '*Unburned*',recursive = T,full.names = T)
files = list.files(path = fp,pattern = '*eddypro*',recursive = T,full.names = T)

#load the headers and data into their own lists

h   = lapply(files, fread,skip = 0,nrow = 0)
bm.dat = lapply(files, fread,skip = 2,header = F,fill = T, na.strings=c('-9999','NA','NaN','NAN'),drop=c('_0_0_1'))

#assign the headers to the data

for (i in 1:length(h)) {
  names(bm.dat[[i]]) = names(h[[i]])
  bm.dat[[i]][,`_0_0_1`:=NULL]
  
}

#make all the lists into one dataframe


for (i in 1:length(bm.dat)) {
  if(is.character(bm.dat[[i]]$date) == TRUE){
    bm.dat[[i]]$date = as.IDate(bm.dat[[i]]$date,format = '%m/%d/%Y',tz = 'UTC')}}
    

    

met = bm.dat[[1]]
for (i in 2:length(bm.dat)) {
 met = rbind.fill(met,bm.dat[[i]])
}

#create a timestamp from the date and time)

met$ts = as.POSIXct(x = paste(met$date,met$time,sep = ' '),format='%Y-%m-%d %H:%M',tz = 'UTC')

```
# Longwave in
```{r}
ggplot(data = met)+
  geom_point(aes(ts,LWIN_1_1_1))+
  scale_y_continuous(limits = c(0,500),
                     expression('Longwave In ('*W/m^2*')'))+
  scale_x_datetime(limits = as.POSIXct(c("2019-7-15",'2022-12-31')))
```
## Limits
```{r}
library(cowplot)

LWIN_1_1_1.limits = replace(met$LWIN_1_1_1, met$LWIN_1_1_1 < 125 | met$LWIN_1_1_1 > 410,NA)


```

```{r}
ggplot(data = met)+
  geom_point(aes(ts,LWIN_1_1_1))+
  scale_y_continuous(limits = c(150,500),
                     expression('Longwave In ('*W/m^2*')'))+
  scale_x_datetime(limits = as.POSIXct(c("2020-10-15",'2020-11-20')))

ggplot(data = met)+
  geom_point(aes(ts,LWIN_1_1_1))+
  geom_hline(aes(yintercept = 345),col='red')+
  scale_y_continuous(limits = c(200,500),
                     expression('Longwave In ('*W/m^2*')'))+
  scale_x_datetime(limits = as.POSIXct(c("2020-11-3",'2020-11-8')))

met$LWIN_1_1_1.c = LWIN_1_1_1.limits
met$LWIN_1_1_1.c <- ifelse(LWIN_1_1_1.limits > 345 & (met$date >=  '2020-11-5' & met$date <= '2020-11-6'),NA,met$LWIN_1_1_1.c)

ggplot(data = met)+
  geom_point(aes(ts,LWIN_1_1_1.c))+
  geom_hline(aes(yintercept = 345),col='red')+
  scale_y_continuous(limits = c(200,500),
                     expression('Longwave In ('*W/m^2*')'))+
  scale_x_datetime(limits = as.POSIXct(c("2020-11-3",'2020-11-8')))

#Questionable period, solstice time 2021. Leaving in for now

ggplot(data = met)+
  geom_point(aes(ts,LWIN_1_1_1))+
  scale_y_continuous(limits = c(150,500),
                     expression('Longwave In ('*W/m^2*')'))+
  scale_x_datetime(limits = as.POSIXct(c("2021-11-15",'2022-1-20')))

                                 

```
#Longwave Out
```{r}
ggplot(met,aes(x=ts))+
  geom_point( aes(y=LWOUT_1_1_1))+
  scale_y_continuous(limits= c(120,655))+
  scale_x_datetime(limits = as.POSIXct(c('2019-7-12','2022-12-31')))
```

```{r}
monthlycleaning = data.frame(month = seq(1,12),
                             minrad = c(130,130,150,170,190,230,250,250,230,190,160,130),
                             maxrad = c(380,410,420,450,500,520,520,500,490,470,450,400))
                             

met=met%>% 
  #select(-c(minflux,maxflux))%>%
  mutate(month=month(ts))%>%
  left_join(monthlycleaning,by=c('month'))


LWOUT_1_1_1.limits = met%>%
  mutate(LWOUT_1_1_1.limits= ifelse(LWOUT_1_1_1 >= minrad & LWOUT_1_1_1 <= maxrad,
                                 LWOUT_1_1_1,
                                 NA))%>% 
  pull(LWOUT_1_1_1.limits)
plot(LWOUT_1_1_1.limits)

ggplot(met,aes(x=ts))+
  geom_ribbon(aes(ymin= minrad, ymax= maxrad),fill='yellow')+
  geom_point( aes(y=LWOUT_1_1_1.limits))+
  scale_y_continuous(limits= c(80,660))+
  scale_x_datetime(limits = as.POSIXct(c('2019-7-12','2022-12-30')))
```

```{r}

#Weird Dec Period. on second thought this may be good data based on other trends


ggplot(met,aes(x=ts))+
  geom_point( aes(y=LWOUT_1_1_1.limits))+
  geom_hline(aes(yintercept = 275),col='red')+
  scale_y_continuous(limits= c(150,360))+
  scale_x_datetime(limits = as.POSIXct(c('2021-10-12','2022-3-30')))

met$LWOUT_1_1_1.c = LWOUT_1_1_1.limits

#met$LWOUT_1_1_1.c <- ifelse(LWOUT_1_1_1.limits > 275 & (met$date >=  '2021-12-5' & met$date <= '2022-1-6'),NA,met$LWOUT_1_1_1.c)

ggplot(met,aes(x=ts))+
  geom_point( aes(y=LWOUT_1_1_1.c))+
  geom_hline(aes(yintercept = 275),col='red')+
  scale_y_continuous(limits= c(150,360))+
  scale_x_datetime(limits = as.POSIXct(c('2021-10-12','2022-3-30')))

lw = ggplot(data = met)+
  geom_point(aes(ts,LWIN_1_1_1.limits))+
  geom_hline(aes(yintercept = 410),col='red')+
  geom_hline(aes(yintercept = 125),col='red')+
  scale_y_continuous(limits = c(0,500),
                     expression('Longwave In ('*W/m^2*')'))+
  scale_x_datetime(limits = as.POSIXct(c("2019-7-15",'2022-12-31')))

airt = ggplot(data = met)+
  geom_point(aes(ts,TA_1_1_1))+
  geom_hline(aes(yintercept = 310),col='red')+
  geom_hline(aes(yintercept = 240),col='red')+
  scale_y_continuous(limits = c(220,310),
                     expression('Air Temp ('*degree*C*')'))+
  scale_x_datetime(limits = as.POSIXct(c("2019-7-15",'2022-12-31')))

plot_grid(lw,airt,ncol = 1)

```

# Shortwave in
```{r}
ggplot(data = met)+
  geom_point(aes(ts,SWIN_1_1_1))+
  scale_y_continuous(limits = c(0,1000),
                     expression('Shortwave In ('*W/m^2*')'))+
  scale_x_datetime(limits = as.POSIXct(c("2019-7-15",'2022-12-31')))
```

```{r}

hist(met$SWIN_1_1_1,breaks=100)
plot(met$ts,met$SWIN_1_1_1,ylim = c(0,950));abline(h=945,col= 'red');abline(h=-1, col='red')
SWIN_1_1_1.limits <- met$SWIN_1_1_1
SWIN_1_1_1.limits = replace(met$SWIN_1_1_1, met$SWIN_1_1_1 > 945, NA)
SWIN_1_1_1.limits[met$SWIN_1_1_1 < 0] <- 0
hist(SWIN_1_1_1.limits,breaks=100)
plot(met$ts,SWIN_1_1_1.limits)
```


## Rolling SD (Not a fan of it here-MM)
```{r}
f = SWIN_1_1_1.limits # first make a new flux vector to apply the above filters
# prepare the inputs for a zero-phase (forward and reverse) filter  
ind       = which(complete.cases(f))   # first save the index of all the NAs
b         = rep(1,8)/8                 # moving average coefficient
a         = 1                          # coefficient of the ARMA filter
mad_i    = filtfilt(b, a, na.omit(f)) #create a forward and reverse ARMA filter
mad_filt = f                          # make a copy of the full fluxes again
mad_filt[ind] = mad_i                # apply the filter where the real data exist

n = 7*48 # set the length of the rolling filter, 48 half hours in day * x days
roll.mad = rollapply(data = mad_filt,
                     width = n,
                     FUN = sd,
                     partial = TRUE,
                     na.rm = T,
                     fill = NA)  #create a rolling MAD or sd or other
roll.mad[is.na(mad_filt)] = NA  #make NA values where NAs exist in the real data


plot(met$ts,met$SWIN_1_1_1,xlim = as.POSIXct(c('2019-7-1','2022-12-31')),col='red',type = 'l');points(met$ts,mad_filt)

#plot(met$ts,roll.mad,xlim = as.POSIXct(c('2019-7-1','2022-12-31')),col='red',type = 'l')
```

```{r}
#adjust this value (N) to tweak how many MADs to be away from the norm
N = 8

#Add clean value to dataframe (_.c)

met$SWIN_1_1_1.c = ifelse(abs(SWIN_1_1_1.limits - mad_filt) > (N * roll.mad),NA,SWIN_1_1_1.limits)

#Compare cleaned vs. uncleaned

plot(met$ts,met$SWIN_1_1_1,col='red',ylim = c(-1,925));points(met$ts,met$SWIN_1_1_1.c)
```

```{r}
ggplot(data = met)+
  geom_ribbon(aes(x = ts,ymax = mad_filt+roll.mad*6,ymin = mad_filt-roll.mad*6,fill='6'))+
  geom_ribbon(aes(x = ts,ymax = mad_filt+roll.mad*3,ymin = mad_filt-roll.mad*3,fill='3'))+
  geom_ribbon(aes(x = ts,ymax = mad_filt+roll.mad*2,ymin = mad_filt-roll.mad*2,fill='2'))+
  geom_ribbon(aes(x = ts,ymax = mad_filt+roll.mad*1,ymin = mad_filt-roll.mad*1,fill='1'))+
  geom_point(aes(ts,SWIN_1_1_1.limits),col='black')+
  geom_point(aes(ts,SWIN_1_1_1.c),col='red')+
  scale_y_continuous(limits = c(-500,500))+
scale_x_datetime(limits = as.POSIXct(c('2021-11-6','2021-12-31'),format="%F"))
```
# Shortwave Out
```{r}
ggplot(data = met)+
  geom_point(aes(ts,SWOUT_1_1_1))+
  scale_y_continuous(limits = c(-20,600),
                     expression('Shortwave Out ('*W/m^2*')'))+
  scale_x_datetime(limits = as.POSIXct(c("2019-7-6",'2022-12-31')))
```

```{r}

hist(met$SWOUT_1_1_1,breaks=100)
plot(met$ts,met$SWOUT_1_1_1,ylim = c(0,650));abline(h=520,col= 'red');abline(h=0, col='red')
SWOUT_1_1_1.limits <- met$SWOUT_1_1_1
SWOUT_1_1_1.limits[met$SWOUT_1_1_1 < 0] <- 0
hist(SWOUT_1_1_1.limits,breaks=100)
plot(met$ts,SWOUT_1_1_1.limits)
```
## Rolling SD 
```{r}
f = SWOUT_1_1_1.limits # first make a new flux vector to apply the above filters
# prepare the inputs for a zero-phase (forward and reverse) filter  
ind       = which(complete.cases(f))   # first save the index of all the NAs
b         = rep(1,8)/8                 # moving average coefficient
a         = 1                          # coefficient of the ARMA filter
mad_i    = filtfilt(b, a, na.omit(f)) #create a forward and reverse ARMA filter
mad_filt = f                          # make a copy of the full fluxes again
mad_filt[ind] = mad_i                # apply the filter where the real data exist

n = 7*48 # set the length of the rolling filter, 48 half hours in day * x days
roll.mad = rollapply(data = mad_filt,
                     width = n,
                     FUN = sd,
                     partial = TRUE,
                     na.rm = T,
                     fill = NA)  #create a rolling MAD or sd or other
roll.mad[is.na(mad_filt)] = NA  #make NA values where NAs exist in the real data


plot(met$ts,SWOUT_1_1_1.limits,xlim = as.POSIXct(c('2019-7-1','2022-12-31')),col='red',type = 'l');points(met$ts,mad_filt)

#plot(met$ts,roll.mad,xlim = as.POSIXct(c('2019-7-1','2022-12-31')),col='red',type = 'l')
```

```{r}
#adjust this value (N) to tweak how many MADs to be away from the norm
N = 8

#Add clean value to dataframe (_.c)

met$SWOUT_1_1_1.c = ifelse(abs(SWOUT_1_1_1.limits - mad_filt) > (N * roll.mad),NA,SWOUT_1_1_1.limits)

#Compare cleaned vs. uncleaned

plot(met$ts,SWOUT_1_1_1.limits,col='red',ylim = c(0,600));points(met$ts,met$SWOUT_1_1_1.c)
```
```{r}
ggplot(data = met)+
  geom_ribbon(aes(x = ts,ymax = mad_filt+roll.mad*6,ymin = mad_filt-roll.mad*6,fill='6'))+
  geom_ribbon(aes(x = ts,ymax = mad_filt+roll.mad*3,ymin = mad_filt-roll.mad*3,fill='3'))+
  geom_ribbon(aes(x = ts,ymax = mad_filt+roll.mad*2,ymin = mad_filt-roll.mad*2,fill='2'))+
  geom_ribbon(aes(x = ts,ymax = mad_filt+roll.mad*1,ymin = mad_filt-roll.mad*1,fill='1'))+
  geom_point(aes(ts,SWOUT_1_1_1.limits),col='black')+
  geom_point(aes(ts,SWOUT_1_1_1.c),col='red')+
  scale_y_continuous(limits = c(-100,150))+
scale_x_datetime(limits = as.POSIXct(c('2021-11-6','2022-1-23'),format="%F"))
```
# Albedo 
```{r}

#I cut all the zero values out!!! -MM

albedo = met$SWOUT_1_1_1.c / met$SWIN_1_1_1.c

plot(met$ts,albedo,ylim = c(0,1.5));abline(h=1,col= 'red');abline(h=0, col='red')

albedo.limits = replace(albedo, albedo < 0.1 | albedo > 1,NA)

plot(met$ts,albedo.limits)

```
## Rolling SD 
```{r}
f = albedo.limits # first make a new flux vector to apply the above filters
# prepare the inputs for a zero-phase (forward and reverse) filter  
ind       = which(complete.cases(f))   # first save the index of all the NAs
b         = rep(1,8)/8                 # moving average coefficient
a         = 1                          # coefficient of the ARMA filter
mad_i    = filtfilt(b, a, na.omit(f)) #create a forward and reverse ARMA filter
mad_filt = f                          # make a copy of the full fluxes again
mad_filt[ind] = mad_i                # apply the filter where the real data exist

n = 7*48 # set the length of the rolling filter, 48 half hours in day * x days
roll.mad = rollapply(data = mad_filt,
                     width = n,
                     FUN = sd,
                     partial = TRUE,
                     na.rm = T,
                     fill = NA)  #create a rolling MAD or sd or other
roll.mad[is.na(mad_filt)] = NA  #make NA values where NAs exist in the real data


plot(met$ts,albedo.limits,xlim = as.POSIXct(c('2019-7-1','2022-12-31')),col='red',type = 'l');points(met$ts,mad_filt)

plot(met$ts,roll.mad,xlim = as.POSIXct(c('2019-7-1','2022-12-31')),col='red',type = 'l')
```

```{r}
#adjust this value (N) to tweak how many MADs to be away from the norm
N = 3

#Add clean value to dataframe (_.c)

met$ALB_1_1_1.c = ifelse(abs(albedo.limits - mad_filt) > (N * roll.mad),NA,albedo.limits)

#Compare cleaned vs. uncleaned

plot(met$ts,albedo.limits,col='red',ylim = c(0,1));points(met$ts,met$ALB_1_1_1.c)
```

```{r}
ggplot(data = met)+
  geom_ribbon(aes(x = ts,ymax = mad_filt+roll.mad*6,ymin = mad_filt-roll.mad*6,fill='6'))+
  geom_ribbon(aes(x = ts,ymax = mad_filt+roll.mad*3,ymin = mad_filt-roll.mad*3,fill='3'))+
  geom_ribbon(aes(x = ts,ymax = mad_filt+roll.mad*2,ymin = mad_filt-roll.mad*2,fill='2'))+
  geom_ribbon(aes(x = ts,ymax = mad_filt+roll.mad*1,ymin = mad_filt-roll.mad*1,fill='1'))+
  geom_point(aes(ts,albedo.limits),col='black')+
  geom_point(aes(ts,ALB_1_1_1.c),col='red')+
  scale_y_continuous(limits = c(-1,1.9))+
scale_x_datetime(limits = as.POSIXct(c('2022-7-6','2022-12-31'),format="%F"))
```

# Net Radiation

```{r}
ggplot(data = met)+
  geom_point(aes(ts, RN_1_1_1),col='black')+
  scale_y_continuous(limits = c(-250,650),
                     expression('Net Radiation ('*W/m^2*')'))+
  scale_x_datetime(limits = as.POSIXct(c('2019-7-6','2022-12-31')))
```
## Limits
```{r}

hist(met$RN_1_1_1,breaks=100)
plot(met$ts,met$RN_1_1_1,ylim = c(-300,700));abline(h=650,col= 'red');abline(h=-200, col='red')
RN_1_1_1.limits <- met$RN_1_1_1
RN_1_1_1.limits = replace(met$RN_1_1_1,met$RN_1_1_1 > 650 | met$RN_1_1_1  < -200,NA)
hist(RN_1_1_1.limits,breaks=100)
```



## Rolling SD 
```{r}
f = RN_1_1_1.limits # first make a new flux vector to apply the above filters
# prepare the inputs for a zero-phase (forward and reverse) filter  
ind       = which(complete.cases(f))   # first save the index of all the NAs
b         = rep(1,8)/8                 # moving average coefficient
a         = 1                          # coefficient of the ARMA filter
mad_i    = filtfilt(b, a, na.omit(f)) #create a forward and reverse ARMA filter
mad_filt = f                          # make a copy of the full fluxes again
mad_filt[ind] = mad_i                # apply the filter where the real data exist

n = 7*48 # set the length of the rolling filter, 48 half hours in day * x days
roll.mad = rollapply(data = mad_filt,
                     width = n,
                     FUN = sd,
                     partial = TRUE,
                     na.rm = T,
                     fill = NA)  #create a rolling MAD or sd or other
roll.mad[is.na(mad_filt)] = NA  #make NA values where NAs exist in the real data


plot(met$ts,RN_1_1_1.limits,xlim = as.POSIXct(c('2019-7-1','2022-12-31')),col='red',type = 'l');points(met$ts,mad_filt)

plot(met$ts,roll.mad,xlim = as.POSIXct(c('2019-7-1','2022-12-31')),col='red',type = 'l')
```

```{r}
#adjust this value (N) to tweak how many MADs to be away from the norm
N = 5

#Add clean value to dataframe (_.c)

met$RN_1_1_1.c = ifelse(abs(RN_1_1_1.limits - mad_filt) > (N * roll.mad),NA,RN_1_1_1.limits)

#Compare cleaned vs. uncleaned

plot(met$ts,RN_1_1_1.limits,col='red',ylim = c(-250,650));points(met$ts,met$RN_1_1_1.c)
```

```{r}
ggplot(data = met)+
  geom_ribbon(aes(x = ts,ymax = mad_filt+roll.mad*6,ymin = mad_filt-roll.mad*6,fill='6'))+
  geom_ribbon(aes(x = ts,ymax = mad_filt+roll.mad*3,ymin = mad_filt-roll.mad*3,fill='3'))+
  geom_ribbon(aes(x = ts,ymax = mad_filt+roll.mad*2,ymin = mad_filt-roll.mad*2,fill='2'))+
  geom_ribbon(aes(x = ts,ymax = mad_filt+roll.mad*1,ymin = mad_filt-roll.mad*1,fill='1'))+
  geom_point(aes(ts,RN_1_1_1.limits),col='black')+
  geom_point(aes(ts,RN_1_1_1.c),col='red')+
  scale_y_continuous(limits = c(-250,400))+
scale_x_datetime(limits = as.POSIXct(c('2022-1-1','2022-3-23'),format="%F"))
```
# PAR
```{r}
ggplot(data = met)+
  geom_point(aes(ts,PPFD_1_1_1),col='black')+
  scale_y_continuous(limits = c(-500,2000),
                     expression('PAR ('*mu*mol/m^2/s*')'))+
  scale_x_datetime(limits = as.POSIXct(c('2019-7-6','2022-12-31')))
```
## Limits
```{r}

hist(met$PPFD_1_1_1,breaks=100)
PPFD_1_1_1.raw = met$PPFD_1_1_1
PPFD_1_1_1.raw = replace(met$PPFD_1_1_1, met$PPFD_1_1_1 < -10 | met$PPFD_1_1_1 > 1900, NA)
plot(met$ts,PPFD_1_1_1.raw)
PPFD_1_1_1.limits = PPFD_1_1_1.raw
PPFD_1_1_1.limits[PPFD_1_1_1.raw < 0] <- 0
hist(PPFD_1_1_1.limits,breaks=100)
```

## Rolling SD 
```{r}
f = PPFD_1_1_1.limits # first make a new flux vector to apply the above filters
# prepare the inputs for a zero-phase (forward and reverse) filter  
ind       = which(complete.cases(f))   # first save the index of all the NAs
b         = rep(1,8)/8                 # moving average coefficient
a         = 1                          # coefficient of the ARMA filter
mad_i    = filtfilt(b, a, na.omit(f)) #create a forward and reverse ARMA filter
mad_filt = f                          # make a copy of the full fluxes again
mad_filt[ind] = mad_i                # apply the filter where the real data exist

n = 7*48 # set the length of the rolling filter, 48 half hours in day * x days
roll.mad = rollapply(data = mad_filt,
                     width = n,
                     FUN = sd,
                     partial = TRUE,
                     na.rm = T,
                     fill = NA)  #create a rolling MAD or sd or other
roll.mad[is.na(mad_filt)] = NA  #make NA values where NAs exist in the real data


plot(met$ts,PPFD_1_1_1.limits,xlim = as.POSIXct(c('2019-7-1','2022-12-31')),col='red',type = 'l');points(met$ts,mad_filt)

plot(met$ts,roll.mad,xlim = as.POSIXct(c('2019-7-1','2022-12-31')),col='red',type = 'l')
```

```{r}
#adjust this value (N) to tweak how many MADs to be away from the norm
N = 8

#Add clean value to dataframe (_.c)

met$PPFD_1_1_1.c = ifelse(abs(PPFD_1_1_1.limits - mad_filt) > (N * roll.mad),NA,PPFD_1_1_1.limits)

#Compare cleaned vs. uncleaned

plot(met$ts,PPFD_1_1_1.limits,col='red',ylim = c(-25,1950));points(met$ts,met$PPFD_1_1_1.c)
```

```{r}
ggplot(data = met)+
  geom_ribbon(aes(x = ts,ymax = mad_filt+roll.mad*6,ymin = mad_filt-roll.mad*6,fill='6'))+
  geom_ribbon(aes(x = ts,ymax = mad_filt+roll.mad*3,ymin = mad_filt-roll.mad*3,fill='3'))+
  geom_ribbon(aes(x = ts,ymax = mad_filt+roll.mad*2,ymin = mad_filt-roll.mad*2,fill='2'))+
  geom_ribbon(aes(x = ts,ymax = mad_filt+roll.mad*1,ymin = mad_filt-roll.mad*1,fill='1'))+
  geom_point(aes(ts,PPFD_1_1_1.limits),col='black')+
  geom_point(aes(ts,PPFD_1_1_1.c),col='red')+
  scale_y_continuous(limits = c(-550,1800))+
scale_x_datetime(limits = as.POSIXct(c('2021-10-6','2021-12-31'),format="%F"))
```
#Soil Heat Flux 
```{r}

ggplot(data = met)+
  geom_point(aes(ts,SHF_1_1_1,col='SHF 1'))+
  geom_point(aes(ts,SHF_2_1_1,col='SHF 2'))+
  geom_point(aes(ts,SHF_3_1_1,col='SHF 3'))+
  scale_y_continuous(limits = c(-100,175),
                     expression ('Soil Heat Flux ('*W/m^2*')'))+
  scale_color_manual(values = c('red','black','blue'))+
  scale_x_datetime(limits = as.POSIXct(c('2019-7-16','2022-12-31')))
```
#Soil Heat Flux 1
```{r}
hist(met$SHF_1_1_1, breaks = 100)

ggplot(data = met)+
  geom_point(aes(ts,SHF_1_1_1,col='SHF 1'))+
  scale_y_continuous(limits = c(-380,450),
                     expression ('Soil Heat Flux ('*W/m^2*')'))+
  scale_color_manual(values = c('red'))+
  scale_x_datetime(limits = as.POSIXct(c('2019-7-16','2022-12-31')))

ggplot(data = met)+
  geom_point(aes(ts,SHF_1_1_1,col='SHF 1'))+
  geom_point(aes(ts,SHF_2_1_1,col='SHF 2'))+
  scale_y_continuous(limits = c(-80,350),
                     expression ('Soil Heat Flux ('*W/m^2*')'))+
  scale_color_manual(values = c('red','blue'))+
  scale_x_datetime(limits = as.POSIXct(c('2021-10-1','2022-3-11')))

#Don't know if we should keep that similar trend at the beginning of Feb, semi-precise but not accurate based on prior readouts (as of now it's cut after end Dec)

```
## Limits
```{r}
met$SHF_1_1_1.c = met$SHF_1_1_1
met$SHF_1_1_1.c <- ifelse(met$SHF_1_1_1 < 400 & (met$date >=  '2021-12-25' & met$date <= '2022-12-31'),NA,met$SHF_1_1_1.c)

ggplot(data = met)+
  geom_point(aes(ts,SHF_1_1_1.c,col='SHF 1'))+
  scale_y_continuous(limits = c(-80,350),
                     expression ('Soil Heat Flux ('*W/m^2*')'))+
  scale_color_manual(values = c('red'))+
  scale_x_datetime(limits = as.POSIXct(c('2019-7-16','2022-12-31')))
```
# Soil Heat Flux 2
```{r}
ggplot(data = met)+
  geom_point(aes(ts,SHF_2_1_1,col='SHF 2'))+
  scale_y_continuous(limits = c(-90,100),
                     expression ('Soil Heat Flux ('*W/m^2*')'))+
  scale_color_manual(values = c('blue'))+
  scale_x_datetime(limits = as.POSIXct(c('2019-7-16','2022-12-31')))



ggplot(data = met)+
  geom_point(aes(ts,SHF_2_1_1,col='SHF 2'))+
  scale_y_continuous(limits = c(-50,50),
                     expression ('Soil Heat Flux ('*W/m^2*')'))+
  scale_color_manual(values = c('blue','red','yellow'))+
  scale_x_datetime(limits = as.POSIXct(c('2021-11-16','2022-1-25')))

met$SHF_2_1_1.c=met$SHF_2_1_1
```
# Soil Heat Flux 3
```{r}
ggplot(data = met)+
  geom_point(aes(ts,SHF_3_1_1,col='SHF 3'))+
  scale_y_continuous(limits = c(-80,120),
                     expression ('Soil Heat Flux ('*W/m^2*')'))+
  scale_color_manual(values = c('black'))+
  scale_x_datetime(limits = as.POSIXct(c('2019-7-16','2022-12-31')))

ggplot(data = met)+
  geom_point(aes(ts,SHF_3_1_1,col='SHF 3'))+
  scale_y_continuous(limits = c(-80,120),
                     expression ('Soil Heat Flux ('*W/m^2*')'))+
  scale_color_manual(values = c('black'))+
  scale_x_datetime(limits = as.POSIXct(c('2019-7-16','2022-12-31')))

met$SHF_3_1_1.c = met$SHF_3_1_1

```
# Air T
```{r}
ggplot(data = met)+
  geom_point(aes(ts,TA_1_1_1),col='black')+
  scale_y_continuous(limits = c(235,310),
                     expression('Air Temperature ('*Kelvin*')'))+
  scale_x_datetime(limits = as.POSIXct(c('2020-11-6','2020-11-30')))
```

```{r}
hist(met$TA_1_1_1, breaks = 100)
ggplot(data = met)+
  geom_point(aes(ts,TA_1_1_1),col='black')+
  scale_y_continuous(limits = c(235,310),
                     expression('Air Temperature ('*Kelvin*')'))+
  scale_x_datetime(limits = as.POSIXct(c('2021-11-16','2022-1-31')))

met$TA_1_1_1.c = met$TA_1_1_1

```
#Relative Humidity
```{r}
ggplot(data = met)+
  geom_point(aes(ts,RH_1_1_1),col='black')+
  scale_y_continuous(limits = c(0,100),
                     expression('Relative Humidity ('*percent*')'))+
  scale_x_datetime(limits = as.POSIXct(c('2019-7-6','2022-12-31')))

met$RH_1_1_1.c = met$RH_1_1_1
```
```{r}
ggplot(data = met)+
  geom_point(aes(ts, SWC_1_1_1*100,col='SWC 1'))+
  geom_point(aes(ts, SWC_2_1_1*100,col='SWC 2'))+
  geom_point(aes(ts, SWC_3_1_1*100,col='SWC 3'))+
  scale_y_continuous(limits = c(0,100),
                     expression(' VWC'))+
  scale_x_datetime(limits = as.POSIXct(c("2019-7-6",'2022-12-31')))
```
# Volumetric Water Content 1 
```{r}
ggplot(data = met)+
  geom_point(aes(ts, SWC_1_1_1,col='SWC 1'))+
  scale_y_continuous(limits = c(0,1),
                     expression('% VWC'))+
  scale_x_datetime(limits = as.POSIXct(c("2019-7-6",'2022-12-31')))
```
## Rolling SD 
```{r}
f = met$SWC_1_1_1 # first make a new flux vector to apply the above filters
# prepare the inputs for a zero-phase (forward and reverse) filter  
ind       = which(complete.cases(f))   # first save the index of all the NAs
b         = rep(1,8)/8                 # moving average coefficient
a         = 1                          # coefficient of the ARMA filter
mad_i    = filtfilt(b, a, na.omit(f)) #create a forward and reverse ARMA filter
mad_filt = f                          # make a copy of the full fluxes again
mad_filt[ind] = mad_i                # apply the filter where the real data exist

n = 7*48 # set the length of the rolling filter, 48 half hours in day * x days
roll.mad = rollapply(data = mad_filt,
                     width = n,
                     FUN = sd,
                     partial = TRUE,
                     na.rm = T,
                     fill = NA)  #create a rolling MAD or sd or other
roll.mad[is.na(mad_filt)] = NA  #make NA values where NAs exist in the real data


plot(met$ts,met$SWC_1_1_1,xlim = as.POSIXct(c('2019-7-1','2022-12-31')),col='red',type = 'l');points(met$ts,mad_filt)

plot(met$ts,roll.mad,xlim = as.POSIXct(c('2019-7-1','2022-12-31')),col='red',type = 'l')
```

```{r}
#adjust this value (N) to tweak how many MADs to be away from the norm
N = 3

#Add clean value to dataframe (_.c)

met$SWC_1_1_1.c = ifelse(abs(met$SWC_1_1_1 - mad_filt) > (N * roll.mad),NA,met$SWC_1_1_1)

#Compare cleaned vs. uncleaned

plot(met$ts,met$SWC_1_1_1,col='red',ylim = c(0,1));points(met$ts,met$SWC_1_1_1.c)
```

```{r}
ggplot(data = met)+
  geom_ribbon(aes(x = ts,ymax = mad_filt+roll.mad*6,ymin = mad_filt-roll.mad*6,fill='6'))+
  geom_ribbon(aes(x = ts,ymax = mad_filt+roll.mad*3,ymin = mad_filt-roll.mad*3,fill='3'))+
  geom_ribbon(aes(x = ts,ymax = mad_filt+roll.mad*2,ymin = mad_filt-roll.mad*2,fill='2'))+
  geom_ribbon(aes(x = ts,ymax = mad_filt+roll.mad*1,ymin = mad_filt-roll.mad*1,fill='1'))+
  geom_point(aes(ts,met$SWC_1_1_1),col='black')+
  geom_point(aes(ts,met$SWC_1_1_1.c),col='red')+
  scale_y_continuous(limits = c(0,1))+
scale_x_datetime(limits = as.POSIXct(c('2022-4-6','2022-10-23'),format="%F"))
```

# Volumetric Water Content 2 
```{r}
ggplot(data = met)+
  geom_point(aes(ts, SWC_2_1_1,col='SWC 2'))+
  scale_y_continuous(limits = c(0,1),
                     expression('% WC'))+
  scale_x_datetime(limits = as.POSIXct(c("2019-7-6",'2022-12-31')))
```
## Rolling SD 
```{r}
f = met$SWC_2_1_1 # first make a new flux vector to apply the above filters
# prepare the inputs for a zero-phase (forward and reverse) filter  
ind       = which(complete.cases(f))   # first save the index of all the NAs
b         = rep(1,8)/8                 # moving average coefficient
a         = 1                          # coefficient of the ARMA filter
mad_i    = filtfilt(b, a, na.omit(f)) #create a forward and reverse ARMA filter
mad_filt = f                          # make a copy of the full fluxes again
mad_filt[ind] = mad_i                # apply the filter where the real data exist

n = 7*48 # set the length of the rolling filter, 48 half hours in day * x days
roll.mad = rollapply(data = mad_filt,
                     width = n,
                     FUN = sd,
                     partial = TRUE,
                     na.rm = T,
                     fill = NA)  #create a rolling MAD or sd or other
roll.mad[is.na(mad_filt)] = NA  #make NA values where NAs exist in the real data


plot(met$ts,mad_filt,xlim = as.POSIXct(c('2019-7-1','2022-12-31')),col='red',type = 'l');points(met$ts,met$SWC_2_1_1)

plot(met$ts,roll.mad,xlim = as.POSIXct(c('2019-7-1','2022-12-31')),col='red',type = 'l')
```

```{r}
#adjust this value (N) to tweak how many MADs to be away from the norm
N = 3

#Add clean value to dataframe (_.c)

met$SWC_2_1_1.c = ifelse(abs(met$SWC_2_1_1 - mad_filt) > (N * roll.mad),NA,met$SWC_2_1_1)

#Compare cleaned vs. uncleaned

plot(met$ts,met$SWC_2_1_1,col='red',ylim = c(0,1));points(met$ts,met$SWC_2_1_1.c)
```

```{r}
ggplot(data = met)+
  geom_ribbon(aes(x = ts,ymax = mad_filt+roll.mad*6,ymin = mad_filt-roll.mad*6,fill='6'))+
  geom_ribbon(aes(x = ts,ymax = mad_filt+roll.mad*3,ymin = mad_filt-roll.mad*3,fill='3'))+
  geom_ribbon(aes(x = ts,ymax = mad_filt+roll.mad*2,ymin = mad_filt-roll.mad*2,fill='2'))+
  geom_ribbon(aes(x = ts,ymax = mad_filt+roll.mad*1,ymin = mad_filt-roll.mad*1,fill='1'))+
  geom_point(aes(ts,met$SWC_2_1_1),col='black')+
  geom_point(aes(ts,met$SWC_2_1_1.c),col='red')+
  scale_y_continuous(limits = c(-1,2))+
scale_x_datetime(limits = as.POSIXct(c('2022-4-6','2022-10-23'),format="%F"))
```

# Volumetric Water Content 3 
```{r}
ggplot(data = met)+
  geom_point(aes(ts, SWC_3_1_1,col='SWC 3'))+
  scale_y_continuous(limits = c(0,1),
                     expression('% WC'))+
  scale_x_datetime(limits = as.POSIXct(c("2019-7-6",'2022-12-31')))
```
## Rolling SD 
```{r}
f = met$SWC_3_1_1 # first make a new flux vector to apply the above filters
# prepare the inputs for a zero-phase (forward and reverse) filter  
ind       = which(complete.cases(f))   # first save the index of all the NAs
b         = rep(1,8)/8                 # moving average coefficient
a         = 1                          # coefficient of the ARMA filter
mad_i    = filtfilt(b, a, na.omit(f)) #create a forward and reverse ARMA filter
mad_filt = f                          # make a copy of the full fluxes again
mad_filt[ind] = mad_i                # apply the filter where the real data exist

n = 7*48 # set the length of the rolling filter, 48 half hours in day * x days
roll.mad = rollapply(data = mad_filt,
                     width = n,
                     FUN = sd,
                     partial = TRUE,
                     na.rm = T,
                     fill = NA)  #create a rolling MAD or sd or other
roll.mad[is.na(mad_filt)] = NA  #make NA values where NAs exist in the real data


plot(met$ts,mad_filt,xlim = as.POSIXct(c('2019-7-1','2022-12-31')),col='red',type = 'l');points(met$ts,met$SWC_3_1_1)

plot(met$ts,roll.mad,xlim = as.POSIXct(c('2019-7-1','2022-12-31')),col='red',type = 'l')
```

```{r}
#adjust this value (N) to tweak how many MADs to be away from the norm
N = 3

#Add clean value to dataframe (_.c)

met$SWC_3_1_1.c = ifelse(abs(met$SWC_3_1_1 - mad_filt) > (N * roll.mad),NA,met$SWC_3_1_1)

#Compare cleaned vs. uncleaned

plot(met$ts,met$SWC_3_1_1,col='red',ylim = c(0,1));points(met$ts,met$SWC_3_1_1.c)
```

```{r}
ggplot(data = met)+
  geom_ribbon(aes(x = ts,ymax = mad_filt+roll.mad*6,ymin = mad_filt-roll.mad*6,fill='6'))+
  geom_ribbon(aes(x = ts,ymax = mad_filt+roll.mad*3,ymin = mad_filt-roll.mad*3,fill='3'))+
  geom_ribbon(aes(x = ts,ymax = mad_filt+roll.mad*2,ymin = mad_filt-roll.mad*2,fill='2'))+
  geom_ribbon(aes(x = ts,ymax = mad_filt+roll.mad*1,ymin = mad_filt-roll.mad*1,fill='1'))+
  geom_point(aes(ts,met$SWC_3_1_1),col='black')+
  geom_point(aes(ts,met$SWC_3_1_1.c),col='red')+
  scale_y_continuous(limits = c(-.5,1.5))+
scale_x_datetime(limits = as.POSIXct(c('2022-4-6','2022-10-23'),format="%F"))
```

#All Soil T 
```{r}
ggplot(data = met)+
  geom_point(aes(ts, TS_1_1_1,col='Soil T 1'))+
  geom_point(aes(ts, TS_2_1_1,col='Soil T 2'))+
  geom_point(aes(ts, TS_3_1_1,col='Soil T 3'))+
  scale_y_continuous(limits = c(260,290),
                     expression('Soil T'))+
  scale_x_datetime(limits = as.POSIXct(c("2019-7-6",'2022-12-31')))
```

# Soil T 1
```{r}
ggplot(data = met)+
  geom_point(aes(ts, TS_1_1_1,col='Soil T 1'))+
  geom_hline(yintercept = 273)+
  scale_y_continuous(limits = c(260,290),
                     expression('Soil T'))+
  scale_x_datetime(limits = as.POSIXct(c("2019-7-6",'2022-12-31')))
```

## Rolling SD 
```{r}
f = met$TS_1_1_1 # first make a new flux vector to apply the above filters
# prepare the inputs for a zero-phase (forward and reverse) filter  
ind       = which(complete.cases(f))   # first save the index of all the NAs
b         = rep(1,8)/8                 # moving average coefficient
a         = 1                          # coefficient of the ARMA filter
mad_i    = filtfilt(b, a, na.omit(f)) #create a forward and reverse ARMA filter
mad_filt = f                          # make a copy of the full fluxes again
mad_filt[ind] = mad_i                # apply the filter where the real data exist

n = 7*48 # set the length of the rolling filter, 48 half hours in day * x days
roll.mad = rollapply(data = mad_filt,
                     width = n,
                     FUN = sd,
                     partial = TRUE,
                     na.rm = T,
                     fill = NA)  #create a rolling MAD or sd or other
roll.mad[is.na(mad_filt)] = NA  #make NA values where NAs exist in the real data


plot(met$ts,mad_filt,xlim = as.POSIXct(c('2019-7-1','2022-12-31')),col='red',type = 'l');points(met$ts,met$TS_1_1_1)

plot(met$ts,roll.mad,xlim = as.POSIXct(c('2019-7-1','2022-12-31')),col='red',type = 'l')
```

```{r}
#adjust this value (N) to tweak how many MADs to be away from the norm
N = 3

#Add clean value to dataframe (_.c)

met$TS_1_1_1.c = ifelse(abs(met$TS_1_1_1 - mad_filt) > (N * roll.mad),NA,met$TS_1_1_1)

#Compare cleaned vs. uncleaned

plot(met$ts,met$TS_1_1_1,col='red',ylim = c(250,300));points(met$ts,met$TS_1_1_1.c)
```

```{r} 
## ??
ggplot(data = met)+
  geom_ribbon(aes(x = ts,ymax = mad_filt+roll.mad*6,ymin = mad_filt-roll.mad*6,fill='6'))+
  geom_ribbon(aes(x = ts,ymax = mad_filt+roll.mad*3,ymin = mad_filt-roll.mad*3,fill='3'))+
  geom_ribbon(aes(x = ts,ymax = mad_filt+roll.mad*2,ymin = mad_filt-roll.mad*2,fill='2'))+
  geom_ribbon(aes(x = ts,ymax = mad_filt+roll.mad*1,ymin = mad_filt-roll.mad*1,fill='1'))+
  geom_point(aes(ts,met$TS_1_1_1),col='black')+
  geom_point(aes(ts,met$TS_1_1_1.c),col='red')+
  scale_y_continuous(limits = c(250,300))+
scale_x_datetime(limits = as.POSIXct(c('2022-10-16','2022-12-2'),format="%F"))
```
# Soil T 2
```{r}
ggplot(data = met)+
  geom_point(aes(ts, TS_2_1_1,col='Soil T 2'))+
  geom_hline(yintercept = 273)+
  scale_y_continuous(limits = c(260,290),
                     expression('Soil T'))+
  scale_x_datetime(limits = as.POSIXct(c("2019-7-6",'2022-12-31')))
```

## Rolling SD 
```{r}
f = met$TS_2_1_1 # first make a new flux vector to apply the above filters
# prepare the inputs for a zero-phase (forward and reverse) filter  
ind       = which(complete.cases(f))   # first save the index of all the NAs
b         = rep(1,8)/8                 # moving average coefficient
a         = 1                          # coefficient of the ARMA filter
mad_i    = filtfilt(b, a, na.omit(f)) #create a forward and reverse ARMA filter
mad_filt = f                          # make a copy of the full fluxes again
mad_filt[ind] = mad_i                # apply the filter where the real data exist

n = 7*48 # set the length of the rolling filter, 48 half hours in day * x days
roll.mad = rollapply(data = mad_filt,
                     width = n,
                     FUN = sd,
                     partial = TRUE,
                     na.rm = T,
                     fill = NA)  #create a rolling MAD or sd or other
roll.mad[is.na(mad_filt)] = NA  #make NA values where NAs exist in the real data


plot(met$ts,mad_filt,xlim = as.POSIXct(c('2019-7-1','2022-12-31')),col='red',type = 'l');points(met$ts,met$TS_2_1_1)

plot(met$ts,roll.mad,xlim = as.POSIXct(c('2019-7-1','2022-12-31')),col='red',type = 'l')
```

```{r}
#adjust this value (N) to tweak how many MADs to be away from the norm
N = 3

#Add clean value to dataframe (_.c)

met$TS_2_1_1.c = ifelse(abs(met$TS_2_1_1 - mad_filt) > (N * roll.mad),NA,met$TS_2_1_1)

#Compare cleaned vs. uncleaned

plot(met$ts,met$TS_2_1_1,col='red',ylim = c(250,300));points(met$ts,met$TS_2_1_1.c)
```

```{r}
ggplot(data = met)+
  geom_ribbon(aes(x = ts,ymax = mad_filt+roll.mad*6,ymin = mad_filt-roll.mad*6,fill='6'))+
  geom_ribbon(aes(x = ts,ymax = mad_filt+roll.mad*3,ymin = mad_filt-roll.mad*3,fill='3'))+
  geom_ribbon(aes(x = ts,ymax = mad_filt+roll.mad*2,ymin = mad_filt-roll.mad*2,fill='2'))+
  geom_ribbon(aes(x = ts,ymax = mad_filt+roll.mad*1,ymin = mad_filt-roll.mad*1,fill='1'))+
  geom_point(aes(ts,met$TS_2_1_1),col='black')+
  geom_point(aes(ts,met$TS_2_1_1.c),col='red')+
  scale_y_continuous(limits = c(250,300))+
scale_x_datetime(limits = as.POSIXct(c('2020-6-6','2020-11-23'),format="%F"))
```
# Soil T 3
```{r}
ggplot(data = met)+
  geom_point(aes(ts, TS_3_1_1,col='Soil T 3'))+
  geom_hline(yintercept = 273)+
  scale_y_continuous(limits = c(260,290),
                     expression('Soil T'))+
  scale_x_datetime(limits = as.POSIXct(c("2019-7-6",'2022-12-31')))
```

## Rolling SD 
```{r}
f = met$TS_3_1_1 # first make a new flux vector to apply the above filters
# prepare the inputs for a zero-phase (forward and reverse) filter  
ind       = which(complete.cases(f))   # first save the index of all the NAs
b         = rep(1,8)/8                 # moving average coefficient
a         = 1                          # coefficient of the ARMA filter
mad_i    = filtfilt(b, a, na.omit(f)) #create a forward and reverse ARMA filter
mad_filt = f                          # make a copy of the full fluxes again
mad_filt[ind] = mad_i                # apply the filter where the real data exist

n = 7*48 # set the length of the rolling filter, 48 half hours in day * x days
roll.mad = rollapply(data = mad_filt,
                     width = n,
                     FUN = sd,
                     partial = TRUE,
                     na.rm = T,
                     fill = NA)  #create a rolling MAD or sd or other
roll.mad[is.na(mad_filt)] = NA  #make NA values where NAs exist in the real data


plot(met$ts,mad_filt,xlim = as.POSIXct(c('2019-7-1','2022-12-31')),col='red',type = 'l');points(met$ts,met$TS_3_1_1)

plot(met$ts,roll.mad,xlim = as.POSIXct(c('2019-7-1','2022-12-31')),col='red',type = 'l')
```

```{r}
#adjust this value (N) to tweak how many MADs to be away from the norm
N = 3

#Add clean value to dataframe (_.c)

met$TS_3_1_1.c = ifelse(abs(met$TS_3_1_1 - mad_filt) > (N * roll.mad),NA,met$TS_3_1_1)

#Compare cleaned vs. uncleaned

plot(met$ts,met$TS_3_1_1,col='red',ylim = c(250,300));points(met$ts,met$TS_3_1_1.c)
```

```{r}
ggplot(data = met)+
  geom_ribbon(aes(x = ts,ymax = mad_filt+roll.mad*6,ymin = mad_filt-roll.mad*6,fill='6'))+
  geom_ribbon(aes(x = ts,ymax = mad_filt+roll.mad*3,ymin = mad_filt-roll.mad*3,fill='3'))+
  geom_ribbon(aes(x = ts,ymax = mad_filt+roll.mad*2,ymin = mad_filt-roll.mad*2,fill='2'))+
  geom_ribbon(aes(x = ts,ymax = mad_filt+roll.mad*1,ymin = mad_filt-roll.mad*1,fill='1'))+
  geom_point(aes(ts,met$TS_3_1_1),col='black')+
  geom_point(aes(ts,met$TS_3_1_1.c),col='red')+
  scale_y_continuous(limits = c(250,300))+
scale_x_datetime(limits = as.POSIXct(c('2020-6-6','2020-11-23'),format="%F"))
```
# Save

```{r}
write.csv(x = df,file = 'C:/Permafrost Pathways/Data/Cleaned/YKDBurned_Met_clean.csv',row.names = F,quote = F)
```